### 2023-02-16 main.tex
update main.tex && main.bib

\documentclass[twocolumn,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{CJKutf8}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{indentfirst}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }
\usepackage[a4paper, top = 2.5cm, bottom = 2.5cm, left = 3.17cm, right = 3.17cm]{geometry}
\setlength{\parindent}{12pt}

\title{zero-shot nas}
\author{謝承翰}
\date{2023}

\begin{document}
\begin{CJK*}{UTF8}{bsmi}

\maketitle

\section{摘要}
近年來，人造神經網路(Artificial neural network; ANN)在各領域中有廣泛的運用，例如: 影像辨識、影音辨識，以及自然語言處理(Natural Language Processing; NLP)。\par
過去大部分的人造神經網路架構，都是根據經驗手動尋找、調整，所需的資源、時間過多，研究如何自動搜尋神經網路架構(Neural Architecture Search; NAS)的重要性因而上升。\par
但以往的神經網路架構搜尋演算法，在尋找的過程中，必須訓練一部分神經網路後才能得知架構的好壞，耗費許多時間、資源，故近年許多Traning-free的神經架構搜尋演算法不斷被提出，Traning-free演算法使用Training-Free Score Function評價神經網路架構，而不需訓練，相較以往，Traning-free的演算法更迅速、耗費的資源更少。\par
然而Training-Free Score Function與神經網路訓練後的準確度相關性不高，搜尋的結果欠佳，本研究會結合三種不同的Training-Free Score Function，搭配基因演算法(Genetic Algorithm; GA)搜尋架構，並在NAS-Bench-101, NAS-Bench-201等可復現的架構集驗證結果。預計提出一個速度、準確度兼顧的神經網路架構搜尋演算法。\par

\section{參考文獻}
\begin{thebibliography}{9}
\end{thebibliography}

\end{CJK*}
\end{document}

### 2023-02-16 main.tex
modify abstract section to eng. ver.

@@
 \title{zero-shot nas}
-\author{謝承翰}
+\author{Hsieh Cheng-Han}
 \date{2023}
@@
 
-\section{摘要}
-近年來，人造神經網路(Artificial neural network; ANN)在各領域中有廣泛的運用，例如: 影像辨識、影音辨識，以及自然語言處理(Natural Language Processing; NLP)。\par
-過去大部分的人造神經網路架構，都是根據經驗手動尋找、調整，所需的資源、時間過多，研究如何自動搜尋神經網路架構(Neural Architecture Search; NAS)的重要性因而上升。\par
-但以往的神經網路架構搜尋演算法，在尋找的過程中，必須訓練一部分神經網路後才能得知架構的好壞，耗費許多時間、資源，故近年許多Traning-free的神經架構搜尋演算法不斷被提出，Traning-free演算法使用Training-Free Score Function評價神經網路架構，而不需訓練，相較以往，Traning-free的演算法更迅速、耗費的資源更少。\par
-然而Training-Free Score Function與神經網路訓練後的準確度相關性不高，搜尋的結果欠佳，本研究會結合三種不同的Training-Free Score Function，搭配基因演算法(Genetic Algorithm; GA)搜尋架構，並在NAS-Bench-101, NAS-Bench-201等可復現的架構集驗證結果。預計提出一個速度、準確度兼顧的神經網路架構搜尋演算法。\par
+\section{Abstract}
+In the last few years, Artificial Neural Network (ANN) has been used in a variety of fields, i.e., image classification, speech recognition, and Natural Language Processing (NLP).\par
+Most of the architectures of ANN are hand-designed by experts, consuming lots of time and resource.
+This problem induce the researches of Neural Architecture Search (NAS) algorithm, providing an automated, fast, and accurate approach to build a good architecture of ANN.\par
+However, the NAS algorithm in the past is time-consuming, which is caused by the fact that, during the searching, a candidate of architectures must be trained to know how the performance of this architecture.
+Thus, plenty of training-free NAS algorithm are developed in recent years.
+By using training-free score function to evaluate an architecture, there's no requirement for training architectures anymore.
+Compare with training-need NAS algorithm, training-free NAS algorithm tend to be faster and consuming less resource.\par
+Neverthesless, the low correlation between single Training-Free Score Function and the performance of an architecture limits the performance of training-free NAS algorithms.
+To mitigate this problem, we propose a genetic-based training-free NAS algorithm with hybrid training-free score function, which combines three highly heterogeneous training-free score functions to evaluate an architecture.
+To evaluate the performance of the proposed algorithm, we compared it with several NAS algorithms, including weight-sharing methods, non-weight-sharing methods, and NASWOT.
+We expect develope a faster and more accurate training-free NAS algorithm.\par
 
-\section{參考文獻}
 \begin{thebibliography}{9}

### 2023-02-16 main.tex
update main.tex: modify the abstract

@@
 
-\title{zero-shot nas}
+\title{GA-based Training-Free NAS Algorithm with Hybrid Score Function}
 \author{Hsieh Cheng-Han}
@@
 \section{Abstract}
-In the last few years, Artificial Neural Network (ANN) has been used in a variety of fields, i.e., image classification, speech recognition, and Natural Language Processing (NLP).\par
+    In the last few years, Artificial Neural Network (ANN) has been used in a variety of fields, i.e., image classification\cite{}, speech recognition\cite{}, and Natural Language Processing\cite{}.\par
 Most of the architectures of ANN are hand-designed by experts, consuming lots of time and resource.
 This problem induce the researches of Neural Architecture Search (NAS) algorithm, providing an automated, fast, and accurate approach to build a good architecture of ANN.\par
-However, the NAS algorithm in the past is time-consuming, which is caused by the fact that, during the searching, a candidate of architectures must be trained to know how the performance of this architecture.
+    However, the NAS algorithm\cite{} in the past is time-consuming, which is caused by the fact that, during the searching, a candidate of architectures must be trained to know how the performance of this architecture.
 Thus, plenty of training-free NAS algorithm are developed in recent years.
 By using training-free score function to evaluate an architecture, there's no requirement for training architectures anymore.
-Compare with training-need NAS algorithm, training-free NAS algorithm tend to be faster and consuming less resource.\par
+Compare with training-required NAS algorithm, training-free NAS algorithm tend to be faster and consuming less resource.\par
 Neverthesless, the low correlation between single Training-Free Score Function and the performance of an architecture limits the performance of training-free NAS algorithms.

### 2023-02-16 main.tex
update main.tex: remove the citation

@@
 \section{Abstract}
-    In the last few years, Artificial Neural Network (ANN) has been used in a variety of fields, i.e., image classification\cite{}, speech recognition\cite{}, and Natural Language Processing\cite{}.\par
+    In the last few years, Artificial Neural Network (ANN) has been used in a variety of fields, i.e., image classification, speech recognition, and Natural Language Processing.\par
 Most of the architectures of ANN are hand-designed by experts, consuming lots of time and resource.
 This problem induce the researches of Neural Architecture Search (NAS) algorithm, providing an automated, fast, and accurate approach to build a good architecture of ANN.\par
-    However, the NAS algorithm\cite{} in the past is time-consuming, which is caused by the fact that, during the searching, a candidate of architectures must be trained to know how the performance of this architecture.
+    However, the NAS algorithms in the past were time-consuming, which were caused by the fact that, during the searching, a candidate of architectures must be trained to know how the performance of this architecture.
 Thus, plenty of training-free NAS algorithm are developed in recent years.
 By using training-free score function to evaluate an architecture, there's no requirement for training architectures anymore.
-Compare with training-required NAS algorithm, training-free NAS algorithm tend to be faster and consuming less resource.\par
+Compare with training-required NAS algorithms, training-free NAS algorithms tend to be faster and consuming less resource.\par
     Neverthesless, the low correlation between single Training-Free Score Function and the performance of an architecture limits the performance of training-free NAS algorithms.
 To mitigate this problem, we propose a genetic-based training-free NAS algorithm with hybrid training-free score function, which combines three highly heterogeneous training-free score functions to evaluate an architecture.
-To evaluate the performance of the proposed algorithm, we compared it with several NAS algorithms, including weight-sharing methods, non-weight-sharing methods, and NASWOT.
+To evaluate the performance of the proposed algorithm, we compared it with several NAS algorithms, including weight-sharing methods, non-weight-sharing methods, and neural architecture search without training (NASWOT).
 We expect develope a faster and more accurate training-free NAS algorithm.\par

### 2023-02-17 main.tex
update main.tex: modify the layout a bit

@@
 \section{Abstract}
-    In the last few years, Artificial Neural Network (ANN) has been used in a variety of fields, i.e., image classification, speech recognition, and Natural Language Processing.\par
+    In the last few years, artificial neural network (ANN) has been used in a variety of fields, i.e., image classification, speech recognition, and Natural Language Processing.\par
+
     Most of the architectures of ANN are hand-designed by experts, consuming lots of time and resource.
-This problem induce the researches of Neural Architecture Search (NAS) algorithm, providing an automated, fast, and accurate approach to build a good architecture of ANN.\par
+This problem induce the researches of neural architecture search (NAS) algorithm, providing an automated, fast, and accurate approach to build a good architecture of ANN.\par
+
     However, the NAS algorithms in the past were time-consuming, which were caused by the fact that, during the searching, a candidate of architectures must be trained to know how the performance of this architecture.
@@
 Compare with training-required NAS algorithms, training-free NAS algorithms tend to be faster and consuming less resource.\par
+
     Neverthesless, the low correlation between single Training-Free Score Function and the performance of an architecture limits the performance of training-free NAS algorithms.

### 2023-02-28 paper/main.tex
move draft to paper/

\documentclass[twocolumn,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{CJKutf8}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{indentfirst}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    }
\usepackage[a4paper, top = 2.5cm, bottom = 2.5cm, left = 3.17cm, right = 3.17cm]{geometry}
\setlength{\parindent}{12pt}

\title{GA-based Training-Free NAS Algorithm with Hybrid Score Function}
\author{Hsieh Cheng-Han}
\date{2023}

\begin{document}
\begin{CJK*}{UTF8}{bsmi}

\maketitle

\section{Abstract}

    Most neural architecture search methods (NASs) are time-consuming caused by 
    the fact that, during the searching, a candidate architectures must be 
    trained to evaluate how good of this architecture. This is why some of 
    training-free NAS algorithms have been proposed in recent years.

    Although the training-free NASs are typically faster than training-based 
    NAS method, however, the correlation between score value and the result 
    of an architecture is not well enough in most cases.

    To address this problem, we propose a genetic-based training-free NAS 
    algorithm with hybrid training-free score function, which combines three 
    highly heterogeneous training-free score functions to evaluate an architecture. 
    In this method, the genetic algorithm plays a role to guide the searches 
    of NAS algorithm while the hybrid training-free score function plays the 
    role to evaluate a new candidate architecture during the convergencr process 
    of GA. More precisely, the first score function is noise immunity for 
    neural architecture search without search (NINASWOT), as an evaluation of 
    pattern recognition, second one is Maximum-Entropy Detection (MAE-DET), 
    as an evaluation of the entropy of an architecture and the third one is 
    condition number of neural tangent kernel (NTK), as an evaluation of 
    the speed of converge.

    To evaluate the performance of the proposed algorithm, we compared it 
    with several NAS algorithms, including weight-sharing methods, 
    non-weight-sharing methods, and neural architecture search without training (NASWOT). 
    We expect develope a faster and more accurate training-free NAS algorithm.

\begin{thebibliography}{9}
\end{thebibliography}

\end{CJK*}
\end{document}

### 2023-03-01 score/__init__.py
update score/__init__.py: add del network in get_means_stds to release the memory

@@ -19,6 +19,7 @@ def get_mean_std(searchspace, sample_n, train_loader, device, args):
         scores_ntk.append(ntk_score(network, train_loader, device))
         network = init_net_gaussian(network, device)
         scores_entropy.append(entropy_score(network, train_loader, device, args))
+        del network
 
     scores_naswot  = np.array(scores_naswot)
     scores_ni      = np.array(scores_ni)

### 2023-03-01 score/entropy_score.py
update score/entropy_score.py, ninaswot_score, ntk_score: add del network and torch.cuda.empty_cache() to release the memory

@@ -26,6 +26,7 @@ def init_net_gaussian(net, device):
     return net
 
 def entropy_score(network, train_loader, device, args):
+    #print(f"before entropy cuda memory allocated = {torch.cuda.memory_allocated(0)/1024/1024/1024}")
     network.features = []
     def forward_hook(module, inp, out):
         try:
@@ -43,10 +44,12 @@ def entropy_score(network, train_loader, device, args):
     def backward_hook(module, inp, out):
         module.visitied_backwards = True
 
+    forward_handler  = []
+    backward_handler = []
     for name, module in network.named_modules():
         if 'ReLU' in str(type(module)):
-            module.register_forward_hook(forward_hook)
-            module.register_backward_hook(backward_hook)
+            forward_handler.append(module.register_forward_hook(forward_hook))
+            backward_handler.append(module.register_backward_hook(backward_hook))
 
     network = network.to(device)
     data_iter = iter(train_loader)
@@ -60,6 +63,11 @@ def entropy_score(network, train_loader, device, args):
     scores = 0
     for i in range(len(network.features)):
         scores += torch.log(1+torch.mean(network.features[i]))
+    for i in range(len(forward_handler)):
+        forward_handler[i].remove()
+        backward_handler[i].remove()
     del network.features
-    return scores
+    torch.cuda.empty_cache()
+    #print(f"after entropy cuda memory allocated = {torch.cuda.memory_allocated(0)/1024/1024/1024}")
+    return scores.detach().cpu()
 

### 2023-03-01 score/ninaswot_score.py

@@ -27,6 +27,7 @@ def get_batch_jacobian(net, x, target, device, args=None):
     return jacob, target.detach(), y.detach(), out.detach()
 
 def naswot_score(network, train_loader, device, args):
+    #print(f"before naswot cuda memory allocated = {torch.cuda.memory_allocated(0)/1024/1024/1024}")
     if args.dropout:
         add_dropout(network, args.sigma)
     if args.init != '':
@@ -50,11 +51,12 @@ def naswot_score(network, train_loader, device, args):
         def counting_backward_hook(module, inp, out):    
             module.visited_backwards = True    
 
-                
+        forward_handler  = []
+        backward_handler = []
         for name, module in network.named_modules():    
-            if 'ReLU' in str(type(module)):    
-                module.register_forward_hook(counting_forward_hook)    
-                module.register_backward_hook(counting_backward_hook)    
+            if 'ReLU' in str(type(module)):
+                forward_handler.append(module.register_forward_hook(counting_forward_hook))
+                backward_handler.append(module.register_backward_hook(counting_backward_hook))
 
     network = network.to(device)    
     s = []
@@ -72,10 +74,18 @@ def naswot_score(network, train_loader, device, args):
     else:
         s.append(get_score_func(args.score)(jacobs, labels))
     
+    #print(f"after naswot cuda memory allocated = {torch.cuda.memory_allocated(0)/1024/1024/1024}")
+    for i in range(len(foward_handler)):
+        forward_handler[i].remove()
+        backward_handler[i].remove()
+
+    del network
+    torch.cuda.empty_cache()
     return np.mean(s)
 
 @torch.no_grad()
 def ni_score(network, train_loader, device, args):
+    #print(f"before ni cuda memory allocated = {torch.cuda.memory_allocated(0)/1024/1024/1024}")
     network = network.to(device)
     data_iter = iter(train_loader)
     x, target = next(data_iter)
@@ -88,16 +98,19 @@ def ni_score(network, train_loader, device, args):
     o_, _ = network(x2)
     o = o.detach().cpu().numpy()
     o_ = o_.detach().cpu().numpy()
+    #print(f"after ni cuda memory allocated = {torch.cuda.memory_allocated(0)/1024/1024/1024}")
+    del network
+    torch.cuda.empty_cache()
[…]

### 2023-03-01 score/ntk_score.py

@@ -2,7 +2,8 @@ import numpy as np
 import torch
 import time
 
-def ntk_score(network, train_loader, device, recalbn=0, train_mode=False, num_batch=1):
+def ntk_score(network, train_loader, device, recalbn=0, train_mode=True, num_batch=1):
+    #print(f"before ntk cuda memory allocated = {torch.cuda.memory_allocated(0)/1024/1024/1024}")
     ntk = []
     if train_mode:
         network.train()
@@ -28,11 +29,14 @@ def ntk_score(network, train_loader, device, recalbn=0, train_mode=False, num_ba
                     grad.append(W.grad.view(-1).detach())
             grads.append(torch.cat(grad, -1))
             network.zero_grad()
-            torch.cuda.empty_cache()
+            #torch.cuda.empty_cache()
     ######
     grads = torch.stack(grads, 0)
     ntk = torch.einsum('nc,mc->nm', [grads, grads])
     conds = []
     eigenvalues, _ = torch.symeig(ntk)  # ascending
     score = np.nan_to_num((eigenvalues[-1] / eigenvalues[0]).item(), copy=True, nan=100000.0)
-    return score
+    del network
+    torch.cuda.empty_cache()
+    #print(f"after ntk cuda memory allocated = {torch.cuda.memory_allocated(0)/1024/1024/1024}")
+    return 1/score

### 2023-03-01 score_networks.py
update score_networks.py: add some prompt, and modify to calculate three scroe function with (1,1,1) weights

@@ -33,7 +33,7 @@ parser.add_argument('--trainval', action='store_true')
 parser.add_argument('--dropout', action='store_true')
 parser.add_argument('--dataset', default='cifar10', type=str)
 parser.add_argument('--maxofn', default=1, type=int, help='score is the max of this many evaluations of the network')
-parser.add_argument('--n_samples', default=100, type=int)
+parser.add_argument('--n_samples', default=15, type=int)
 parser.add_argument('--n_runs', default=500, type=int)
 parser.add_argument('--stem_out_channels', default=16, type=int, help='output channels of stem convolution (nasbench101)')
 parser.add_argument('--num_stacks', default=3, type=int, help='#stacks of modules (nasbench101)')
@@ -84,21 +84,35 @@ try:
 except:
     accs = np.zeros(len(searchspace))
 
-#means, stds = score.get_mean_std(searchspace, 100, train_loader, device, args)
-means, stds = {"ntk": 0}, {"ntk": 1}
+print(f"Start calculate means and stds in {args.n_samples} samples")
+#print(f"now cuda memory allocated: {torch.cuda.memory_allocated(0)/1024/1024/1024}")
+means, stds = get_mean_std(searchspace, 15, train_loader, device, args)
+print(f"Done")
+print(f"means = {means}")
+print(f"stds  = {stds}")
+#means, stds = {"ntk": 0}, {"ntk": 1}
 
 nruns = tqdm(total = len(searchspace))
 times = []
+print(f"now score the whole arches")
 for i, (uid, network) in enumerate(searchspace):
     st = time.time()
     try:
-        #scores_ninaswot[i] = ninaswot_score(network, train_loader, device, stds, means, args)
         standardize = lambda x, m, s: (x-m)/s
+        
+        # ninaswot
+        # ninaswot has mean 0, and std sqrt5 (naswot*2+ni)
+        scores_ninaswot[i] = standardize(ninaswot_score(network, train_loader, device, stds, means, args), 0, np.sqrt(5))
+        
+        # ntk
         scores_ntk[i] = standardize(ntk_score(network, train_loader, device, train_mode=args.trainval), means["ntk"], stds["ntk"])
-        #network = init_net_gaussian(network, device)
-        #scores_entropy[i]  = standardize(entropy_score(network, train_loader, device, args), means["entropy"], stds["entropy"])
 
-        scores[i] = scores_ntk[i]
+        # entropy
[…]

### 2023-03-01 score/ninaswot_score.py
fix typo[4~

@@ -75,7 +75,7 @@ def naswot_score(network, train_loader, device, args):
         s.append(get_score_func(args.score)(jacobs, labels))
     
     #print(f"after naswot cuda memory allocated = {torch.cuda.memory_allocated(0)/1024/1024/1024}")
-    for i in range(len(foward_handler)):
+    for i in range(len(forward_handler)):
         forward_handler[i].remove()
         backward_handler[i].remove()
 

### 2023-03-01 paper/main.tex
update paper/main.tex: fix some typo

@@
 
-    Most neural architecture search methods (NASs) are time-consuming caused by 
-    the fact that, during the searching, a candidate architectures must be 
+    Most neural architecture searches (NASs) are time-consuming caused by 
+    the fact that, during the searching, a candidate architecture must be 
     trained to evaluate how good of this architecture. This is why some of 

### 2023-03-01 search/GA.py
update search/GA.py: modify evaulate function in GA.py

@@ -48,14 +48,17 @@ class GA():
             self.population[i].acc = acc
             self.population[i].uid = uid
             if self.population[i].gene not in self.DICT:
-                self.population[i].fitness = self.DICT[self.population[i].gene] = net_score.scores(network, self.train_loader, self.device, self.stds, self.means, self.args)
+                self.population[i].fitness = self.DICT[self.population[i].gene] = (standardize(ninaswot_score(network, self.train_loader, self.device, self.stds, self.means, self.args), self.means["ninaswot"], self.stds["ninaswot"]), standardize(ntk_score(network, self.train_loader, self.device, train_mode=args.trainval), self.means["ntk"], self.stds["ntk"]), standardize(entropy_score(network, self.train_loader, self.device, self.args), self.means["entropy"], self.stds["entropy"]))
             else:
                 self.population[i].fitness = self.DICT[self.population[i].gene]
+            # TODO
+            """
             if self.population[i].fitness > self.best_chrom.fitness or self.best_chrom.gene == "":
                 self.best_chrom.fitness = self.population[i].fitness
                 self.best_chrom.acc = self.population[i].acc
                 self.best_chrom.uid = self.population[i].uid
                 self.best_chrom.gene = copy.deepcopy(self.population[i].gene)
+            """
             del network
 
     def mutation(self, chrom):

### 2023-03-01 score/__init__.py
update score/__init__.py: add standardize()

@@ -4,6 +4,9 @@ from .ninaswot_score import ninaswot_score, ni_score, naswot_score, get_batch_ja
 from .entropy_score import entropy_score, init_net_gaussian
 import numpy as np
 
+def stadnardize(x, m, s):
+    return (x-m)/s
+
 def get_mean_std(searchspace, sample_n, train_loader, device, args):
     scores_naswot  = []
     scores_ni      = []

### 2023-03-01 GA_search.py
update GA_search.py: add "ninaswot" key in means and stds

@@ -12,7 +12,7 @@ from statistics import mean
 import time
 from utils import add_dropout
 from search import GA
-from score import net_score
+from score import *
 
 
 parser = argparse.ArgumentParser(description='NAS Without Training')
@@ -80,21 +80,9 @@ else:
     acc_type = 'x-test'
     val_acc_type = 'x-valid'
 
-scores_nas = []
-scores_gu = []
-arches = np.random.randint(0, 15625, 100)
-for arch in arches:
-    uid = searchspace[arch]
-    network = searchspace.get_network(uid)
-    scores_nas.append(net_score.score_nas(network, train_loader, device, args))
-    scores_gu.append(net_score.score_gu(network, train_loader, device, args))
-
-scores_nas = np.array(scores_nas)
-scores_gu = np.array(scores_gu)
-calstd = lambda x: np.ma.masked_invalid(x).std()
-calmean = lambda x: np.ma.masked_invalid(x).mean()
-stds = {"nas": calstd(scores_nas), "gu": calstd(scores_gu)}
-means = {"nas": calmean(scores_nas), "gu": calmean(scores_gu)}
+means, stds = get_mean_std(searchspace, args.n_samples, train_loader, device, args)
+means["ninaswot"] = 0
+stds["ninaswot"] = np.sqrt(5)
 
 print(f"parameter:\nnumber of population={args.maxn_pop}\nnumber of iteration={args.maxn_iter}\nprobability of mutation={args.prob_mut}\nprobability of crossover={args.prob_cr}")
 

### 2023-03-01 score_networks.py
update score_networks.py: comment the standardize lambda

@@ -98,7 +98,7 @@ print(f"now score the whole arches")
 for i, (uid, network) in enumerate(searchspace):
     st = time.time()
     try:
-        standardize = lambda x, m, s: (x-m)/s
+        #standardize = lambda x, m, s: (x-m)/s
         
         # ninaswot
         # ninaswot has mean 0, and std sqrt5 (naswot*2+ni)

### 2023-03-02 paper/main.tex
modify some words

@@
     neural architecture search without search (NINASWOT), as an evaluation of 
-    pattern recognition, second one is Maximum-Entropy Detection (MAE-DET), 
+    pattern recognition ability, second one is maximum-entropy detection (MAE-DET), 
     as an evaluation of the entropy of an architecture and the third one is 

### 2023-03-03 paper/main.tex
update main.tex: move Intro-eng to Introduction section. Add IEEE format (now using) and ACM format. Add citation.

@@
-\documentclass[twocolumn,10pt]{article}
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+%\documentclass[sigconf]{acmart}
+%\let\Bbbk\relax %% fix bug
 \usepackage[utf8]{inputenc}
-\usepackage{CJKutf8}
 \usepackage{graphicx}
 \usepackage{listings}
-\usepackage{hyperref}
+\usepackage{url}
 \usepackage{indentfirst}
-
-\hypersetup{
-    colorlinks=true,
-    linkcolor=blue,
-    filecolor=magenta,      
-    urlcolor=cyan,
-    }
-\usepackage[a4paper, top = 2.5cm, bottom = 2.5cm, left = 3.17cm, right = 3.17cm]{geometry}
-\setlength{\parindent}{12pt}
+\usepackage{comment}
+\usepackage{algorithm}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{amstext}
+\usepackage{amsopn}
+\usepackage{algpseudocode}
 
@@
 \begin{document}
-\begin{CJK*}{UTF8}{bsmi}
 
@@
 
-\begin{thebibliography}{9}
-\end{thebibliography}
+\section{Introduction}
 
-\end{CJK*}
+% introduction
+    Neural architecture search (NAS) has recently drawn a big amount of 
+    attention, since the ability to automatically design a "good" neural 
+    architecture. By leveraging machine learning algorithms (Zoph \& Le,\ \cite{https://doi.org/10.48550/arxiv.1611.01578}), 
+    NAS algorithms can explore a search space, which is comprised of 
+    numerous potential architectures, to find out a good architectures 
+    that outperform those designed by human experts. In recent years, 
+    the use of NAS is widespread, from object detection (Sun et al.,\ \cite{https://doi.org/10.48550/arxiv.2111.13336}), 
+    image recognition (Mellor et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.04647}) 
+    and speech recognition (Zheng et al.,\ \cite{https://doi.org/10.48550/arxiv.2011.05649}, 
+    Mehrotra et al.,\ \cite{mehrotra2021nasbenchasr}) to 
+    natural language processing(Jiang et al.,\ \cite{jiang-etal-2019-improved}, 
+    Klyuchnikov et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.07116}, 
+    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2005.14187}).
+
+    Despite the promising results of NAS, there are still many challenges 
+    to conquer. One of the major problems is the extremely high computational 
+    cost to search for an optimal architecture, which can make NAS impractical 
+    for real-world applications, particularly on resource-constrained 
+    platforms like embedded system. The reason why NAS is costly is that 
+    during the searching, a candidate architecture must be trained to 
+    evaluate how good of this architecture.
+
+    To overcome this challenge, recent works developed and proposed lots 
+    of method which is so called training-free NAS. Some use mean absolute 
+    error random sampling (MRS) (Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.1805.07159}, 
+    Camero et al.,\ \cite{Camero_2021}, Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.2106.15295}) 
+    as a training-free score function and some use neural tangent kernel 
+    (NTK) (Chen et al.,\ \cite{https://doi.org/10.48550/arxiv.2102.11535}, 
+    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2203.09137}, 
+    Shu et al.,\ \cite{https://doi.org/10.48550/arxiv.2109.00817}), while some use 
+    gradient-based methods (Zhang \& Jia,\ \cite{https://doi.org/10.48550/arxiv.2110.08616}, 
+    Cavagnero et al.,\ \cite{https://doi.org/10.48550/arxiv.2207.05135}, 
+    Abdelfattah et al.,\ \cite{https://doi.org/10.48550/arxiv.2101.08134}).
+% what is unknown?
+    However, most of score functions suffer from low correlation between 
+    score value and the result of an architecture, leading to a trap that 
+    no matter how good the search method is used, we can hardly find an 
+    optimal architecture.
+% how and why
+    The major problem causes the low correlation is that a single score 
+    function can only evaluate one perspect/characteristic of an architecture.
+% method
+    By cooperating three heterogeneous score functions with genetic-based 
+    search method, we shall evaulate an architecture from different aspects. 
+    More specifically, the first score function is noise immunity for neural 
+    architecture search without search (NINASWOT) (Wu et al.\ \cite{10.1145/3491396.3506510}). 
+    Based on the work of Mellor et al., they proposed the measurement of 
+    the correlation between binary activation paterns of input data at each 
+    ReLU layer. Later, Wu et al. found a high score obtained by such a 
+    function may not correspond to a high-performence model. Thus, they 
+    additionally applied noisy immunity method, called NINASWOT. Second one 
+    is maximum-entropy detection (MAE-DET) (Sun et al.\ \cite{https://doi.org/10.48550/arxiv.2111.13336}). 
+    Based on the work of Sun et al., they proposed to find the maximum of 
+    the differential entropy by calculating the variance of the output at 
+    the final layer with the input Gaussian noise images. Third one is 
+    condition number of  neural tangent kernel (NTK) (Chen et al.\ \cite{https://doi.org/10.48550/arxiv.2102.11535}), 
+    which is defined as 
+    \begin{equation}
+        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
+    \end{equation}
+    Chen et al. used the condition number of NTK as the score function to estimate the performance of a network.
+% results
+    It's shall find good architectures in reasonable time and computational resource.
+% conclusion
+    The major contribution of this paper can be summarized as follow:
+    \begin{itemize}
+        \item 
+    \end{itemize}
+
+    The remainder of this paper is organized as follows:
+
+    \bibliographystyle{IEEEtran}
+    \bibliography{main}
 \end{document}

### 2023-03-04 paper/main.tex
beautify the layout of main.tex

@@
     attention, since the ability to automatically design a "good" neural 
-    architecture. By leveraging machine learning algorithms (Zoph \& Le,\ \cite{https://doi.org/10.48550/arxiv.1611.01578}), 
-    NAS algorithms can explore a search space, which is comprised of 
-    numerous potential architectures, to find out a good architectures 
-    that outperform those designed by human experts. In recent years, 
-    the use of NAS is widespread, from object detection (Sun et al.,\ \cite{https://doi.org/10.48550/arxiv.2111.13336}), 
+    architecture. By leveraging machine learning algorithms (Zoph \& Le,
+    \ \cite{https://doi.org/10.48550/arxiv.1611.01578}), NAS algorithms 
+    can explore a search space, which is comprised of numerous potential 
+    architectures, to find out a good architectures that outperform those 
+    designed by human experts. In recent years, the use of NAS is widespread, 
+    from object detection (Sun et al.,\ \cite{https://doi.org/10.48550/arxiv.2111.13336}), 
     image recognition (Mellor et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.04647}) 
     and speech recognition (Zheng et al.,\ \cite{https://doi.org/10.48550/arxiv.2011.05649}, 
-    Mehrotra et al.,\ \cite{mehrotra2021nasbenchasr}) to 
-    natural language processing(Jiang et al.,\ \cite{jiang-etal-2019-improved}, 
+    Mehrotra et al.,\ \cite{mehrotra2021nasbenchasr}) to natural language 
+    processing(Jiang et al.,\ \cite{jiang-etal-2019-improved}, 
     Klyuchnikov et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.07116}, 
@@
     Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2203.09137}, 
-    Shu et al.,\ \cite{https://doi.org/10.48550/arxiv.2109.00817}), while some use 
-    gradient-based methods (Zhang \& Jia,\ \cite{https://doi.org/10.48550/arxiv.2110.08616}, 
+    Shu et al.,\ \cite{https://doi.org/10.48550/arxiv.2109.00817}), while 
+    some use gradient-based methods (Zhang \& Jia,\ \cite{https://doi.org/10.48550/arxiv.2110.08616}, 
     Cavagnero et al.,\ \cite{https://doi.org/10.48550/arxiv.2207.05135}, 

### 2023-03-04 score_networks.py
modify to score three indicator.

@@ -63,7 +63,9 @@ if 'valid' in args.dataset:
 train_loader = datasets.get_data(args.dataset, args.data_loc, args.trainval, args.batch_size, args.augtype, args.repeat, args)
 os.makedirs(args.save_loc, exist_ok=True)
 
-filename = f'{args.save_loc}/{args.save_string}_{args.score}_{args.nasspace}_{savedataset}{"_" + args.init + "_" if args.init != "" else args.init}_{"_dropout" if args.dropout else ""}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
+filename_NINASWOT = f'{args.save_loc}/NINASWOT_logdet_{args.nasspace}_{savedataset}{"_" + args.init + "_" if args.init != "" else args.init}_{"_dropout" if args.dropout else ""}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
+filename_entropy  = f'{args.save_loc}/entropy_mean_{args.nasspace}_{savedataset}{"_" + args.init + "_" if args.init != "" else args.init}_{"_dropout" if args.dropout else ""}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
+filename_NTKC  = f'{args.save_loc}/ntkc_{args.nasspace}_{savedataset}{"_" + args.init + "_" if args.init != "" else args.init}_{"_dropout" if args.dropout else ""}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
 accfilename = f'{args.save_loc}/{args.save_string}_accs_{args.nasspace}_{savedataset}_{args.trainval}'
 
 if args.dataset == 'cifar10':
@@ -85,12 +87,10 @@ except:
     accs = np.zeros(len(searchspace))
 
 print(f"Start calculate means and stds in {args.n_samples} samples")
-#print(f"now cuda memory allocated: {torch.cuda.memory_allocated(0)/1024/1024/1024}")
 means, stds = get_mean_std(searchspace, 15, train_loader, device, args)
 print(f"Done")
 print(f"means = {means}")
 print(f"stds  = {stds}")
-#means, stds = {"ntk": 0}, {"ntk": 1}
 
[…]

### 2023-03-04 plot_scores.py
modify to score three aspect

@@ -4,24 +4,17 @@ import numpy as np
 import matplotlib.pyplot as plt
 import matplotlib as mp
 import matplotlib
-matplotlib.use('Agg')
 from decimal import Decimal
 from scipy.special import logit, expit
 from scipy import stats
 import seaborn as sns
 
-'''
-font = {
-        'size'   : 18}
-
-matplotlib.rc('font', **font)
-'''
 SMALL_SIZE = 10
 MEDIUM_SIZE = 12
 BIGGER_SIZE = 14
 
 plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
-plt.rc('axes', titlesize=BIGGER_SIZE)     # fontsize of the axes title
+plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
 plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
 plt.rc('xtick', labelsize=MEDIUM_SIZE)    # fontsize of the tick labels
 plt.rc('ytick', labelsize=MEDIUM_SIZE)    # fontsize of the tick labels
@@ -56,230 +49,48 @@ parser.add_argument('--num_labels', default=1, type=int, help='#classes (nasbenc
 
 args = parser.parse_args()
 
-print(f'{args.batch_size}')
 random.seed(args.seed)
 np.random.seed(args.seed)
 
-filename = f'{args.save_loc}/{args.save_string}_{args.score}_{args.nasspace}_{args.dataset}{"_" + args.init + "_" if args.init != "" else args.init}_{"_dropout" if args.dropout else ""}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}.npy'
+filename_ninaswot = f'{args.save_loc}/ninaswot_logdet_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}.npy'
+filename_entropy  = f'{args.save_loc}/entropy_mean_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}.npy'
[…]

### 2023-03-04 score_networks.py

@@ -63,10 +63,10 @@ if 'valid' in args.dataset:
 train_loader = datasets.get_data(args.dataset, args.data_loc, args.trainval, args.batch_size, args.augtype, args.repeat, args)
 os.makedirs(args.save_loc, exist_ok=True)
 
-filename_NINASWOT = f'{args.save_loc}/NINASWOT_logdet_{args.nasspace}_{savedataset}{"_" + args.init + "_" if args.init != "" else args.init}_{"_dropout" if args.dropout else ""}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
-filename_entropy  = f'{args.save_loc}/entropy_mean_{args.nasspace}_{savedataset}{"_" + args.init + "_" if args.init != "" else args.init}_{"_dropout" if args.dropout else ""}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
-filename_NTKC  = f'{args.save_loc}/ntkc_{args.nasspace}_{savedataset}{"_" + args.init + "_" if args.init != "" else args.init}_{"_dropout" if args.dropout else ""}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
-accfilename = f'{args.save_loc}/{args.save_string}_accs_{args.nasspace}_{savedataset}_{args.trainval}'
+filename_ninaswot = f'{args.save_loc}/ninaswot_logdet_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
+filename_entropy  = f'{args.save_loc}/entropy_mean_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
+filename_ntk  = f'{args.save_loc}/ntk_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
+accfilename = f'{args.save_loc}/{args.save_string}_accs_{args.nasspace}_{args.dataset}_{args.trainval}'
 
[…]

### 2023-03-04 score_networks.py
test mode off

@@ -104,17 +104,14 @@ for i, (uid, network) in enumerate(searchspace):
         
         # ninaswot
         # ninaswot has mean 0, and std sqrt5 (naswot*2+ni)
-        #scores_ninaswot[i] = standardize(ninaswot_score(network, train_loader, device, stds, means, args), means["ninaswot"], stds["ninaswot"])
-        scores_ninaswot[i] = np.random.normal(0, 10)
+        scores_ninaswot[i] = standardize(ninaswot_score(network, train_loader, device, stds, means, args), means["ninaswot"], stds["ninaswot"])
 
         # ntk
-        #scores_ntk[i] = -standardize(ntk_score(network, train_loader, device, train_mode=args.trainval), means["ntk"], stds["ntk"])
-        scores_ntk[i] = np.random.normal(0,10)
+        scores_ntk[i] = -standardize(ntk_score(network, train_loader, device, train_mode=args.trainval), means["ntk"], stds["ntk"])
 
         # entropy
-        #network = init_net_gaussian(network, device)
-        #scores_entropy[i] = standardize(entropy_score(network, train_loader, device, args), means["entropy"], stds["entropy"])
-        scores_entropy[i] = np.random.normal(0, 20)
+        network = init_net_gaussian(network, device)
+        scores_entropy[i] = standardize(entropy_score(network, train_loader, device, args), means["entropy"], stds["entropy"])
 
         accs[i] = searchspace.get_final_accuracy(uid, acc_type, args.trainval)
         if i % 1000 == 0:

### 2023-03-04 replot.py
update replot.py which plots from .pickle

@@ -1,0 +1,6 @@
+import pickle
+import sys
+import matplotlib.pyplot as plt
+print(sys.argv[1])
+fig = pickle.load(open(sys.argv[1], 'rb'))
+plt.show()

### 2023-03-05 paper/main.tex
update

@@
     \end{equation}
-    Chen et al. used the condition number of NTK as the score function to estimate the performance of a network.
+    Chen et al. used the condition number of NTK as the score function to 
+    estimate the performance of a network.
 % results
-    It's shall find good architectures in reasonable time and computational resource.
+    It's shall find good architectures in reasonable time and computational 
+    resource.
 % conclusion
@@
     \begin{itemize}
+        \item Use hybrid score functions method to predict the performance 
+        of an architecture
         \item 
+        \item The simulation results show that 
     \end{itemize}
 
-    The remainder of this paper is organized as follows:
+    The remainder of this paper is organized as follows: Section 2 provides a 
+    brief introduction to state-of-the-art NAS techniques and describe the 
+    method in detail. Section 3 gives a detailed descriptions of the proposed 
+    method. Section 4 provides the results of the simulation.
 

### 2023-03-06 plot_scores.py
remove redundant file

@@ -1,96 +1,0 @@
-import argparse
-import random
-import numpy as np
-import matplotlib.pyplot as plt
-import matplotlib as mp
-import matplotlib
-from decimal import Decimal
-from scipy.special import logit, expit
-from scipy import stats
-import seaborn as sns
-
-SMALL_SIZE = 10
-MEDIUM_SIZE = 12
-BIGGER_SIZE = 14
-
-plt.rc('font', size=MEDIUM_SIZE)          # controls default text sizes
-plt.rc('axes', titlesize=MEDIUM_SIZE)     # fontsize of the axes title
-plt.rc('axes', labelsize=MEDIUM_SIZE)    # fontsize of the x and y labels
-plt.rc('xtick', labelsize=MEDIUM_SIZE)    # fontsize of the tick labels
-plt.rc('ytick', labelsize=MEDIUM_SIZE)    # fontsize of the tick labels
-plt.rc('legend', fontsize=MEDIUM_SIZE)    # legend fontsize
-plt.rc('figure', titlesize=BIGGER_SIZE)  # fontsize of the figure title
-
-parser = argparse.ArgumentParser(description='NAS Without Training')
-parser.add_argument('--data_loc', default='../cifardata/', type=str, help='dataset folder')
-parser.add_argument('--api_loc', default='../NAS-Bench-201-v1_0-e61699.pth',
-                    type=str, help='path to API')
-parser.add_argument('--save_loc', default='results', type=str, help='folder to save results')
-parser.add_argument('--save_string', default='naswot', type=str, help='prefix of results file')
-parser.add_argument('--score', default='hook_logdet', type=str, help='the score to evaluate')
-parser.add_argument('--nasspace', default='nasbench201', type=str, help='the nas search space to use')
-parser.add_argument('--batch_size', default=128, type=int)
-parser.add_argument('--repeat', default=1, type=int, help='how often to repeat a single image with a batch')
-parser.add_argument('--augtype', default='none', type=str, help='which perturbations to use')
-parser.add_argument('--sigma', default=0.05, type=float, help='noise level if augtype is "gaussnoise"')
-parser.add_argument('--init', default='', type=str)
-parser.add_argument('--GPU', default='0', type=str)
[…]

### 2023-03-06 score/__init__.py
fix a little glitch

@@ -3,6 +3,9 @@ from .ntk_score import ntk_score
 from .ninaswot_score import ninaswot_score, ni_score, naswot_score, get_batch_jacobian
 from .entropy_score import entropy_score, init_net_gaussian
 import numpy as np
+from tqdm import tqdm
+import time
+from statistics import mean
 
 def standardize(x, m, s):
     return (x-m)/s
@@ -13,7 +16,11 @@ def get_mean_std(searchspace, sample_n, train_loader, device, args):
     scores_entropy = []
     scores_ntk     = []
     arches = np.random.randint(0, len(searchspace), sample_n)
+    nruns = tqdm(total = sample_n)
+    times = []
     for arch in arches:
+        st = time.time()
+
         uid = searchspace[arch]
         network = searchspace.get_network(uid)
 
@@ -22,6 +29,9 @@ def get_mean_std(searchspace, sample_n, train_loader, device, args):
         scores_ntk.append(ntk_score(network, train_loader, device))
         network = init_net_gaussian(network, device)
         scores_entropy.append(entropy_score(network, train_loader, device, args))
+        times.append(time.time() - st)
+        nruns.set_description(f"average elapse={mean(times):.2f}")
+        nruns.update(1)
         del network
 
     scores_naswot  = np.array(scores_naswot)
@@ -34,6 +44,6 @@ def get_mean_std(searchspace, sample_n, train_loader, device, args):
     stds  = {"naswot": calstd(scores_naswot), "ni": calstd(scores_ni), "entropy": calstd(scores_entropy), "ntk": calstd(scores_ntk)}
     means = {"naswot": calmean(scores_naswot), "ni": calmean(scores_ni), "entropy": calmean(scores_entropy), "ntk": calmean(scores_ntk)}
     
-    del scores_naswot, scores_ni, scores_ntk, scores_entropy
+    del scores_naswot, scores_ni, scores_ntk, scores_entropy, times
 
-    return stds, means
+    return means, stds

### 2023-03-06 score_networks.py

@@ -14,7 +14,7 @@ from utils import add_dropout, init_network
 from statistics import mean
 from score import *
 
-parser = argparse.ArgumentParser(description='NAS Without Training')
+parser = argparse.ArgumentParser(description='Genetic-Based NAS with Hybrid Score Functions')
 parser.add_argument('--data_loc', default='../cifardata/', type=str, help='dataset folder')
 parser.add_argument('--api_loc', default='../NAS-Bench-201.pth',
                     type=str, help='path to API')
@@ -63,10 +63,12 @@ if 'valid' in args.dataset:
 train_loader = datasets.get_data(args.dataset, args.data_loc, args.trainval, args.batch_size, args.augtype, args.repeat, args)
 os.makedirs(args.save_loc, exist_ok=True)
 
-filename_ninaswot = f'{args.save_loc}/ninaswot_logdet_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
-filename_entropy  = f'{args.save_loc}/entropy_mean_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
+filename_ninaswot = f'{args.save_loc}/ninaswot_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
+filename_entropy  = f'{args.save_loc}/entropy_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
 filename_ntk  = f'{args.save_loc}/ntk_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}'
-accfilename = f'{args.save_loc}/{args.save_string}_accs_{args.nasspace}_{args.dataset}_{args.trainval}'
+filename_acc = f'{args.save_loc}/{args.save_string}_accs_{args.nasspace}_{args.dataset}_{args.trainval}'
+
[…]

### 2023-03-06 plot_2d_scores.py
2d plot

@@ -1,0 +1,85 @@
+import argparse
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import stats
+
+parser = argparse.ArgumentParser(description='Genetic-Based NAS with Hybrid Score Functions')
+parser.add_argument('--data_loc', default='../cifardata/', type=str, help='dataset folder')
+parser.add_argument('--api_loc', default='../NAS-Bench-201-v1_0-e61699.pth',
+                    type=str, help='path to API')
+parser.add_argument('--save_loc', default='results', type=str, help='folder to save results')
+parser.add_argument('--save_string', default='naswot', type=str, help='prefix of results file')
+parser.add_argument('--score', default='hook_logdet', type=str, help='the score to evaluate')
+parser.add_argument('--nasspace', default='nasbench201', type=str, help='the nas search space to use')
+parser.add_argument('--batch_size', default=128, type=int)
+parser.add_argument('--repeat', default=1, type=int, help='how often to repeat a single image with a batch')
+parser.add_argument('--augtype', default='none', type=str, help='which perturbations to use')
+parser.add_argument('--sigma', default=0.05, type=float, help='noise level if augtype is "gaussnoise"')
+parser.add_argument('--init', default='', type=str)
+parser.add_argument('--GPU', default='0', type=str)
+parser.add_argument('--seed', default=1, type=int)
+parser.add_argument('--trainval', action='store_true')
+parser.add_argument('--dropout', action='store_true')
+parser.add_argument('--dataset', default='cifar10', type=str)
+parser.add_argument('--maxofn', default=1, type=int, help='score is the max of this many evaluations of the network')
+parser.add_argument('--n_samples', default=100, type=int)
+parser.add_argument('--n_runs', default=500, type=int)
+parser.add_argument('--stem_out_channels', default=16, type=int, help='output channels of stem convolution (nasbench101)')
+parser.add_argument('--num_stacks', default=3, type=int, help='#stacks of modules (nasbench101)')
+parser.add_argument('--num_modules_per_stack', default=3, type=int, help='#modules per stack (nasbench101)')
[…]

### 2023-03-06 plot_3d_scores.py
3d plot

@@ -1,0 +1,69 @@
+import argparse
+import numpy as np
+import matplotlib.pyplot as plt
+
+parser = argparse.ArgumentParser(description='Genetic-Based NAS with Hybrid Score Function')
+parser.add_argument('--data_loc', default='../cifardata/', type=str, help='dataset folder')
+parser.add_argument('--api_loc', default='../NAS-Bench-201-v1_0-e61699.pth',
+                    type=str, help='path to API')
+parser.add_argument('--save_loc', default='results', type=str, help='folder to save results')
+parser.add_argument('--save_string', default='naswot', type=str, help='prefix of results file')
+parser.add_argument('--score', default='hook_logdet', type=str, help='the score to evaluate')
+parser.add_argument('--nasspace', default='nasbench201', type=str, help='the nas search space to use')
+parser.add_argument('--batch_size', default=128, type=int)
+parser.add_argument('--repeat', default=1, type=int, help='how often to repeat a single image with a batch')
+parser.add_argument('--augtype', default='none', type=str, help='which perturbations to use')
+parser.add_argument('--sigma', default=0.05, type=float, help='noise level if augtype is "gaussnoise"')
+parser.add_argument('--init', default='', type=str)
+parser.add_argument('--GPU', default='0', type=str)
+parser.add_argument('--seed', default=1, type=int)
+parser.add_argument('--trainval', action='store_true')
+parser.add_argument('--dropout', action='store_true')
+parser.add_argument('--dataset', default='cifar10', type=str)
+parser.add_argument('--maxofn', default=1, type=int, help='score is the max of this many evaluations of the network')
+parser.add_argument('--n_samples', default=100, type=int)
+parser.add_argument('--n_runs', default=500, type=int)
+parser.add_argument('--stem_out_channels', default=16, type=int, help='output channels of stem convolution (nasbench101)')
+parser.add_argument('--num_stacks', default=3, type=int, help='#stacks of modules (nasbench101)')
+parser.add_argument('--num_modules_per_stack', default=3, type=int, help='#modules per stack (nasbench101)')
[…]

### 2023-03-06 process_data.py
process data like add together

@@ -1,0 +1,71 @@
+import argparse
+import numpy as np
+from scipy import stats
+
+parser = argparse.ArgumentParser(description='Genetic-Based NAS with Hybrid Score Functions')
+parser.add_argument('--data_loc', default='../cifardata/', type=str, help='dataset folder')
+parser.add_argument('--api_loc', default='../NAS-Bench-201.pth',
+                    type=str, help='path to API')
+parser.add_argument('--save_loc', default='results', type=str, help='folder to save results')
+parser.add_argument('--save_string', default='naswot', type=str, help='prefix of results file')
+parser.add_argument('--score', default='hook_logdet', type=str, help='the score to evaluate')
+parser.add_argument('--nasspace', default='nasbench201', type=str, help='the nas search space to use')
+parser.add_argument('--batch_size', default=128, type=int)
+parser.add_argument('--repeat', default=1, type=int, help='how often to repeat a single image with a batch')
+parser.add_argument('--augtype', default='none', type=str, help='which perturbations to use')
+parser.add_argument('--sigma', default=0.05, type=float, help='noise level if augtype is "gaussnoise"')
+parser.add_argument('--init', default='', type=str)
+parser.add_argument('--GPU', default='0', type=str)
+parser.add_argument('--seed', default=1, type=int)
+parser.add_argument('--trainval', action='store_true')
+parser.add_argument('--dropout', action='store_true')
+parser.add_argument('--dataset', default='cifar10', type=str)
+parser.add_argument('--maxofn', default=1, type=int, help='score is the max of this many evaluations of the network')
+parser.add_argument('--n_samples', default=100, type=int)
+parser.add_argument('--n_runs', default=500, type=int)
+parser.add_argument('--stem_out_channels', default=16, type=int, help='output channels of stem convolution (nasbench101)')
+parser.add_argument('--num_stacks', default=3, type=int, help='#stacks of modules (nasbench101)')
+parser.add_argument('--num_modules_per_stack', default=3, type=int, help='#modules per stack (nasbench101)')
[…]

### 2023-03-06 score.sh
add process & plot example

@@ -1,4 +1,11 @@
-python score_networks.py --save_string all_score --trainval --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 0 --dataset cifar10
+python score_networks.py --save_string all_score --trainval --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 0 --n_samples 50 --dataset cifar10
+
+<<plot_example
+python process_data.py --oper ninaswot_add_ntk_add_entropy --save_string all_score --save_loc $1 --trainval --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 0 --n_samples 50 --dataset cifar10
+python plot_2d_scores.py --targets acc-ninaswot_add_ntk_add_entropy --save_string all_score --save_loc $1 --trainval --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 0 --n_samples 50 --dataset cifar10
+python plot_3d_scores.py --save_string all_score --save_loc $1 --trainval --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 0 --n_samples 50 --dataset cifar10
+plot_example
+
 #python score_networks.py --save_string all_score --trainval --augtype none --repeat 1 --score 1_-1_1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 0 --dataset cifar100 --data_loc ../cifar100/
 #python score_networks.py --save_string all_score --trainval --augtype none --repeat 1 --score 1_-1_1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 0 --dataset ImageNet16-120 --data_loc ../imagenet16/Imagenet16/
 

### 2023-03-06 paper/main.tex

--- 2023-03-04 paper/main.tex
@@
     Despite the promising results of NAS, there are still many challenges 
-    to conquer. One of the major problems is the extremely high computational 
+    to conquer. One major problem is the extremely high computational 
     cost to search for an optimal architecture, which can make NAS impractical 
@@
     Abdelfattah et al.,\ \cite{https://doi.org/10.48550/arxiv.2101.08134}).
+
 % what is unknown?
     However, most of score functions suffer from low correlation between 
-    score value and the result of an architecture, leading to a trap that 
-    no matter how good the search method is used, we can hardly find an 
-    optimal architecture.
-% how and why
+    score value and the result of an architecture, leading to a predicament 
+    that no matter how good the search method is used, we can hardly find 
+    an optimal architecture. 
     The major problem causes the low correlation is that a single score 
     function can only evaluate one perspect/characteristic of an architecture.
+
 % method
-    By cooperating three heterogeneous score functions with genetic-based 
-    search method, we shall evaulate an architecture from different aspects. 
-    More specifically, the first score function is noise immunity for neural 
-    architecture search without search (NINASWOT) (Wu et al.\ \cite{10.1145/3491396.3506510}). 
-    Based on the work of Mellor et al., they proposed the measurement of 
-    the correlation between binary activation paterns of input data at each 
-    ReLU layer. Later, Wu et al. found a high score obtained by such a 
-    function may not correspond to a high-performence model. Thus, they 
-    additionally applied noisy immunity method, called NINASWOT. Second one 
-    is maximum-entropy detection (MAE-DET) (Sun et al.\ \cite{https://doi.org/10.48550/arxiv.2111.13336}). 
+    Based on the fact above, we propose cooperating three heterogeneous score 
+    functions with genetic-based search method, we shall evaulate an architecture 
+    from different aspects. More specifically, the first score function is 
+    noise immunity for neural architecture search without training (NINASWOT) 
+    (Wu et al.\ \cite{10.1145/3491396.3506510}). Starting with the work of Mellor 
+    et al., they proposed the measurement of the correlation between binary 
+    activation paterns of input data at each ReLU layer, named as neural architecture 
+    search without training (NASWOT). Later, Wu et al. found a high score obtained 
+    by such a function may not correspond to a high-performence model. Thus, 
+    they additionally applied noisy immunity method on NASWOT, named as NINASWOT. 
+    Second one is maximum-entropy detection (MAE-DET) (Sun et al.\ \cite{https://doi.org/10.48550/arxiv.2111.13336}). 
     Based on the work of Sun et al., they proposed to find the maximum of 
     the differential entropy by calculating the variance of the output at 
-    the final layer with the input Gaussian noise images. Third one is 
-    condition number of  neural tangent kernel (NTK) (Chen et al.\ \cite{https://doi.org/10.48550/arxiv.2102.11535}), 
-    which is defined as 
+    the final layer with the input Gaussian noise images and random weights on 
+    Gaussian distribution. Third one is condition number of neural tangent kernel 
+    (NTK) (Chen et al.\ \cite{https://doi.org/10.48550/arxiv.2102.11535}), which is 
+    defined as 
     \begin{equation}
@@
     \end{equation}
-    Chen et al. used the condition number of NTK as the score function to estimate the performance of a network.
+    Chen et al. used the condition number of NTK as the score to estimate the performance of an architecture.
+
 % results
-    It's shall find good architectures in reasonable time and computational resource.
+    The simulation results on cifar-10, cifar-100, and ImageNet-16-120 
+    shall show that the proposed method can find good architectures in 
+    reasonable time and computational resource. (TODO)
+
 % conclusion
@@
     \begin{itemize}
-        \item 
+        \item Develope a genetic-based neural architecture search method based on three hybrid score function.
+        \item (TODO)
     \end{itemize}
 
-    The remainder of this paper is organized as follows:
+    The remainder of this paper is organized as follows: Section 2 provides the 
+    detail about the three heterogeneous score functions. Section 3 gives a detailed 
+    description about the proposed method. Section 4 provide the simulation results 
+    in different search space. The conclusion and further prospect are gived in Section 5.
 

### 2023-03-06 results/20230306/find_the_problem.py
update experiment 20230306

@@ -1,0 +1,57 @@
+import numpy as np
+import sys
+
+ninaswot = np.load("ninaswot_nasbench201_cifar10_none_0.05_1_True_128_1_1.npy")
+entropy  = np.load("entropy_nasbench201_cifar10_none_0.05_1_True_128_1_1.npy")
+ntk      = np.load("ntk_nasbench201_cifar10_none_0.05_1_True_128_1_1.npy")
+tot      = ninaswot + entropy + ntk
+acc      = np.load("all_score_accs_nasbench201_cifar10_True.npy")
+
+the_problems = np.load("acc-ninaswot_add_ntk_add_entropy_the_problems_nasbench201_cifar10_none_0.05_1_True_128_1_1.npy")
+
+max_acc = np.argmax(acc)
+print(f"the max acc is {max_acc}")
+print(f"no.\tacc\tninas\tentropy\tntk\ttot")
+print(f"{max_acc}\t{acc[max_acc]:.3f}\t{ninaswot[max_acc]:.3f}\t{entropy[max_acc]:.3f}\t{ntk[max_acc]:.3f}\t{tot[max_acc]:.3f}")
+print(f"===========================================================================")
+print(f"the problems are here:")
+print(f"no.\tacc\tninas\tentropy\tntk\ttot")
+for the_problem in the_problems:
+    #if ninaswot[the_problem] < ninaswot[max_acc]:continue
+    #if entropy[the_problem] < entropy[max_acc]:continue
+    #if ntk[the_problem] < ntk[max_acc]:continue
+    print(f"{the_problem}\t{acc[the_problem]:.3f}\t{ninaswot[the_problem]:.3f}\t{entropy[the_problem]:.3f}\t{ntk[the_problem]:.3f}\t{tot[the_problem]:.3f}")
+
+class arch():
+    def __init__(self, no, acc, ninaswot, entropy, ntk, tot):
+        self.no = no
+        self.acc = acc
+        self.ninaswot = ninaswot
+        self.entropy = entropy
+        self.ntk = ntk
+        self.tot = tot
+
+arches = []
+for i in range(len(acc)):
+    arches.append(arch(i, acc[i], ninaswot[i], entropy[i], ntk[i], tot[i]))
+
+def sort_and_prune(arches, what, proposition):
+    arches.sort(key = lambda this: eval(f"this.{what}"), reverse = True)
+    print("================================================")
[…]

### 2023-03-06 plot_2d_scores.py
add mask which acc < max_acc but score > max_acc_score

@@ -51,6 +51,24 @@ for fname in filenames:
 
 scores = [np.load(filenames[i]) for i in range(len(filenames))]
 
+assert len(scores[0]) == 15625, "the length of scores isn't correct"
+
+####
+mask = np.full(scores[0].shape, False)
+for i, fname in enumerate(filenames):
+    if "acc" in fname:
+        max_score = np.argmax(scores[i])
+        mask = scores[1-i] > scores[1-i][max_score]
+the_problems = []
+for i in range(len(mask)):
+    if mask[i] == True:
+        the_problems.append(i)
+the_problems = np.array(the_problems)
+wheres_the_problems = f'{args.save_loc}/acc-{targets[1]}_the_problems_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.trainval}_{args.batch_size}_{args.maxofn}_{args.seed}.npy'
+np.save(wheres_the_problems, the_problems)
+print(f"save the problems: {the_problems}")
+####
+
 mask = scores[1] < 0 | np.isinf(scores[1]) | np.isnan(scores[1])
 
 scores[0] = scores[0][~mask]

### 2023-03-12 paper/main.tex
update related work section

@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-%\documentclass[sigconf]{acmart}
-%\let\Bbbk\relax %% fix bug
+%\documentclass[conference]{IEEEtran}
+%\IEEEoverridecommandlockouts
+\documentclass[sigconf]{acmart}
+\let\Bbbk\relax %% fix bug
 \usepackage[utf8]{inputenc}
-\usepackage{graphicx}
-\usepackage{listings}
-\usepackage{url}
-\usepackage{indentfirst}
-\usepackage{comment}
-\usepackage{algorithm}
+
+% =======================
 \usepackage{amssymb}
@@
 \usepackage{amsopn}
+%\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+
+\usepackage{textcomp}
+
+\usepackage{boxedminipage}
+\usepackage{enumerate}
+\usepackage{multirow}
+\usepackage{url}
+\usepackage{times}
+\usepackage{version}
+% \usepackage[pdftex]{graphicx}
+\usepackage{epsfig}
+\usepackage{epsf}
+%\usepackage{graphics}
+\usepackage{caption}
+\usepackage{subfigure}
+\usepackage{algorithm}
 \usepackage{algpseudocode}
+%\PassOptionsToPackage{bookmarks={false}}{hyperref}
+%%%%%%%%%%%%
+\usepackage{comment}
+\usepackage{multicol}
+\usepackage{booktabs}
+\usepackage{dblfloatfix}
+% ==========================
+\input lstset.tex
+\input macros.tex
 
-\title{GA-based Training-Free NAS Algorithm with Hybrid Score Function}
-\author{Hsieh Cheng-Han}
-\date{2023}
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
 
@@
 
-\maketitle
+\title{GA-based Training-Free NAS Algorithm with Hybrid Score Function}
 
-\section{Abstract}
+\author{Hsieh Cheng-Han}
+\email{emiliaistruelove@gmail.com}
+\affiliation{%
+  \institution{Department of Computer Science and Engineering, National Sun Yat-sen University}
+  \streetaddress{70 Lienhai Rd}
+  \city{Kaohsiung}
+  \country{Taiwan}
+}
+
+\author{Chun-Wei Tsai}
+\email{cwtsai@mail.cse.nsysu.edu.tw}
+\affiliation{%
+  \institution{Department of Computer Science and Engineering, National Sun Yat-sen University}
+  \streetaddress{70 Lienhai Rd}
+  \city{Kaohsiung}
+  \country{Taiwan}
+}
+
+\begin{abstract}
 
@@
 
+\end{abstract}
+\maketitle
+
 \section{Introduction}
+\label{sec:introduction}
 
@@
     attention, since the ability to automatically design a "good" neural 
-    architecture. By leveraging machine learning algorithms (Zoph \& Le,
-    \ \cite{https://doi.org/10.48550/arxiv.1611.01578}), NAS algorithms 
-    can explore a search space, which is comprised of numerous potential 
-    architectures, to find out a good architectures that outperform those 
-    designed by human experts. In recent years, the use of NAS is widespread, 
-    from object detection (Sun et al.,\ \cite{https://doi.org/10.48550/arxiv.2111.13336}), 
-    image recognition (Mellor et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.04647}) 
-    and speech recognition (Zheng et al.,\ \cite{https://doi.org/10.48550/arxiv.2011.05649}, 
-    Mehrotra et al.,\ \cite{mehrotra2021nasbenchasr}) to natural language 
-    processing(Jiang et al.,\ \cite{jiang-etal-2019-improved}, 
-    Klyuchnikov et al.,\ \cite{https://doi.org/10.48550/arxiv.2006.07116}, 
-    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2005.14187}).
+    architecture. By leveraging machine learning algorithms \cite{https://doi.org/10.48550/arxiv.1611.01578}, 
+    NAS algorithms can explore a search space, which is comprised of numerous 
+    potential architectures, to find out a good architectures that outperform 
+    those designed by human experts. In recent years, the use of NAS is 
+    widespread, from object detection \cite{https://doi.org/10.48550/arxiv.2111.13336}, 
+    image recognition \cite{https://doi.org/10.48550/arxiv.2006.04647} 
+    and speech recognition \cite{https://doi.org/10.48550/arxiv.2011.05649} 
+    \cite{mehrotra2021nasbenchasr} to natural language 
+    processing. \cite{jiang-etal-2019-improved} 
+    \cite{https://doi.org/10.48550/arxiv.2006.07116} 
+    \cite{https://doi.org/10.48550/arxiv.2005.14187}
 
@@
     To overcome this challenge, recent works developed and proposed lots 
-    of method which is so called training-free NAS. Some use mean absolute 
-    error random sampling (MRS) (Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.1805.07159}, 
-    Camero et al.,\ \cite{Camero_2021}, Camero et al.,\ \cite{https://doi.org/10.48550/arxiv.2106.15295}) 
-    as a training-free score function and some use neural tangent kernel 
-    (NTK) (Chen et al.,\ \cite{https://doi.org/10.48550/arxiv.2102.11535}, 
-    Wang et al.,\ \cite{https://doi.org/10.48550/arxiv.2203.09137}, 
-    Shu et al.,\ \cite{https://doi.org/10.48550/arxiv.2109.00817}), while 
-    some use gradient-based methods (Zhang \& Jia,\ \cite{https://doi.org/10.48550/arxiv.2110.08616}, 
-    Cavagnero et al.,\ \cite{https://doi.org/10.48550/arxiv.2207.05135}, 
-    Abdelfattah et al.,\ \cite{https://doi.org/10.48550/arxiv.2101.08134}).
+    of method which is so called training-free NAS. 
+    % NINASWOT
+    For example, Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed the 
+    measurement of the correlation between the binary activation paterns, 
+    induced by the untrained network at two inputs, named as neural architecture 
+    search without training (NASWOT). The correlation is defined as the 
+    logarithmic determinant of the kernel matrix, as follows:
+    \begin{equation}
+        s=\log\lvert K_H\rvert
+    \end{equation}
+    where $K_H$ is the kernel matrix.
+    Later, Wu et al. \cite{10.1145/3491396.3506510} found a high score 
+    obtained by such a function may not correspond to a high-performence 
+    model. Thus, they additionally applied noisy immunity method on NASWOT, 
+    named as noisy immunity for NASWOT (NINASWOT).
+    % NTK
+    For another example, Chen et al. proposed to compute the condition 
+    number of neural tangent kernel (NTK) \cite{https://doi.org/10.48550/arxiv.2102.11535} 
+    \cite{https://doi.org/10.48550/arxiv.2203.09137} \cite{https://doi.org/10.48550/arxiv.2109.00817}, 
+    which is defined as 
+    \begin{equation}
+        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
+    \end{equation}
+    and used as the score to estimate the trainability of an architecture.
+	% unknown
 
@@
 % method
-    Based on the fact above, we propose cooperating three heterogeneous score 
+    To address the problem, we propose cooperating three heterogeneous score 
     functions with genetic-based search method, we shall evaulate an architecture 
     from different aspects. More specifically, the first score function is 
-    noise immunity for neural architecture search without training (NINASWOT) 
-    (Wu et al.\ \cite{10.1145/3491396.3506510}). Starting with the work of Mellor 
-    et al., they proposed the measurement of the correlation between binary 
-    activation paterns of input data at each ReLU layer, named as neural architecture 
-    search without training (NASWOT). Later, Wu et al. found a high score obtained 
-    by such a function may not correspond to a high-performence model. Thus, 
-    they additionally applied noisy immunity method on NASWOT, named as NINASWOT. 
-    Second one is maximum-entropy detection (MAE-DET) (Sun et al.\ \cite{https://doi.org/10.48550/arxiv.2111.13336}). 
-    Based on the work of Sun et al., they proposed to find the maximum of 
-    the differential entropy by calculating the variance of the output at 
-    the final layer with the input Gaussian noise images and random weights on 
-    Gaussian distribution. Third one is condition number of neural tangent kernel 
-    (NTK) (Chen et al.\ \cite{https://doi.org/10.48550/arxiv.2102.11535}), which is 
-    defined as 
-    \begin{equation}
-        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
-    \end{equation}
-    Chen et al. used the condition number of NTK as the score to estimate the performance of an architecture.
-
-% results
-    The simulation results on cifar-10, cifar-100, and ImageNet-16-120 
-    shall show that the proposed method can find good architectures in 
-    reasonable time and computational resource. (TODO)
+    NINASWOT \cite{10.1145/3491396.3506510} as an indicator of the ability 
+    to distinguish two images. The second one is the condition number of NTK 
+    \cite{https://doi.org/10.48550/arxiv.2102.11535} as score to estimate the 
+    trainability of an architecture. The last one is (TBD).
 
@@
     \begin{itemize}
-        \item Develope a genetic-based neural architecture search method based on three hybrid score function.
-        \item (TODO)
+        \item Develope a genetic-based neural architecture search method based on three hybrid score functions.
+        \item Cooperating three score functions to get a higher correlation between score and accuracy.
     \end{itemize}
+    % expect what
 
@@
     description about the proposed method. Section 4 provide the simulation results 
-    in different search space. The conclusion and further prospect are gived in Section 5.
+    in different search space. The conclusion and further prospect are gived in 
+    Section 5.
+
+    \section{Related Works}
+    In these days, the studies of training-free neural architecture search (NAS) 
+    go viral, since the ability to accelerate the design of a neural network 
+    architecture used on specific application, while in the same time, by using 
+    training-free score function, training-free NAS cleverly avoid the drawback 
+    of long-time training.
+
+    Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed a 
+    score function without the requirement for training. 
+    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ mapped through a neural 
+    network as $f(x_i)$. The indicator variables from each ReLU units in $f$ 
+    at $x_i$ form a binary code $c_i$ that define the linear region.
+    The correlation between binary codes for the whole mini-batch can be examined 
+    by computing the kernel matrix
+    \begin{equation}
+        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
+    \end{equation}
+    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
+    distance between the binary code $c_i$ and $c_j$.
+    With the kernel matrix, the score of an architecture can be evaluate as 
+    follow:
+    \begin{equation}
+        s=\log\lvert K_H\rvert
+    \end{equation}
+    The rationale behind is to see how dissimilar the linear region activated by 
+    the ReLU units.
+
+    On the other hand, Chen et al. proposed using the condition number of NTK 
+    as an evaluation of the trainability, definde as
+    \begin{equation}
+        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
+    \end{equation}
+    where $\lambda_{\textrm{max}}(\hat\Theta)$ and $\lambda_{\textrm{min}}(\hat\Theta)$ 
+    are the maximum and minimum eigenvalues of NTK ($\hat\Theta$) respectively.
+    The rationale behind is based on the work of Lee et al. \cite{Lee_2020} and 
+    Xiao et al. \cite{DBLP:journals/corr/abs-1912-13053}, which concluded briefly, 
+    the training dynamics of a wide neural network can be solved as 
+    \begin{equation}
+        \mu_t(\textbf{X}_{\textrm{train}})=(\textbf{I}-e^{-\eta\hat\Theta_{\textrm{train}}t})\textbf{Y}_{\textrm{train}}
+    \end{equation}
 

### 2023-03-13 paper/main.tex

@@
     The rationale behind is to see how dissimilar the linear region activated by 
-    the ReLU units.
+    the ReLU units between two inputs. An architecture shall learn better 
+    when inputs are well separated.
+    Later, Wu et al. \cite{10.1145/3491396.3506510}
 
-    On the other hand, Chen et al. proposed using the condition number of NTK 
-    as an evaluation of the trainability, definde as
+    On the other hand, instead of using the correlation of binary activation 
+    patterns as score. Chen et al. proposed using the condition number of NTK 
+    as an evaluation of the trainability, defined as
     \begin{equation}

### 2023-03-14 GA_search.py
modify the prompt

@@ -46,7 +46,7 @@ parser.add_argument('--train', action='store_true')
 parser.add_argument('--activations', action='store_true')
 parser.add_argument('--cosine', action='store_true')
 parser.add_argument('--dataset', default='cifar10', type=str)
-parser.add_argument('--n_samples', default=15, type=int)
+parser.add_argument('--n_samples', default=50, type=int)
 parser.add_argument('--n_runs', default=500, type=int)
 parser.add_argument('--stem_out_channels', default=16, type=int, help='output channels of stem convolution (nasbench101)')
 parser.add_argument('--num_stacks', default=3, type=int, help='#stacks of modules (nasbench101)')
@@ -93,7 +93,7 @@ print(f"Initialize the train loader...")
 print(f"dataset = {args.dataset}, data location = {args.data_loc}, validation = {args.valid}")
 train_loader = datasets.get_data(args.dataset, args.data_loc, args.valid, args.batch_size, args.repeat, args)
 
-print(f"Initialize the nas bench...")
+print(f"Initialize the nas bench api...")
 args.dataset, acc_type = remap_dataset_names(args.dataset, args.valid, args.test, args.train)
 print(f"dataset = {args.dataset}, validation = {args.valid}")
 searchspace = nasspace.get_search_space(args)
@@ -107,9 +107,10 @@ acc       = []
 topscores = []
 
 print(f"Now calculate means and standards.")
-#means, stds = get_mean_std(searchspace, args.n_samples, train_loader, device, args)
+means, stds = get_mean_std(searchspace, args.n_samples, train_loader, device, args)
 
 # cifar10
+"""
 means = {}
 stds = {}
 means["ni"] = -0.08314655303955078
@@ -122,7 +123,7 @@ means["entropy"] = 721.064296875
 stds["entropy"] = 280.67810232781636
 means["ninaswot"] = 0
 stds["ninaswot"]  = np.sqrt(5)
-
+"""
 # cifar100
 """
 means = {}

### 2023-03-14 search.sh
used gpu 1 -> gpu 0

@@ -1,2 +1,2 @@
-python GA_search.py --maxn_pop 100 --maxn_iter 10 --prob_mut 0.1 --prob_cr 0.8 --save_string all_score --valid --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 1 --n_samples 50 --data_loc ../cifardata/ --dataset cifar10 
+python GA_search.py --maxn_pop 100 --maxn_iter 10 --prob_mut 0.1 --prob_cr 0.8 --save_string all_score --valid --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 0 --n_samples 50 --data_loc ../cifardata/ --dataset cifar10 
 #python GA_search.py --maxn_pop 100 --maxn_iter 10 --prob_mut 0.1 --prob_cr 0.8 --save_string all_score --valid --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 0 --n_samples 50 --data_loc ../ImageNet16 --dataset ImageNet16-120

### 2023-03-14 search/GA.py
fix cheat code bug

@@ -16,9 +16,9 @@ class GA():
     def __init__(self, MAXN_CONNECTION, MAXN_OPERATION, searchspace, train_loader, device, stds, means, acc_type, args):
         #### cheat
         if args.valid:
-            base_loc  = "/home/jasonzzz/Genetic-Based-Neural-Architecture-Search-with-Hybrid-Score-Functions/results/score/{args.dataset}"
+            base_loc  = f"/home/jasonzzz/Genetic-Based-Neural-Architecture-Search-with-Hybrid-Score-Functions/results/score/{args.dataset}"
         elif args.test:
-            base_loc  = "/home/jasonzzz/Genetic-Based-Neural-Architecture-Search-with-Hybrid-Score-Functions/results/score/{args.dataset}-test"
+            base_loc  = f"/home/jasonzzz/Genetic-Based-Neural-Architecture-Search-with-Hybrid-Score-Functions/results/score/{args.dataset}-test"
         self.ninaswot = np.load(f"{base_loc}/ninaswot_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.ntk      = np.load(f"{base_loc}/ntk_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.entropy  = np.load(f"{base_loc}/entropy_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")

### 2023-03-14 search/GA_based_on_rank.py

@@ -15,9 +15,9 @@ class GA():
     def __init__(self, MAXN_CONNECTION, MAXN_OPERATION, searchspace, train_loader, device, stds, means, acc_type, args):
         #### cheat
         if args.valid:
-            base_loc  = "/home/jasonzzz/Genetic-Based-Neural-Architecture-Search-with-Hybrid-Score-Functions/results/score/{args.dataset}"
+            base_loc  = f"/home/jasonzzz/Genetic-Based-Neural-Architecture-Search-with-Hybrid-Score-Functions/results/score/{args.dataset}"
         elif args.test:
-            base_loc  = "/home/jasonzzz/Genetic-Based-Neural-Architecture-Search-with-Hybrid-Score-Functions/results/score/{args.dataset}-test"
+            base_loc  = f"/home/jasonzzz/Genetic-Based-Neural-Architecture-Search-with-Hybrid-Score-Functions/results/score/{args.dataset}-test"
 
         self.ninaswot = np.load(f"{base_loc}/ninaswot_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.ntk      = np.load(f"{base_loc}/ntk_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")

### 2023-03-14 search/GA.py
fix bug

@@ -62,7 +62,7 @@ class GA():
                 #(standardize(ninaswot_score(network, self.train_loader, self.device, self.stds, self.means, self.args), self.means["ninaswot"], self.stds["ninaswpt"]), \
                 #-standardize(ntk_score(network, self.train_loader, self.device), self.means["ntk"], self.stds["ntk"]), \
                 #standardize(entropy_score(network, self.train_loader, self.device, self.args), self.means["entropy"], self.stds["entropy"]))
-                self.population[i].fitness = self.DICT[self.population[i].gene] = self.ninaswot[self.populatopn[i].uid]
+                self.population[i].fitness = self.DICT[self.population[i].gene] = self.ninaswot[self.population[i].uid]
             else:
                 self.population[i].fitness = self.DICT[self.population[i].gene]
             if self.population[i].fitness > self.best_chrom.fitness or self.best_chrom.gene == "":

### 2023-03-14 search/GA_based_on_rank.py
fix bug

@@ -44,7 +44,6 @@ class GA():
         self.means = means
         self.acc_type = acc_type
         self.best_chrom = chromosome()
-        self.proposition = eval(args.proposition)
         self.candiate = {"ninaswot":[], "ntk":[]}
         self.NAS_201_ops = ['none', 'skip_connect', 'nor_conv_1x1', 'nor_conv_3x3', 'avg_pool_3x3']
 
@@ -169,7 +168,7 @@ class GA():
             rank[chrom.uid] = rk+1
         for rk, chrom in enumerate(self.candiate["ntk"]):
             rank[chrom.uid] += rk+1
-            if best_rank > rank[chrom.uid] or best_rank == None:
+            if best_rank == None or best_rank > rank[chrom.uid]:
                 best_rank = rank[chrom.uid]
                 self.best_chrom = chrom
 

### 2023-03-14 GA_search.py
now GA_search use rank-based GA

@@ -10,8 +10,8 @@ from tqdm import trange
 from statistics import mean, stdev
 import time
 from utils import add_dropout
-#from search.GA_based_on_rank import GA
-from search.GA import GA
+from search.GA_based_on_rank import GA
+#from search.GA import GA
 from score import *
 
 
@@ -159,8 +159,8 @@ for N in runs:
     acc.append(acc_)
 
     times.append(time.time()-start)
-    #runs.set_description(f"acc: {mean(acc):.3f}%  acc std: {(stdev(acc) if len(acc) > 1 else 0):.3f}  topscores:({topscores[-1][0]:.3f},{topscores[-1][1]:.3f},{topscores[-1][2]:.3f})  time:{mean(times):.2f}")
-    runs.set_description(f"acc: {mean(acc):.3f}%  acc std: {(stdev(acc) if len(acc) > 1 else 0):.3f}  uid: {uid}  topscores:{topscores[-1]:.3f}  time:{mean(times):.2f}")
+    runs.set_description(f"acc: {mean(acc):.3f}%  acc std: {(stdev(acc) if len(acc) > 1 else 0):.3f}  topscores:({topscores[-1][0]:.3f},{topscores[-1][1]:.3f},{topscores[-1][2]:.3f})  time:{mean(times):.2f}")
+    #runs.set_description(f"acc: {mean(acc):.3f}%  acc std: {(stdev(acc) if len(acc) > 1 else 0):.3f}  uid: {uid}  topscores:{topscores[-1]:.3f}  time:{mean(times):.2f}")
 
 print(f"Final mean accuracy: {np.mean(acc)}")
 
@@ -170,5 +170,5 @@ state = {'accs': acc,
          'topscores': topscores,
          }
 
-fname = f"{args.save_loc}/{args.save_string}_{args.nasspace}_{args.dateset}_{args.kernel}_{args.dropout}_{args.augtype}_{args.sigma}_{args.repeat}_{args.batch_size}_{args.n_runs}_{args.n_samples}_{args.seed}_{args.valid}_{args.test}_{args.maxn_pop}_{args.maxn_iter}_{args.prob_cr}_{args.prob_mut}.t7"
[…]

### 2023-03-14 paper/main.tex

@@
     when inputs are well separated.
-    Later, Wu et al. \cite{10.1145/3491396.3506510}
+    Based on the work of Mellor et al., Wu et al. \cite{10.1145/3491396.3506510} 
+    found, in some case, an architecture with high NASWOT score may put different 
+    input data, which are originally in the same class, to different classes.
+
+    To fix this defect, Wu et al. proposed using noise immunity to additionally 
+    evaluate an architecture. The score function first pick a mini-batch of data, 
+    denoted $X$, and then add Gaussion noise on it, denoted $X'$ and defined by $X'=X+z$ 
+    where $z$ is the Gaussion noise. By passing $X$ and $X'$ through the untrained 
+    architecture, the sum of the square differences between outputs 
+    $O=\begin{matrix}o_1,o_2,\cdots,o_C\end{matrix}$ and 
+    $O'=\begin{matrix}o_1',o_2',\cdots,o_C'\end{matrix}$ can be calculated as 
+    follows:
+    \begin{equation}
+        n=-\sum^C_{n=1}(o_i-o_i')^2
+    \end{equation}
+    where $C$ is the number of classes determined by the input data.
 
@@
     The rationale behind is based on the work of Lee et al. \cite{Lee_2020} and 
-    Xiao et al. \cite{DBLP:journals/corr/abs-1912-13053}, which concluded briefly, 
-    the training dynamics of a wide neural network can be solved as 
-    \begin{equation}
-        \mu_t(\textbf{X}_{\textrm{train}})=(\textbf{I}-e^{-\eta\hat\Theta_{\textrm{train}}t})\textbf{Y}_{\textrm{train}}
+    Xiao et al. \cite{https://doi.org/10.48550/arxiv.1912.13053}, which concluded briefly, 
+    the training dynamics of a wide neural network can be written in terms of the 
+    spectrum of the NTK:
+    \begin{equation}\label{eq:6}
+        \mu_t(\textbf{X}_{\textrm{train}})_i=(\textbf{I}-e^{-\eta\lambda_it})\textbf{Y}_{\textrm{train,}i}
     \end{equation}
+    where $\lambda_i$ are the eigenvalues of $\hat\Theta_{\textrm{train}}$ 
+    and they're ordered as $\lambda_0\geq\cdots\geq\lambda_m$. 
+    According to the hypothesis proposed by Lee et al. \cite{Lee_2020}, the maximum 
+    feasible learning rate scale as $\eta\sim2/\lambda_0$. Plug this scaling for 
+    $\eta$ in Eq. \ref{eq:6}, we see that the $\lambda_m$ will converge exponentially 
+    at a rate given by $1/K_N$ where $K_N=\frac{\lambda_0}{\lambda_m}$.
+    Then it can be concluded that if $K_N$ is lower, the corresponding architecture is 
+    more trainable.
 

### 2023-03-14 search/GA_based_on_rank.py
remove the duplicated architecture in candiate list

@@ -44,7 +44,7 @@ class GA():
         self.means = means
         self.acc_type = acc_type
         self.best_chrom = chromosome()
-        self.candiate = {"ninaswot":[], "ntk":[]}
+        self.candiate = {"ninaswot":set(), "ntk":set()}
         self.NAS_201_ops = ['none', 'skip_connect', 'nor_conv_1x1', 'nor_conv_3x3', 'avg_pool_3x3']
 
     def init_population(self):
@@ -68,9 +68,9 @@ class GA():
                 #(standardize(ninaswot_score(network, self.train_loader, self.device, self.stds, self.means, self.args), self.means["ninaswot"], self.stds["ninaswot"]), \
                 #-standardize(ntk_score(network, self.train_loader, self.device), self.means["ntk"], self.stds["ntk"]), \
                 #standardize(entropy_score(network, self.train_loader, self.device, self.args), self.means["entropy"], self.stds["entropy"]))
-                self.population[i].fitness = self.DICT[self.population[i].gene] = (self.ninaswot[self.population[i].uid], self.ntk[self.population[i].uid], self.ninaswot[self.population[i].uid]+self.ntk[self.population[i].uid])
+                self.population[i].fitness = self.DICT[self.population[i].uid] = (self.ninaswot[self.population[i].uid], self.ntk[self.population[i].uid], self.ninaswot[self.population[i].uid]+self.ntk[self.population[i].uid])
             else:
-                self.population[i].fitness = self.DICT[self.population[i].gene]
+                self.population[i].fitness = self.DICT[self.population[i].uid]
 
             """
             # global optimum
@@ -148,34 +148,35 @@ class GA():
             self.evaluate()
             
             offsprings.sort(key = lambda this: this.fitness[0], reverse = True) # ninaswot rank
-            self.candiate["ninaswot"].append(offsprings[0])
-            self.candiate["ntk"].append(offsprings[0])
+            self.candiate["ninaswot"].add(offsprings[0].uid)
+            self.candiate["ntk"].add(offsprings[0].uid)
 
             offsprings.sort(key = lambda this: this.fitness[1], reverse = True) # ntk rank
-            self.candiate["ninaswot"].append(offsprings[0])
-            self.candiate["ntk"].append(offsprings[0])
+            self.candiate["ninaswot"].add(offsprings[0].uid)
[…]

### 2023-03-14 GA_search.py
make cheat means and stds

@@ -107,38 +107,38 @@ acc       = []
 topscores = []
 
 print(f"Now calculate means and standards.")
-means, stds = get_mean_std(searchspace, args.n_samples, train_loader, device, args)
+#means, stds = get_mean_std(searchspace, args.n_samples, train_loader, device, args)
 
-# cifar10
-"""
-means = {}
-stds = {}
-means["ni"] = -0.08314655303955078
-stds["ni"]  =  0.1266118600610186
-means["naswot"] = 1595.0483017680253
-stds["naswot"] = 77.00454622052088
-means["ntk"] = 8064.954524536133
-stds["ntk"] = 21509.86140267155
-means["entropy"] = 721.064296875
-stds["entropy"] = 280.67810232781636
-means["ninaswot"] = 0
-stds["ninaswot"]  = np.sqrt(5)
-"""
-# cifar100
-"""
-means = {}
-stds = {}
-means["ni"] = -0.07765040397644044
-stds["ni"]  =  0.12295018402244674
-means["naswot"] = 1592.1985007236365
-stds["naswot"] = 77.2502068400697
-means["ntk"] = 9979.810939865112
-stds["ntk"] = 23336.402907292802
-means["entropy"] = 721.064296875
-stds["entropy"] = 280.67810232781636
-means["ninaswot"] = 0
-stds["ninaswot"]  = np.sqrt(5)
-"""
+if args.dataset == 'cifar10-valid':
+    # cifar10-valid
+    means = {}
+    stds = {}
+    means["ni"]       =    -0.08287504196166992
+    stds["ni"]        =     0.1338795386377707
+    means["naswot"]   =  1595.1744876295015
+    stds["naswot"]    =    76.14891987423042
+    means["ntk"]      = 10149.060118942261
+    stds["ntk"]       = 28253.425318545123
+    means["ninaswot"] = 0
+    stds["ninaswot"]  = np.sqrt(5)
+elif args.dataset == 'cifar100':
+    # cifar100
+    means, stds = get_mean_std(searchspace, args.n_samples, train_loader, device, args)
+    """
+    means = {}
+    stds = {}
+    means["ni"] = -0.07765040397644044
+    stds["ni"]  =  0.12295018402244674
+    means["naswot"] = 1592.1985007236365
+    stds["naswot"] = 77.2502068400697
+    means["ntk"] = 9979.810939865112
+    stds["ntk"] = 23336.402907292802
+    means["ninaswot"] = 0
[…]

### 2023-03-14 score/__init__.py
add 'ninaswot' to the dict

@@ -47,8 +47,8 @@ def get_mean_std(searchspace, sample_n, train_loader, device, args):
     
     calstd  = lambda x: np.ma.masked_invalid(x).std()
     calmean = lambda x: np.ma.masked_invalid(x).mean()
-    stds  = {"naswot": calstd(scores_naswot), "ni": calstd(scores_ni), "ntk": calstd(scores_ntk)}
-    means = {"naswot": calmean(scores_naswot), "ni": calmean(scores_ni), "ntk": calmean(scores_ntk)}
+    stds  = {"naswot": calstd(scores_naswot), "ni": calstd(scores_ni), "ntk": calstd(scores_ntk), "ninaswot": np.sqrt(5)}
+    means = {"naswot": calmean(scores_naswot), "ni": calmean(scores_ni), "ntk": calmean(scores_ntk), "ninaswot": 0}
     
     del scores_naswot, scores_ni, scores_ntk, times
 

### 2023-03-16 GA_search.py
add new argument --search_algo, and add the corresponding prompt

@@ -51,16 +51,20 @@ parser.add_argument('--num_stacks', default=3, type=int, help='#stacks of module
 parser.add_argument('--num_modules_per_stack', default=3, type=int, help='#modules per stack (nasbench101)')
 parser.add_argument('--num_labels', default=1, type=int, help='#classes (nasbench101)')
 
-parser.add_argument('--search_algo', default="", type=str)
+parser.add_argument('--search_algo', default="ori", type=str)
 
 
 args = parser.parse_args()
 
-if args.search_algo == "":
+
+if args.search_algo == "ori" or args.search_algo == "original" or args.search_algo == "origin" or args.search_algo == "base":
+    print(f"use search algorithm: GA origin ver.")
     from search.GA import GA
 elif args.search_algo == "mm":
+    print(f"use search algorithm: GA multiple metric ver.")
     from search.GA_mm import GA
 elif args.search_algo == "rk" or args.search_algo == "based_on_rank":
+    print(f"use search algorithm: GA rank-based ver.")
     from search.GA_based_on_rank import GA
 else:
     assert False, f"no such search algorithm: {args.GA}"

### 2023-03-16 search/GA_based_on_rank.py
fix the cutoff strategy bug

@@ -158,7 +158,7 @@ class GA():
             
             #offsprings.sort(key = lambda this: this.fitness[2], reverse = True) # tot rank
             # ageing
-            offsprings = offsprings[:int(len(offsprings)*0.3)]
+            offsprings = offsprings[-int(len(offsprings)*0.3):]
         
         self.candiate["tot"].extend(list(self.candiate["ninaswot"]))
         self.candiate["tot"].extend(list(self.candiate["ntk"]))

### 2023-03-16 search/GA_mm.py

@@ -135,8 +135,8 @@ class GA():
                 offsprings.append(offspring0)
                 offsprings.append(offspring1)
             
-            offsprings.sort(key = lambda this: this.fitness, reverse = True)
-            offsprings = offsprings[:int(0.3*len(offsprings))]
+            #offsprings.sort(key = lambda this: this.fitness)
+            offsprings = offsprings[-int(0.6*len(offsprings)):]
             
             self.population = offsprings
             self.evaluate()

### 2023-03-16 GA_search.py
add some prompt

@@ -58,13 +58,13 @@ args = parser.parse_args()
 
 
 if args.search_algo == "ori" or args.search_algo == "original" or args.search_algo == "origin" or args.search_algo == "base":
-    print(f"use search algorithm: GA origin ver.")
+    print(f"Use search algorithm: GA origin ver.")
     from search.GA import GA
 elif args.search_algo == "mm":
-    print(f"use search algorithm: GA multiple metric ver.")
+    print(f"Use search algorithm: GA multiple metric ver.")
     from search.GA_mm import GA
 elif args.search_algo == "rk" or args.search_algo == "based_on_rank":
-    print(f"use search algorithm: GA rank-based ver.")
+    print(f"Use search algorithm: GA rank-based ver.")
     from search.GA_based_on_rank import GA
 else:
     assert False, f"no such search algorithm: {args.GA}"
@@ -78,7 +78,9 @@ random.seed(args.seed)
 np.random.seed(args.seed)
 torch.manual_seed(args.seed)
 
+print(f"Use GPU {args.GPU}...")
 device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
+print(f"The current device used is {device}")
 
 def remap_dataset_names(dataset, valid, test, train):
     cifar10 = 'cifar10'
@@ -113,7 +115,7 @@ args.dataset, acc_type = remap_dataset_names(args.dataset, args.valid, args.test
 print(f"dataset = {args.dataset}, validation = {args.valid}")
 searchspace = nasspace.get_search_space(args)
 
-print(f"Make sure {args.save_loc} exist.")
+print(f"Making sure {args.save_loc} exist.")
 os.makedirs(args.save_loc, exist_ok=True)
 
 times     = []
@@ -121,7 +123,7 @@ chosen    = []
 acc       = []
 topscores = []
 
-print(f"Now calculate means and standards.")
+print(f"Currently calculate means and standards.")
 #means, stds = get_mean_std(searchspace, args.n_samples, train_loader, device, args)
 
 if args.dataset == 'cifar10-valid':
@@ -155,14 +157,14 @@ else:
     means, stds = get_mean_std(searchspace, args.n_samples, train_loader, device, args)
 
 
-print(f"Calculation is done.")
+print(f"Calculation of means and stds is done.")
 print(f"means = {means}\nstds = {stds}")
 print(f"========================================")
 
[…]

### 2023-03-16 score/synflow_score.py
fix typo && fix bug: +network.eval() and +network.to(device) && take logit from the output of network(input) && make score numpy.float

@@ -1,5 +1,5 @@
-import pytorch
-import pytorch.nn as nn
+import torch
+import torch.nn as nn
 import numpy as np
 
 def synflow_score(network, train_loader, device):
@@ -8,19 +8,24 @@ def synflow_score(network, train_loader, device):
         signs = {}
         for name, param in network.state_dict().items():
             signs[name] = torch.sign(param)
-            params.abs_()
+            param.abs_()
         return signs
 
     @torch.no_grad()
     def nonlinearize(network, signs):
         for name, param in network.state_dict().items():
             param.mul_(signs[name])
+    
+    #?
+    network.eval()
+
+    network = network.to(device)
     signs = linearize(network)
 
     data, _ = next(iter(train_loader))
     input_dim = list(data[0,:].shape)
     input = torch.ones([1]+input_dim).to(device)
-    output = network(input)
+    output, logit = network(input)
     torch.sum(output).backward()
 
     grads_abs = []
@@ -45,4 +50,4 @@ def synflow_score(network, train_loader, device):
         score += torch.sum(grads_abs[i])
 
     nonlinearize(network, signs)
-    return score.cpu().numpy()
+    return score.detach().cpu().numpy()

### 2023-03-16 score_networks.py
imporve the prompt && add synflow score && temporarily disable other scoring

@@ -46,6 +46,8 @@ parser.add_argument('--num_modules_per_stack', default=3, type=int, help='#modul
 parser.add_argument('--num_labels', default=1, type=int, help='#classes (nasbench101)')
 
 args = parser.parse_args()
+
+print(f"Use GPU {args.GPU}")
 os.environ['CUDA_VISIBLE_DEVICES'] = args.GPU
 
 # Reproducibility
@@ -56,9 +58,7 @@ np.random.seed(args.seed)
 torch.manual_seed(args.seed)
 
 device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
-print(f"Current device is {device}")
-dataset = 'fake' if 'fake' in args.dataset else args.dataset
-args.dataset = args.dataset.replace('fake', '')
+print(f"Current device used is {device}")
 
 def remap_dataset_names(dataset, valid, test, train):
     cifar10 = 'cifar10'
@@ -83,10 +83,10 @@ def remap_dataset_names(dataset, valid, test, train):
         return ImageNet16_120, 'x-test'
     assert False, "Unknown dataset: {args.dataset}"
 
-print(f"Initialize the train loader.")
+print(f"Initialize the train loader...")
 train_loader = datasets.get_data(args.dataset, args.data_loc, args.valid, args.batch_size, args.repeat, args)
 
-print(f"Initialize the nasspace.")
+print(f"Initialize the nasspace...")
 args.dataset, acc_type = remap_dataset_names(args.dataset, args.valid, args.test, args.train)
 print(f"dataset = {args.dataset}, valid = {args.valid}, test = {args.test}")
 searchspace = nasspace.get_search_space(args)
@@ -96,16 +96,17 @@ os.makedirs(args.save_loc, exist_ok=True)
 filename_ninaswot = f'{args.save_loc}/ninaswot_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.valid}_{args.batch_size}_{args.maxofn}_{args.seed}'
 #filename_entropy  = f'{args.save_loc}/entropy_{args.nasspace}_{args.dataset}_{args.augtype}_{args.sigma}_{args.repeat}_{args.valid}_{args.batch_size}_{args.maxofn}_{args.seed}'
[…]

### 2023-03-16 score/__init__.py
add synflow score

@@ -2,8 +2,9 @@ from utils import add_dropout, init_network
 
 from .ntk_score import ntk_score
 from .ninaswot_score import ninaswot_score, ni_score, naswot_score
-from .entropy_score import entropy_score, init_net_gaussian
-from .gradsign_score import gradsign_score
+#from .entropy_score import entropy_score, init_net_gaussian
+#from .gradsign_score import gradsign_score
+from .synflow_score import synflow_score
 
 import numpy as np
 from tqdm import tqdm
@@ -19,6 +20,7 @@ def get_mean_std(searchspace, sample_n, train_loader, device, args):
     #scores_entropy  = []
     #scores_gradsign = []
     scores_ntk      = []
+    scores_synflow  = []
     arches = np.random.randint(0, len(searchspace), sample_n)
     nruns = tqdm(total = sample_n)
     times = []
@@ -30,7 +32,9 @@ def get_mean_std(searchspace, sample_n, train_loader, device, args):
 
         scores_naswot.append(naswot_score(network, train_loader, device, args))
         scores_ni.append(ni_score(network, train_loader, device, args))
-        scores_ntk.append(ntk_score(network, train_loader, device))
+        #scores_ntk.append(ntk_score(network, train_loader, device))
+        scores_ntk.append(0)
+        scores_synflow.append(synflow_score(network, train_loader, device))
         #scores_gradsign.append(gradsign_score(network, train_loader, device))
         #network = init_net_gaussian(network, device)
         #scores_entropy.append(entropy_score(network, train_loader, device, args))
@@ -42,15 +46,16 @@ def get_mean_std(searchspace, sample_n, train_loader, device, args):
     scores_naswot   = np.array(scores_naswot)
     scores_ni       = np.array(scores_ni)
     scores_ntk      = np.array(scores_ntk)
+    scores_synflow  = np.array(scores_synflow)
     #scores_entropy = np.array(scores_entropy)
     #scores_gradsign = np.array(scores_gradsign)
     
     calstd  = lambda x: np.ma.masked_invalid(x).std()
     calmean = lambda x: np.ma.masked_invalid(x).mean()
-    stds  = {"naswot": calstd(scores_naswot), "ni": calstd(scores_ni), "ntk": calstd(scores_ntk), "ninaswot": np.sqrt(5)}
[…]

### 2023-03-16 search/GA_based_on_rank.py
add synflow but not apply yet && decreasing ageing cutoff rate: 0.3->0.7

@@ -5,7 +5,7 @@ import numpy as np
 
 class chromosome():
     def __init__(self, gene = "", fitness = (0,0,0), acc = 0, uid = 0):
-        """ fitness: (ninaswot, ntk, ...) """
+        """ fitness: (ninaswot, ntk, ..., tot) """
         self.gene = gene
         self.fitness = fitness
         self.acc = acc
@@ -21,12 +21,12 @@ class GA():
 
         self.ninaswot = np.load(f"{base_loc}/ninaswot_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.ntk      = np.load(f"{base_loc}/ntk_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
-        self.entropy  = np.load(f"{base_loc}/entropy_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
+        self.synflow  = np.load(f"{base_loc}/synflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         ####
 
         assert len(self.ninaswot) == 15625, "broken: ninaswot"
         assert len(self.ntk) == 15625, "broken: ntk"
-        assert len(self.entropy) == 15625, "broken: entropy"
+        assert len(self.synflow) == 15625, "broken: synflow"
         ####
         self.MAXN_POPULATION = args.maxn_pop
         self.MAXN_ITERATION = args.maxn_iter
@@ -158,7 +158,7 @@ class GA():
             
             #offsprings.sort(key = lambda this: this.fitness[2], reverse = True) # tot rank
             # ageing
-            offsprings = offsprings[-int(len(offsprings)*0.3):]
+            offsprings = offsprings[-int(len(offsprings)*0.7):]
         
         self.candiate["tot"].extend(list(self.candiate["ninaswot"]))
         self.candiate["tot"].extend(list(self.candiate["ntk"]))

### 2023-03-16 paper/main.tex
add #search algorithm in related work

@@
     In these days, the studies of training-free neural architecture search (NAS) 
-    go viral, since the ability to accelerate the design of a neural network 
-    architecture used on specific application, while in the same time, by using 
-    training-free score function, training-free NAS cleverly avoid the drawback 
-    of long-time training.
+    go viral, since the ability to accelerate the procedure for designing a neural 
+    network architecture used on specific application, while additionally, 
+    training-free NAS cleverly avoid the drawback of long-time training by using 
+    various training-free score functions.
 
-    Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed a 
-    score function without the requirement for training. 
-    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ mapped through a neural 
-    network as $f(x_i)$. The indicator variables from each ReLU units in $f$ 
-    at $x_i$ form a binary code $c_i$ that define the linear region.
+    % naswot
+    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. proposed a 
+    score function without the requirement for training. Here we call it neural 
+    architecture search without training (NASWOT) score function. 
+    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
+    architecture as $f(x_i)$. The activated ReLU units in every layer of the architecture 
+    form a binary code $c_i$ that define the linear region.
     The correlation between binary codes for the whole mini-batch can be examined 
@@
     when inputs are well separated.
+
+    % ninaswot
     Based on the work of Mellor et al., Wu et al. \cite{10.1145/3491396.3506510} 
-    found, in some case, an architecture with high NASWOT score may put different 
+    found, in some case, an architecture with high score may put different 
     input data, which are originally in the same class, to different classes. 
-
     To fix this defect, Wu et al. proposed using noise immunity to additionally 
-    evaluate an architecture. The score function first pick a mini-batch of data, 
-    denoted $X$, and then add Gaussion noise on it, denoted $X'$ and defined by $X'=X+z$ 
-    where $z$ is the Gaussion noise. By passing $X$ and $X'$ through the untrained 
-    architecture, the sum of the square differences between outputs 
+    evaluate an architecture. The score function picks a mini-batch of data, 
+    denoted $X$, and then applies Gaussion noise on it, denoted $X'$ and defined 
+    by $X'=X+z$ where $z$ is the Gaussion noise. By passing $X$ and $X'$ through 
+    the untrained architecture, the sum of the square differences between outputs 
     $O=\begin{matrix}o_1,o_2,\cdots,o_C\end{matrix}$ and 
@@
     where $C$ is the number of classes determined by the input data.
+    According to the experiment outcome of Wu et al., noise immunity can separate 
+    those are unable to distinguish $X$ and $X'$ from architectures with high NASWOT 
+    score, which just complements the NASWOT score funcion.
 
+    % ntk
     On the other hand, instead of using the correlation of binary activation 
@@
     are the maximum and minimum eigenvalues of NTK ($\hat\Theta$) respectively.
-    The rationale behind is based on the work of Lee et al. \cite{Lee_2020} and 
-    Xiao et al. \cite{https://doi.org/10.48550/arxiv.1912.13053}, which concluded briefly, 
+    The rationale is based on the work of Lee et al. \cite{Lee_2020} and 
+    Xiao et al. \cite{https://doi.org/10.48550/arxiv.1912.13053}, which concluded briefly here, 
     the training dynamics of a wide neural network can be written in terms of the 
@@
 
+	% search algorithm
+    Another important component of training-free NAS is search algorithm. There're 
+    various search algorithms that applied on training-free NAS. The search algorithm 
+    that gained much attention in recent years is evolutionary algorithms (EAs) \cite{Liu_2023}.
+    In \cite{10.1145/3491396.3506510}, Wu et al. used genetic algorithm (GA), a popular 
+    evolutionary algorithm which has great potential to search a vast search space. 
+    The NINASWOT score is used as fitness of a chromosome in genetic algorithm. And 
+    the tournament selection is used to select an architecture with good NINASWOT score.
+    Cavagnero et al. \cite{https://doi.org/10.48550/arxiv.2207.05135} used a custom 
+	tournament selection with ageing (REA). Instead of discarding less fitting 
+	individuals, REA discards the elder individuals, and thus explore more search 
+	space.
+
+    Though the search algorithm is very powerful to search a vast space, the key to the holy 
+    grail of training-free NAS is still the training-free score functions. Our work studies 
+    the right way to combining the score functions which complements each others, and explore 
+    the potential of rank-based GA.
+
+    \section{the proposed algorithm}
+    In our work, however, we use rank-based GA. Rather than use single fitness to select, 
+    the method preserve the top 1 in NINASWOT score and also the top 1 in the condition 
+    number of NTK. After the evolution,
+
     \bibliographystyle{IEEEtran}

### 2023-03-16 paper/main.tex
update related work (figure of ni && advices)

@@
 
-    Most neural architecture searches (NASs) are time-consuming caused by 
-    the fact that, during the searching, a candidate architecture must be 
-    trained to evaluate how good of this architecture. This is why some of 
-    training-free NAS algorithms have been proposed in recent years.
-
+    % dont we
+    % To address
+    % To evaluate
     Although the training-free NASs are typically faster than training-based 
@@
     of an architecture is not well enough in most cases.
-
     To address this problem, we propose a genetic-based training-free NAS 
@@
     neural architecture search without search (NINASWOT), as an evaluation of 
-    pattern recognition ability, second one is maximum-entropy detection (MAE-DET), 
-    as an evaluation of the entropy of an architecture and the third one is 
-    condition number of neural tangent kernel (NTK), as an evaluation of 
-    the speed of converge.
+    pattern recognition ability, second one is condition number of neural 
+    tangent kernel (NTK), as an evaluation of trainability.
 
-    To evaluate the performance of the proposed algorithm, we compared it 
-    with several NAS algorithms, including weight-sharing methods, 
+    To evaluate the performance of the proposed algorithm, this paper compared 
+    it with several NAS algorithms, including weight-sharing methods, 
     non-weight-sharing methods, and neural architecture search without training (NASWOT). 
@@
     potential architectures, to find out a good architectures that outperform 
-    those designed by human experts. In recent years, the use of NAS is 
+    those designed by human experts. "In recent years", the use of NAS is 
     widespread, from object detection \cite{https://doi.org/10.48550/arxiv.2111.13336}, 
@@
 
+    % reduce 
     Despite the promising results of NAS, there are still many challenges 
@@
     induced by the untrained network at two inputs, named as neural architecture 
-    search without training (NASWOT). The correlation is defined as the 
-    logarithmic determinant of the kernel matrix, as follows:
-    \begin{equation}
-        s=\log\lvert K_H\rvert
-    \end{equation}
-    where $K_H$ is the kernel matrix.
+    search without training (NASWOT). 
     Later, Wu et al. \cite{10.1145/3491396.3506510} found a high score 
@@
     \cite{https://doi.org/10.48550/arxiv.2203.09137} \cite{https://doi.org/10.48550/arxiv.2109.00817}, 
-    which is defined as 
+    which is defined as % delete math formula
     \begin{equation}
@@
     The correlation between binary codes for the whole mini-batch can be examined 
-    by computing the kernel matrix
+    by computing the kernel matrix % add figure
     \begin{equation}
@@
     % ninaswot
+    \begin{figure*}[htb]
+        \vspace{-\baselineskip}
+        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
+        \caption{A simple example to illustrate the procedure of noise immunity.}
+        \label{fig:ni}
+        \centering
+        \vspace{-\baselineskip}
+    \end{figure*}
     Based on the work of Mellor et al., Wu et al. \cite{10.1145/3491396.3506510} 
@@
     patterns as score. Chen et al. proposed using the condition number of NTK 
-    as an evaluation of the trainability, defined as
+    as an evaluation of the trainability, defined as % add figure
     \begin{equation}

### 2023-03-16 paper/main.tex
update related work

@@
     \cite{https://doi.org/10.48550/arxiv.2203.09137} \cite{https://doi.org/10.48550/arxiv.2109.00817}, 
-    which is defined as % delete math formula
-    \begin{equation}
-        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
-    \end{equation}
-    and used as the score to estimate the trainability of an architecture.
+    which is used as the score to estimate the trainability of an architecture.
 	% unknown

### 2023-03-19 search/GA_based_on_rank.py
add logsynflow as metric

@@ -4,8 +4,8 @@ import random
 import numpy as np
 
 class chromosome():
-    def __init__(self, gene = "", fitness = (0,0,0), acc = 0, uid = 0):
-        """ fitness: (ninaswot, ntk, ..., tot) """
+    def __init__(self, gene = None, fitness = None, acc = None, uid = None):
+        """ fitness: (ninaswot, ntk, logsynflow, tot) """
         self.gene = gene
         self.fitness = fitness
         self.acc = acc
@@ -22,6 +22,7 @@ class GA():
         self.ninaswot = np.load(f"{base_loc}/ninaswot_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.ntk      = np.load(f"{base_loc}/ntk_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.synflow  = np.load(f"{base_loc}/synflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
+        self.logsynflow  = np.load(f"{base_loc}/logsynflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         ####
 
         assert len(self.ninaswot) == 15625, "broken: ninaswot"
@@ -44,7 +45,7 @@ class GA():
         self.means = means
         self.acc_type = acc_type
         self.best_chrom = chromosome()
-        self.candiate = {"ninaswot":set(), "ntk":set(), "tot":[]}
+        self.candiate = {"ninaswot":set(), "ntk":set(), "logsynflow":set(), "tot":[]}
         self.NAS_201_ops = ['none', 'skip_connect', 'nor_conv_1x1', 'nor_conv_3x3', 'avg_pool_3x3']
 
     def init_population(self):
@@ -61,14 +62,21 @@ class GA():
     def evaluate(self):
         for i in range(len(self.population)):
             network, uid, acc = gene2net(self.population[i].gene, self.NAS_201_ops, self.searchspace, self.acc_type, self.args.valid)
+            del network
             self.population[i].acc = acc
             self.population[i].uid = uid
-            if self.population[i].gene not in self.DICT:
+            if self.population[i].uid not in self.DICT:
+                uid = self.population[i].uid
                 #self.population[i].fitness = self.DICT[self.population[i].gene] = \
[…]

### 2023-03-19 search/GA_mm.py
add logsynflow as metric

@@ -6,11 +6,11 @@ from tqdm import tqdm
 import time
 
 class chromosome():
-    def __init__(self, gene = "", fitness = 0, acc = 0, uid = 0):
+    def __init__(self, gene = "", fitness = None, acc = None, uid = None):
         self.gene = gene
         self.fitness = fitness
-        self.acc = 0
-        self.uid = 0
+        self.acc = acc
+        self.uid = uid
 
 class GA():
     def __init__(self, MAXN_CONNECTION, MAXN_OPERATION, searchspace, train_loader, device, stds, means, acc_type, args):
@@ -22,6 +22,7 @@ class GA():
         self.ninaswot = np.load(f"{base_loc}/ninaswot_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.ntk      = np.load(f"{base_loc}/ntk_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.synflow  = np.load(f"{base_loc}/synflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
+        self.logsynflow  = np.load(f"{base_loc}/logsynflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         ####
         self.MAXN_POPULATION = args.maxn_pop
         self.MAXN_ITERATION = args.maxn_iter
@@ -61,17 +62,20 @@ class GA():
                 #self.population[i].fitness = self.DICT[self.population[i].gene] = \
                 #(standardize(ninaswot_score(network, self.train_loader, self.device, self.stds, self.means, self.args), self.means["ninaswot"], self.stds["ninaswpt"]), \
                 #-standardize(ntk_score(network, self.train_loader, self.device), self.means["ntk"], self.stds["ntk"])
-                self.population[i].fitness = self.DICT[self.population[i].gene] = self.ninaswot[self.population[i].uid] + self.ntk[self.population[i].uid]
+                x = self.ninaswot[self.population[i].uid] + self.ntk[self.population[i].uid] + self.logsynflow[self.population[i].uid]
+                self.population[i].fitness = self.DICT[self.population[i].gene] = x if np.isfinite(x) else -np.inf
             else:
                 self.population[i].fitness = self.DICT[self.population[i].gene]
-            if self.population[i].fitness > self.best_chrom.fitness or self.best_chrom.gene == "":
[…]

### 2023-03-20 paper/main.tex
remove the search algorithm in related works

@@
     To address the problem, we propose cooperating three heterogeneous score 
-    functions with genetic-based search method, we shall evaulate an architecture 
+    functions with genetic-based search method, which evaulate an architecture 
     from different aspects. More specifically, the first score function is 
@@
     \section{Related Works}
+    \begin{figure*}[htb]
+        \vspace{-\baselineskip}
+        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/naswot.pdf}}
+        \caption{A simple example to illustrate the procedure of NASWOT.}
+        \label{fig:naswot}
+        \centering
+        \vspace{-\baselineskip}
+    \end{figure*}
     In these days, the studies of training-free neural architecture search (NAS) 
@@
     score function without the requirement for training. Here we call it neural 
-    architecture search without training (NASWOT) score function. 
+    architecture search without training (NASWOT) score function. \xfig{fig:naswot} 
+	gives a simple example to illustrate the procedure of NASWOT score function. 
     Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
@@
     The correlation between binary codes for the whole mini-batch can be examined 
-    by computing the kernel matrix % add figure
+    by computing the kernel matrix 
     \begin{equation}
@@
     To fix this defect, Wu et al. proposed using noise immunity to additionally 
-    evaluate an architecture. The score function picks a mini-batch of data, 
-    denoted $X$, and then applies Gaussion noise on it, denoted $X'$ and defined 
-    by $X'=X+z$ where $z$ is the Gaussion noise. By passing $X$ and $X'$ through 
-    the untrained architecture, the sum of the square differences between outputs 
+    evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
+    noise immunity score evaluate an architecture. The score function picks a 
+    mini-batch of data, denoted $X$, and then applies Gaussion noise on it, 
+    denoted $X'$ and defined by $X'=X+z$ where $z$ is the Gaussion noise. 
+    By passing $X$ and $X'$ through the untrained architecture, the sum of the 
+    square differences between outputs 
     $O=\begin{matrix}o_1,o_2,\cdots,o_C\end{matrix}$ and 
@@
 
-	% search algorithm
-    Another important component of training-free NAS is search algorithm. There're 
-    various search algorithms that applied on training-free NAS. The search algorithm 
-    that gained much attention in recent years is evolutionary algorithms (EAs) \cite{Liu_2023}.
-    In \cite{10.1145/3491396.3506510}, Wu et al. used genetic algorithm (GA), a popular 
-    evolutionary algorithm which has great potential to search a vast search space. 
-    The NINASWOT score is used as fitness of a chromosome in genetic algorithm. And 
-    the tournament selection is used to select an architecture with good NINASWOT score.
-    Cavagnero et al. \cite{https://doi.org/10.48550/arxiv.2207.05135} used a custom 
-	tournament selection with ageing (REA). Instead of discarding less fitting 
-	individuals, REA discards the elder individuals, and thus explore more search 
-	space.
+	% synflow?
 
-    Though the search algorithm is very powerful to search a vast space, the key to the holy 
-    grail of training-free NAS is still the training-free score functions. Our work studies 
-    the right way to combining the score functions which complements each others, and explore 
-    the potential of rank-based GA.
+    % conclusion
 

### 2023-03-20 score.sh
remove unused command

@@ -12,33 +12,5 @@ python score_networks.py --save_loc results/score/ImageNet16-120 --save_string a
 python score_networks.py --save_loc results/score/cifar10-test --save_string all_score --test --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 1 --n_samples 50 --dataset cifar10
 python score_networks.py --save_loc results/score/cifar100-test --save_string all_score --test --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 1 --dataset cifar100
 python score_networks.py --save_loc results/score/ImageNet16-120-test --save_string all_score --test --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 1 --dataset ImageNet16-120 --data_loc ../ImageNet16/
-<<block
-python score_networks.py --trainval --augtype none --repeat 1 --score hook_logdet --sigma 0.05 --nasspace nds_pnas --batch_size 128 --GPU 3
-python score_networks.py --trainval --augtype none --repeat 1 --score hook_logdet --sigma 0.05 --nasspace nds_enas --batch_size 128 --GPU 3
-python score_networks.py --trainval --augtype none --repeat 1 --score hook_logdet --sigma 0.05 --nasspace nds_darts --batch_size 128 --GPU 3
-python score_networks.py --trainval --augtype none --repeat 1 --score hook_logdet --sigma 0.05 --nasspace nds_darts_fix-w-d --batch_size 128 --GPU 3
-python score_networks.py --trainval --augtype none --repeat 1 --score hook_logdet --sigma 0.05 --nasspace nds_nasnet --batch_size 128 --GPU 3
-python score_networks.py --trainval --augtype none --repeat 1 --score hook_logdet --sigma 0.05 --nasspace nds_amoeba --batch_size 128 --GPU 3
-python score_networks.py --trainval --augtype none --repeat 1 --score hook_logdet --sigma 0.05 --nasspace nds_resnet --batch_size 128 --GPU 3
-python score_networks.py --trainval --augtype none --repeat 1 --score hook_logdet --sigma 0.05 --nasspace nds_resnext-a --batch_size 128 --GPU 3
[…]

### 2023-03-20 score_networks.py
re-scoring logsynflow with new designed logsynflow

@@ -149,7 +149,7 @@ for i, (uid, network) in enumerate(searchspace):
             #np.save(filenames['ntk'], scores['ntk'])
             #np.save(filenames['entropy'], scores['entropy'])
             #np.save(filenames['gradsign'], scores['gradsign'])
-            np.save(filenames['synflow'], scores['synflow'])
+            #np.save(filenames['synflow'], scores['synflow'])
             np.save(filenames['logsynflow'], scores['logsynflow'])
             #np.save(filenames['acc'], accs)
     except Exception as e:
@@ -179,6 +179,6 @@ for i, (uid, network) in enumerate(searchspace):
 #np.save(filenames['ntk'], scores['ntk'])
 #np.save(filenames['entropy'], scores['entropy'])
 #np.save(filenames['gradsign'], scores['gradsign'])
-np.save(filenames['synflow'], scores['synflow'])
+#np.save(filenames['synflow'], scores['synflow'])
 np.save(filenames['logsynflow'], scores['logsynflow'])
 #np.save(filenames['acc'], accs)

### 2023-03-20 score/logsynflow_score.py
abs(log(grad) * weight) -> abs(log(grad)) * weight && filter those who are nan,inf,-inf

@@ -32,22 +32,22 @@ def logsynflow_score(network, train_loader, device):
     
     def synflow(layer):
         if layer.weight.grad is not None:
-            return torch.abs(torch.log(layer.weight.grad) * layer.weight)
+            res = torch.abs(torch.log(layer.weight.grad)) * layer.weight
+            res = res[res.isfinite()]
+            return res
         else:
             return torch.zeros_like(layer.weight)
 
+    score = 0
     for layer in network.modules():
         if isinstance(layer, nn.Conv2d) or isinstance(layer, nn.Linear):
-            grads_abs.append(synflow(layer))
+            score += torch.sum(synflow(layer))
 
     """
     for p in parameters():
         scores[id(p)] = torch.clone(np.log(p.grad) * p).detach().abs_().cpu().numpy()
         p.grad.data.zero_()
     """
-    score = 0
-    for i in range(len(grads_abs)):
-        score += torch.sum(grads_abs[i])
 
     nonlinearize(network, signs)
     return score.detach().cpu().numpy()

### 2023-03-20 search/GA_mm.py
disable logsynflow

@@ -21,8 +21,8 @@ class GA():
             base_loc  = f"/home/jasonzzz/Genetic-Based-Neural-Architecture-Search-with-Hybrid-Score-Functions/results/score/{args.dataset}-test"
         self.ninaswot = np.load(f"{base_loc}/ninaswot_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.ntk      = np.load(f"{base_loc}/ntk_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
-        self.synflow  = np.load(f"{base_loc}/synflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
-        self.logsynflow  = np.load(f"{base_loc}/logsynflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
+        #self.synflow  = np.load(f"{base_loc}/synflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
+        #self.logsynflow  = np.load(f"{base_loc}/logsynflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         ####
         self.MAXN_POPULATION = args.maxn_pop
         self.MAXN_ITERATION = args.maxn_iter
@@ -62,7 +62,7 @@ class GA():
                 #self.population[i].fitness = self.DICT[self.population[i].gene] = \
                 #(standardize(ninaswot_score(network, self.train_loader, self.device, self.stds, self.means, self.args), self.means["ninaswot"], self.stds["ninaswpt"]), \
                 #-standardize(ntk_score(network, self.train_loader, self.device), self.means["ntk"], self.stds["ntk"])
-                x = self.ninaswot[self.population[i].uid] + self.ntk[self.population[i].uid] + self.logsynflow[self.population[i].uid]
+                x = self.ninaswot[self.population[i].uid] + self.ntk[self.population[i].uid]
                 self.population[i].fitness = self.DICT[self.population[i].gene] = x if np.isfinite(x) else -np.inf
             else:
                 self.population[i].fitness = self.DICT[self.population[i].gene]

### 2023-03-20 search/GA_based_on_rank.py
disable logsynflow

@@ -5,7 +5,7 @@ import numpy as np
 
 class chromosome():
     def __init__(self, gene = None, fitness = None, acc = None, uid = None):
-        """ fitness: (ninaswot, ntk, logsynflow, tot) """
+        """ fitness: (ninaswot, ntk,..., tot) """
         self.gene = gene
         self.fitness = fitness
         self.acc = acc
@@ -21,13 +21,13 @@ class GA():
 
         self.ninaswot = np.load(f"{base_loc}/ninaswot_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         self.ntk      = np.load(f"{base_loc}/ntk_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
-        self.synflow  = np.load(f"{base_loc}/synflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
-        self.logsynflow  = np.load(f"{base_loc}/logsynflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
+        #self.synflow  = np.load(f"{base_loc}/synflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
+        #self.logsynflow  = np.load(f"{base_loc}/logsynflow_nasbench201_{args.dataset}_none_0.05_1_{args.valid}_128_1_1.npy")
         ####
 
         assert len(self.ninaswot) == 15625, "broken: ninaswot"
         assert len(self.ntk) == 15625, "broken: ntk"
-        assert len(self.synflow) == 15625, "broken: synflow"
+        #assert len(self.synflow) == 15625, "broken: synflow"
         ####
         self.MAXN_POPULATION = args.maxn_pop
         self.MAXN_ITERATION = args.maxn_iter
@@ -45,7 +45,7 @@ class GA():
         self.means = means
         self.acc_type = acc_type
         self.best_chrom = chromosome()
-        self.candiate = {"ninaswot":set(), "ntk":set(), "logsynflow":set(), "tot":[]}
+        self.candiate = {"ninaswot":set(), "ntk":set(), "tot":[]}
         self.NAS_201_ops = ['none', 'skip_connect', 'nor_conv_1x1', 'nor_conv_3x3', 'avg_pool_3x3']
 
     def init_population(self):
@@ -71,10 +71,10 @@ class GA():
[…]

### 2023-03-20 search.sh
rk->ori

@@ -1,2 +1,2 @@
-python GA_search.py --search_algo rk --maxn_pop 50 --maxn_iter 40 --prob_mut 0.08 --prob_cr 0.7 --save_string all_score --valid --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 1 --n_samples 50 --data_loc ./cifardata/ --dataset cifar10 
+python GA_search.py --search_algo ori --maxn_pop 50 --maxn_iter 40 --prob_mut 0.08 --prob_cr 0.7 --save_string all_score --valid --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 1 --n_samples 50 --data_loc ./cifardata/ --dataset cifar100
 #python GA_search.py --search_algo rk --maxn_pop 100 --maxn_iter 10 --prob_mut 0.1 --prob_cr 0.8 --save_string all_score --valid --augtype none --repeat 1 --sigma 0.05 --nasspace nasbench201 --batch_size 128 --GPU 1 --n_samples 50 --data_loc ./ImageNet16 --dataset ImageNet16-120

### 2023-05-31 paper/main.tex
complete related work first part

@@
     it with several NAS algorithms, including weight-sharing methods, 
-    non-weight-sharing methods, and neural architecture search without training (NASWOT). 
-    We expect develope a faster and more accurate training-free NAS algorithm.
+    non-weight-sharing methods, and several state-of-the-art training-free score 
+    functions. 
+    The final result shows that in big search space, like nats-bench sss, the 
+    proposed algorithm outperforms most of NAS methods.
 
@@
     of method which is so called training-free NAS. 
-    % NINASWOT
+    % NASWOT
     For example, Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed the 
@@
     search without training (NASWOT). 
-    Later, Wu et al. \cite{10.1145/3491396.3506510} found a high score 
-    obtained by such a function may not correspond to a high-performence 
-    model. Thus, they additionally applied noisy immunity method on NASWOT, 
-    named as noisy immunity for NASWOT (NINASWOT).
+    % logsynflow
+    On the other hand, Lee et al. \cite{lee2019snip} proposed purning parameters based on a saliency matric, 
+    which then extended further by Wang et al. \cite{wang2020picking} and Tanaka et al. \cite{tanaka2020pruning}. 
+    In \cite{tanaka2020pruning}, Tanaka et al. proposed Iterative Synaptic Flow Pruning 
+    (SynFlow) algorithm which intends to deal with the layer collapse problem when purning a network. 
+    The score function used in the algorithm is so-called \it{synaptic saliency} \rm{score}. 
+    Later, Abdelfattah et al. \cite{abdelfattah2021zerocost} extended SynFlow to score 
+    a network architecture by summing synaptic saliency score over all parameters in the model. 
+    Cavagnero et al. \cite{Cavagnero_2023} found that SynFlow is likely to suffer from gradient explosion, then 
+    proposed the LogSynFlow score function which prevents the problem. 
     % NTK
@@
     which is used as the score to estimate the trainability of an architecture.
-	% unknown
 
 % what is unknown?
-    However, most of score functions suffer from low correlation between 
-    score value and the result of an architecture, leading to a predicament 
+    However, \xtab{table:corr_score} shows most of score functions suffer from low correlation between 
+    score value and the final accuracy of an architecture, leading to a predicament 
     that no matter how good the search method is used, we can hardly find 
@@
     function can only evaluate one perspect/characteristic of an architecture. 
+    \begin{table*}[htb]
+        \caption{\textsc{The Kendall and Spearman correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench \cite{Dong_2021}. 
+        Each metric has been computed three times with different initialisations and the average is taken as final score. The data is from \cite{Cavagnero_2023}.}}
+        \begin{tabular}{ccccccc}\toprule
+            Training-free score function & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ 
+            \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7} & Kendall & Spearman & Kendall & Spearman & Kendall & Spearman \\ \midrule
+            \bf{NTK} & -0.33 & -0.49 & -0.30 & -0.45 & -0.39 & -0.56 \\
+            \bf{Snip} & 0.45 & 0.61 & 0.47 & 0.62 & 0.41 & 0.55 \\
+            \bf{Fisher} & 0.39 & 0.54 & 0.40 & 0.55 & 0.36 & 0.48 \\
+            \bf{Grasp} & 0.28 & 0.41 & 0.35 & 0.50 & 0.35 & 0.49 \\
+            \bf{NASWOT} & 0.61 & 0.79 & 0.62 & 0.81 & 0.60 & 0.78 \\
+            \bf{SynFlow} & 0.57 & 0.77 & 0.56 & 0.76 & 0.56 & 0.75 \\
+            \bf{LogSynFlow} & 0.61 & 0.81 & 0.60 & 0.79 & 0.59 & 0.78 \\ \bottomrule
+            \label{table:corr_score}
+          \vspace{-\baselineskip}
+        \end{tabular}
+    \end{table*}
 
@@
     To address the problem, we propose cooperating three heterogeneous score 
-    functions with genetic-based search method, which evaulate an architecture 
+    functions with rank-based search method, which evaulate an architecture 
     from different aspects. More specifically, the first score function is 
-    NINASWOT \cite{10.1145/3491396.3506510} as an indicator of the ability 
-    to distinguish two images. The second one is the condition number of NTK 
-    \cite{https://doi.org/10.48550/arxiv.2102.11535} as score to estimate the 
-    trainability of an architecture. The last one is (TBD).
+    NI \cite{10092788} as an indicator of the ability to distinguish two images. 
+    The second one is NASWOT as score to estimate the ability of expression 
+    of an architecture. The last one is logsynflow used as the measurement of 
+    trainability. 
+    By combining these three training-free score functions, this paper also 
+    compares the different search algorithms, e.g., random search, genetic 
+    algorithm (GA) \cite{mitchell1998introduction}, simulated annealing algorithm (SA)
+    \cite{kirkpatrick1983optimization}.
 
@@
     \begin{itemize}
-        \item Develope a genetic-based neural architecture search method based on three hybrid score functions.
-        \item Cooperating three score functions to get a higher correlation between score and accuracy.
+        \item Cooperating three score functions to obtain better ability for searching top accuracy neural architectures. 
+        \item Develope a rank-based neural architecture search with several search algorithms. 
     \end{itemize}
@@
 
-    The remainder of this paper is organized as follows: Section 2 provides the 
-    detail about the three heterogeneous score functions. Section 3 gives a detailed 
-    description about the proposed method. Section 4 provide the simulation results 
-    in different search space. The conclusion and further prospect are gived in 
-    Section 5.
+    The remainder of this paper is organized as follows: \xsec{sec:related_work} provides the 
+    detail about the three heterogeneous score functions. \xsec{sec:proposed} gives a detailed 
+    description about the proposed method. \xsec{sec:results} begins with parameters setting and 
+    provide the simulation results following is the experiment results in different search space. 
+    The conclusion and further prospect are gived in \xsec{sec:conclusion}.
 
     \section{Related Works}
+    \label{sec:related_work}
     \begin{figure*}[htb]
@@
     \end{figure*}
-    In these days, the studies of training-free neural architecture search (NAS) 
-    go viral, since the ability to accelerate the procedure for designing a neural 
-    network architecture used on specific application, while additionally, 
-    training-free NAS cleverly avoid the drawback of long-time training by using 
-    various training-free score functions.
-
+    \subsection{Training-free Score Function}
     % naswot
     In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. proposed a 
-    score function without the requirement for training. Here we call it neural 
-    architecture search without training (NASWOT) score function. \xfig{fig:naswot} 
+    score function without the requirement for training which is named neural 
+    architecture search without training (NASWOT). \xfig{fig:naswot} 
 	gives a simple example to illustrate the procedure of NASWOT score function. 
@@
 
-    % ninaswot
+    % ni
     \begin{figure*}[htb]
@@
     \end{figure*}
-    Based on the work of Mellor et al., Wu et al. \cite{10.1145/3491396.3506510} 
-    found, in some case, an architecture with high score may put different 
-    input data, which are originally in the same class, to different classes. 
-    To fix this defect, Wu et al. proposed using noise immunity to additionally 
+    Wu et al. \cite{10092788} found, in some case, an architecture with high 
+    NASWOT score may classify the same kind of input data into different classes. 
+    To fix this defect, Wu et al. proposed using noise immunity (NI) to 
     evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
     noise immunity score evaluate an architecture. The score function picks a 
-    mini-batch of data, denoted $X$, and then applies Gaussion noise on it, 
-    denoted $X'$ and defined by $X'=X+z$ where $z$ is the Gaussion noise. 
-    By passing $X$ and $X'$ through the untrained architecture, the sum of the 
-    square differences between outputs 
-    $O=\begin{matrix}o_1,o_2,\cdots,o_C\end{matrix}$ and 
-    $O'=\begin{matrix}o_1',o_2',\cdots,o_C'\end{matrix}$ can be calculated as 
-    follows: 
+    mini-batch of data, denoted $X$, and then applies Gaussion noise on it. 
+    The process can be defined by $X'=X+z$ where $z$ is the Gaussion noise. 
+    By passing $X$ and $X'$ through the untrained architecture, then computing 
+    the difference of square of each feature maps captured at all pooling layers, 
+    denoted $\eta$. According to the fact that the input data are the same kind, 
+    the small $\eta$ the better the noise immunity of the architecture is.
+
+    % logsynflow
+    Besides from these two model-dependent aspects, Tanaka et al. \cite{tanaka2020pruning} 
+    generalized synaptic saliency scores, and proposed SynFlow algorithm to avoids layer 
+    collapse when performing purning. 
+    Inspired from \cite{tanaka2020pruning}, \cite{wang2020picking}, \cite{lee2019snip}, 
+    Abdelfattah et al. \cite{abdelfattah2021zerocost} proposed summing synaptic saliency scores 
+    over all parameters in the model as an accuracy estimator to a architecture.
+
+    Besides from these two model-dependent aspects, roots from The Lottery Ticket Hypothesis 
+    \cite{frankle2019lottery}, saliency matric is used on purning network parameters in 
+    \cite{lee2019snip}, which can be formula as 
     \begin{equation}
-        n=-\sum^C_{n=1}(o_i-o_i')^2
+        \label{equ:snip}
+        S_p(\theta)=\lvert\frac{\partial \mathcal L}{\partial \theta}\odot\theta\rvert
     \end{equation}
-    where $C$ is the number of classes determined by the input data.
-    According to the experiment outcome of Wu et al., noise immunity can separate 
-    those are unable to distinguish $X$ and $X'$ from architectures with high NASWOT 
-    score, which just complements the NASWOT score funcion.
-
-    % ntk
-    On the other hand, instead of using the correlation of binary activation 
-    patterns as score. Chen et al. proposed using the condition number of NTK 
-    as an evaluation of the trainability, defined as % add figure
+    where $\mathcal L$ is the loss function of a neural network with parameters $\theta$ 
+    and $\theta$ is the Hadamard product. 
+    The saliency matric approximates the change in loss when purning a specific parameters.
+    Later, Wang et al. \cite{wang2020picking} approximates the change in gradient norm when 
+    purning the network, which defined as 
     \begin{equation}
-        \mathcal{K_N}=\frac{\lambda_{\textrm{max}}(\hat\Theta)}{\lambda_{\textrm{min}}(\hat\Theta)}
+        \label{equ:grap}
+        S_p(\theta)=-(H\frac{\partial \mathcal L}{\partial \theta})\odot\theta
     \end{equation}
-    where $\lambda_{\textrm{max}}(\hat\Theta)$ and $\lambda_{\textrm{min}}(\hat\Theta)$ 
-    are the maximum and minimum eigenvalues of NTK ($\hat\Theta$) respectively.
-    The rationale is based on the work of Lee et al. \cite{Lee_2020} and 
-    Xiao et al. \cite{https://doi.org/10.48550/arxiv.1912.13053}, which concluded briefly here, 
-    the training dynamics of a wide neural network can be written in terms of the 
-    spectrum of the NTK:
-    \begin{equation}\label{eq:6}
-        \mu_t(\textbf{X}_{\textrm{train}})_i=(\textbf{I}-e^{-\eta\lambda_it})\textbf{Y}_{\textrm{train,}i}
+    where $\mathcal L$ is the change in gradient norm instead of loss function and $H$ is 
+    the Hessian. 
+    In \cite{tanaka2020pruning}, Tanaka et al. generalized the synaptic saliency scores as 
+    \begin{equation}
+        \label{equ:synflow}
+        S_p(\theta)=\frac{\partial \mathcal L}{\partial \theta}\odot\theta
     \end{equation}
-    where $\lambda_i$ are the eigenvalues of $\hat\Theta_{\textrm{train}}$ 
-    and they're ordered as $\lambda_0\geq\cdots\geq\lambda_m$. 
-    According to the hypothesis proposed by Lee et al. \cite{Lee_2020}, the maximum 
-    feasible learning rate scale as $\eta\sim2/\lambda_0$. Plug this scaling for 
-    $\eta$ in Eq. \ref{eq:6}, we see that the $\lambda_m$ will converge exponentially 
-    at a rate given by $1/K_N$ where $K_N=\frac{\lambda_0}{\lambda_m}$.
-    Then it can be concluded that if $K_N$ is lower, the corresponding architecture is 
-    more trainable.
-
-	% synflow?
+    which is named SynFlow. 
+    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, conclude that summing 
+    synaptic saliency score over all parameters in the model can be used to score a network 
+    architecture, which is formula as
+    \begin{equation}
+        \label{equ:zero_cost}
+        S_n=\sum^N_i S_p(\theta)_i
+    \end{equation}
+    Finally, Cavagnero et al. \cite{Cavagnero_2023} imporved SynFlow, which is likely to fall into 
+    gradient explosion problem, and proposed LogSynFlow score function, simply scaling down the gradient. 
+    The formula is defined by 
+    \begin{equation}
+        \label{equ:logsynflow}
+        S(\theta)=\theta\cdot\log(\frac{\partial \mathcal L}{\partial \theta}+1)
+    \end{equation}
 
     % conclusion
+    \subsection{Search Algorithm}
 
-    \section{the proposed algorithm}
-    In our work, however, we use rank-based GA. Rather than use single fitness to select, 
-    the method preserve the top 1 in NINASWOT score and also the top 1 in the condition 
-    number of NTK. After the evolution,
+    \section{The Proposed Algorithm}
+    \label{sec:proposed}
+    In this work,
+
+    \section{experiment result}
+    \label{sec:results}
+
+    \subsection*{natsbenchsss}
+    \begin{table*}[htb]
+        %\normalsize
+        %\centering
+        \newcommand{\z}{\phantom{0}}
+        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms.}}
+          \vspace{-\baselineskip}
+        \begin{tabular}{@{}lccccccl@{}}\toprule
+        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
+        & & validation & test & validation & test & validation & test \\ \midrule
+        &&&&\textbf{Non-weight sharing}&&&\\
+        AREA      & $12,000$ & $84.62 \pm \z{0.41}$                & $93.16 \pm 0.16$               & $59.24 \pm \z{1.11}$                 & $69.56 \pm \z{0.96}$                & $37.58 \pm 1.09$                 & $45.30 \pm \z{0.91}$                \\
+        REA       & $12,000$ & $90.26 \pm \z{0.22}$                & $93.17 \pm 0.21$               & $69.48 \pm \z{0.76}$                 & $69.49 \pm \z{0.94}$                & $44.84 \pm 0.72$                 & $45.47 \pm \z{0.91}$                \\
+        RS        & $12,000$ & $90.08 \pm \z{0.24}$                & $93.01 \pm 0.29$               & $69.14 \pm \z{0.94}$                 & $69.17 \pm \z{1.00}$                & $44.66 \pm 1.02$                 & $44.83 \pm \z{1.05}$                \\
+        RL        & $12,000$ & $90.17 \pm \z{0.23}$                & $93.08 \pm 0.21$               & $69.23 \pm \z{0.87}$                 & $69.29 \pm \z{1.08}$                & $44.68 \pm 0.91$                 & $45.05 \pm \z{0.93}$                \\
+        BOHB      & $12,000$ & $90.05 \pm \z{0.30}$                & $93.03 \pm 0.20$               & $69.04 \pm \z{0.76}$                 & $69.16 \pm \z{0.90}$                & $44.71 \pm 0.78$                 & $44.91 \pm \z{1.05}$                \\ \midrule
+        %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
+        &&&&\textbf{Training-free}&&&\\
+        NI (N=1,000) & $X$ & $89.56\pm \z{0.147}$ & $92.55\pm 0.187$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        NASWOT (N=1,000) & $X$ & $89.25\pm \z{0.412}$ & $92.21\pm 0.298$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        logsynflow (N=1,000) & $X$ & $89.61\pm \z{0.101}$ & $92.60\pm 0.188$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        rk (N=1000) & $X$ & $89.59\pm \z{0.136}$ & $92.51\pm 0.171$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        GA-rk & $457.54$ & $90.29\pm \z{0.149}$ & $93.27\pm0.193$ & $69.88\pm \z{0.497}$ & $70.06\pm \z{0.481}$ & $45.57\pm 0.425$ & $46.19\pm \z{0.846}$ \\ 
+        SA-rk & $682.36$ & $90.37\pm \z{0.204}$ & $93.29\pm0.182$ & $70.11\pm \z{0.457}$ & $70.32\pm \z{0.458}$ & $45.38\pm 0.499$ & $46.45\pm \z{0.687}$ \\ \bottomrule
+        \end{tabular}
+        \label{table:overall_sss}
+          \vspace{-\baselineskip}
+      \end{table*}
+
+    \subsection*{nasbench201}
+    \begin{table*}[htb]
+        %\normalsize
+        %\centering
+        \newcommand{\z}{\phantom{0}}
+        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms.}}
+          \vspace{-\baselineskip}
+        \begin{tabular}{@{}lccccccl@{}}\toprule
+        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
+        & & validation & test & validation & test & validation & test \\ \midrule
+        &&&&\textbf{Non-weight sharing}&&&\\
+        AREA      & $12,000$ & $91.18 \pm \z{0.43}$                & $93.95 \pm \z{0.39}$               & $71.84 \pm \z{1.21}$                 & $71.92 \pm \z{1.29}$                & $45.04 \pm 1.03$                 & $45.40 \pm \z{1.14}$                \\
+        REA       & $12,000$ & $91.08 \pm \z{0.54}$                & $93.89 \pm \z{0.50}$               & $71.69 \pm \z{1.34}$                 & $71.83 \pm \z{1.33}$                & $44.96 \pm 1.41$                 & $45.30 \pm \z{1.51}$                \\
+        RS        & $12,000$ & $90.91 \pm \z{0.33}$                & $93.67 \pm \z{0.33}$               & $70.91 \pm \z{1.04}$                 & $70.99 \pm \z{0.99}$                & $44.52 \pm 0.99$                 & $44.56 \pm \z{1.25}$                \\
+        RL        & $12,000$ & $90.87 \pm \z{0.41}$                & $93.63 \pm \z{0.36}$               & $70.62 \pm \z{1.08}$                 & $70.77 \pm \z{1.05}$                & $44.20 \pm 1.22$                 & $44.23 \pm \z{1.37}$                \\
+        BOHB      & $12,000$ & $88.47 \pm \z{1.19}$                & $91.79 \pm \z{1.11}$               & $67.18 \pm \z{2.05}$                 & $67.50 \pm \z{2.05}$                & $38.94 \pm 3.58$                 & $39.00 \pm \z{3.73}$                \\ \midrule
+        &&&&\textbf{Weight sharing}&&&\\
+        RSWS      & $\z{4,154}$  & $76.95 \pm 16.74$                & $82.60 \pm 12.10$               & $52.51 \pm 18.33$                & $52.93 \pm 18.32$                   & $29.76 \pm 9.50$                 & $29.16 \pm 9.61$               \\
+        DARTS-V1  & $\z{5,475}$  & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm \z{0.00}$                \\
+        DARTS-V2  & $16,114$ & $39.77 \pm \z{0.00}$               & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                & $15.61 \pm \z{0.00}$                   & $16.43 \pm 0.00$                 & $16.32 \pm \z{0.00}$                \\
+        GDAS      & $11,183$ & $90.05 \pm \z{0.23}$                & $93.46 \pm \z{0.13}$               & $71.02 \pm \z{0.31}$                 & $70.56 \pm \z{0.24}$                & $41.77 \pm 1.24$                 & $41.96 \pm \z{0.90}$                \\
+        SETN      & $16,787$ & $84.25 \pm \z{5.05}$                & $88.01 \pm \z{4.52}$               & $59.72 \pm \z{7.30}$                & $59.91 \pm \z{7.51}$                   & $33.93 \pm 3.85$                 & $33.48 \pm \z{4.22}$                \\
+        ENAS      & $\z{7,061}$  & $40.11 \pm \z{3.28}$                & $56.33 \pm \z{3.70}$               & $14.09 \pm \z{1.60}$                 & $14.77 \pm \z{1.45}$                & $16.20 \pm 0.48$                 & $15.93 \pm \z{0.67}$                \\ \midrule
+        &&&&\textbf{Training-free}&&&\\
+        NI (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        NASWOT (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        logsynflow (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        rk (N=1000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        GA-rk & $747.25$ & $89.93\pm \z{0.196}$ & $93.41\pm0.083$ & $70.70\pm \z{0.417}$ & $70.76\pm \z{0.378}$ & $42.70\pm 1.315$ & $43.10\pm \z{1.428}$ \\ 
+        SA-rk & $X$ & $89.95\pm \z{0.194}$ & $93.37\pm0.114$ & $70.69\pm \z{0.391}$ & $70.75\pm \z{0.532}$ & $X\pm X$ & $43.10\pm \z{1.506}$ \\ \bottomrule
+        \end{tabular}
+        \label{table:overall_201}
+          \vspace{-\baselineskip}
+      \end{table*}
+
+    \section{Conclusion}
+    \label{sec:conclusion}
 

### 2023-05-31 paper/main.tex
update related work part2

@@
     \subsection{Search Algorithm}
+    First assume that input data $D$ are separated into two subset, $D_r$ and $D_t$. Further more, 
+    assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $A_s$ the 
+    search algorithm of NAS, and $\mathcal A_L$ the learning algorithm. Then, NAS problem can be 
+    described as an optimization problem as follows: 
+    \begin{equation}
+        \label{equ:nas}
+        \mathbb N^*=\max_{\mathbb N^b\in\mathbb N}\mathcal F_A(\mathcal A_L(\mathbb N^b, D_r), D_t)
+    \end{equation}
+    where $\mathbb N$ is a set of neural architectures, namely, the search space of NAS. 
+    For non-training-free NAS 
+    \begin{equation}
+        \label{equ:non-training_free_nas}
+        \mathbb N^b=\mathcal A_S(\mathcal F_A(\mathcal A_L(\mathbb N^s, D_r), D_t), \mathbb N)
+    \end{equation}
+    and for training-free NAS 
+    \begin{equation}
+        \label{equ:training_free_nas}
+        \mathbb N^b=\mathcal A_S(\mathcal F_S(\mathbb N^s, D_r), \mathbb N)
+    \end{equation}
+    It can be seen that training-free NAS is comprised of two part, search algorithm $A_S$ and score 
+    function $F_S$. 
+    There are several search algorithms applied on NAS, including random search, bayesian optimization, 
+    reinforcement learning, differentiable search algorithm, metaheuristic algorithm, and hybrid 
+    heuristic algorithm. 
+    In \cite{https://doi.org/10.48550/arxiv.2006.04647} \cite{Lopes_2021}, random search is applied on. 
+    The advantage of random search is simple, easy to implement, and the result can be token as a 
+    baseline to more comprehensive search algorithm.
+
+    In \cite{10092788}, search economic (SE) \cite{7379579} is applied on.
 

### 2023-05-31 paper/main.tex
update paper

@@
 
-\title{GA-based Training-Free NAS Algorithm with Hybrid Score Function}
+\title{Rank-based Training-Free NAS Algorithm}
 
@@
     of NAS algorithm while the hybrid training-free score function plays the 
-    role to evaluate a new candidate architecture during the convergencr process 
-    of GA. More precisely, the first score function is noise immunity for 
-    neural architecture search without search (NINASWOT), as an evaluation of 
-    pattern recognition ability, second one is condition number of neural 
-    tangent kernel (NTK), as an evaluation of trainability.
+    role to evaluate a new candidate architecture during the convergence process 
+    of GA. More precisely, the first score function is noise immunity (NI), as 
+    an evaluation of the ability to tolerate noise, second one is NASWOT score, as 
+    an measurement of the pattern recognition ability, finally, the last one is 
+    LogSynFlow score, as an evaluation of trainability.
 
@@
     functions. 
-    The final result shows that in big search space, like nats-bench sss, the 
+    The final result shows that in relatively larger search space, like nats-bench sss, the 
     proposed algorithm outperforms most of NAS methods.
@@
     \label{sec:related_work}
-    \begin{figure*}[htb]
-        \vspace{-\baselineskip}
-        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/naswot.pdf}}
-        \caption{A simple example to illustrate the procedure of NASWOT.}
-        \label{fig:naswot}
-        \centering
-        \vspace{-\baselineskip}
-    \end{figure*}
     \subsection{Training-free Score Function}
@@
 
-    % ni
-    \begin{figure*}[htb]
+    \begin{figure*}[!htb]
         \vspace{-\baselineskip}
-        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
-        \caption{A simple example to illustrate the procedure of noise immunity.}
-        \label{fig:ni}
+        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/naswot.pdf}}
+        \caption{A simple example to illustrate the procedure of NASWOT.}
+        \label{fig:naswot}
         \centering
@@
     \end{figure*}
+
+    % ni
     Wu et al. \cite{10092788} found, in some case, an architecture with high 
@@
     the small $\eta$ the better the noise immunity of the architecture is.
+
+    \begin{figure*}[!hb]
+        \vspace{-\baselineskip}
+        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
+        \caption{A simple example to illustrate the procedure of noise immunity.}
+        \label{fig:ni}
+        \centering
+        \vspace{-\baselineskip}
+    \end{figure*}
 
@@
 
-    % conclusion
     \subsection{Search Algorithm}
@@
     function $F_S$. 
-    There are several search algorithms applied on NAS, including random search, bayesian optimization, 
-    reinforcement learning, differentiable search algorithm, metaheuristic algorithm, and hybrid 
-    heuristic algorithm. 
+    There are several search algorithms applied on NAS, including random search, reinforcement learning, and
+    metaheuristic algorithm.
+
     In \cite{https://doi.org/10.48550/arxiv.2006.04647} \cite{Lopes_2021}, random search is applied on. 
     The advantage of random search is simple, easy to implement, and the result can be token as a 
-    baseline to more comprehensive search algorithm.
+    baseline compared to more comprehensive search algorithm. Generally speaking, when applying random 
+    search on a samll search space, e.g., nasbench201 \cite{dong2020nasbench201}, the performance is 
+    similar to other search algorithms. But when it comes to a relatively larger search space, e.g., nasbench101 
+    \cite{ying2019nasbench101} and natsbenchsss \cite{Dong_2021}, random search can no longer standout 
+    in other search algorithms.
 
-    In \cite{10092788}, search economic (SE) \cite{7379579} is applied on.
+    In \cite{zoph2017neural}, reinforcement learning is used to find the maximum accuracy of an architecture 
+    generated by a network architecture controller. The actions $a_{1:T}$ of the reinforcement learning is 
+    equivalent to updating the parameters $\theta_c$ for the controller. More specifically, the goal is to maximize 
+    its expected reward, defined by 
+    \begin{equation}
+        \label{equ:reinforcement_rw}
+        J(\theta_c)=E_{P(a_{1:T};\theta_c)}[R]
+    \end{equation}
+    and the gradient of $J(\theta_c)$ is defined by
+    \begin{equation}
+        \label{equ:reinforcement_grad}
+        \nabla_{\theta_c} J(\theta_c)=\sum^T_t=1 E_{P(a_{1:T};\theta_c)}[\nabla_{\theta_c}\log P(a_t\mid a_{(t-1):1};\theta_c)R]
+    \end{equation}
+
+    And in \cite{10.1145/3491396.3506510}, Wu et al. leveraged genetic algorithm (GA) as search strategy. 
+    By encoding the network architecture, the architecture can be viewed as gene. Therefore, GA can be 
+    easily applied on. 
+    Later in \cite{10092788}, Wu et al. used search economic (SE) \cite{7379579} as search strategy. The 
+    basic idea of SEs is to first divide the search space into a set of subspaces and investiagte those 
+    subspaces based on the expected value of each subspace. The expected value is comprised of 
+    \begin{itemize}
+        \item The number of times the subspace has been investiagted. 
+        \item The average objective value of the new candidate solutions in the subspace at current iteration. 
+        \item The best solution so far in this subspace. 
+    \end{itemize}
 
@@
     \subsection*{natsbenchsss}
+    The result of natsbenchsss is shown in \xtab{table:overall_sss}.
     \begin{table*}[htb]
@@
     \subsection*{nasbench201}
+    The result of nasbench201 is shown in \xtab{table:overall_201}.
     \begin{table*}[htb]

### 2023-06-08 score/synflow_score.py
fix synflow score

@@ -17,9 +17,9 @@ def synflow_score(network, train_loader, device):
         for name, param in network.state_dict().items():
             param.mul_(signs[name])
     
-    network = copy.deepcopy(network)
+    #network = copy.deepcopy(network)
     # disable BN layer and dropout
-    network.eval()
+    #network.eval()
 
     network = network.to(device)
     signs = linearize(network)
@@ -30,7 +30,7 @@ def synflow_score(network, train_loader, device):
     output, logit = network(input)
     torch.sum(output).backward()
 
-    grads_abs = []
+    grads = []
     
     def synflow(layer):
         if layer.weight.grad is not None:
@@ -39,17 +39,12 @@ def synflow_score(network, train_loader, device):
             return torch.zeros_like(layer.weight)
 
     for layer in network.modules():
-        if isinstance(layer, nn.Conv2d) or isinstance(layer, nn.Linear):
-            grads_abs.append(synflow(layer))
+        if isinstance(layer, nn.Conv2d) or isinstance(layer, nn.Linear) or isinstance(layer, nn.BatchNorm2d):
+            grads.append(synflow(layer))
 
-    """
-    for p in parameters():
-        scores[id(p)] = torch.clone(np.log(p.grad) * p).detach().abs_().cpu().numpy()
-        p.grad.data.zero_()
-    """
     score = 0
-    for i in range(len(grads_abs)):
-        score += torch.sum(grads_abs[i])
+    for i in range(len(grads)):
+        score += torch.sum(grads[i])
 
     nonlinearize(network, signs)
-    return torch.abs(score).detach().cpu().numpy()
+    return score.detach().cpu().numpy()

### 2023-06-08 search/RD_rk_abstract.py
prevent kendalltau=nan

@@ -95,10 +95,10 @@ class abstract_RD():
         ind_rk = [totrk[uid] for uid in indices]
         #ind_rk = np.argsort(ind_rk)
         rk_tau, p = kendalltau(ind_rk, accs)
-        ni_tau, p = kendalltau(scores["ni"][np.isfinite(scores["ni"])], accs[np.isfinite(scores["ni"])])
-        naswot_tau, p = kendalltau(scores["naswot"][np.isfinite(scores["naswot"])], accs[np.isfinite(scores["naswot"])])
+        ni_tau, p = kendalltau(np.array(scores["ni"])[np.isfinite(scores["ni"])], np.array(accs)[np.isfinite(scores["ni"])])
+        naswot_tau, p = kendalltau(np.array(scores["naswot"])[np.isfinite(scores["naswot"])], np.array(accs)[np.isfinite(scores["naswot"])])
         #logsyn_tau, p = kendalltau(scores["logsynflow"], accs)
-        synflow_tau, p = kendalltau(scores["synflow"][np.isfinite(scores["synflow"])], accs[np.isfinite(scores["synflow"])])
+        synflow_tau, p = kendalltau(np.array(scores["synflow"])[np.isfinite(scores["synflow"])], np.array(accs)[np.isfinite(scores["synflow"])])
         rk_time = time.time() - rk_st
         ####
         #print(f"ni tau = {ni_tau}, naswot tau = {naswot_tau}, logsynflow tau = {logsyn_tau}, synflow tau = {synflow_tau}, rk tau = {rk_tau}")

### 2023-06-08 search/GA_rk_abstract.py
remove unused comment

@@ -6,7 +6,6 @@ import numpy as np
 
 class chromosome():
     def __init__(self, gene = None, fitness = None, acc = None, uid = None):
-        """ fitness: (naswot, ntk, ni, logsynflow, tot) """
         self.gene = gene
         self.fitness = fitness
         self.acc = acc

### 2023-06-08 RD_search.py
update nasbench101 case

@@ -105,7 +105,10 @@ for N in runs:
     times["tot"].append(time.time()-start)
 
     #runs.set_description(f"acc_ni: {mean(accs['ni']):.3f}({std(accs['ni']):.3f}),t:{mean(times['ni']):.3f}, acc_naswot: {mean(accs['naswot']):.3f}({std(accs['naswot']):.3f}),t:{mean(times['naswot']):.3f}, acc_logsyn: {mean(accs['logsynflow']):.3f}({std(accs['logsynflow']):.3f}),t:{mean(times['logsynflow']):.3f}, acc_syn: {mean(accs['synflow']):.3f}({std(accs['synflow']):.3f}),t:{mean(times['synflow']):.3f} rk-based: {mean(accs['rank-based']):.3f}({std(accs['rank-based']):.3f}), t:{mean(times['rk']):.3f}")
-    runs.set_description(f"acc_ni: {mean(accs['ni']):.3f}({std(accs['ni']):.3f}),t:{mean(times['ni']):.3f}, acc_naswot: {mean(accs['naswot']):.3f}({std(accs['naswot']):.3f}),t:{mean(times['naswot']):.3f}, acc_syn: {mean(accs['synflow']):.3f}({std(accs['synflow']):.3f}),t:{mean(times['synflow']):.3f} rk-based: {mean(accs['rank-based']):.3f}({std(accs['rank-based']):.3f}), t:{mean(times['rk']):.3f}")
+    if args.nasspace == "nasbench101":
+        runs.set_description(f"acc_ni: {mean(accs['ni'])*100:.3f}({std(accs['ni'])*100:.3f}),t:{mean(times['ni']):.3f}, acc_naswot: {mean(accs['naswot'])*100:.3f}({std(accs['naswot'])*100:.3f}),t:{mean(times['naswot']):.3f}, acc_syn: {mean(accs['synflow'])*100:.3f}({std(accs['synflow'])*100:.3f}),t:{mean(times['synflow']):.3f} rk-based: {mean(accs['rank-based'])*100:.3f}({std(accs['rank-based'])*100:.3f}), t:{mean(times['rk']):.3f}")
+    else: 
[…]

### 2023-06-08 RD_search.py
nasspace: nasbench101 api return acc*100 instead. RD_search: so there's no need to separate a special case

@@ -105,10 +105,7 @@ for N in runs:
     times["tot"].append(time.time()-start)
 
     #runs.set_description(f"acc_ni: {mean(accs['ni']):.3f}({std(accs['ni']):.3f}),t:{mean(times['ni']):.3f}, acc_naswot: {mean(accs['naswot']):.3f}({std(accs['naswot']):.3f}),t:{mean(times['naswot']):.3f}, acc_logsyn: {mean(accs['logsynflow']):.3f}({std(accs['logsynflow']):.3f}),t:{mean(times['logsynflow']):.3f}, acc_syn: {mean(accs['synflow']):.3f}({std(accs['synflow']):.3f}),t:{mean(times['synflow']):.3f} rk-based: {mean(accs['rank-based']):.3f}({std(accs['rank-based']):.3f}), t:{mean(times['rk']):.3f}")
-    if args.nasspace == "nasbench101":
-        runs.set_description(f"acc_ni: {mean(accs['ni'])*100:.3f}({std(accs['ni'])*100:.3f}),t:{mean(times['ni']):.3f}, acc_naswot: {mean(accs['naswot'])*100:.3f}({std(accs['naswot'])*100:.3f}),t:{mean(times['naswot']):.3f}, acc_syn: {mean(accs['synflow'])*100:.3f}({std(accs['synflow'])*100:.3f}),t:{mean(times['synflow']):.3f} rk-based: {mean(accs['rank-based'])*100:.3f}({std(accs['rank-based'])*100:.3f}), t:{mean(times['rk']):.3f}")
-    else: 
-        runs.set_description(f"acc_ni: {mean(accs['ni']):.3f}({std(accs['ni']):.3f}),t:{mean(times['ni']):.3f}, acc_naswot: {mean(accs['naswot']):.3f}({std(accs['naswot']):.3f}),t:{mean(times['naswot']):.3f}, acc_syn: {mean(accs['synflow']):.3f}({std(accs['synflow']):.3f}),t:{mean(times['synflow']):.3f} rk-based: {mean(accs['rank-based']):.3f}({std(accs['rank-based']):.3f}), t:{mean(times['rk']):.3f}")
[…]

### 2023-06-08 nasspace.py

@@ -173,18 +173,18 @@ class Nasbench101:
     def get_accuracy(self, unique_hash, acc_type, trainval=True):
         spec = self.get_spec(unique_hash)
         _, stats = self.api.get_metrics_from_spec(spec)
-        maxacc = 0.
+        maxacc = 0
         for ep in stats:
             for statmap in stats[ep]:
                 newacc = statmap['final_test_accuracy']
                 if newacc > maxacc:
                     maxacc = newacc
-        return maxacc
+        return maxacc*100
     def get_final_accuracy(self, uid, acc_type, trainval):
         spec = self.get_spec(uid)
         if trainval:
-            return self.api.query(spec)["validation_accuracy"]
-        return self.api.query(spec)["test_accuracy"]
+            return self.api.query(spec)["validation_accuracy"]*100
+        return self.api.query(spec)["test_accuracy"]*100
     def get_training_time(self, unique_hash):
         spec = self.get_spec(unique_hash)
         _, stats = self.api.get_metrics_from_spec(spec)

### 2023-06-08 search/RD_rk_abstract.py
remove unused code

@@ -100,12 +100,6 @@ class abstract_RD():
         #logsyn_tau, p = kendalltau(scores["logsynflow"], accs)
         synflow_tau, p = kendalltau(np.array(scores["synflow"])[np.isfinite(scores["synflow"])], np.array(accs)[np.isfinite(scores["synflow"])])
         rk_time = time.time() - rk_st
-        ####
-        #print(f"ni tau = {ni_tau}, naswot tau = {naswot_tau}, logsynflow tau = {logsyn_tau}, synflow tau = {synflow_tau}, rk tau = {rk_tau}")
-        #np.savez("./correlation_info.npy", ind_rk = ind_rk, score_ni = scores["ni"], score_naswot = scores["naswot"], score_synflow = scores["synflow"], score_logsyn = scores["logsynflow"], acc = accs, rk_tau = np.array([rk_tau]), ni_tau = np.array([ni_tau]), naswot_tau = np.array([naswot_tau]), synflow_tau = np.array([synflow_tau]), logsyn_tau = np.array([logsyn_tau]))
-        print(f"ni tau = {ni_tau}, naswot tau = {naswot_tau}, synflow tau = {synflow_tau}, rk tau = {rk_tau}")
-        np.savez("./correlation_info.npy", ind_rk = ind_rk, score_ni = scores["ni"], score_naswot = scores["naswot"], score_synflow = scores["synflow"], acc = accs, rk_tau = np.array([rk_tau]), ni_tau = np.array([ni_tau]), naswot_tau = np.array([naswot_tau]), synflow_tau = np.array([synflow_tau]))
-        ####
         
         bestuid = (rk_ni[-1], 
                    rk_naswot[-1], 

### 2023-06-08 GA_search.py
use logsynflow

@@ -45,7 +45,7 @@ searchspace = nasspace.get_search_space(args)
 print(f"Making sure {args.save_loc} exist.")
 os.makedirs(args.save_loc, exist_ok=True)
 
-algo_module = importlib.import_module(f"search.{args.nasspace}_GA_rk")
+algo_module = importlib.import_module(f"search.GA.{args.nasspace}_GA_rk")
 GA = getattr(algo_module, "GA")
 GA_kwargs = {"searchspace": searchspace, "train_loader": train_loader, "device": device, "args": args}
 if args.nasspace == "nasbench201":
@@ -58,7 +58,6 @@ topscores = []
 naswot_acc = []
 ni_acc = []
 logsynflow_acc = []
-synflow_acc = []
 
 print(f"parameter:\nnumber of population={args.maxn_pop}\nnumber of iteration={args.maxn_iter}\nprobability of mutation={args.prob_mut}\nprobability of crossover={args.prob_cr}")
 
@@ -69,10 +68,10 @@ for N in runs:
 
     sol = GA(**GA_kwargs)
     if args.verbose:
-        score, acc_, uid, rk, naswotacc, niacc, synflowacc = sol.search()
+        score, acc_, uid, rk, naswotacc, niacc, logsynflowacc = sol.search()
         naswot_acc.append(naswotacc)
         ni_acc.append(niacc)
-        synflow_acc.append(synflowacc)
+        logsynflow_acc.append(logsynflowacc)
         ninaswot_acc.append(ninaswotacc)
     else:
         score, acc_, uid, rk = sol.search()
@@ -82,7 +81,7 @@ for N in runs:
 
     times.append(time.time()-start)
     if args.verbose:
-        runs.set_description(f"rk-acc: {mean(acc):.3f}%({std(acc):.3f}), naswot-acc: {mean(naswot_acc):.3f}%({std(naswot_acc):.3f}), ni-acc: {mean(ni_acc):.3f}%({std(ni_acc):.3f}), syn-acc: {mean(synflow_acc):.3f}%({std(synflow_acc):.3f})")
[…]

### 2023-06-08 RD_search.py

@@ -51,18 +51,18 @@ print(f"Making sure {args.save_loc} exist.")
 os.makedirs(args.save_loc, exist_ok=True)
 
 times = []
-accs = {"ni": [], "naswot": [], "logsynflow": [], "synflow": [], "rank-based": []}
+accs = {"ni": [], "naswot": [], "logsynflow": [], "rank-based": []}
 
 Encoder = encoder.get_encoder(args.nasspace)
 
-algo_module = importlib.import_module(f"search.{args.nasspace}_RD_rk")
+algo_module = importlib.import_module(f"search.RD.{args.nasspace}_RD_rk")
 RD = getattr(algo_module, "RD")
 RD_kwargs = {"searchspace": searchspace, "train_loader": train_loader, "device": device, "args": args, "acc_type": None, "Encoder": Encoder}
 if args.nasspace == "nasbench201":
     RD_kwargs["acc_type"] = acc_type
 
-taus = {"rk":[], "ni": [], "naswot": [], "logsynflow": [], "synflow":[]}
-times = {"rk":[], "ni":[], "naswot":[], "logsynflow":[], "synflow":[], "tot":[]}
+taus = {"rk":[], "ni": [], "naswot": [], "logsynflow": []}
+times = {"rk":[], "ni":[], "naswot":[], "logsynflow":[], "tot":[]}
 cnt = 0
 runs = trange(args.n_runs, desc='acc: ')
 for N in runs:
@@ -72,49 +72,44 @@ for N in runs:
     sol = RD(**RD_kwargs)
     bestuid_, taus_, maxacc, rk_maxacc, times_ = sol.search()
 
-    niuid, naswotuid, synflowuid, bestrk_uid = bestuid_
-    rk_tau, ni_tau, naswot_tau, synflow_tau = taus_
-    ni_time, naswot_time, synflow_time, rk_time = times_
+    niuid, naswotuid, logsynflowuid, bestrk_uid = bestuid_
+    rk_tau, ni_tau, naswot_tau, logsynflow_tau = taus_
+    ni_time, naswot_time, logsynflow_time, rk_time = times_
 
     taus['rk'].append(rk_tau)
     taus['ni'].append(ni_tau)
     taus['naswot'].append(naswot_tau)
-    #taus['logsynflow'].append(logsyn_tau)
-    taus['synflow'].append(synflow_tau)
+    taus['logsynflow'].append(logsyn_tau)
     
     try:
         niuid = int(niuid)
         naswotuid = int(naswotuid)
[…]

### 2023-06-08 SA_search.py

@@ -47,7 +47,7 @@ searchspace = nasspace.get_search_space(args)
 print(f"Making sure {args.save_loc} exist.")
 os.makedirs(args.save_loc, exist_ok=True)
 
-algo_module = importlib.import_module(f"search.{args.nasspace}_SA_rk")
+algo_module = importlib.import_module(f"search.SA.{args.nasspace}_SA_rk")
 SA = getattr(algo_module, "SA")
 SA_kwargs = {"searchspace": searchspace, "train_loader": train_loader, "acc_type": None, "device": device, "args": args}
 if args.nasspace == "nasbench201":

### 2023-06-08 search/RD/nasbench101_RD_rk.py

@@ -1,0 +1,23 @@
+import random
+import numpy as np
+import torch
+import sys
+import time
+from score import *
+from .RD_rk_abstract import abstract_RD
+
+class RD(abstract_RD):
+    def __init__(self, **kwargs):
+        super().__init__(**kwargs)
+
+    def search(self):
+        overhead_st = time.time()
+        cnt = 0
+        codebase = self.Encoder.get_nrand_code(self.args.n_samples)
+        indices = np.array([self.searchspace.query_index_by_arch(self.searchspace.get_spec_by_arch(*self.Encoder.parse_code(c[0], c[1], c[2]))) for c in codebase])
+        overhead = time.time() - overhead_st
+
+        bestuid, taus, maxacc, rk_maxacc, times = self.ranking(indices, [1,1,1], cnt)
+        times = tuple([x+overhead for x in times])
+
+        return bestuid, taus, maxacc, rk_maxacc, times

### 2023-06-08 search/RD/nasbench201_RD_rk.py

@@ -1,0 +1,23 @@
+import random
+import numpy as np
+import torch
+import sys
+import time
+from score import *
+from .RD_rk_abstract import abstract_RD
+
+class RD(abstract_RD):
+    def __init__(self, **kwargs):
+        super().__init__(**kwargs)
+
+    def search(self):
+        overhead_st = time.time()
+        cnt = 0
+        codebase = self.Encoder.get_nrand_code(self.args.n_samples)
+        indices = np.array([self.searchspace.get_index_by_code(self.Encoder.parse_code(c)) for c in codebase])
+        overhead = time.time() - overhead_st
+
+        bestuid, taus, maxacc, rk_maxacc, times = self.ranking(indices, [1,1,1], cnt)
+        times = tuple([x+overhead for x in times])
+
+        return bestuid, taus, maxacc, rk_maxacc, times

### 2023-06-08 search/RD/natsbenchsss_RD_rk.py

@@ -1,0 +1,23 @@
+import random
+import numpy as np
+import torch
+import sys
+import time
+from score import *
+from .RD_rk_abstract import abstract_RD
+
+class RD(abstract_RD):
+    def __init__(self, **kwargs):
+        super().__init__(**kwargs)
+
+    def search(self):
+        overhead_st = time.time()
+        cnt = 0
+        codebase = self.Encoder.get_nrand_code(self.args.n_samples)
+        indices = np.array([self.Encoder.parse_code(c) for c in codebase])
+        overhead = time.time() - overhead_st
+
+        bestuid, taus, maxacc, rk_maxacc, times = self.ranking(indices, [1,1,1], cnt)
+        times = tuple([x+overhead for x in times])
+
+        return bestuid, taus, maxacc, rk_maxacc, times

### 2023-06-08 search/SA/nasbench101_SA_rk.py

@@ -1,0 +1,30 @@
+import random
+import numpy as np
+import torch
+import sys
+from tqdm import trange
+import time
+from score import *
+from .SA_rk_abstract import abstract_SA
+from encoder import encoder
+
+class SA(abstract_SA):
+    def __init__(self, **kwargs):
+        super().__init__(**kwargs)
+        self.NAS_101_ops = ['conv_1x1', 'conv_3x3', 'maxpool']
+        self.Encoder = encoder.get_encoder("nasbench101")
+
+    def neighbor(self, arch):
+        random.shuffle(arch[1])
+        pos = random.sample([*range(0,5)], random.randint(0,5))
+        for p in pos:
+            arch[2][p] = (arch[2][p] + random.randint(0,2)) % 3
+        for i in range(len(arch)):
+            arch[i] = tuple(arch[i])
+        return arch
+
+    def rand_arch_generate(self):
+        return self.Encoder.get_rand_code()
+
+    def list2arch(self, l):
+        return self.searchspace.get_spec_by_arch(*self.Encoder.parse_code(list(l[0]), list(l[1]), list(l[2])))

### 2023-06-08 search/SA/nasbench201_SA_rk.py

@@ -1,0 +1,26 @@
+import random
+import numpy as np
+import torch
+import sys
+from tqdm import trange
+import time
+from score import *
+from .SA_rk_abstract import abstract_SA
+
+class SA(abstract_SA):
+    def __init__(self, **kwargs):
+        super().__init__(**kwargs)
+        self.NAS_201_ops = ['none', 'skip_connect', 'nor_conv_1x1', 'nor_conv_3x3', 'avg_pool_3x3']
+
+    def neighbor(self, arch):
+        new_arch = arch
+        pos = random.sample([*range(6)], random.randint(0, 5))
+        for p in pos:
+            new_arch[p] = (new_arch[p] + random.randint(0, 4)) % 5
+        return new_arch
+
+    def rand_arch_generate(self):
+        return [random.choice([*range(5)]) for i in range(6)]
+
+    def list2arch(self, l):
+        return "|{}~0|+|{}~0|{}~1|+|{}~0|{}~1|{}~2|".format(*map(lambda op: self.NAS_201_ops[op], l))

### 2023-06-08 search/GA_rk_abstract.py
move to their dir

@@ -1,135 +1,0 @@
-from score import *
-import copy
-import random
-import os
-import numpy as np
-
-class chromosome():
-    def __init__(self, gene = None, fitness = None, acc = None, uid = None):
-        self.gene = gene
-        self.fitness = fitness
-        self.acc = acc
-        self.uid = uid
-
-class abstract_GA():
-    def __init__(self, searchspace, train_loader, device, args):
-        self.MAXN_POPULATION = args.maxn_pop
-        self.MAXN_ITERATION = args.maxn_iter
-        self.PROB_MUTATION = args.prob_mut
-        self.PROB_CROSS = args.prob_cr
-        self.DICT = {}
-        self.population = []
-        self.searchspace = searchspace
-        self.train_loader = train_loader
-        self.args = args
-        self.device = device
-        self.best_chrom = {"ni": chromosome(), "naswot": chromosome(), "logsynflow": chromosome()}
-        self.candiate = {"logsynflow":set(), "naswot":set(), "ni":set()}
-
-    def init_population(self):
-        #TODO
-        pass
-
-    def mutation(self, chrom):
-        #TODO
-        pass
-
-    def evaulate(self):
-        #TODO
-        pass
-
-    def crossover(self):
-        #TODO
-        pass
-
-    def uid2net(self, uid):
-        #TODO
-        pass
-
-    def select_2chrom_fromN(self, N=3):
-        cand = random.sample(self.population, N)
-        totrk = dict(zip([chrom.uid for chrom in cand], [0 for i in range(N)]))
-        rk_naswot     = sorted(cand, key = lambda x: x.fitness[0], reverse = True)
-        rk_ni         = sorted(cand, key = lambda x: x.fitness[1], reverse = True)
-        rk_logsynflow = sorted(cand, key = lambda x: x.fitness[2], reverse = True)
-        for rk, chrom in enumerate(rk_ni):
-            totrk[chrom.uid] += rk
-        
-        for rk, chrom in enumerate(rk_naswot):
-            totrk[chrom.uid] += rk
-
-        for rk, chrom in enumerate(rk_logsynflow):
-            totrk[chrom.uid] += rk
-
-        chosen = [*map(lambda x: x[0], sorted(totrk.items(), key = lambda x: x[1])[:2])]
-        res = [*filter(lambda x: x.uid == chosen[0] or x.uid == chosen[1], cand)]
-        return res
-
-    def add_candiates_by(self, idx, metrice):
[…]

### 2023-06-08 search/RD_rk_abstract.py

@@ -1,108 +1,0 @@
-import random
-import numpy as np
-import torch
-import os
-import sys
-from score import *
-from scipy.stats import kendalltau
-import time
-
-class abstract_RD():
-    def __init__(self, searchspace, train_loader, acc_type, Encoder, device, args):
-        self.searchspace = searchspace
-        self.train_loader = train_loader
-        self.device = device
-        self.args = args
-        self.acc_type = acc_type
-        self.Encoder = Encoder
-
-    def ranking(self, indices, weight, cnt):
-        rk_st = time.time()
-        scores = {"ni": [], "naswot": [], "logsynflow": []}
-        
-        ni_time = 0
-        naswot_time = 0
-        logsyn_time = 0
-        for uid in indices:
-            overhead_st = time.time()
-            try:
-                uid = int(uid)
-            except:
-                pass
-            network = self.searchspace.get_network(uid, self.args)
-            network = network.to(self.device)
-            overhead = time.time() - overhead_st
-
-            ni_st = time.time()
-            scores["ni"].append(ni_score(network, self.train_loader, self.device, self.args))
-            ni_time += time.time() - ni_st + overhead
-            
-            naswot_st = time.time()
-            scores["naswot"].append(naswot_score(network, self.train_loader, self.device, self.args))
-            naswot_time += time.time() - naswot_st + overhead
-            
-            logsyn_st = time.time()
-            scores["logsynflow"].append(logsynflow_score(network, self.train_loader, self.device))
-            logsyn_time += time.time() - logsyn_st + overhead
-
-            del network
-
-        totrk = dict(zip([uid for uid in indices], [0 for i in range(self.args.n_samples)]))
-        
-        m_ni = np.argsort(scores["ni"])
-        rk_ni = indices[m_ni]
-        for rk, id in enumerate(rk_ni):
-            totrk[id] += (self.args.n_samples - rk)
-        
-        m_naswot = np.argsort(scores["naswot"])
-        rk_naswot = indices[m_naswot]
-        for rk, id in enumerate(rk_naswot):
-            totrk[id] += (self.args.n_samples - rk)
-
-        m_logsyn = np.argsort(scores["logsynflow"])
-        rk_logsyn = indices[m_logsyn]
-        bestrk = np.inf
-        for rk, id in enumerate(rk_logsyn):
[…]

### 2023-06-08 search/SA_rk_abstract.py

@@ -1,119 +1,0 @@
-import random
-import numpy as np
-import torch
-import sys
-from tqdm import trange
-import time
-from score import *
-
-class abstract_SA():
-    def __init__(self, searchspace, train_loader, acc_type, device, args):
-        self.end_T = args.end_T
-        self.maxn_iter = args.maxn_iter
-        self.Rt = args.Rt
-        self.init_T = args.init_T
-        self.maxN = args.maxN
-        self.searchspace = searchspace
-        self.train_loader = train_loader
-        self.device = device
-        self.acc_type = acc_type
-        self.args = args
-        self.DICT = {}
-
-    def neighbor(self, arch):
-        #TODO
-        assert False, f"implemenation isn't completed"
-        pass
-    
-    def rand_arch_generate(self):
-        #TODO
-        assert False, f"implemenation isn't completed"
-        pass
-
-    def search(self):
-        now_arch = self.rand_arch_generate()
-        now_sol_uid = best_sol_uid = self.searchspace.query_index_by_arch(self.list2arch(now_arch))
-        T = self.init_T
-        while T > self.end_T:
-            for i in range(self.maxn_iter):
-                neighbors = set()
-                while len(neighbors) < self.maxN:
-                    neighbors.add(tuple(self.neighbor(list(now_arch))))
-                neighbors.add(tuple(now_arch))
-                
-                neighbors = list(neighbors)
-                now_uid = self.searchspace.query_index_by_arch(self.list2arch(now_arch))
-                indices = [self.searchspace.query_index_by_arch(self.list2arch(arch)) for arch in neighbors]
-                
-                # E
-                rk_ni, rk_naswot, rk_logsynflow, bestrk_uid, maxacc, rk_maxacc, ind_rk = self.ranking(np.array(indices), [1,1,1])
-
-                # trans
-                dt = ind_rk[indices.index(bestrk_uid)] - ind_rk[indices.index(now_uid)]
-                if np.log(random.uniform(0,1)) < dt/T:
-                    pass
-                else:
-                    now_sol_uid = bestrk_uid
-                    now_arch = neighbors[indices.index(bestrk_uid)]
-                
-                best_sol_uid = bestrk_uid
-
-            T *= self.Rt
[…]

### 2023-06-08 search/nasbench101_GA_rk.py

@@ -1,104 +1,0 @@
-from score import *
-import copy
-import random
-import os
-import numpy as np
-from .GA_rk_abstract import abstract_GA, chromosome
-from encoder import encoder
-import torch
-
-class GA(abstract_GA):
-    def __init__(self, **kwargs):
-        super().__init__(**kwargs)
-        self.MAXN_CONNECTION = 6
-        self.MAXN_OPERATION = 3
-        self.NAS_101_ops = ['conv1x1-bn-relu', 'conv3x3-bn-relu', 'maxpool3x3']
-        self.Encoder = encoder.get_encoder("nasbench101")
-        torch.autograd.set_detect_anomaly(True)
-
-    def init_population(self):
-        s = set()
-        while len(s) < self.MAXN_POPULATION:
-            bb, br, op = self.Encoder.get_rand_code()
-            bb, br, op = tuple(bb), tuple(br), tuple(op)
-            s.add((bb,br,op))
-        s = list(s)
-        for i in range(len(s)):
-            s[i] = list(s[i])
-            s[i][0], s[i][1], s[i][2] = list(s[i][0]), list(s[i][1]), list(s[i][2])
-        self.population = [chromosome(gene) for gene in s]
-
-    def evaluate(self):
-        for i in range(len(self.population)):
-            network, uid, acc = gene2net(self.population[i].gene, self.Encoder, self.searchspace, None, self.args.valid, self.args)
-            #del network
-            self.population[i].acc = acc
-            self.population[i].uid = uid
-            if self.population[i].uid not in self.DICT:
-                uid = self.population[i].uid
-                """ fitness: (naswot, ni, logsynflow) """
-                x = [naswot_score(network, self.train_loader, self.device, self.args), \
-                ni_score(network, self.train_loader, self.device, self.args), \
-                logsynflow_score(network, self.train_loader, self.device)]
-
-                self.population[i].fitness = self.DICT[uid] = tuple(x)
-            else:
-                self.population[i].fitness = self.DICT[self.population[i].uid]
-            del network
-            
-            # global optimum
-            if self.args.verbose:
-                if self.best_chrom["naswot"].gene == None or self.population[i].fitness[0] > self.best_chrom["naswot"].fitness[0]:
[…]

### 2023-06-08 search/nasbench101_RD_rk.py

@@ -1,23 +1,0 @@
-import random
-import numpy as np
-import torch
-import sys
-import time
-from score import *
-from .RD_rk_abstract import abstract_RD
-
-class RD(abstract_RD):
-    def __init__(self, **kwargs):
-        super().__init__(**kwargs)
-
-    def search(self):
-        overhead_st = time.time()
-        cnt = 0
-        codebase = self.Encoder.get_nrand_code(self.args.n_samples)
-        indices = np.array([self.searchspace.query_index_by_arch(self.searchspace.get_spec_by_arch(*self.Encoder.parse_code(c[0], c[1], c[2]))) for c in codebase])
-        overhead = time.time() - overhead_st
-
-        bestuid, taus, maxacc, rk_maxacc, times = self.ranking(indices, [1,1,1], cnt)
-        times = tuple([x+overhead for x in times])
-
-        return bestuid, taus, maxacc, rk_maxacc, times

### 2023-06-08 search/nasbench101_SA_rk.py

@@ -1,30 +1,0 @@
-import random
-import numpy as np
-import torch
-import sys
-from tqdm import trange
-import time
-from score import *
-from .SA_rk_abstract import abstract_SA
-from encoder import encoder
-
-class SA(abstract_SA):
-    def __init__(self, **kwargs):
-        super().__init__(**kwargs)
-        self.NAS_101_ops = ['conv_1x1', 'conv_3x3', 'maxpool']
-        self.Encoder = encoder.get_encoder("nasbench101")
-
-    def neighbor(self, arch):
-        random.shuffle(arch[1])
-        pos = random.sample([*range(0,5)], random.randint(0,5))
-        for p in pos:
-            arch[2][p] = (arch[2][p] + random.randint(0,2)) % 3
-        for i in range(len(arch)):
-            arch[i] = tuple(arch[i])
-        return arch
-
-    def rand_arch_generate(self):
-        return self.Encoder.get_rand_code()
-
-    def list2arch(self, l):
-        return self.searchspace.get_spec_by_arch(*self.Encoder.parse_code(list(l[0]), list(l[1]), list(l[2])))

### 2023-06-08 search/nasbench201_GA_rk.py

@@ -1,99 +1,0 @@
-from score import *
-import copy
-import random
-import os
-import numpy as np
-from .GA_rk_abstract import abstract_GA, chromosome
-
-class GA(abstract_GA):
-    def __init__(self, **kwargs):
-        self.acc_type = kwargs["acc_type"]
-        del kwargs["acc_type"]
-        super().__init__(**kwargs)
-        self.MAXN_CONNECTION = 6
-        self.MAXN_OPERATION = 5
-        self.NAS_201_ops = ['none', 'skip_connect', 'nor_conv_1x1', 'nor_conv_3x3', 'avg_pool_3x3']
-
-    def init_population(self):
-        self.population = [chromosome("".join([(bin(1<<random.randint(0, self.MAXN_OPERATION-1))[2:]).zfill(self.MAXN_OPERATION) for j in range(self.MAXN_CONNECTION)])) for i in range(self.MAXN_POPULATION)]
-
-    def evaluate(self):
-        for i in range(len(self.population)):
-            network, uid, acc = gene2net(self.population[i].gene, self.NAS_201_ops, self.searchspace, self.acc_type, self.args.valid, self.args)
-            #del network
-            self.population[i].acc = acc
-            self.population[i].uid = uid
-            if self.population[i].uid not in self.DICT:
-                uid = self.population[i].uid
-                """ fitness: (naswot, ni, logsynflow) """
-                x = [naswot_score(network, self.train_loader, self.device, self.args), \
-                ni_score(network, self.train_loader, self.device, self.args), \
-                logsynflow_score(network, self.train_loader, self.device)]
-
-                self.population[i].fitness = self.DICT[uid] = tuple(x)
-            else:
-                self.population[i].fitness = self.DICT[self.population[i].uid]
-            del network
-            
-            # global optimum
-            if self.args.verbose:
-                if self.best_chrom["naswot"].gene == None or self.population[i].fitness[0] > self.best_chrom["naswot"].fitness[0]:
-                    self.best_chrom["naswot"].fitness = self.population[i].fitness
-                    self.best_chrom["naswot"].acc = self.population[i].acc
-                    self.best_chrom["naswot"].uid = self.population[i].uid
[…]

### 2023-06-08 search/nasbench201_RD_rk.py

@@ -1,23 +1,0 @@
-import random
-import numpy as np
-import torch
-import sys
-import time
-from score import *
-from .RD_rk_abstract import abstract_RD
-
-class RD(abstract_RD):
-    def __init__(self, **kwargs):
-        super().__init__(**kwargs)
-
-    def search(self):
-        overhead_st = time.time()
-        cnt = 0
-        codebase = self.Encoder.get_nrand_code(self.args.n_samples)
-        indices = np.array([self.searchspace.get_index_by_code(self.Encoder.parse_code(c)) for c in codebase])
-        overhead = time.time() - overhead_st
-
-        bestuid, taus, maxacc, rk_maxacc, times = self.ranking(indices, [1,1,1], cnt)
-        times = tuple([x+overhead for x in times])
-
-        return bestuid, taus, maxacc, rk_maxacc, times

### 2023-06-08 search/nasbench201_SA_rk.py

@@ -1,26 +1,0 @@
-import random
-import numpy as np
-import torch
-import sys
-from tqdm import trange
-import time
-from score import *
-from .SA_rk_abstract import abstract_SA
-
-class SA(abstract_SA):
-    def __init__(self, **kwargs):
-        super().__init__(**kwargs)
-        self.NAS_201_ops = ['none', 'skip_connect', 'nor_conv_1x1', 'nor_conv_3x3', 'avg_pool_3x3']
-
-    def neighbor(self, arch):
-        new_arch = arch
-        pos = random.sample([*range(6)], random.randint(0, 5))
-        for p in pos:
-            new_arch[p] = (new_arch[p] + random.randint(0, 4)) % 5
-        return new_arch
-
-    def rand_arch_generate(self):
-        return [random.choice([*range(5)]) for i in range(6)]
-
-    def list2arch(self, l):
-        return "|{}~0|+|{}~0|{}~1|+|{}~0|{}~1|{}~2|".format(*map(lambda op: self.NAS_201_ops[op], l))

### 2023-06-08 search/natsbenchsss_GA_rk.py

@@ -1,80 +1,0 @@
-from score import *
-import copy
-import random
-import os
-import numpy as np
-from .GA_rk_abstract import abstract_GA, chromosome
-
-class GA(abstract_GA):
-    def __init__(self, **kwargs):
-        super().__init__(**kwargs)
-        self.NATS_SSS_ops = [8, 16, 24, 32, 40, 48, 56, 64]
-
-    def init_population(self):
-        self.population = [chromosome(random.sample(range(0, 8), k=5)) for i in range(self.MAXN_POPULATION)]
-
-    def evaluate(self):
-        for i in range(len(self.population)):
-            network, uid, acc = gene2net(self.population[i].gene, self.NATS_SSS_ops, self.searchspace, None, self.args.valid, self.args)
-            #del network
-            self.population[i].acc = acc
-            self.population[i].uid = uid
-            if self.population[i].uid not in self.DICT:
-                uid = self.population[i].uid
-                """ fitness: (naswot, ni, logsynflow) """
-                x = [naswot_score(network, self.train_loader, self.device, self.args), \
-                ni_score(network, self.train_loader, self.device, self.args), \
-                logsynflow_score(network, self.train_loader, self.device)]
-
-                self.population[i].fitness = self.DICT[uid] = tuple(x)
-            else:
-                self.population[i].fitness = self.DICT[self.population[i].uid]
-            del network
-            
-            # global optimum
-            if self.args.verbose:
-                if self.best_chrom["naswot"].gene == None or self.population[i].fitness[0] > self.best_chrom["naswot"].fitness[0]:
-                    self.best_chrom["naswot"].fitness = self.population[i].fitness
-                    self.best_chrom["naswot"].acc = self.population[i].acc
-                    self.best_chrom["naswot"].uid = self.population[i].uid
-                    self.best_chrom["naswot"].gene = copy.deepcopy(self.population[i].gene)
-                if self.best_chrom["ni"].gene == None or self.population[i].fitness[1] > self.best_chrom["ni"].fitness[1]:
-                    self.best_chrom["ni"].fitness = self.population[i].fitness
-                    self.best_chrom["ni"].acc = self.population[i].acc
-                    self.best_chrom["ni"].uid = self.population[i].uid
[…]

### 2023-06-08 search/natsbenchsss_RD_rk.py

@@ -1,23 +1,0 @@
-import random
-import numpy as np
-import torch
-import sys
-import time
-from score import *
-from .RD_rk_abstract import abstract_RD
-
-class RD(abstract_RD):
-    def __init__(self, **kwargs):
-        super().__init__(**kwargs)
-
-    def search(self):
-        overhead_st = time.time()
-        cnt = 0
-        codebase = self.Encoder.get_nrand_code(self.args.n_samples)
-        indices = np.array([self.Encoder.parse_code(c) for c in codebase])
-        overhead = time.time() - overhead_st
-
-        bestuid, taus, maxacc, rk_maxacc, times = self.ranking(indices, [1,1,1], cnt)
-        times = tuple([x+overhead for x in times])
-
-        return bestuid, taus, maxacc, rk_maxacc, times

### 2023-06-08 search/natsbenchsss_SA_rk.py

@@ -1,26 +1,0 @@
-import random
-import numpy as np
-import torch
-import sys
-from tqdm import trange
-import time
-from score import *
-from .SA_rk_abstract import abstract_SA
-
-class SA(abstract_SA):
-    def __init__(self, **kwargs):
-        super().__init__(**kwargs)
-        self.NATS_SSS_ops = [8, 16, 24, 32, 40, 48, 56, 64]
-
-    def neighbor(self, arch):
-        new_arch = arch
-        pos = random.sample([*range(5)], random.randint(0, 5))
-        for p in pos:
-            new_arch[p] = (new_arch[p] + random.randint(0, 7)) % 8
-        return new_arch
-        
-    def rand_arch_generate(self):
-        return [random.choice([*range(8)]) for i in range(5)]
-
-    def list2arch(self, l):
-        return "{}:{}:{}:{}:{}".format(*map(lambda op: self.NATS_SSS_ops[op], l))

### 2023-06-08 paper/main.tex
update paper

@@
 
+\algrenewcommand\alglinenumber[1]{\footnotesize #1}
+
+\algnewcommand\algorithmicassume{\textbf{Assumption:}}
+\algnewcommand\Assume{\item[\algorithmicassume]}
+
+\algnewcommand\algorithmicinput{\textbf{Input:}}
+\algnewcommand\Input{\item[\algorithmicinput]}
+
 \begin{document}
@@
     % To evaluate
-    Although the training-free NASs are typically faster than training-based 
-    NAS method, however, the correlation between score value and the result 
-    of an architecture is not well enough in most cases.
-    To address this problem, we propose a genetic-based training-free NAS 
-    algorithm with hybrid training-free score function, which combines three 
-    highly heterogeneous training-free score functions to evaluate an architecture. 
-    In this method, the genetic algorithm plays a role to guide the searches 
-    of NAS algorithm while the hybrid training-free score function plays the 
-    role to evaluate a new candidate architecture during the convergence process 
-    of GA. More precisely, the first score function is noise immunity (NI), as 
-    an evaluation of the ability to tolerate noise, second one is NASWOT score, as 
-    an measurement of the pattern recognition ability, finally, the last one is 
-    LogSynFlow score, as an evaluation of trainability.
-
+    Although the training-free neural architecture search (NAS) are typically 
+    faster than training-based NAS methods, however, the correlation between 
+    the measurement and the final accuracy of an architecture is not well 
+    enough in most cases. 
+    To address this problem, we propose a rank-based training-free NAS 
+    algorithm, which combines three complement training-free score functions 
+    to evaluate an architecture by ranking. 
+    More precisely, noise immunity (NI) and the correlation between binary 
+    activation paterns, named as NASWOT, are used as measurement of image recognition 
+    ability, and, SynFlow are used as measurement of trainability. 
+    With that, a modified version of simulated annealing (SA) algorithm 
+    can applies on and obtains a better performance on searching high accuracy 
+    architectures. 
     To evaluate the performance of the proposed algorithm, this paper compared 
@@
     non-weight-sharing methods, and several state-of-the-art training-free score 
-    functions. 
-    The final result shows that in relatively larger search space, like nats-bench sss, the 
-    proposed algorithm outperforms most of NAS methods.
+    functions. The final result shows that in relatively larger search space, 
+    like NATS-Bench SSS, the proposed algorithm outperforms most of NAS methods.
 
@@
     potential architectures, to find out a good architectures that outperform 
-    those designed by human experts. "In recent years", the use of NAS is 
+    those designed by human experts. Recently, the use of NAS is 
     widespread, from object detection \cite{https://doi.org/10.48550/arxiv.2111.13336}, 
@@
     search without training (NASWOT). 
-    % logsynflow
+    % synflow
     On the other hand, Lee et al. \cite{lee2019snip} proposed purning parameters based on a saliency matric, 
@@
     % NTK
-    For another example, Chen et al. proposed to compute the condition 
-    number of neural tangent kernel (NTK) \cite{https://doi.org/10.48550/arxiv.2102.11535} 
-    \cite{https://doi.org/10.48550/arxiv.2203.09137} \cite{https://doi.org/10.48550/arxiv.2109.00817}, 
-    which is used as the score to estimate the trainability of an architecture.
+    For another example, Chen et al. \cite{https://doi.org/10.48550/arxiv.2102.11535} proposed to compute the condition 
+    number of neural tangent kernel (NTK) \cite{https://doi.org/10.48550/arxiv.2203.09137} 
+    \cite{https://doi.org/10.48550/arxiv.2109.00817}, which is used as the score to estimate the trainability of an 
+    architecture.
 
 % what is unknown?
+    % table放第一頁 不然就不要放
+    % 做成圖表放第一頁
     However, \xtab{table:corr_score} shows most of score functions suffer from low correlation between 
-    score value and the final accuracy of an architecture, leading to a predicament 
+    score values and the final accuracy of architectures, leading to a predicament 
     that no matter how good the search method is used, we can hardly find 
@@
     function can only evaluate one perspect/characteristic of an architecture. 
-    \begin{table*}[htb]
-        \caption{\textsc{The Kendall and Spearman correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench \cite{Dong_2021}. 
-        Each metric has been computed three times with different initialisations and the average is taken as final score. The data is from \cite{Cavagnero_2023}.}}
-        \begin{tabular}{ccccccc}\toprule
-            Training-free score function & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ 
-            \cmidrule(lr){2-3}\cmidrule(lr){4-5}\cmidrule(lr){6-7} & Kendall & Spearman & Kendall & Spearman & Kendall & Spearman \\ \midrule
-            \bf{NTK} & -0.33 & -0.49 & -0.30 & -0.45 & -0.39 & -0.56 \\
-            \bf{Snip} & 0.45 & 0.61 & 0.47 & 0.62 & 0.41 & 0.55 \\
-            \bf{Fisher} & 0.39 & 0.54 & 0.40 & 0.55 & 0.36 & 0.48 \\
-            \bf{Grasp} & 0.28 & 0.41 & 0.35 & 0.50 & 0.35 & 0.49 \\
-            \bf{NASWOT} & 0.61 & 0.79 & 0.62 & 0.81 & 0.60 & 0.78 \\
-            \bf{SynFlow} & 0.57 & 0.77 & 0.56 & 0.76 & 0.56 & 0.75 \\
-            \bf{LogSynFlow} & 0.61 & 0.81 & 0.60 & 0.79 & 0.59 & 0.78 \\ \bottomrule
+    \begin{table}[tb]
+        \caption{\textsc{The Kendall correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench \cite{Dong_2021}. 
+        Each metric has been computed three times with different initialisations and the average is taken as final score.}}
+        \resizebox{0.48\textwidth}{!}{
+            \begin{tabular}{cccc}\toprule
+                Training-free score function & CIFAR-10 & CIFAR-100 & ImageNet-16-120 \\ 
+                \midrule
+                \bf{NTK}                     & -0.33    & -0.30     & -0.39 \\
+                \bf{Snip}                    & 0.45     & 0.47      & 0.41  \\
+                \bf{Fisher}                  & 0.39     & 0.40      & 0.36  \\
+                \bf{Grasp}                   & 0.28     & 0.35      & 0.35  \\
+                \bf{NASWOT}                  & 0.61     & 0.62      & 0.60  \\
+                \bf{SynFlow}                 & 0.57     & 0.56      & 0.56  \\
+                \bf{LogSynFlow}              & 0.61     & 0.60      & 0.59  \\
+                \bf{Rank-Based (ours)}       & X        & X         & X     \\ \bottomrule
                 \label{table:corr_score}
@@
             \end{tabular}
-    \end{table*}
-
-% method
-    To address the problem, we propose cooperating three heterogeneous score 
-    functions with rank-based search method, which evaulate an architecture 
-    from different aspects. More specifically, the first score function is 
-    NI \cite{10092788} as an indicator of the ability to distinguish two images. 
-    The second one is NASWOT as score to estimate the ability of expression 
-    of an architecture. The last one is logsynflow used as the measurement of 
-    trainability. 
-    By combining these three training-free score functions, this paper also 
-    compares the different search algorithms, e.g., random search, genetic 
-    algorithm (GA) \cite{mitchell1998introduction}, simulated annealing algorithm (SA)
-    \cite{kirkpatrick1983optimization}.
-
-    % conclusion
-    The major contribution of this paper can be summarized as follow:
-    \begin{itemize}
-        \item Cooperating three score functions to obtain better ability for searching top accuracy neural architectures. 
-        \item Develope a rank-based neural architecture search with several search algorithms. 
-    \end{itemize}
-    % expect what
-
-    The remainder of this paper is organized as follows: \xsec{sec:related_work} provides the 
-    detail about the three heterogeneous score functions. \xsec{sec:proposed} gives a detailed 
-    description about the proposed method. \xsec{sec:results} begins with parameters setting and 
-    provide the simulation results following is the experiment results in different search space. 
-    The conclusion and further prospect are gived in \xsec{sec:conclusion}.
-
-    \section{Related Works}
-    \label{sec:related_work}
-    \subsection{Training-free Score Function}
-    % naswot
-    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. proposed a 
-    score function without the requirement for training which is named neural 
-    architecture search without training (NASWOT). \xfig{fig:naswot} 
-	gives a simple example to illustrate the procedure of NASWOT score function. 
-    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
-    architecture as $f(x_i)$. The activated ReLU units in every layer of the architecture 
-    form a binary code $c_i$ that define the linear region.
-    The correlation between binary codes for the whole mini-batch can be examined 
-    by computing the kernel matrix 
-    \begin{equation}
-        K_H=\begin{pmatrix}N_A-d_H(c_1,c_2)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_1)\end{pmatrix}
-    \end{equation}
-    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
-    distance between the binary code $c_i$ and $c_j$. 
-    With the kernel matrix, the score of an architecture can be evaluate as 
-    follow: 
-    \begin{equation}
-        s=\log\lvert K_H\rvert
-    \end{equation}
-    The rationale behind is to see how dissimilar the linear region activated by 
-    the ReLU units between two inputs. An architecture shall learn better 
-    when inputs are well separated.
-
-    \begin{figure*}[!htb]
+        }
+    \end{table}
+    \begin{figure*}[b]
         \vspace{-\baselineskip}
@@
     \end{figure*}
+% method
+    To address the problem, we propose cooperating three complement score 
+    functions by ranking, which allows every score functions evaluate an 
+    architecture without losing fairness. 
+    The first score function is noise immunity (NI) \cite{10092788}, as 
+    an indicator of the ability to distinguish two images. 
+    The second one is NASWOT, as score to estimate the ability of expression 
+    of an architecture and also a complement of NI. 
+    The last one is SNIP used as the measurement of trainability and 
+    also as a complement to NI and NASWOT. 
+    With these three complement score functions, an evaluation of an 
+    architecture is not simply from a single aspect but three different 
+    aspects, which is like estimate the weight of an object by not only 
+    the length but its height and width. 
+    %compares the different search algorithms for NAS, e.g., random search, genetic 
+    %algorithm (GA) \cite{mitchell1998introduction}, simulated annealing algorithm (SA)
+    %\cite{kirkpatrick1983optimization}.
 
-    % ni
+    % conclusion
+    %The major contribution of this paper can be summarized as follow:
+    %\begin{itemize}
+    %    \item Cooperating three score functions to obtain better ability for searching top accuracy neural architectures. 
+    %    \item Develope simulated annealing algorithms with rank-based score. 
+    %\end{itemize}
+    % expect what
+
+    The remainder of this paper is organized as follows: \xsec{sec:related_work} provides the 
+    detail about the three complement score functions. \xsec{sec:proposed} gives a detailed 
+    description about the proposed method. \xsec{sec:results} begins with parameters setting and 
+    provide the simulation results following is the experiment results in different search space. 
+    The conclusion and further prospect are gived in \xsec{sec:conclusion}.
+
+    \section{Related Works}
+    \label{sec:related_work}
+    \subsection{Training-free Score Functions}
+    % naswot 對圖描述多一點
+    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. proposed a 
+    score function without the requirement for training which is named neural 
+    architecture search without training (NASWOT). \xfig{fig:naswot} 
+	gives a simple example to illustrate the procedure of NASWOT score function. 
+    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
+    architecture. The activated ReLU units in every layer of the architecture 
+    form a binary code $c_i$ that define the linear region.
+    The correlation between binary codes for the whole mini-batch can be examined 
+    by computing the kernel matrix 
+    \begin{equation}
+        K_H=\begin{pmatrix}N_A-d_H(c_1,c_1)&\cdots&N_A-d_H(c_1,c_N)\\\vdots&\ddots&\vdots\\N_A-d_H(c_N,c_1)&\cdots&N_A-d_H(c_N,c_N)\end{pmatrix},
+    \end{equation}
+    where $N_A$ is the number of ReLU units and $d_H(c_i,c_j)$ is the hamming 
+    distance between the binary code $c_i$ and $c_j$. 
+    With the kernel matrix, the score of an architecture can be evaluated as 
+    follow: 
+    \begin{equation}
+        s=\log\lvert K_H\rvert,
+    \end{equation}
+    The rationale behind is that, the more different between the binary codes 
+    the better the architecture learns. And the determinant of the kernel matrix 
+    measures how "different" they are by calculating the volume formed by the 
+    row vector of $K_H$.
+
+    %to see how dissimilar the linear region activated by 
+    %the ReLU units between two inputs. An architecture shall learn better 
+    %when inputs are well separated.
+
+    % ni 對圖描述多一點
     Wu et al. \cite{10092788} found, in some case, an architecture with high 
@@
     evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
-    noise immunity score evaluate an architecture. The score function picks a 
+    noise immunity evaluate an architecture. The score function picks a 
     mini-batch of data, denoted $X$, and then applies Gaussion noise on it. 
@@
 
-    \begin{figure*}[!hb]
+    \begin{figure*}[tb]
         \vspace{-\baselineskip}
@@
 
-    % logsynflow
-    Besides from these two model-dependent aspects, Tanaka et al. \cite{tanaka2020pruning} 
-    generalized synaptic saliency scores, and proposed SynFlow algorithm to avoids layer 
-    collapse when performing purning. 
-    Inspired from \cite{tanaka2020pruning}, \cite{wang2020picking}, \cite{lee2019snip}, 
-    Abdelfattah et al. \cite{abdelfattah2021zerocost} proposed summing synaptic saliency scores 
-    over all parameters in the model as an accuracy estimator to a architecture.
-
-    Besides from these two model-dependent aspects, roots from The Lottery Ticket Hypothesis 
-    \cite{frankle2019lottery}, saliency matric is used on purning network parameters in 
-    \cite{lee2019snip}, which can be formula as 
+    % synflow
+    % 再調
+    Besides from these two image-related aspects, there is another aspect to evaluate  
+    a network. 
+    \textit{The Lottery Ticket Hypothesis} \cite{frankle2019lottery}, reveals that a 
+    network may have a "core" which decides the final accuracy of the network. 
+    How to pruning a network correctly is therefore tempting. Lee et al. 
+    \cite{lee2019snip} proposed to use connection sensitivity as a criterion to prune 
+    the network which can be briefly viewed as 
     \begin{equation}
-        \label{equ:snip}
-        S_p(\theta)=\lvert\frac{\partial \mathcal L}{\partial \theta}\odot\theta\rvert
+        \label{equ:snip_connection_sensitivity}
+        s_j=\lvert w_j\frac{\partial L}{\partial w_j}\rvert,
     \end{equation}
-    where $\mathcal L$ is the loss function of a neural network with parameters $\theta$ 
-    and $\theta$ is the Hadamard product. 
-    The saliency matric approximates the change in loss when purning a specific parameters.
-    Later, Wang et al. \cite{wang2020picking} approximates the change in gradient norm when 
-    purning the network, which defined as 
+    where $\textbf{w}$ is the weight of the netwrok, $w_j$ the $j$-th element of 
+    $\textbf{w}$. The meaning behind is to approximate the contribution 
+    to the change of the loss function from a specific connection. By pruning the 
+    connections which has relatively small contribution, the expensive prune, retrain 
+    cycles, can be prevented. 
+    Later, Wang et al. \cite{wang2020picking} noticed that SNIP with a high pruning ratio 
+    tends to cause layer-collapse, which prune all parameters in a single weight layer. 
+    Therefore, they propose to approximate the change in gradient norm which defined as 
     \begin{equation}
         \label{equ:grap}
-        S_p(\theta)=-(H\frac{\partial \mathcal L}{\partial \theta})\odot\theta
+        S_p(\bf{\theta})=-(H\frac{\partial \mathcal L}{\partial \bf{\theta}})\odot\bf{\theta},
     \end{equation}
-    where $\mathcal L$ is the change in gradient norm instead of loss function and $H$ is 
-    the Hessian. 
+    where $H$ is the Hessian matrix, $\bf{\theta}$ the parameters, and $\odot$ is Hadamard product. 
     In \cite{tanaka2020pruning}, Tanaka et al. generalized the synaptic saliency scores as 
@@
         \label{equ:synflow}
-        S_p(\theta)=\frac{\partial \mathcal L}{\partial \theta}\odot\theta
+        S_p(\theta)=\frac{\partial \mathcal L}{\partial \theta}\odot\theta,
     \end{equation}
@@
 
-    \subsection{Search Algorithm}
+    \subsection{Search Algorithms}
     First assume that input data $D$ are separated into two subset, $D_r$ and $D_t$. Further more, 
-    assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $A_s$ the 
+    assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $\mathcal A_s$ the 
     search algorithm of NAS, and $\mathcal A_L$ the learning algorithm. Then, NAS problem can be 
@@
     \end{equation}
-    It can be seen that training-free NAS is comprised of two part, search algorithm $A_S$ and score 
-    function $F_S$. 
+    It can be seen that training-free NAS is comprised of two part, search algorithm $\mathcal A_S$ and score 
+    function $\mathcal F_S$. 
     There are several search algorithms applied on NAS, including random search, reinforcement learning, and
@@
 
-    And in \cite{10.1145/3491396.3506510}, Wu et al. leveraged genetic algorithm (GA) as search strategy. 
+    As for an example of metaheuristic algorithm, in \cite{10.1145/3491396.3506510}, Wu et al. leveraged 
+    genetic algorithm (GA) as search strategy. 
     By encoding the network architecture, the architecture can be viewed as gene. Therefore, GA can be 
@@
     \end{itemize}
+    Based on these design, SE can avoid fall into local optimum, while search for high expected value instead.
 
-    \section{The Proposed Algorithm}
+    \section{Methods}
     \label{sec:proposed}
-    In this work,
+    \subsection{Motivation}
+    The motivation origins from these three questions:
+
+    \textit{1. Can we combine multiple score functions to improve the correlation between score values and the final accuracy of architectures?}
+
+    The answer is yes. It's konwn that if the chosen score functions can complement with 
+    each others, the new correlation can eventually beyond the original ones. \cite{10.1145/3491396.3506510} 
+    shows that possibility. When an architecture gain a high NASWOT score, it may classify 
+    images, which are in the same class originally, into different classes. NI here comes 
+    to rescue. By measuring the noise immunity of an architecture, the miss-classifying 
+    can be solved. Thus, if mix NASWOT with NI, the correlation increases. An example 
+    is shown in \xfig{fig:ninaswot}.
+    \begin{figure*}[htb]
+        \vspace{-\baselineskip}
+        \begin{center}
+            \begin{tabular}{ccc}
+                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/naswot-acc.pdf}}}
+                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ni-acc.pdf}}}
+                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ninaswot-acc.pdf}}}
+            \end{tabular}
+            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NAS-Bench-201 in the CIFAR-10 dataset 
+            (b) NI score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset. 
+            (c) NI score + NASWOT score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset.}
+            \label{fig:ninaswot}
+        \end{center}
+        \vspace{-\baselineskip}
+    \end{figure*}
+
+    \textit{2. How to combine multiple different kinds of score functions together and prevent one from overwhelming the others numerically?}
+
+    One possible way is normalization, but the necessary information is known only 
+    after evaluating the whole search space, e.g., range, mean or standard deviation, which is practically 
+    impossible. In order to achieve the goal, the proposed score function, named rank-based NAS, leverage 
+    multiple score functions by ranking, which provides a solution to have equal contribution from each 
+    score function.
+
+    \textit{3. How to choose the score functions?}
+
+    As mentioned, the key is to choose the complement of a score function. For example, 
+    NASWOT and NI. And for NASWOT and NI, which are both description of the ability of 
+    the graphic recognition of an architecture. The complement of them can be a measurement 
+    of trainability, e.g., SynFlow, NTK, which means whether this architecture is easy to 
+    train or not.
+
+    \subsection{Rank-Based Score Function}
+    \begin{algorithm}[h]
+        \caption{The Rank Algorithm}\label{alg:rank-based}
+        \begin{algorithmic}[1]
+            \Input ${\mathbb N}^{s}\subset{\mathbb N}^{*}$
+            \For{$\text{each }{\mathbb N}^i\text{ in }{\mathbb N}^s$}
+                \For{$\text{each }j\in\{1,\ldots,M\}$}
+                    \State $s_{{\mathcal F}_{j}}({\mathbb N}^i)={\mathcal F}_{j}({\mathbb N}^i)$
+                \EndFor
+            \EndFor
+            \For{$\text{each }j\in\{1,\ldots,M\}$}
+                \State $r_{{\mathcal F}_{j}}({\mathbb N}^i)$ = index of ${\mathbb N}^i$ in list $[s_{{\mathcal F}_{j}}({\mathbb N}^1),\ldots,s_{{\mathcal F}_{j}}({\mathbb N}^{\lvert {\mathbb N}^s\rvert})]$ \par sorted by descending order
+            \EndFor
+            \State $r({\mathbb N}^i)=\sum^M_{j=0} r_{{\mathcal F}_{j}}({\mathbb N}^i)$
+            \State $i^*=\arg\min_{i}\{r({\mathbb N}^i)\}$
+            \State $\textbf{Return }{\mathbb N}^{i^*}$
+        \end{algorithmic}
+    \end{algorithm}
+
+    The proposed rank-based score function is outlined in \xalg{alg:rank-based}. The first step is to evaluate the 
+    network architectures in the subset, denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The evaluation 
+    of an architecture determined by $j$-th score function is denoted $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating 
+    the subset of search space, the rank of each score function is calculated, denoted $r_{\mathcal F}$. Then the final 
+    rank, $r$, calculated by summing up the ranks. 
+    If a network architecture gains higher score in these score functions, the final rank should be higher (smaller index) too. 
+    Therefore, the highest (minimum) rank in $r$ shall be the best network architecture. In summary, the rank-based score 
+    function makes the contribution of each score function even.
+
+    \subsection{Simulated Annealing with Rank-Based Score function}
+
+    \begin{figure*}[htb]
+        \centering
+        \hspace*{-\baselineskip}
+        \vspace*{-\baselineskip}
+        \includegraphics[]{asset/SA.pdf}
+        \caption{A simple example to illustrate an iteration of SA with Rank-based score function.}
+        \label{fig:SA}
+    \end{figure*}
+
+    \xfig{fig:SA} illustrates how SA with rank-based score function works in an iteration.
 

### 2023-06-10 RD_search.py
fix typo

@@ -79,7 +79,8 @@ for N in runs:
     taus['rk'].append(rk_tau)
     taus['ni'].append(ni_tau)
     taus['naswot'].append(naswot_tau)
-    taus['logsynflow'].append(logsyn_tau)
+    taus['logsynflow'].append(logsynflow_tau)
+    #print(taus)
     
     try:
         niuid = int(niuid)

### 2023-06-10 encoder/encoder.py
get_rand_code will return tuple

@@ -89,7 +89,7 @@ class nasbench101_encoder:
     def get_rand_code(self):
         operations = self.get_rand_operations()
         backbone,branch = self.get_rand_backbone_branch()
-        return backbone,branch,operations
+        return tuple(backbone),tuple(branch),tuple(operations)
     
     def get_nrand_code(self, n):
         s = set()

### 2023-06-10 nasspace.py
use natsbench tss api instead of nasbench201, 'cause it's so slow

@@ -327,6 +327,15 @@ class NatsbenchTSS:
     def __getitem__(self, index):
         return index
 
+    def get_index_by_code(self,code):
+        node_str = "|{}~0|+|{}~0|{}~1|+|{}~0|{}~1|{}~2|".format(*[self.operations[c] for c in code[:6]])
+        index = self.api.query_index_by_arch(node_str)
+        return index
+
+    def get_arch_str_by_code(self,code):
+        node_str = "|{}~0|+|{}~0|{}~1|+|{}~0|{}~1|{}~2|".format(*[self.operations[c] for c in code[:6]])
+        return node_str
+
     def query_index_by_arch(self, arch):
         return self.api.query_index_by_arch(arch)
 
@@ -444,7 +453,8 @@ class NDS:
 
 def get_search_space(args):
     if args.nasspace == 'nasbench201':
-        return Nasbench201(args.dataset, args.api_loc)
+        #return Nasbench201(args.dataset, args.api_loc)
+        return NatsbenchTSS(args.dataset, args.api_loc, args)
     elif args.nasspace == 'nasbench101':
         return Nasbench101(args.dataset, args.api_loc, args)
     elif args.nasspace == 'natsbenchsss':

### 2023-06-10 score/logsynflow_score.py
bug fix

@@ -34,8 +34,8 @@ def logsynflow_score(network, train_loader, device):
     
     def synflow(layer):
         if layer.weight.grad is not None:
-            res = torch.abs(torch.log(layer.weight.grad)) * layer.weight
-            res = res[res.isfinite()]
+            res = torch.abs(torch.log(layer.weight.grad+1) * layer.weight)
+            #res = res[res.isfinite()]
             return res
         else:
             return torch.zeros_like(layer.weight)
@@ -45,11 +45,4 @@ def logsynflow_score(network, train_loader, device):
         if isinstance(layer, nn.Conv2d) or isinstance(layer, nn.Linear):
             score += torch.sum(synflow(layer))
 
-    """
-    for p in parameters():
-        scores[id(p)] = torch.clone(np.log(p.grad) * p).detach().abs_().cpu().numpy()
-        p.grad.data.zero_()
-    """
-
-    nonlinearize(network, signs)
     return score.detach().cpu().numpy()

### 2023-06-10 score/synflow_score.py
no need to nonlinearize the net, 'cause the net is just a copy

@@ -46,5 +46,4 @@ def synflow_score(network, train_loader, device):
     for i in range(len(grads)):
         score += torch.sum(grads[i])
 
-    nonlinearize(network, signs)
     return score.detach().cpu().numpy()

### 2023-06-10 search/GA/natsbenchsss_GA_rk.py
use Encoder for uniform reason

@@ -4,14 +4,16 @@ import random
 import os
 import numpy as np
 from .GA_rk_abstract import abstract_GA, chromosome
+from encoder import encoder
 
 class GA(abstract_GA):
     def __init__(self, **kwargs):
         super().__init__(**kwargs)
         self.NATS_SSS_ops = [8, 16, 24, 32, 40, 48, 56, 64]
+        self.Encoder = encoder.get_encoder("natsbenchsss")
 
     def init_population(self):
-        self.population = [chromosome(random.sample(range(0, 8), k=5)) for i in range(self.MAXN_POPULATION)]
+        self.population = self.Encoder.get_nrand_code(self.MAXN_POPULATION)
 
     def evaluate(self):
         for i in range(len(self.population)):

### 2023-06-10 search/SA/natsbenchsss_SA_rk.py

@@ -6,11 +6,13 @@ from tqdm import trange
 import time
 from score import *
 from .SA_rk_abstract import abstract_SA
+from encoder import encoder
 
 class SA(abstract_SA):
     def __init__(self, **kwargs):
         super().__init__(**kwargs)
         self.NATS_SSS_ops = [8, 16, 24, 32, 40, 48, 56, 64]
+        self.Encoder = encoder.get_encoder("natsbenchsss")
 
     def neighbor(self, arch):
         new_arch = arch
@@ -20,7 +22,7 @@ class SA(abstract_SA):
         return new_arch
         
     def rand_arch_generate(self):
-        return [random.choice([*range(8)]) for i in range(5)]
+        return list(self.Encoder.get_rand_code())
 
     def list2arch(self, l):
         return "{}:{}:{}:{}:{}".format(*map(lambda op: self.NATS_SSS_ops[op], l))

### 2023-06-10 search/SA/SA_rk_abstract.py
uid -> int(uid) or keep it

@@ -59,19 +59,26 @@ class abstract_SA():
                 best_sol_uid = bestrk_uid
 
             T *= self.Rt
-        return best_sol_uid, self.searchspace.get_final_accuracy(int(best_sol_uid) if type(best_sol_uid)!=str else best_sol_uid, self.acc_type, self.args.valid)
+            try:
+                best_sol_uid = int(best_sol_uid)
+            except:
+                pass
+        return best_sol_uid, self.searchspace.get_final_accuracy(best_sol_uid, self.acc_type, self.args.valid)
     
     def ranking(self, indices, weight):
         scores = {"ni": [], "naswot": [], "logsynflow": []}
         
         for uid in indices:
-            uid = int(uid)
+            try:
+                uid = int(uid)
+            except:
+                pass
             network = self.searchspace.get_network(uid, self.args)
             network = network.to(self.device)
             if uid not in self.DICT:
                 nisc = ni_score(network, self.train_loader, self.device, self.args)
                 naswotsc = naswot_score(network, self.train_loader, self.device, self.args)
-                logsynsc = logsynflow_score(network, self.train_loader, self.device)
+                logsynflowsc = logsynflow_score(network, self.train_loader, self.device)
                 scores["ni"].append(nisc)
                 scores["naswot"].append(naswotsc)
                 scores["logsynflow"].append(logsynflowsc)

### 2023-06-10 search/GA/nasbench201_GA_rk.py
use encoding

@@ -4,6 +4,8 @@ import random
 import os
 import numpy as np
 from .GA_rk_abstract import abstract_GA, chromosome
+from encoder import encoder
+import torch
 
 class GA(abstract_GA):
     def __init__(self, **kwargs):
@@ -13,21 +15,23 @@ class GA(abstract_GA):
         self.MAXN_CONNECTION = 6
         self.MAXN_OPERATION = 5
         self.NAS_201_ops = ['none', 'skip_connect', 'nor_conv_1x1', 'nor_conv_3x3', 'avg_pool_3x3']
+        self.Encoder = encoder.get_encoder("nasbench201")
 
     def init_population(self):
-        self.population = [chromosome("".join([(bin(1<<random.randint(0, self.MAXN_OPERATION-1))[2:]).zfill(self.MAXN_OPERATION) for j in range(self.MAXN_CONNECTION)])) for i in range(self.MAXN_POPULATION)]
+        self.population = [chromosome(self.Encoder.get_rand_code()) for i in range(self.MAXN_POPULATION)]
+        #self.population = [chromosome("".join([(bin(1<<random.randint(0, self.MAXN_OPERATION-1))[2:]).zfill(self.MAXN_OPERATION) for j in range(self.MAXN_CONNECTION)])) for i in range(self.MAXN_POPULATION)]
 
     def evaluate(self):
         for i in range(len(self.population)):
-            network, uid, acc = gene2net(self.population[i].gene, self.NAS_201_ops, self.searchspace, self.acc_type, self.args.valid, self.args)
+            network, uid, acc = gene2net(self.population[i].gene, self.Encoder, self.NAS_201_ops, self.searchspace, self.acc_type, self.args.valid, self.args)
             #del network
             self.population[i].acc = acc
             self.population[i].uid = uid
             if self.population[i].uid not in self.DICT:
                 uid = self.population[i].uid
                 """ fitness: (naswot, ni, logsynflow) """
-                x = [naswot_score(network, self.train_loader, self.device, self.args), \
-                ni_score(network, self.train_loader, self.device, self.args), \
+                x = [naswot_score(network, self.train_loader, self.device, self.args), 
+                ni_score(network, self.train_loader, self.device, self.args), 
[…]

### 2023-06-10 search/SA/nasbench201_SA_rk.py

@@ -6,21 +6,25 @@ from tqdm import trange
 import time
 from score import *
 from .SA_rk_abstract import abstract_SA
+from encoder import encoder
 
 class SA(abstract_SA):
     def __init__(self, **kwargs):
         super().__init__(**kwargs)
         self.NAS_201_ops = ['none', 'skip_connect', 'nor_conv_1x1', 'nor_conv_3x3', 'avg_pool_3x3']
+        self.Encoder = encoder.get_encoder("nasbench201")
 
     def neighbor(self, arch):
-        new_arch = arch
+        l1, l2, l3 = arch[:6], arch[6], arch[7:]
         pos = random.sample([*range(6)], random.randint(0, 5))
         for p in pos:
-            new_arch[p] = (new_arch[p] + random.randint(0, 4)) % 5
-        return new_arch
+            l1[p] = (l1[p] + random.randint(0, 4)) % 5
+
+        return l1+l2+l3
 
     def rand_arch_generate(self):
-        return [random.choice([*range(5)]) for i in range(6)]
+        return self.Encoder.get_rand_code()
 
     def list2arch(self, l):
-        return "|{}~0|+|{}~0|{}~1|+|{}~0|{}~1|{}~2|".format(*map(lambda op: self.NAS_201_ops[op], l))
+        l = list(l)
+        return self.searchspace.get_arch_str_by_code(self.Encoder.parse_code(l))

### 2023-06-10 search/SA/nasbench101_SA_rk.py
make the element arch mutable

@@ -15,6 +15,7 @@ class SA(abstract_SA):
         self.Encoder = encoder.get_encoder("nasbench101")
 
     def neighbor(self, arch):
+        arch = [list(x) for x in arch]
         random.shuffle(arch[1])
         pos = random.sample([*range(0,5)], random.randint(0,5))
         for p in pos:

### 2023-06-11 paper/main.tex
update paper

@@
                 \bf{LogSynFlow}              & 0.61     & 0.60      & 0.59  \\
-                \bf{Rank-Based (ours)}       & X        & X         & X     \\ \bottomrule
+                \bf{Rank (ours)}             & X        & X         & X     \\ \bottomrule
                 \label{table:corr_score}
@@
     the difference of square of each feature maps captured at all pooling layers, 
-    denoted $\eta$. According to the fact that the input data are the same kind, 
-    the small $\eta$ the better the noise immunity of the architecture is.
+    denoted $\eta$. More specifically, first, calculate the matrix $\kappa$ defined by 
+    \begin{equation}
+        \label{equ:ni_kappa}
+        \kappa=\begin{pmatrix}\frac{(\tau_{1,1}-\tau'_{1,1})^2}{\lvert \tau_{1,1}\rvert}&\cdots&\frac{(\tau_{1,N}-\tau'_{1,N})^2}{\lvert \tau_{1,N}\rvert}\\\vdots&\ddots&\vdots\\\frac{(\tau_{L,1}-\tau'_{L,1})^2}{\lvert \tau_{L,1}\rvert}&\cdots&\frac{(\tau_{L,N}-\tau'_{L,N})^2}{\lvert \tau_{L,N}\rvert}\end{pmatrix},
+    \end{equation}
+    where $L$ is the total number of pooling layers; $N$ the size of mini-batch, 
+    and $\tau_{i,j}$ and $\tau'_{i,j}$ are the feature maps which $X$ passing and 
+    the one perturbed by $X'$ at the $i$-th pooling layer and $j$-th input 
+    data of the mini-batch, respectively. 
+    Then $\eta$ can be calculated by 
+    \begin{equation}
+        \label{equ:ni_eta}
+        \eta=\ln(\epsilon+e_L\kappa e_N),
+    \end{equation}
+    where $\epsilon$ is a small positive number, and $e_L$ and $e_N$ are a row 
+    vector of 1's of size $L$ and a column vector of 1's of size $N$, respectively. 
+    According to the fact that the input data are the same kind, the smaller $\eta$ 
+    is, the better the noise immunity of the architecture is.
 
@@
         \label{equ:snip_connection_sensitivity}
-        s_j=\lvert w_j\frac{\partial L}{\partial w_j}\rvert,
+        s_j=\lvert \frac{\partial \mathcal L}{\partial w_j}w_j\rvert,
     \end{equation}
     where $\textbf{w}$ is the weight of the netwrok, $w_j$ the $j$-th element of 
-    $\textbf{w}$. The meaning behind is to approximate the contribution 
+    $\textbf{w}$, and $\mathcal L$ is the empirical risk. The meaning behind is to approximate the contribution 
     to the change of the loss function from a specific connection. By pruning the 
@@
     Later, Wang et al. \cite{wang2020picking} noticed that SNIP with a high pruning ratio 
-    tends to cause layer-collapse, which prune all parameters in a single weight layer. 
-    Therefore, they propose to approximate the change in gradient norm which defined as 
+    tends to cause \textit{layer-collapse}, which prunes all parameters in a single weight 
+    layer. Therefore, they propose Gradient Signal Preservation (GraSP) algorithm, which 
+    aims to preserve the gradient flow at initialization by approximating the change in 
+    gradient norm defined as 
     \begin{equation}
         \label{equ:grap}
-        S_p(\bf{\theta})=-(H\frac{\partial \mathcal L}{\partial \bf{\theta}})\odot\bf{\theta},
+        S_p(\theta)=-(\textbf{H}\frac{\partial \mathcal L}{\partial \theta})\odot\theta,
     \end{equation}
-    where $H$ is the Hessian matrix, $\bf{\theta}$ the parameters, and $\odot$ is Hadamard product. 
-    In \cite{tanaka2020pruning}, Tanaka et al. generalized the synaptic saliency scores as 
+    where $\textbf{H}$ is the Hessian matrix, $\theta$ the parameters, and $\odot$ is Hadamard product. 
+    In \cite{tanaka2020pruning}, to solve the problem that the existing pruning algorithms, e.g., 
+    Magnitude, SNIP, GraSP, using global-masking usually encounter layer-collapse which will make 
+    the pruned network untrainable. 
+    Tanaka et al. generalized the synaptic saliency scores as 
     \begin{equation}
         \label{equ:synflow}
-        S_p(\theta)=\frac{\partial \mathcal L}{\partial \theta}\odot\theta,
+        S_p(\theta)=\frac{\partial \mathcal R}{\partial \theta}\odot\theta,
     \end{equation}
-    which is named SynFlow. 
-    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, conclude that summing 
-    synaptic saliency score over all parameters in the model can be used to score a network 
-    architecture, which is formula as 
+    where $\mathcal R$ is a scalar loss function, and proposed Iterative Synaptic Flow Pruning (SynFlow) 
+    algorithm which is an extension of magnitude pruning algorithm and avoids layer-collapse. 
+    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, proposed to score a 
+    network by summing the synaptic saliency score over all parameters in the model, which is 
+    defined as 
     \begin{equation}
         \label{equ:zero_cost}
-        S_n=\sum^N_i S_p(\theta)_i
+        S_n=\sum^N_i S_p(\theta)_i.
     \end{equation}
+    The rationale behind is to calculate all the contribution to the loss function of parameters. 
+    The higher the score of an architecture, the more trainable this architecture is. 
     Finally, Cavagnero et al. \cite{Cavagnero_2023} imporved SynFlow, which is likely to fall into 
-    gradient explosion problem, and proposed LogSynFlow score function, simply scaling down the gradient. 
+    gradient explosion problem, and proposed LogSynFlow which simply scaling down the gradient. 
     The formula is defined by 
@@
     \label{sec:proposed}
+
     \subsection{Motivation}
@@
     of trainability, e.g., SynFlow, NTK, which means whether this architecture is easy to 
-    train or not.
+    train or not. In this paper, NI, NASWOT, and LogSynFlow are used in the ranking algorithm.
 
-    \subsection{Rank-Based Score Function}
+    \subsection{The Ranking Algorithm}
     \begin{algorithm}[h]
-        \caption{The Rank Algorithm}\label{alg:rank-based}
+        \caption{The Ranking Algorithm}\label{alg:rank-based}
         \begin{algorithmic}[1]
-            \Input ${\mathbb N}^{s}\subset{\mathbb N}^{*}$
+            \Input{a subspace, ${\mathbb N}^{s}$, from search space, ${\mathbb N}^{*}$}
             \For{$\text{each }{\mathbb N}^i\text{ in }{\mathbb N}^s$}
@@
             \State $r({\mathbb N}^i)=\sum^M_{j=0} r_{{\mathcal F}_{j}}({\mathbb N}^i)$
-            \State $i^*=\arg\min_{i}\{r({\mathbb N}^i)\}$
-            \State $\textbf{Return }{\mathbb N}^{i^*}$
+            %\State $i^*=\arg\min_{i}\{r({\mathbb N}^i)\}$
+            %\State $\textbf{Return }{\mathbb N}^{i^*}$
+            \State $\textbf{Return }r$
         \end{algorithmic}
@@
 
-    The proposed rank-based score function is outlined in \xalg{alg:rank-based}. The first step is to evaluate the 
-    network architectures in the subset, denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The evaluation 
-    of an architecture determined by $j$-th score function is denoted $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating 
-    the subset of search space, the rank of each score function is calculated, denoted $r_{\mathcal F}$. Then the final 
-    rank, $r$, calculated by summing up the ranks. 
-    If a network architecture gains higher score in these score functions, the final rank should be higher (smaller index) too. 
-    Therefore, the highest (minimum) rank in $r$ shall be the best network architecture. In summary, the rank-based score 
-    function makes the contribution of each score function even.
+    The proposed ranking algorithm is outlined in \xalg{alg:rank-based}. 
+    The first step is to evaluate the network architectures in the subset, 
+    denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The 
+    evaluation of an architecture determined by $j$-th score function is 
+    denoted $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating the subset 
+    of search space, the rank of each score function is calculated, denoted 
+    $r_{\mathcal F}$. Then the final rank, $r$, calculated by summing up 
+    the ranks. If a network architecture gains higher score in these score 
+    functions, the final rank should be higher (smaller index) too. Therefore, 
+    the highest (minimum) rank in $r$ shall be the best network architecture. 
+    In summary, the rank-based score function makes the contribution of 
+    each score function even, and therefore evaluate an architecture from 
+    different aspects. In this paper, NI and NASWOT are used as a complement 
+    set, which take the ability of images generalization and distinction. 
+    Lastly, LogSynFlow complements NI and NASWOT which takes the trainability 
+    into account.
 
@@
 
-    \begin{figure*}[htb]
-        \centering
-        \hspace*{-\baselineskip}
-        \vspace*{-\baselineskip}
-        \includegraphics[]{asset/SA.pdf}
-        \caption{A simple example to illustrate an iteration of SA with Rank-based score function.}
-        \label{fig:SA}
-    \end{figure*}
+    \begin{algorithm}[h]
+        \caption{The Simulated Annealing with Ranking Algorithm}\label{alg:SA}
+        \begin{algorithmic}[1]
+            \Input{search space $\mathbb N^*$, initial temperature $T$, ending temperature $\tau$, 
+            a real number between 0 and 1, $\alpha$, the number of iteration, $I$}
+            \State $s^*=s=\text{sample a random architecture from }\Bbb N^*$
+            \While{$T>\tau$}
+                \For{$\text{ each }i \in [1\ldots I]$}
+                    \State $r=\text{Ranking}(\{s\}\cup U(s))$ \Comment{Ranking $s$ with the neighbourhood of $s$, denoted $U(s)$}
+                    \State $s^*=\arg\min\{r(\Bbb N^i)\}$ \Comment{Update the expected best algorithm}
+                    \State $\Delta E=r(s^*)-r(s)$
+                    \State $x\sim \mathcal U(0,1)$ \Comment{Sample $x$ from a uniform distribution between 0 and 1}
+                    \If{$x\geq e^{\frac{\Delta E}{T}}$} \Comment{Accept by probability}
+                        \State $s\leftarrow s^*$
+                    \EndIf
+                \EndFor
+                \State $T\leftarrow T\times \alpha$
+            \EndWhile
+            \State $\textbf{Return }s^*$ \Comment{Return the best architecture}
+        \end{algorithmic}
+    \end{algorithm}
 
-    \xfig{fig:SA} illustrates how SA with rank-based score function works in an iteration.
+    The modified version of the simulated annealing algorithm with ranking algorithm 
+    is outlined in \xalg{alg:SA}. The first step is to sample a architecture, denoted 
+    $s$, from search space. Then use $s$ as a "seed" to generate the neighbourhood of it, 
+    applying ranking algorithm on the neighbourhood, $\{s\}\cup U(s)$. After ranking, 
+    the expected best architecture can be determined and update, but the seed for next 
+    iteration will be replaced by $s^*$ according to probability, $e^{\frac{\Delta E}{T}}$.
+    After the $I$ iterations, the temperature scales down by $\alpha$. The algorithm 
+    is done when $T\leq\tau$, and the best architecture will be retruned.
+
+    %\begin{figure*}[htb]
+    %    \centering
+    %    \hspace*{-\baselineskip}
+    %    \vspace*{-\baselineskip}
+    %    \includegraphics[]{asset/SA.pdf}
+    %    \caption{A simple example to illustrate an iteration of SA with Rank-based score function.}
+    %    \label{fig:SA}
+    %\end{figure*}
+    %\xfig{fig:SA} illustrates how SA with rank-based score function works in an iteration.
 
@@
     \label{sec:results}
-
-    \subsection*{natsbenchsss}
-    The result of natsbenchsss is shown in \xtab{table:overall_sss}.
+    \subsection{Environment and Parameter Settings}
+    The experiment is conducted on a PC with Intel Core i7-11700K (3.60 GHz, 16-MB Cache, and 16 cores), 
+    a single NVIDIA RTX3070 Ti GPU with 8 GB memory, driver version 520.61.05, CUDA version 11.8, and 
+    65 GB available memory running on Ubuntu 20.04.1 with linux kernel 5.15.0-73-generic. All the program 
+    is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. 
+    \subsection{NATS-bench-SSS}
+    The result of NATS-bench-SSS is shown in \xtab{table:overall_sss}.
     \begin{table*}[htb]
@@
         \newcommand{\z}{\phantom{0}}
-        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms.}}
+        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-SSS.}}
           \vspace{-\baselineskip}
-        \begin{tabular}{@{}lccccccl@{}}\toprule
+        \begin{tabular}{@{}lccccccc@{}}\toprule
         Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
@@
         NASWOT (N=1,000)     & $X$ & $89.25\pm \z{0.412}$ & $92.21\pm 0.298$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        logsynflow (N=1,000) & $X$ & $89.61\pm \z{0.101}$ & $92.60\pm 0.188$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        LogSynFlow (N=1,000) & $X$ & $89.61\pm \z{0.101}$ & $92.60\pm 0.188$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
         rk (N=1000)          & $X$ & $89.59\pm \z{0.136}$ & $92.51\pm 0.171$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
@@
 
-    \subsection*{nasbench201}
-    The result of nasbench201 is shown in \xtab{table:overall_201}.
+    \subsection{NAS-Bench-201}
+    The result of NAS-Bench-201 is shown in \xtab{table:overall_201}.
     \begin{table*}[htb]
@@
         \newcommand{\z}{\phantom{0}}
-        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms.}}
+        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-201.}}
           \vspace{-\baselineskip}
-        \begin{tabular}{@{}lccccccl@{}}\toprule
+        \begin{tabular}{@{}lrcccccc@{}}\toprule
         Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
@@
         &&&&\textbf{Non-weight sharing}&&&\\
-        AREA      & $12,000$ & $91.18 \pm \z{0.43}$                & $93.95 \pm \z{0.39}$               & $71.84 \pm \z{1.21}$                 & $71.92 \pm \z{1.29}$                & $45.04 \pm 1.03$                 & $45.40 \pm \z{1.14}$                \\
-        REA       & $12,000$ & $91.08 \pm \z{0.54}$                & $93.89 \pm \z{0.50}$               & $71.69 \pm \z{1.34}$                 & $71.83 \pm \z{1.33}$                & $44.96 \pm 1.41$                 & $45.30 \pm \z{1.51}$                \\
-        RS        & $12,000$ & $90.91 \pm \z{0.33}$                & $93.67 \pm \z{0.33}$               & $70.91 \pm \z{1.04}$                 & $70.99 \pm \z{0.99}$                & $44.52 \pm 0.99$                 & $44.56 \pm \z{1.25}$                \\
-        RL        & $12,000$ & $90.87 \pm \z{0.41}$                & $93.63 \pm \z{0.36}$               & $70.62 \pm \z{1.08}$                 & $70.77 \pm \z{1.05}$                & $44.20 \pm 1.22$                 & $44.23 \pm \z{1.37}$                \\
-        BOHB      & $12,000$ & $88.47 \pm \z{1.19}$                & $91.79 \pm \z{1.11}$               & $67.18 \pm \z{2.05}$                 & $67.50 \pm \z{2.05}$                & $38.94 \pm 3.58$                 & $39.00 \pm \z{3.73}$                \\ \midrule
+        AREA      & $12,000$ & $91.18 \pm \z{0.43}$                & $93.95 \pm \z{0.39}$               & $71.84 \pm \z{1.21}$                 & $71.92 \pm \z{1.29}$                & $45.04 \pm 1.03$                 & $45.40 \pm 1.14$                \\
+        REA       & $12,000$ & $91.08 \pm \z{0.54}$                & $93.89 \pm \z{0.50}$               & $71.69 \pm \z{1.34}$                 & $71.83 \pm \z{1.33}$                & $44.96 \pm 1.41$                 & $45.30 \pm 1.51$                \\
+        RS        & $12,000$ & $90.91 \pm \z{0.33}$                & $93.67 \pm \z{0.33}$               & $70.91 \pm \z{1.04}$                 & $70.99 \pm \z{0.99}$                & $44.52 \pm 0.99$                 & $44.56 \pm 1.25$                \\
+        RL        & $12,000$ & $90.87 \pm \z{0.41}$                & $93.63 \pm \z{0.36}$               & $70.62 \pm \z{1.08}$                 & $70.77 \pm \z{1.05}$                & $44.20 \pm 1.22$                 & $44.23 \pm 1.37$                \\
+        BOHB      & $12,000$ & $88.47 \pm \z{1.19}$                & $91.79 \pm \z{1.11}$               & $67.18 \pm \z{2.05}$                 & $67.50 \pm \z{2.05}$                & $38.94 \pm 3.58$                 & $39.00 \pm 3.73$                \\ \midrule
         &&&&\textbf{Weight sharing}&&&\\
-        RSWS      & $\z{4,154}$  & $76.95 \pm 16.74$                & $82.60 \pm 12.10$               & $52.51 \pm 18.33$                & $52.93 \pm 18.32$                   & $29.76 \pm 9.50$                 & $29.16 \pm 9.61$               \\
-        DARTS-V1  & $\z{5,475}$  & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm \z{0.00}$                \\
-        DARTS-V2  & $16,114$ & $39.77 \pm \z{0.00}$               & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                & $15.61 \pm \z{0.00}$                   & $16.43 \pm 0.00$                 & $16.32 \pm \z{0.00}$                \\
-        GDAS      & $11,183$ & $90.05 \pm \z{0.23}$                & $93.46 \pm \z{0.13}$               & $71.02 \pm \z{0.31}$                 & $70.56 \pm \z{0.24}$                & $41.77 \pm 1.24$                 & $41.96 \pm \z{0.90}$                \\
-        SETN      & $16,787$ & $84.25 \pm \z{5.05}$                & $88.01 \pm \z{4.52}$               & $59.72 \pm \z{7.30}$                & $59.91 \pm \z{7.51}$                   & $33.93 \pm 3.85$                 & $33.48 \pm \z{4.22}$                \\
-        ENAS      & $\z{7,061}$  & $40.11 \pm \z{3.28}$                & $56.33 \pm \z{3.70}$               & $14.09 \pm \z{1.60}$                 & $14.77 \pm \z{1.45}$                & $16.20 \pm 0.48$                 & $15.93 \pm \z{0.67}$                \\ \midrule
+        RSWS      & $4,154$  & $76.95 \pm 16.74$                   & $82.60 \pm 12.10$                  & $52.51 \pm 18.33$                    & $52.93 \pm 18.32$                   & $29.76 \pm 9.50$                 & $29.16 \pm 9.61$                \\
+        DARTS-V1  & $5,475$  & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm 0.00$                \\
+        DARTS-V2  & $16,114$ & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm 0.00$                \\
+        GDAS      & $11,183$ & $90.05 \pm \z{0.23}$                & $93.46 \pm \z{0.13}$               & $71.02 \pm \z{0.31}$                 & $70.56 \pm \z{0.24}$                & $41.77 \pm 1.24$                 & $41.96 \pm 0.90$                \\
+        SETN      & $16,787$ & $84.25 \pm \z{5.05}$                & $88.01 \pm \z{4.52}$               & $59.72 \pm \z{7.30}$                 & $59.91 \pm \z{7.51}$                & $33.93 \pm 3.85$                 & $33.48 \pm 4.22$                \\
+        ENAS      & $7,061$  & $40.11 \pm \z{3.28}$                & $56.33 \pm \z{3.70}$               & $14.09 \pm \z{1.60}$                 & $14.77 \pm \z{1.45}$                & $16.20 \pm 0.48$                 & $15.93 \pm 0.67$                \\ \midrule
         &&&&\textbf{Training-free}&&&\\
@@
         NASWOT (N=1,000)     & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        logsynflow (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+        LogSynFlow (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
         rk (N=1000)          & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
@@
 
+      \subsection{NAS-Bench-101}
+      The result of NAS-Bench-101 is shown in \xtab{table:overall_101}.
+      \begin{table}[htb]
+        %\normalsize
+        %\centering
+        \newcommand{\z}{\phantom{0}}
+        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-101.}}
+          \vspace{-\baselineskip}
+        \resizebox{0.5 \textwidth}{!}{
+        \begin{tabular}{@{}lrcc@{}}\toprule
+        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} \\ \cmidrule(lr){3-4}
+               &            & validation & test \\ \midrule
+               &            &            \textbf{Non-weight sharing}&\\
+        AREA   & $12,000$   & $93.67 \pm \z{0.48}$  & $93.02 \pm \z{0.48}$\\
+        REA    & $12,000$   & $93.63 \pm \z{0.50}$  & $93.02 \pm \z{0.52}$\\ \midrule
+               &            &            \textbf{Weight sharing}&\\
+        DARTS-V1 & $20,483$ & $83.50 \pm \z{0.11}$ & $83.74 \pm \z{0.03}$ \\
+        ENAS     & $22,325$ & $93.83 \pm \z{0.28}$ & $93.34 \pm \z{0.26}$ \\ \midrule
+                 &          &            \textbf{Training-free}&\\
+        Zero-Cost NASWOT     & $18,940$  & $91.72 \pm \z{1.80}$ & $91.29 \pm \z{1.82}$ \\
+        NI (N=1,000)         & $280$ & $93.15 \pm \z{1.48}$ & $92.72 \pm \z{1.06}$ \\ 
+        NASWOT (N=1,000)     & $162$ & $92.40 \pm \z{4.07}$ & $91.97 \pm \z{4.20}$ \\ 
+        LogSynFlow (N=1,000) & $105$ & $90.70 \pm \z{8.41}$ & $90.98 \pm \z{2.56}$ \\ 
+        rank (N=1000)        & $516$ & $92.84 \pm \z{1.19}$ & $92.51 \pm \z{1.14}$ \\ 
+        GA-rank              & $X$   & $X \pm X$ & $X\pm X$\\ 
+        SA-rank              & $374$ & $93.01 \pm \z{1.19}$ & $92.37 \pm \z{1.63}$  \\ \bottomrule
+        \end{tabular}
+        }
+        \label{table:overall_101}
+          \vspace{-\baselineskip}
+      \end{table}
+
     \section{Conclusion}

### 2023-07-09 paper/main.tex
update paper

@@
 
+\algnewcommand\algorithmicparameter{\textbf{Parameter:}}
+\algnewcommand\Parameter{\item[\algorithmicparameter]}
+
 \begin{document}
@@
 \begin{abstract}
-
-    % dont we
-    % To address
-    % To evaluate
-    Although the training-free neural architecture search (NAS) are typically 
-    faster than training-based NAS methods, however, the correlation between 
-    the measurement and the final accuracy of an architecture is not well 
-    enough in most cases. 
-    To address this problem, we propose a rank-based training-free NAS 
-    algorithm, which combines three complement training-free score functions 
-    to evaluate an architecture by ranking. 
-    More precisely, noise immunity (NI) and the correlation between binary 
-    activation paterns, named as NASWOT, are used as measurement of image recognition 
-    ability, and, SynFlow are used as measurement of trainability. 
-    With that, a modified version of simulated annealing (SA) algorithm 
-    can applies on and obtains a better performance on searching high accuracy 
-    architectures. 
+    %Although the training-free neural architecture search (NAS) are typically 
+    %faster than training-based NAS methods, however, the correlation between 
+    %the measurement and the final accuracy of an architecture is not well 
+    %enough in most cases. 
+    The training-free neural architecture search (NAS) typically uses one or 
+    two score functions to evaluate how an neural network architecture performs. 
+    However, an architecture shall be treated as a complex system who has 
+    distinct characteristics to measure. 
+    To achieve the goal, we propose a rank-based training-free NAS algorithm, 
+    which combines three training-free score functions which is "complementary" 
+    to each others to evaluate an architecture by ranking. 
+    In this work, noise immunity (NI) considers the image generalization 
+    ability of the architecture, the correlation between binary activation 
+    paterns, named as NASWOT, considers image distinction ability, and LogSynFlow 
+    takes trainability into account. With that, a modified version of simulated 
+    annealing (SA) algorithm, \palg, can applies on and obtains a better 
+    performance on searching high accuracy architectures. 
     To evaluate the performance of the proposed algorithm, this paper compared 
     it with several NAS algorithms, including weight-sharing methods, 
-    non-weight-sharing methods, and several state-of-the-art training-free score 
-    functions. The final result shows that in relatively larger search space, 
-    like NATS-Bench SSS, the proposed algorithm outperforms most of NAS methods.
+    non-weight-sharing methods, and several state-of-the-art training-free 
+    score functions. The final result indicates that \palg outperforms most 
+    of training-free score functions and shows the robustness between different 
+    search spaces.
 
@@
     attention, since the ability to automatically design a "good" neural 
-    architecture. By leveraging machine learning algorithms \cite{https://doi.org/10.48550/arxiv.1611.01578}, 
-    NAS algorithms can explore a search space, which is comprised of numerous 
-    potential architectures, to find out a good architectures that outperform 
-    those designed by human experts. Recently, the use of NAS is 
-    widespread, from object detection \cite{https://doi.org/10.48550/arxiv.2111.13336}, 
+    architecture. By leveraging machine learning algorithms 
+    \cite{https://doi.org/10.48550/arxiv.1611.01578}, NAS algorithms can 
+    explore a search space, which is comprised of numerous potential 
+    architectures, to find out a good architectures that outperform those 
+    designed by human experts. Recently, the use of NAS is widespread, 
+    from object detection \cite{https://doi.org/10.48550/arxiv.2111.13336}, 
     image recognition \cite{https://doi.org/10.48550/arxiv.2006.04647} 
     and speech recognition \cite{https://doi.org/10.48550/arxiv.2011.05649} 
-    \cite{mehrotra2021nasbenchasr} to natural language 
-    processing. \cite{jiang-etal-2019-improved} 
-    \cite{https://doi.org/10.48550/arxiv.2006.07116} 
+    \cite{mehrotra2021nasbenchasr} to natural language processing (NLP). 
+    \cite{jiang-etal-2019-improved} \cite{https://doi.org/10.48550/arxiv.2006.07116} 
     \cite{https://doi.org/10.48550/arxiv.2005.14187} 
-
-    % reduce 
     Despite the promising results of NAS, there are still many challenges 
     to conquer. One major problem is the extremely high computational 
-    cost to search for an optimal architecture, which can make NAS impractical 
-    for real-world applications, particularly on resource-constrained 
+    cost to search for an optimal architecture, which can make NAS 
+    impractical for real-world applications, particularly on resource-constrained 
     platforms like embedded system. The reason why NAS is costly is that 
@@
     % NASWOT
-    For example, Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} proposed the 
-    measurement of the correlation between the binary activation paterns, 
-    induced by the untrained network at two inputs, named as neural architecture 
-    search without training (NASWOT). 
+    For example, Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} 
+    proposed the measurement of the correlation between the binary 
+    activation paterns, induced by the untrained network at two inputs, 
+    abbreviated as NASWOT. 
     % synflow
-    On the other hand, Lee et al. \cite{lee2019snip} proposed purning parameters based on a saliency matric, 
-    which then extended further by Wang et al. \cite{wang2020picking} and Tanaka et al. \cite{tanaka2020pruning}. 
-    In \cite{tanaka2020pruning}, Tanaka et al. proposed Iterative Synaptic Flow Pruning 
-    (SynFlow) algorithm which intends to deal with the layer collapse problem when purning a network. 
-    The score function used in the algorithm is so-called \it{synaptic saliency} \rm{score}. 
-    Later, Abdelfattah et al. \cite{abdelfattah2021zerocost} extended SynFlow to score 
-    a network architecture by summing synaptic saliency score over all parameters in the model. 
-    Cavagnero et al. \cite{Cavagnero_2023} found that SynFlow is likely to suffer from gradient explosion, then 
-    proposed the LogSynFlow score function which prevents the problem. 
+    On the other hand, Lee et al. \cite{lee2019snip} proposed purning 
+    parameters based on a saliency matric, which then extended by Tanaka 
+    et al. \cite{tanaka2020pruning}. In \cite{tanaka2020pruning}, Tanaka 
+    et al. proposed Iterative Synaptic Flow Pruning (SynFlow) algorithm 
+    which intends to deal with the layer collapse problem when purning a 
+    network. The score function used in the algorithm is so-called 
+    \it{synaptic saliency} \rm{score}. Later, Abdelfattah et al. 
+    \cite{abdelfattah2021zerocost} extended SynFlow to score a network 
+    architecture by summing synaptic saliency score over all parameters 
+    in the model. Cavagnero et al. \cite{Cavagnero_2023} found that 
+    SynFlow is likely to suffer from gradient explosion, then proposed 
+    the LogSynFlow score function which prevents the problem. 
     % NTK
-    For another example, Chen et al. \cite{https://doi.org/10.48550/arxiv.2102.11535} proposed to compute the condition 
-    number of neural tangent kernel (NTK) \cite{https://doi.org/10.48550/arxiv.2203.09137} 
-    \cite{https://doi.org/10.48550/arxiv.2109.00817}, which is used as the score to estimate the trainability of an 
-    architecture.
+    For another example, Chen et al. 
+    \cite{https://doi.org/10.48550/arxiv.2102.11535} proposed to compute 
+    the condition number of neural tangent kernel (NTK) 
+    \cite{https://doi.org/10.48550/arxiv.2203.09137} 
+    \cite{https://doi.org/10.48550/arxiv.2109.00817}, which is used as 
+    the score to estimate the trainability of an architecture.
 
@@
     % 做成圖表放第一頁
-    However, \xtab{table:corr_score} shows most of score functions suffer from low correlation between 
-    score values and the final accuracy of architectures, leading to a predicament 
-    that no matter how good the search method is used, we can hardly find 
-    an optimal architecture. 
+    However, \xtab{table:corr_score} shows most of score functions suffer 
+    from low correlation between score values and the final accuracy of 
+    architectures, leading to a predicament that no matter how good the 
+    search method is used, we can hardly find an optimal architecture. 
     The major problem causes the low correlation is that a single score 
-    function can only evaluate one perspect/characteristic of an architecture. 
+    function can only evaluate one characteristic of an architecture. 
     \begin{table}[tb]
-        \caption{\textsc{The Kendall correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench \cite{Dong_2021}. 
-        Each metric has been computed three times with different initialisations and the average is taken as final score.}}
+        \caption{\textsc{The Kendall correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench \cite{Dong_2021}. }}
         \resizebox{0.48\textwidth}{!}{
@@
 % method
-    To address the problem, we propose cooperating three complement score 
-    functions by ranking, which allows every score functions evaluate an 
-    architecture without losing fairness. 
+    To address the problem, we propose cooperating three complementary 
+    score functions by ranking, which allows every score functions 
+    evaluate an architecture without losing fairness. 
     The first score function is noise immunity (NI) \cite{10092788}, as 
-    an indicator of the ability to distinguish two images. 
-    The second one is NASWOT, as score to estimate the ability of expression 
+    a measurement of the ability of image generalization. 
+    The second one is NASWOT, as score to estimate the ability of distinction 
     of an architecture and also a complement of NI. 
-    The last one is SNIP used as the measurement of trainability and 
-    also as a complement to NI and NASWOT. 
-    With these three complement score functions, an evaluation of an 
+    The last one is LogSynFlow used as the measurement of trainability 
+    and also as a complement of NI and NASWOT. 
+    With these three complementary score functions, an evaluation of an 
     architecture is not simply from a single aspect but three different 
@@
 
-    The remainder of this paper is organized as follows: \xsec{sec:related_work} provides the 
-    detail about the three complement score functions. \xsec{sec:proposed} gives a detailed 
-    description about the proposed method. \xsec{sec:results} begins with parameters setting and 
-    provide the simulation results following is the experiment results in different search space. 
-    The conclusion and further prospect are gived in \xsec{sec:conclusion}.
+    The remainder of this paper is organized as follows: 
+    \xsec{sec:related_work} provides the detail about the three 
+    complementary score functions. \xsec{sec:proposed} gives a detailed 
+    description about the proposed method. \xsec{sec:results} begins 
+    with parameters setting and provide the simulation results following 
+    is the experiment results in different search space. The conclusion 
+    and further prospect are gived in \xsec{sec:conclusion}.
 
@@
     \subsection{Training-free Score Functions}
-    % naswot 對圖描述多一點
-    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. proposed a 
-    score function without the requirement for training which is named neural 
-    architecture search without training (NASWOT). \xfig{fig:naswot} 
-	gives a simple example to illustrate the procedure of NASWOT score function. 
-    Consider a mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
+    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. 
+    proposed a score function without the requirement for training which 
+    is abbreviated as NASWOT. \xfig{fig:naswot} gives a simple example 
+    to illustrate the procedure of NASWOT score function. Consider a 
+    mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
     architecture. The activated ReLU units in every layer of the architecture 
-    form a binary code $c_i$ that define the linear region.
-    The correlation between binary codes for the whole mini-batch can be examined 
-    by computing the kernel matrix 
+    form a binary code $c_i$ that define the linear region. The correlation 
+    between binary codes for the whole mini-batch can be examined by computing 
+    the kernel matrix 
     \begin{equation}
@@
 
-    %to see how dissimilar the linear region activated by 
-    %the ReLU units between two inputs. An architecture shall learn better 
-    %when inputs are well separated.
-
-    % ni 對圖描述多一點
     Wu et al. \cite{10092788} found, in some case, an architecture with high 
@@
     evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
-    noise immunity evaluate an architecture. The score function picks a 
+    NI evaluate an architecture. The score function picks a 
     mini-batch of data, denoted $X$, and then applies Gaussion noise on it. 
@@
     By passing $X$ and $X'$ through the untrained architecture, then computing 
-    the difference of square of each feature maps captured at all pooling layers, 
-    denoted $\eta$. More specifically, first, calculate the matrix $\kappa$ defined by 
+    the difference of square of each feature maps captured at all pooling layers. 
+    Calculate the matrix $\kappa$ defined by 
     \begin{equation}
@@
         \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
-        \caption{A simple example to illustrate the procedure of noise immunity.}
+        \caption{A simple example to illustrate the procedure of NI.}
         \label{fig:ni}
@@
     % synflow
-    % 再調
-    Besides from these two image-related aspects, there is another aspect to evaluate  
-    a network. 
+    Besides from image-related aspects, there is another aspect to evaluate a network. 
     \textit{The Lottery Ticket Hypothesis} \cite{frankle2019lottery}, reveals that a 
@@
     \end{equation}
-    where $\textbf{w}$ is the weight of the netwrok, $w_j$ the $j$-th element of 
-    $\textbf{w}$, and $\mathcal L$ is the empirical risk. The meaning behind is to approximate the contribution 
+    where $w_j$ the $j$-th element of the weight of the netwrok, and $\mathcal L$ is 
+    the empirical risk. The meaning behind is to approximate the contribution 
     to the change of the loss function from a specific connection. By pruning the 
@@
 
+    Except using the synaptic saliency score to measure the trainability, 
+    \cite{https://doi.org/10.48550/arxiv.2102.11535} uses the condition number of neural tangent 
+    kernel (NTK) \cite{jacot2020neural} to measure it, which the score can be defined as 
+    \begin{equation}
+        \label{equ:cn_ntk}
+        \frac{\lambda_m}{\lambda_0}, 
+    \end{equation}
+    where $\lambda_0$ is the biggest eigenvalue and $\lambda_m$ is the smallest eigenvalue of the 
+    NTK. The rationale behind is the converge rate of the network is condition by the rate 
+    $\frac{\lambda_m}{\lambda_0}$. The higher the condition is, the faster the converge.
+
     \subsection{Search Algorithms}
-    First assume that input data $D$ are separated into two subset, $D_r$ and $D_t$. Further more, 
+    First assume that input data $D$ are separated into two subset, $D_r$ and $D_t$. Furthermore, 
     assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $\mathcal A_s$ the 
@@
     generated by a network architecture controller. The actions $a_{1:T}$ of the reinforcement learning is 
-    equivalent to updating the parameters $\theta_c$ for the controller. More specifically, the goal is to maximize 
+    equivalent to updating the parameters $\theta_c$ for the controller. The goal is to maximize 
     its expected reward, defined by 
@@
 
-    \subsection{Motivation}
     The motivation origins from these three questions:
 
-    \textit{1. Can we combine multiple score functions to improve the correlation between score values and the final accuracy of architectures?}
+    \textit{1. Can we combine multiple score functions to improve the search performance 
+    or the correlation between score values and the final accuracy of architectures?}
 
-    The answer is yes. It's konwn that if the chosen score functions can complement with 
+    The answer is yes. If the chosen score functions is complementary to 
     each others, the new correlation can eventually beyond the original ones. \cite{10.1145/3491396.3506510} 
@@
     images, which are in the same class originally, into different classes. NI here comes 
-    to rescue. By measuring the noise immunity of an architecture, the miss-classifying 
-    can be solved. Thus, if mix NASWOT with NI, the correlation increases. An example 
-    is shown in \xfig{fig:ninaswot}.
+    to rescue. By measuring the noise immunity of an architecture, the miss-classifying problem 
+    can be solved. Thus, if mix NASWOT with NI, the correlation and performance increases. 
+    An example is shown in \xfig{fig:ninaswot}.
     \begin{figure*}[htb]
@@
 
-    \textit{2. How to combine multiple different kinds of score functions together and prevent one from overwhelming the others numerically?}
+    \textit{2. How to choose the score functions?}
+
+    As mentioned, the key is to choose the complement of a score function. For example, 
+    score functions that evaluate the expressivity/distinction ability shall have other 
+    score functions to evalute the generalization ability. For these two graphic recognition 
+    score functions, the complement of them can be a measurement of trainability.
+
+    \textit{3. How to combine multiple different kinds of score functions together 
+    and prevent one from overwhelming the others numerically?}
 
     One possible way is normalization, but the necessary information is known only 
-    after evaluating the whole search space, e.g., range, mean or standard deviation, which is practically 
-    impossible. In order to achieve the goal, the proposed score function, named rank-based NAS, leverage 
-    multiple score functions by ranking, which provides a solution to have equal contribution from each 
-    score function.
+    after evaluating the whole search space, e.g., range, mean or standard deviation, 
+    which is practically impossible. In order to make the proposed score function 
+    agnostic to the search space, it leverages multiple score functions by ranking, 
+    which also provides a solution to have equal contribution from each score function.
 
-    \textit{3. How to choose the score functions?}
+    \subsection{Simulated Annealing with Ranking Algorithm}
 
-    As mentioned, the key is to choose the complement of a score function. For example, 
-    NASWOT and NI. And for NASWOT and NI, which are both description of the ability of 
-    the graphic recognition of an architecture. The complement of them can be a measurement 
-    of trainability, e.g., SynFlow, NTK, which means whether this architecture is easy to 
-    train or not. In this paper, NI, NASWOT, and LogSynFlow are used in the ranking algorithm.
+    The modified version of the simulated annealing (SA) algorithm with ranking algorithm (\palg)
+    is outlined in \xalg{alg:SA}. The first step is to sample an architecture as current 
+    solution, denoted $s$, from search space. Then use $s$ as a seed to generate the 
+    neighbourhood of it, denoted $U$, and the size of it is decided by a presetting parameter, 
+    the number of generated neighbours, $N$. 
+    After ranking with the seed, the neighbourhood and the historical best architectures set, $H$, 
+    it is maintained by adding the architecture (including $s$) which has highest rank, and 
+    the architecture (excluding $s$) which has highest rank is denoted by $s^*$. 
+    If the rank of $s^*$ is higher than $s$, the current solution will be 
+    replaced by $s^*$, or be replaced by probability, defined by 
+    \begin{equation}
+        \label{equ:SA_rk_prob}
+        e^{-\alpha\frac{\Delta E}{T}},
+    \end{equation}
+    where $T$ is the current temperature, $\Delta E$ the difference of the rank between 
+    $s$ and $s^*$, and $\alpha$ is a constant number adjusts the probability. The bigger 
+    the difference, the smaller the probability to accept the new solution. 
+    After the $I$ iterations, the temperature scales down by $r_t$. The algorithm 
+    is done when $T\leq\tau$, and the current architecture will be retruned. 
+    Notbly, the size of $H$ is based on the maximum searching number of SA, defined by 
+    \begin{equation}
+        \label{equ:SA_rk_size_of_H}
+        \beta (I\cdot N\cdot\frac{\ln{\tau/T}}{\ln{r_t}}),
+    \end{equation}
+    where $\beta$ is a constant number between 0 and 1.
 
-    \subsection{The Ranking Algorithm}
+    \begin{algorithm}[h]
+        \caption{The Simulated Annealing with Ranking Algorithm}\label{alg:SA}
+        \begin{algorithmic}[1]
+            \Input{search space $\mathbb N^*$}
+            \Parameter Initial temperature $T$, ending temperature $\tau$, a real number between 0 and 1, $r_t$, the number of iteration, $I$, the number of generated neighbours, $N$, a real number, $\alpha$
+            \State Initialize historical best architectures set, $H$
+            \State $s=\text{Randomly sample a architecture from }\Bbb N^*$
+            \While{$T>\tau$}
+                \For{$\text{ each }i \in [1\ldots I]$}
+                    \State $U = \text{neighbour(s, }N\text{)}$
+                    \State $\text{Ranking}(\{s\}\cup U\cup H)$
+                    \State Maintain historical best architectures set, $H$
+                    \State $s'=\text{Best architecture excluding }s$
+                    \State $\Delta E=\text{The difference of rank between }s'\text{ and }s$
+                    \State Sample $x$ from uniform distribution between 0 and 1
+                    \If{$\Delta E<0$}
+                        \State $s\leftarrow s'$
+                    \Else
+                        \If{$x\leq e^{-\alpha\frac{\Delta E}{T}}$}
+                            \State $s\leftarrow s'$
+                        \EndIf
+                    \EndIf
+                \EndFor
+                \State $T\leftarrow T\times r_t$
+            \EndWhile
+            \State $\textbf{Return }s$ \Comment{Return the current architecture}
+        \end{algorithmic}
+    \end{algorithm}
+
+    \subsection{Encoding Schema}
+
+    The encoding schema determines the efficiency of searching. The naïve encoding 
+    schema is to use a binary/integer vector as a representation of an architecture. 
+    For example, NAS-Bench-201 provides 5 operations and 6 nodes to select an cell 
+    and cells form an architecture, which implies the whole search space can be 
+    encoded into a 6 integers vector. However, a broken architecture appears since 
+    one of the operations is zeroize, which means the measurement of the broken 
+    architecture is meaningless. To exclude the broken architectures, the encoding 
+    schema in \cite{10092788} is used in this paper. The detail of the encoding 
+    schema differs from each search spaces, but they all share the common core idea, 
+    preserving the critical path in an architecture. The encoding schema guarantees 
+    that there exists at least one path from input to output in a cell, and no 
+    zeroize operation is in it. Based on the encoding schema, the efficiency of 
+    searching can be improved, since it excludes the broken architectures.
+
+    \subsection{Ranking Algorithm}
+
+    The general proposed ranking algorithm is outlined in \xalg{alg:rank-based}. 
+    The first step is to evaluate the network architectures in the subset, 
+    denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The 
+    evaluation of an architecture determined by $j$-th score function is 
+    denoted $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating the subset 
+    of search space, the rank of each score function is calculated, denoted 
+    $r_{\mathcal F}$. Then the final rank, $r$, calculated by summing up 
+    the ranks. If a network architecture gains higher score in these score 
+    functions, the final rank should be higher (smaller index) too. Therefore, 
+    the highest (minimum) rank in $r$ shall be the best network architecture. 
+    In summary, the rank-based score function makes the contribution of 
+    each score function even, and therefore evaluate an architecture from 
+    different aspects.
+
     \begin{algorithm}[h]
@@
         \begin{algorithmic}[1]
-            \Input{a subspace, ${\mathbb N}^{s}$, from search space, ${\mathbb N}^{*}$}
+            \Input{A subspace, ${\mathbb N}^{s}$, from search space, ${\mathbb N}^{*}$}
             \For{$\text{each }{\mathbb N}^i\text{ in }{\mathbb N}^s$}
@@
 
-    The proposed ranking algorithm is outlined in \xalg{alg:rank-based}. 
-    The first step is to evaluate the network architectures in the subset, 
-    denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The 
-    evaluation of an architecture determined by $j$-th score function is 
-    denoted $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating the subset 
-    of search space, the rank of each score function is calculated, denoted 
-    $r_{\mathcal F}$. Then the final rank, $r$, calculated by summing up 
-    the ranks. If a network architecture gains higher score in these score 
-    functions, the final rank should be higher (smaller index) too. Therefore, 
-    the highest (minimum) rank in $r$ shall be the best network architecture. 
-    In summary, the rank-based score function makes the contribution of 
-    each score function even, and therefore evaluate an architecture from 
-    different aspects. In this paper, NI and NASWOT are used as a complement 
-    set, which take the ability of images generalization and distinction. 
-    Lastly, LogSynFlow complements NI and NASWOT which takes the trainability 
-    into account.
+    With the proposed ranking algorithm as framework, the next question is 
+    to choose score functions that are complementary. The recent training-free 
+    score functions can be roughly classified into different kinds. NASWOT, 
+    linear regions distribution \cite{https://doi.org/10.48550/arxiv.2102.11535} \cite{lin2021zennas}, 
+    maximum entropy of an architecture \cite{sun2022maedet} are measurements 
+    to the ability of distinction and expressivity of an architecture; 
+    NI is a measurement to the ability of image generalization of an architecture; 
+    the condition number of NTK, modified version of SNIP, GraSP, SynFlow, and 
+    LogSynFlow are measurements to the ability of trainability of an architecture. 
+    As mentioned, the chosen score function shall be complementary to each other. 
+    In this paper, NI and NASWOT are used as a complementary set, which take 
+    the ability of images generalization and distinction into account. 
+    These complementary set can be generalized as the ability of the graphic 
+    recognition. Therefore, the last missing piece is trainability of an 
+    architecture, which, LogSynFlow is chosen to measure it.
 
-    \subsection{Simulated Annealing with Rank-Based Score function}
+    \section{Experiment Result}
+    \label{sec:results}
 
-    \begin{algorithm}[h]
-        \caption{The Simulated Annealing with Ranking Algorithm}\label{alg:SA}
-        \begin{algorithmic}[1]
-            \Input{search space $\mathbb N^*$, initial temperature $T$, ending temperature $\tau$, 
-            a real number between 0 and 1, $\alpha$, the number of iteration, $I$}
-            \State $s^*=s=\text{sample a random architecture from }\Bbb N^*$
-            \While{$T>\tau$}
-                \For{$\text{ each }i \in [1\ldots I]$}
-                    \State $r=\text{Ranking}(\{s\}\cup U(s))$ \Comment{Ranking $s$ with the neighbourhood of $s$, denoted $U(s)$}
-                    \State $s^*=\arg\min\{r(\Bbb N^i)\}$ \Comment{Update the expected best algorithm}
-                    \State $\Delta E=r(s^*)-r(s)$
-                    \State $x\sim \mathcal U(0,1)$ \Comment{Sample $x$ from a uniform distribution between 0 and 1}
-                    \If{$x\geq e^{\frac{\Delta E}{T}}$} \Comment{Accept by probability}
-                        \State $s\leftarrow s^*$
-                    \EndIf
-                \EndFor
-                \State $T\leftarrow T\times \alpha$
-            \EndWhile
-            \State $\textbf{Return }s^*$ \Comment{Return the best architecture}
-        \end{algorithmic}
-    \end{algorithm}
+    We evalute the performance of the proposed algorithm, \palg, 
+    for searching the architectures of high accuracy. For comparison, several NAS 
+    algorithms are included, e.g., random search (RS), regularized evolution algorithm 
+    (REA) \cite{real2019regularized}, reinforcement learning (RL) \cite{Williams:92}, 
+    Bayesian optimization with hyper band (BOHB) \cite{falkner2018bohb}, RS with 
+    weight-sharing (RSWS) \cite{li2019random}, differentiable architecture search 
+    with first order (DARTS-V1) \cite{liu2019darts}, DARTS with second order 
+    (DARTS-V2) \cite{liu2019darts}, gradient-based search using differentiable 
+    architecture sampler (GDAS) \cite{dong2019searching}, self-evaluated template 
+    network (SETN) \cite{Dong_2019}, efficient NAS (ENAS) \cite{pham2018efficient}, 
+    assisted REA (AREA) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
+    zero-cost NAS \cite{https://doi.org/10.48550/arxiv.2101.08134}, 
+    TE-NAS \cite{https://doi.org/10.48550/arxiv.2102.11535}, gradient kernel-based 
+    NAS (KNAS) \cite{xu2021knas}, RS with NASWOT \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
+    RS with noise immunity (NI) \cite{10092788}, and RS with LogSynFlow \cite{Cavagnero_2023}.
 
-    The modified version of the simulated annealing algorithm with ranking algorithm 
-    is outlined in \xalg{alg:SA}. The first step is to sample a architecture, denoted 
-    $s$, from search space. Then use $s$ as a "seed" to generate the neighbourhood of it, 
-    applying ranking algorithm on the neighbourhood, $\{s\}\cup U(s)$. After ranking, 
-    the expected best architecture can be determined and update, but the seed for next 
-    iteration will be replaced by $s^*$ according to probability, $e^{\frac{\Delta E}{T}}$.
-    After the $I$ iterations, the temperature scales down by $\alpha$. The algorithm 
-    is done when $T\leq\tau$, and the best architecture will be retruned.
+    The three search spaces, NATS-bench-SSS, NATS-bench-TSS 
+    \cite{Dong_2021} and NAS-Bench-101 \cite{ying2019nasbench101}, are used 
+    here to evalute the performance of the NAS algorithms. The architectures 
+    of NATS-bench-TSS is same as NAS-Bench-201 \cite{dong2020nasbench201}. 
+    The architectures in NATS-bench-SSS and NATS-bench-TSS are trained by the three datasets: 
+    CIFAR10, CIFAR100, ImageNet-16-120, while NAS-Bench-101 is trained by one: 
+    CIFAR10.
 
-    %\begin{figure*}[htb]
-    %    \centering
-    %    \hspace*{-\baselineskip}
-    %    \vspace*{-\baselineskip}
-    %    \includegraphics[]{asset/SA.pdf}
-    %    \caption{A simple example to illustrate an iteration of SA with Rank-based score function.}
-    %    \label{fig:SA}
-    %\end{figure*}
-    %\xfig{fig:SA} illustrates how SA with rank-based score function works in an iteration.
-
-    \section{experiment result}
-    \label{sec:results}
     \subsection{Environment and Parameter Settings}
@@
     65 GB available memory running on Ubuntu 20.04.1 with linux kernel 5.15.0-73-generic. All the program 
-    is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. 
+    is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. The simulations of all 
+    nonweight sharing NASs are carried out for 500 runs on all the search spaces except AREA which is 50 runs. 
+    For weight sharing NAS algorithms, each is carried out for 3 runs. And for training-free 
+    algorithms, each is carried out for 100 runs and are given an evaluation 
+    budget of 1000 for all the search space. The parameter settings of \palg are as follows: 
+    initial temperature, ending temperature, rate of decrease of temperature, the number of iteration, 
+    the constant number adjusting acceptance probability, the number of generated neighbours are set 
+    to 1, 0.0008, 0.745, 4, 0.25, 10, so that the maximum number of searching candidates is 1000.
+
     \subsection{NATS-bench-SSS}
-    The result of NATS-bench-SSS is shown in \xtab{table:overall_sss}.
+    In \xtab{table:overall_sss}, the proposed NAS algorithm and ranking function is 
+    compared with the other five nonweight sharing algorithm and NI, NASWOT, LogSynFlow. 
+    For fairness, the searching candidates for the training-free score functions, i.e., 
+    NI, NASWOT, LogSynFlow, Rank, are identical. The performance of ranking function 
+    is similar to NI and lower than LogSynFlow. However, the proposed NAS algorithm 
+    imporved the results significantly and outperforms almost all the compared algorithms.
+
+    %\begin{table*}[htb]
+    %    %\normalsize
+    %    %\centering
+    %    \newcommand{\z}{\phantom{0}}
+    %    \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-SSS.}}
+    %      \vspace{-\baselineskip}
+    %    \begin{tabular}{@{}lccccccc@{}}\toprule
+    %    Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
+    %    & & validation & test & validation & test & validation & test \\ \midrule
+    %    &&&&\textbf{Non-weight sharing}&&&\\
+    %    AREA      & $12,000$ & $84.62 \pm \z{0.41}$                & $93.16 \pm 0.16$               & $59.24 \pm \z{1.11}$                 & $69.56 \pm \z{0.96}$                & $37.58 \pm 1.09$                 & $45.30 \pm \z{0.91}$                \\
+    %    REA       & $12,000$ & $90.26 \pm \z{0.22}$                & $93.17 \pm 0.21$               & $69.48 \pm \z{0.76}$                 & $69.49 \pm \z{0.94}$                & $44.84 \pm 0.72$                 & $45.47 \pm \z{0.91}$                \\
+    %    RS        & $12,000$ & $90.08 \pm \z{0.24}$                & $93.01 \pm 0.29$               & $69.14 \pm \z{0.94}$                 & $69.17 \pm \z{1.00}$                & $44.66 \pm 1.02$                 & $44.83 \pm \z{1.05}$                \\
+    %    RL        & $12,000$ & $90.17 \pm \z{0.23}$                & $93.08 \pm 0.21$               & $69.23 \pm \z{0.87}$                 & $69.29 \pm \z{1.08}$                & $44.68 \pm 0.91$                 & $45.05 \pm \z{0.93}$                \\
+    %    BOHB      & $12,000$ & $90.05 \pm \z{0.30}$                & $93.03 \pm 0.20$               & $69.04 \pm \z{0.76}$                 & $69.16 \pm \z{0.90}$                & $44.71 \pm 0.78$                 & $44.91 \pm \z{1.05}$                \\ \midrule
+    %    %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
+    %    &&&&\textbf{Training-free}&&&\\
+    %    NI (N=1,000)         & $X$ & $89.56\pm \z{0.147}$ & $92.55\pm 0.187$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+    %    NASWOT (N=1,000)     & $X$ & $89.25\pm \z{0.412}$ & $92.21\pm 0.298$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+    %    LogSynFlow (N=1,000) & $X$ & $89.61\pm \z{0.101}$ & $92.60\pm 0.188$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+    %    rk (N=1000)          & $X$ & $89.59\pm \z{0.136}$ & $92.51\pm 0.171$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+    %    GA-rk                & $457.54$ & $90.29\pm \z{0.149}$ & $93.27\pm0.193$ & $69.88\pm \z{0.497}$ & $70.06\pm \z{0.481}$ & $45.57\pm 0.425$ & $46.19\pm \z{0.846}$ \\ 
+    %    SA-rk                & $682.36$ & $90.37\pm \z{0.204}$ & $93.29\pm0.182$ & $70.11\pm \z{0.457}$ & $70.32\pm \z{0.458}$ & $45.38\pm 0.499$ & $46.45\pm \z{0.687}$ \\ \bottomrule
+    %    \end{tabular}
+    %    \label{table:overall_sss}
+    %      \vspace{-\baselineskip}
+    %\end{table*}
+
     \begin{table*}[htb]
@@
                              &          & validation       & test             & validation       & test              & validation       & test \\ \midrule
-        &&&&\textbf{Non-weight sharing}&&&\\
-        AREA      & $12,000$ & $84.62 \pm \z{0.41}$                & $93.16 \pm 0.16$               & $59.24 \pm \z{1.11}$                 & $69.56 \pm \z{0.96}$                & $37.58 \pm 1.09$                 & $45.30 \pm \z{0.91}$                \\
-        REA       & $12,000$ & $90.26 \pm \z{0.22}$                & $93.17 \pm 0.21$               & $69.48 \pm \z{0.76}$                 & $69.49 \pm \z{0.94}$                & $44.84 \pm 0.72$                 & $45.47 \pm \z{0.91}$                \\
-        RS        & $12,000$ & $90.08 \pm \z{0.24}$                & $93.01 \pm 0.29$               & $69.14 \pm \z{0.94}$                 & $69.17 \pm \z{1.00}$                & $44.66 \pm 1.02$                 & $44.83 \pm \z{1.05}$                \\
-        RL        & $12,000$ & $90.17 \pm \z{0.23}$                & $93.08 \pm 0.21$               & $69.23 \pm \z{0.87}$                 & $69.29 \pm \z{1.08}$                & $44.68 \pm 0.91$                 & $45.05 \pm \z{0.93}$                \\
-        BOHB      & $12,000$ & $90.05 \pm \z{0.30}$                & $93.03 \pm 0.20$               & $69.04 \pm \z{0.76}$                 & $69.16 \pm \z{0.90}$                & $44.71 \pm 0.78$                 & $44.91 \pm \z{1.05}$                \\ \midrule
-        %&& Search (s) & test & Search(s) & test & Search(s) & test \\ \midrule
-        &&&&\textbf{Training-free}&&&\\
-        NI (N=1,000)         & $X$ & $89.56\pm \z{0.147}$ & $92.55\pm 0.187$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        NASWOT (N=1,000)     & $X$ & $89.25\pm \z{0.412}$ & $92.21\pm 0.298$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        LogSynFlow (N=1,000) & $X$ & $89.61\pm \z{0.101}$ & $92.60\pm 0.188$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        rk (N=1000)          & $X$ & $89.59\pm \z{0.136}$ & $92.51\pm 0.171$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        GA-rk                & $457.54$ & $90.29\pm \z{0.149}$ & $93.27\pm0.193$ & $69.88\pm \z{0.497}$ & $70.06\pm \z{0.481}$ & $45.57\pm 0.425$ & $46.19\pm \z{0.846}$ \\ 
-        SA-rk                & $682.36$ & $90.37\pm \z{0.204}$ & $93.29\pm0.182$ & $70.11\pm \z{0.457}$ & $70.32\pm \z{0.458}$ & $45.38\pm 0.499$ & $46.45\pm \z{0.687}$ \\ \bottomrule
+                             &          &                  &                  & \textbf{Non-weight sharing} &        &                  &                  \\
+        AREA                 & $12,000$ & $84.62 \pm 0.41$ & $93.16 \pm 0.16$ & $59.24 \pm 1.11$ & $69.56 \pm 0.96$  & $37.58 \pm 1.09$ & $45.30 \pm 0.91$ \\
+        REA                  & $12,000$ & $90.37 \pm 0.20$ & $93.22 \pm 0.16$ & $70.23 \pm 0.50$ & $70.11 \pm 0.61$  & $45.30 \pm 0.69$ & $45.94 \pm 0.92$ \\
+        RS                   & $12,000$ & $90.10 \pm 0.26$ & $93.03 \pm 0.25$ & $69.57 \pm 0.57$ & $69.72 \pm 0.61$  & $45.01 \pm 0.74$ & $45.42 \pm 0.86$ \\
+        RL                   & $12,000$ & $90.25 \pm 0.23$ & $93.16 \pm 0.21$ & $69.84 \pm 0.59$ & $69.96 \pm 0.57$  & $45.06 \pm 0.77$ & $45.71 \pm 0.93$ \\
+        BOHB                 & $12,000$ & $90.07 \pm 0.28$ & $93.01 \pm 0.24$ & $69.75 \pm 0.60$ & $69.90 \pm 0.60$  & $45.11 \pm 0.69$ & $45.56 \pm 0.81$ \\ \midrule
+                             &          &                  &                  & \textbf{Training-free} &             &                  &                  \\
+        NI (N=1,000)         & $293$    & $89.55 \pm 0.16$ & $92.56 \pm 0.21$ & $67.67 \pm 0.91$ & $67.61 \pm 1.06$  & $43.19 \pm 0.73$ & $43.22 \pm 0.53$ \\ 
+        NASWOT (N=1,000)     & $208$    & $89.25 \pm 0.44$ & $92.21 \pm 0.31$ & $65.09 \pm 2.89$ & $64.61 \pm 3.16$  & $41.29 \pm 2.32$ & $41.35 \pm 2.31$ \\ 
+        LogSynFlow (N=1,000) & $123$    & $89.60 \pm 0.11$ & $92.61 \pm 0.18$ & $68.23 \pm 0.49$ & $68.30 \pm 0.54$  & $43.58 \pm 0.58$ & $43.48 \pm 0.40$ \\ 
+        rank (N=1000)        & $612$    & $89.59 \pm 0.14$ & $92.51 \pm 0.17$ & $67.56 \pm 0.75$ & $67.55 \pm 0.82$  & $43.36 \pm 0.62$ & $43.27 \pm 0.45$ \\ 
+        \palg                & $712$    & $90.38 \pm 0.20$ & $93.30 \pm 0.19$ & $69.94 \pm 0.46$ & $70.24 \pm 0.42$  & $45.41 \pm 0.49$ & $46.39 \pm 0.69$ \\ \midrule
+        \palg ver2           & $X$      & $X \pm X$        & $X \pm X$        & $X \pm X$        & $X \pm X$         & $X \pm X$        & $46.43 \pm 0.75$ \\ \midrule
+        Optimal              &          & $90.71$          & $93.65$          & $70.92$          & $71.34$           & $46.73$          & $47.40$          \\ \bottomrule
         \end{tabular}
@@
 
-    \subsection{NAS-Bench-201}
-    The result of NAS-Bench-201 is shown in \xtab{table:overall_201}.
+    \subsection{NATS-Bench-TSS}
+    The result of NATS-Bench-TSS is shown in \xtab{table:overall_201}.
+    %\begin{table*}[htb]
+    %    %\normalsize
+    %    %\centering
+    %    \newcommand{\z}{\phantom{0}}
+    %    \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-201.}}
+    %      \vspace{-\baselineskip}
+    %    \begin{tabular}{@{}lrcccccc@{}}\toprule
+    %    Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
+    %    & & validation & test & validation & test & validation & test \\ \midrule
+    %    &&&&\textbf{Non-weight sharing}&&&\\
+    %    AREA      & $12,000$ & $91.18 \pm \z{0.43}$                & $93.95 \pm \z{0.39}$               & $71.84 \pm \z{1.21}$                 & $71.92 \pm \z{1.29}$                & $45.04 \pm 1.03$                 & $45.40 \pm 1.14$                \\
+    %    REA       & $12,000$ & $91.08 \pm \z{0.54}$                & $93.89 \pm \z{0.50}$               & $71.69 \pm \z{1.34}$                 & $71.83 \pm \z{1.33}$                & $44.96 \pm 1.41$                 & $45.30 \pm 1.51$                \\
+    %    RS        & $12,000$ & $90.91 \pm \z{0.33}$                & $93.67 \pm \z{0.33}$               & $70.91 \pm \z{1.04}$                 & $70.99 \pm \z{0.99}$                & $44.52 \pm 0.99$                 & $44.56 \pm 1.25$                \\
+    %    RL        & $12,000$ & $90.87 \pm \z{0.41}$                & $93.63 \pm \z{0.36}$               & $70.62 \pm \z{1.08}$                 & $70.77 \pm \z{1.05}$                & $44.20 \pm 1.22$                 & $44.23 \pm 1.37$                \\
+    %    BOHB      & $12,000$ & $88.47 \pm \z{1.19}$                & $91.79 \pm \z{1.11}$               & $67.18 \pm \z{2.05}$                 & $67.50 \pm \z{2.05}$                & $38.94 \pm 3.58$                 & $39.00 \pm 3.73$                \\ \midrule
+    %    &&&&\textbf{Weight sharing}&&&\\
+    %    RSWS      & $4,154$  & $76.95 \pm 16.74$                   & $82.60 \pm 12.10$                  & $52.51 \pm 18.33$                    & $52.93 \pm 18.32$                   & $29.76 \pm 9.50$                 & $29.16 \pm 9.61$                \\
+    %    DARTS-V1  & $5,475$  & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm 0.00$                \\
+    %    DARTS-V2  & $16,114$ & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm 0.00$                \\
+    %    GDAS      & $11,183$ & $90.05 \pm \z{0.23}$                & $93.46 \pm \z{0.13}$               & $71.02 \pm \z{0.31}$                 & $70.56 \pm \z{0.24}$                & $41.77 \pm 1.24$                 & $41.96 \pm 0.90$                \\
+    %    SETN      & $16,787$ & $84.25 \pm \z{5.05}$                & $88.01 \pm \z{4.52}$               & $59.72 \pm \z{7.30}$                 & $59.91 \pm \z{7.51}$                & $33.93 \pm 3.85$                 & $33.48 \pm 4.22$                \\
+    %    ENAS      & $7,061$  & $40.11 \pm \z{3.28}$                & $56.33 \pm \z{3.70}$               & $14.09 \pm \z{1.60}$                 & $14.77 \pm \z{1.45}$                & $16.20 \pm 0.48$                 & $15.93 \pm 0.67$                \\ \midrule
+    %    &&&&\textbf{Training-free}&&&\\
+    %    NI (N=1,000)         & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+    %    NASWOT (N=1,000)     & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+    %    LogSynFlow (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+    %    rk (N=1000)          & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
+    %    GA-rk                & $747.25$ & $89.93\pm \z{0.196}$ & $93.41\pm0.083$ & $70.70\pm \z{0.417}$ & $70.76\pm \z{0.378}$ & $42.70\pm 1.315$ & $43.10\pm \z{1.428}$ \\ 
+    %    SA-rk                & $X$ & $89.95\pm \z{0.194}$ & $93.37\pm0.114$ & $70.69\pm \z{0.391}$ & $70.75\pm \z{0.532}$ & $X\pm X$ & $43.10\pm \z{1.506}$ \\ \bottomrule
+    %    \end{tabular}
+    %    \label{table:overall_201}
+    %      \vspace{-\baselineskip}
+    %\end{table*}
     \begin{table*}[htb]
@@
         \newcommand{\z}{\phantom{0}}
-        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-201.}}
+        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-TSS.}}
           \vspace{-\baselineskip}
@@
                              &          & validation           & test             & validation           & test             & validation       & test \\ \midrule
-        &&&&\textbf{Non-weight sharing}&&&\\
-        AREA      & $12,000$ & $91.18 \pm \z{0.43}$                & $93.95 \pm \z{0.39}$               & $71.84 \pm \z{1.21}$                 & $71.92 \pm \z{1.29}$                & $45.04 \pm 1.03$                 & $45.40 \pm 1.14$                \\
-        REA       & $12,000$ & $91.08 \pm \z{0.54}$                & $93.89 \pm \z{0.50}$               & $71.69 \pm \z{1.34}$                 & $71.83 \pm \z{1.33}$                & $44.96 \pm 1.41$                 & $45.30 \pm 1.51$                \\
-        RS        & $12,000$ & $90.91 \pm \z{0.33}$                & $93.67 \pm \z{0.33}$               & $70.91 \pm \z{1.04}$                 & $70.99 \pm \z{0.99}$                & $44.52 \pm 0.99$                 & $44.56 \pm 1.25$                \\
-        RL        & $12,000$ & $90.87 \pm \z{0.41}$                & $93.63 \pm \z{0.36}$               & $70.62 \pm \z{1.08}$                 & $70.77 \pm \z{1.05}$                & $44.20 \pm 1.22$                 & $44.23 \pm 1.37$                \\
-        BOHB      & $12,000$ & $88.47 \pm \z{1.19}$                & $91.79 \pm \z{1.11}$               & $67.18 \pm \z{2.05}$                 & $67.50 \pm \z{2.05}$                & $38.94 \pm 3.58$                 & $39.00 \pm 3.73$                \\ \midrule
-        &&&&\textbf{Weight sharing}&&&\\
-        RSWS      & $4,154$  & $76.95 \pm 16.74$                   & $82.60 \pm 12.10$                  & $52.51 \pm 18.33$                    & $52.93 \pm 18.32$                   & $29.76 \pm 9.50$                 & $29.16 \pm 9.61$                \\
-        DARTS-V1  & $5,475$  & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm 0.00$                \\
-        DARTS-V2  & $16,114$ & $39.77 \pm \z{0.00}$                & $54.30 \pm \z{0.00}$               & $15.03 \pm \z{0.00}$                 & $15.61 \pm \z{0.00}$                & $16.43 \pm 0.00$                 & $16.32 \pm 0.00$                \\
-        GDAS      & $11,183$ & $90.05 \pm \z{0.23}$                & $93.46 \pm \z{0.13}$               & $71.02 \pm \z{0.31}$                 & $70.56 \pm \z{0.24}$                & $41.77 \pm 1.24$                 & $41.96 \pm 0.90$                \\
-        SETN      & $16,787$ & $84.25 \pm \z{5.05}$                & $88.01 \pm \z{4.52}$               & $59.72 \pm \z{7.30}$                 & $59.91 \pm \z{7.51}$                & $33.93 \pm 3.85$                 & $33.48 \pm 4.22$                \\
-        ENAS      & $7,061$  & $40.11 \pm \z{3.28}$                & $56.33 \pm \z{3.70}$               & $14.09 \pm \z{1.60}$                 & $14.77 \pm \z{1.45}$                & $16.20 \pm 0.48$                 & $15.93 \pm 0.67$                \\ \midrule
-        &&&&\textbf{Training-free}&&&\\
-        NI (N=1,000)         & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        NASWOT (N=1,000)     & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        LogSynFlow (N=1,000) & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        rk (N=1000)          & $X$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ & $X\pm \z{X}$ & $X\pm X$ & $X\pm \z{X}$ \\ 
-        GA-rk                & $747.25$ & $89.93\pm \z{0.196}$ & $93.41\pm0.083$ & $70.70\pm \z{0.417}$ & $70.76\pm \z{0.378}$ & $42.70\pm 1.315$ & $43.10\pm \z{1.428}$ \\ 
-        SA-rk                & $X$ & $89.95\pm \z{0.194}$ & $93.37\pm0.114$ & $70.69\pm \z{0.391}$ & $70.75\pm \z{0.532}$ & $X\pm X$ & $43.10\pm \z{1.506}$ \\ \bottomrule
+                             &          &                      &                  & \textbf{Non-weight sharing} &           &                  &                  \\
+        AREA                 & $12,000$ & $91.18 \pm \z{0.43}$ & $93.95 \pm 0.39$ & $71.84 \pm \z{1.21}$ & $71.92 \pm 1.29$ & $45.04 \pm 1.03$ & $45.40 \pm 1.14$ \\
+        REA                  & $12,000$ & $91.25 \pm \z{0.31}$ & $94.02 \pm 0.31$ & $72.28 \pm \z{0.95}$ & $72.23 \pm 0.84$ & $45.71 \pm 0.77$ & $45.77 \pm 0.80$ \\
+        RS                   & $12,000$ & $91.07 \pm \z{0.26}$ & $93.86 \pm 0.23$ & $71.46 \pm \z{0.97}$ & $71.55 \pm 0.97$ & $45.03 \pm 0.91$ & $45.28 \pm 0.97$ \\
+        RL                   & $12,000$ & $91.12 \pm \z{0.25}$ & $93.90 \pm 0.26$ & $71.80 \pm \z{0.94}$ & $71.86 \pm 0.89$ & $45.37 \pm 0.74$ & $45.64 \pm 0.78$ \\
+        BOHB                 & $12,000$ & $91.17 \pm \z{0.27}$ & $93.94 \pm 0.28$ & $72.04 \pm \z{0.93}$ & $72.00 \pm 0.86$ & $45.55 \pm 0.79$ & $45.70 \pm 0.86$ \\ \midrule
+                             &          &                      &                  & \textbf{Weight sharing} &               &                  &                  \\
+        RSWS                 & $4,154$  & $87.60 \pm \z{0.61}$ & $91.05 \pm 0.66$ & $68.27 \pm \z{0.72}$ & $68.26 \pm 0.96$ & $39.73 \pm 0.34$ & $40.69 \pm 0.36$ \\
+        DARTS-V1             & $5,475$  & $49.27 \pm 13.44$    & $59.84 \pm 7.84$ & $61.08 \pm \z{4.37}$ & $61.26 \pm 4.43$ & $38.07 \pm 2.90$ & $37.88 \pm 2.91$ \\
+        DARTS-V2             & $16,114$ & $58.78 \pm 13.44$    & $65.38 \pm 7.84$ & $59.48 \pm \z{5.13}$ & $60.49 \pm 4.95$ & $37.56 \pm 7.10$ & $36.79 \pm 7.59$ \\
+        GDAS                 & $11,183$ & $89.68 \pm \z{0.72}$ & $93.23 \pm 0.13$ & $68.35 \pm \z{2.71}$ & $68.17 \pm 2.50$ & $39.55 \pm 0.00$ & $39.40 \pm 0.00$ \\
+        SETN                 & $16,787$ & $90.00 \pm \z{0.97}$ & $92.72 \pm 4.52$ & $69.19 \pm \z{1.42}$ & $69.36 \pm 1.72$ & $39.77 \pm 0.33$ & $39.51 \pm 0.33$ \\
+        ENAS                 & $7,061$  & $90.20 \pm \z{0.00}$ & $93.76 \pm 0.00$ & $70.21 \pm \z{0.71}$ & $70.67 \pm 0.62$ & $40.78 \pm 0.00$ & $41.44 \pm 0.00$ \\ \midrule
+                             &          &                      &                  & \textbf{Training-free} &                &                  &                  \\
+        NI (N=1,000)         & $X$      & $X \pm \z{X}$        & $93.21 \pm 0.63$ & $X \pm \z{X}$        & $70.40 \pm 0.84$ & $X \pm X$        & $43.34 \pm 2.43$ \\ 
+        NASWOT (N=1,000)     & $X$      & $X \pm \z{X}$        & $92.80 \pm 1.07$ & $X \pm \z{X}$        & $69.66 \pm 1.23$ & $X \pm X$        & $43.84 \pm 2.93$ \\ 
+        LogSynFlow (N=1,000) & $X$      & $X \pm \z{X}$        & $92.92 \pm 0.70$ & $X \pm \z{X}$        & $68.98 \pm 1.97$ & $X \pm X$        & $40.23 \pm 6.45$ \\ 
+        rank (N=1000)        & $X$      & $X \pm \z{X}$        & $93.32 \pm 0.42$ & $X \pm \z{X}$        & $70.10 \pm 1.45$ & $X \pm X$        & $44.07 \pm 2.19$ \\ 
+        \palg                & $X$      & $X \pm \z{X}$        & $\approx93\pm 2$ & $X \pm \z{X}$        & $70.30 \pm 1.26$ & $X \pm X$        & $\approx43\pm 4$ \\ \midrule
+        \palg ver2           & $X$      & $X \pm X$            & $93.55 \pm 0.22$ & $X \pm X$            & $70.63 \pm 0.66$ & $X \pm X$        & $44.63 \pm 1.64$ \\ \midrule
+        Optimal              &          & $91.61$              & $94.37$          & $73.49$              & $73.51$          & $46.73$          & $47.31$          \\ \bottomrule
         \end{tabular}
@@
       The result of NAS-Bench-101 is shown in \xtab{table:overall_101}.
-      \begin{table}[htb]
+      \begin{table*}[t]
         %\normalsize
@@
                                  &            & validation       & test             \\ \midrule
-               &            &            \textbf{Non-weight sharing}&\\
-        AREA   & $12,000$   & $93.67 \pm \z{0.48}$  & $93.02 \pm \z{0.48}$\\
-        REA    & $12,000$   & $93.63 \pm \z{0.50}$  & $93.02 \pm \z{0.52}$\\ \midrule
-               &            &            \textbf{Weight sharing}&\\
-        DARTS-V1 & $20,483$ & $83.50 \pm \z{0.11}$ & $83.74 \pm \z{0.03}$ \\
-        ENAS     & $22,325$ & $93.83 \pm \z{0.28}$ & $93.34 \pm \z{0.26}$ \\ \midrule
-                 &          &            \textbf{Training-free}&\\
-        Zero-Cost NASWOT     & $18,940$  & $91.72 \pm \z{1.80}$ & $91.29 \pm \z{1.82}$ \\
-        NI (N=1,000)         & $280$ & $93.15 \pm \z{1.48}$ & $92.72 \pm \z{1.06}$ \\ 
-        NASWOT (N=1,000)     & $162$ & $92.40 \pm \z{4.07}$ & $91.97 \pm \z{4.20}$ \\ 
-        LogSynFlow (N=1,000) & $105$ & $90.70 \pm \z{8.41}$ & $90.98 \pm \z{2.56}$ \\ 
-        rank (N=1000)        & $516$ & $92.84 \pm \z{1.19}$ & $92.51 \pm \z{1.14}$ \\ 
-        GA-rank              & $X$   & $X \pm X$ & $X\pm X$\\ 
-        SA-rank              & $374$ & $93.01 \pm \z{1.19}$ & $92.37 \pm \z{1.63}$  \\ \bottomrule
+                                 &            & \textbf{Non-weight sharing} &       \\
+            AREA                 & $12,000$   & $93.67 \pm 0.48$ & $93.02 \pm 0.48$ \\
+            REA                  & $12,000$   & $93.63 \pm 0.50$ & $93.02 \pm 0.52$ \\ \midrule
+                                 &            &            \textbf{Weight sharing}& \\
+            DARTS-V1             & $20,483$   & $83.50 \pm 0.11$ & $83.74 \pm 0.03$ \\
+            ENAS                 & $22,325$   & $93.83 \pm 0.28$ & $93.34 \pm 0.26$ \\ \midrule
+                                 &            & \textbf{Training-free} &            \\
+            Zero-Cost NASWOT     & $18,940$   & $91.72 \pm 1.80$ & $91.29 \pm 1.82$ \\
+            NI (N=1,000)         & $280$      & $92.89 \pm 2.10$ & $92.55 \pm 1.33$ \\ 
+            NASWOT (N=1,000)     & $162$      & $92.27 \pm 6.60$ & $92.10 \pm 4.44$ \\ 
+            LogSynFlow (N=1,000) & $105$      & $91.81 \pm 1.52$ & $91.21 \pm 1.71$ \\ 
+            rank (N=1000)        & $516$      & $92.44 \pm 1.42$ & $91.94 \pm 2.01$ \\ 
+            \palg                & $374$      & $92.89 \pm 3.24$ & $92.77 \pm 1.01$ \\ \bottomrule
+            \palg ver2           & $374$      & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \bottomrule
+            Optimal              &            & $X$              & $94.32$          \\ \bottomrule
             \end{tabular}
@@
           \vspace{-\baselineskip}
-      \end{table}
+      \end{table*}
 
@@
     \label{sec:conclusion}
+    In this paper, a novel concept of "complementary" is proposed and used as a basis to choose 
+    traning-free score functions. The new ranking algorithm is then applied on simulated annealing 
+    algorithm. The simulation result shows that the proposed algorithm, namely SA-rk, not only outperforms the most 
+    state-of-art traning-free score functions, but also some of the nontraning-free methods. 
+    The proposed algorithm also shows the robustness, which performs well between different search 
+    spaces vary with neural network structures and size. 
+    The limitation of SA-rk is the lack of versatility, since the score functions are mainly chosen 
+    for common image recognition. That means SA-rk may not be applied on the search of architectures 
+    designed for other usages, i.e, speech recognition, NLP. However, the problem is able to be solved 
+    by choosing the corresponding complementary score functions. Some further questions are that how many 
+    score functions are required for precisely estimating the performance of architectures and what are they?
 

### 2023-07-24 paper/manuscript.tex
rename

%\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
\documentclass[sigconf]{acmart}
\let\Bbbk\relax %% fix bug
\usepackage[utf8]{inputenc}

% =======================
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{amsopn}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\usepackage{textcomp}

\usepackage{boxedminipage}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{url}
\usepackage{times}
\usepackage{version}
% \usepackage[pdftex]{graphicx}
\usepackage{epsfig}
\usepackage{epsf}
%\usepackage{graphics}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{algorithm}
\usepackage{algpseudocode}
%\PassOptionsToPackage{bookmarks={false}}{hyperref}
%%%%%%%%%%%%
\usepackage{comment}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{dblfloatfix}
% ==========================
\input lstset.tex
\input macros.tex

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\algrenewcommand\alglinenumber[1]{\footnotesize #1}

\algnewcommand\algorithmicassume{\textbf{Assumption:}}
\algnewcommand\Assume{\item[\algorithmicassume]}

\algnewcommand\algorithmicinput{\textbf{Input:}}
\algnewcommand\Input{\item[\algorithmicinput]}

\algnewcommand\algorithmicparameter{\textbf{Parameter:}}
\algnewcommand\Parameter{\item[\algorithmicparameter]}

\begin{document}

\title{Rank-based Training-Free NAS Algorithm}

\author{Hsieh Cheng-Han}
\email{emiliaistruelove@gmail.com}
\affiliation{%
  \institution{Department of Computer Science and Engineering, National Sun Yat-sen University}
  \streetaddress{70 Lienhai Rd}
  \city{Kaohsiung}
  \country{Taiwan}
}

\author{Chun-Wei Tsai}
\email{cwtsai@mail.cse.nsysu.edu.tw}
\affiliation{%
  \institution{Department of Computer Science and Engineering, National Sun Yat-sen University}
  \streetaddress{70 Lienhai Rd}
  \city{Kaohsiung}
  \country{Taiwan}
}

\begin{abstract}
    The training-free neural architecture search (NAS) typically uses one or 
    two score functions to evaluate how a neural network architecture performs. 
    However, an architecture shall be treated as a complex system that has 
    distinct characteristics to measure. 
    To achieve the goal, we propose a rank-based training-free NAS algorithm, 
    which combines three training-free score functions which is "complementary" 
    to each other to evaluate an architecture by ranking. 
    In this work, noise immunity (NI) considers the image generalization 
    ability of the architecture, the correlation between binary activation 
    patterns, named NASWOT, considers image distinction ability, and LogSynFlow 
    takes trainability into account. With that, a modified version of simulated 
    annealing (SA) algorithm, \palg{}, can apply and obtain a better 
    performance on searching high-accuracy architectures. 
    To evaluate the performance of the proposed algorithm, this paper compared 
    it with several NAS algorithms, including weight sharing methods, 
    non-weight sharing methods, and several state-of-the-art training-free 
    score functions. The final result indicates that \palg{} outperforms most 
    training-free score functions and shows the robustness between different 
    search spaces.

\end{abstract}
\maketitle

\section{Introduction}
\label{sec:introduction}

% introduction
    Neural architecture search (NAS) has recently drawn a big amount of 
    attention, since the ability to automatically design a "good" neural 
    architecture. By leveraging machine learning algorithms 
    \cite{https://doi.org/10.48550/arxiv.1611.01578}, NAS algorithms can 
    explore a search space, which is comprised of numerous potential 
    architectures, to find out the architectures that outperform those 
    designed by human experts. Recently, the use of NAS has been widespread, 
    from object detection \cite{https://doi.org/10.48550/arxiv.2111.13336}, 
    image recognition \cite{https://doi.org/10.48550/arxiv.2006.04647} 
    and speech recognition \cite{https://doi.org/10.48550/arxiv.2011.05649} 
    \cite{mehrotra2021nasbenchasr} to natural language processing (NLP). 
    \cite{jiang-etal-2019-improved} \cite{https://doi.org/10.48550/arxiv.2006.07116} 
    \cite{https://doi.org/10.48550/arxiv.2005.14187} 
    Despite the promising results of NAS, there are still many challenges 
    to conquer. One major problem is the extremely high computational 
    cost for searching an optimal architecture, which makes NAS 
    impractical for real-world applications, particularly on resource-constrained 
    platforms like embedded system. The reason why NAS is costly is that 
    during searching, a candidate architecture must be trained to 
    evaluate how good of this architecture.

    To overcome this challenge, recent works developed and proposed lots 
    of methods which is so called training-free NAS. 
    % NASWOT
    For example, Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} 
    proposed the measurement of the correlation between the binary 
    activation paterns, induced by the untrained network at two inputs, 
    abbreviated as NASWOT. 
    % synflow
    On the other hand, Lee et al. \cite{lee2019snip} proposed pruning 
    parameters based on a saliency matric, which is then extended by Tanaka 
    et al. \cite{tanaka2020pruning}. In \cite{tanaka2020pruning}, Tanaka 
    et al. proposed Iterative Synaptic Flow Pruning (SynFlow) algorithm 
    which intends to deal with the layer collapse problem when pruning a 
    network. The score function used in the algorithm is so-called 
    \it{synaptic saliency} \rm{score}. Later, Abdelfattah et al. 
    \cite{abdelfattah2021zerocost} extended SynFlow to score a network 
    architecture by summing synaptic saliency score over all parameters 
    in the model. Cavagnero et al. \cite{Cavagnero_2023} found that 
    SynFlow is likely to suffer from gradient explosion, then proposed 
    the LogSynFlow score function which prevents the problem. 
    % NTK
    For another example, Chen et al. 
    \cite{https://doi.org/10.48550/arxiv.2102.11535} proposed to compute 
    the condition number of neural tangent kernel (NTK) 
    \cite{https://doi.org/10.48550/arxiv.2203.09137} 
    \cite{https://doi.org/10.48550/arxiv.2109.00817}, which is used as 
    a score to estimate the trainability of an architecture.

% what is unknown?
    % 做成圖表放第一頁
    However, \xtab{table:corr_score} shows most score functions suffer 
    from the low correlation between score values and the final accuracy of 
    architectures, leading to a predicament that no matter how good the 
    searching algorithm, we can hardly find an optimal architecture. 
    The major problem that causes the low correlation is that a single score 
    function can only evaluate one characteristic of an architecture. 
    \begin{table}[tb]
        \caption{\textsc{The Kendall correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench-TSS \cite{Dong_2021}. }}
        \resizebox{0.45\textwidth}{!}{
            \begin{tabular}{cccc}\toprule
                Training-free score function & CIFAR-10 & CIFAR-100 & ImageNet-16-120 \\ 
                \midrule
                \bf{NTK}                     & -0.50    & -0.47     & -0.49 \\
                \bf{Snip}                    & 0.46     & 0.46      & 0.42  \\
                \bf{Grasp}                   & 0.38     & 0.37      & 0.39  \\
                \bf{NASWOT}                  & 0.62     & 0.65      & 0.62  \\
                \bf{SynFlow}                 & 0.53     & 0.51      & 0.52  \\
                \bf{LogSynFlow}              & 0.57     & 0.55      & 0.55  \\
                \bf{NI}                      & 0.57     & 0.59      & 0.55  \\
                \bf{Rank (ours)}             & -0.69    & -0.70     & -0.67 \\ \bottomrule
                \label{table:corr_score}
            \vspace{-\baselineskip}
            \end{tabular}
        }
    \end{table}
    % TSS
    %             C10 v/t        C100 v/t     I16 v/t  
    % ni        : 0.59/0.57      0.59/0.59    0.55/0.55
    % naswot    : 0.60/0.62      0.64/0.65    0.61/0.62
    % logsynflow: 0.51/0.57      0.54/0.55    0.53/0.55
    % synflow   : 0.48/0.53      0.51/0.51    0.50/0.52
    % ntk       : -0.50/-0.50    -0.50/-0.47  -0.49/-0.49
    % grasp     : 0.33/0.38      0.38/0.37    0.37/0.39
    % snip      : 0.41/0.46      0.46/0.46    0.41/0.42
    % rank      : -0.66/-0.69    -0.70/-0.70  -0.66/-0.67
    %
    \begin{figure*}[b]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/naswot.pdf}}
        \caption{A simple example to illustrate the procedure of NASWOT.}
        \label{fig:naswot}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}
% method
    To address the problem, we propose cooperating three complementary 
    score functions by ranking, which allows every score functions 
    evaluate an architecture without losing fairness. 
    The first score function is noise immunity (NI) \cite{10092788}, as 
    a measurement of the ability of image generalization. 
    The second one is NASWOT, used as a score to estimate the ability of distinction 
    of architecture and also a complement of NI. 
    The last one is LogSynFlow used as the measurement of trainability 
    and also as a complement to NI and NASWOT. 
    With these three complementary score functions, an evaluation of an 
    architecture is not simply from a single aspect but three different 
    parts, which is like estimating the weight of an object by not only 
    the length but its height and width. 
    %compares the different search algorithms for NAS, e.g., random search, genetic 
    %algorithm (GA) \cite{mitchell1998introduction}, simulated annealing algorithm (SA)
    %\cite{kirkpatrick1983optimization}.

    % conclusion
    %The major contribution of this paper can be summarized as follow:
    %\begin{itemize}
    %    \item Cooperating three score functions to obtain better ability for searching top accuracy neural architectures. 
    %    \item Develope simulated annealing algorithms with rank-based score. 
    %\end{itemize}
    % expect what

    The remainder of this paper is organized as follows: 
    \xsec{sec:related_work} provides the detail about the training-free 
    score functions. \xsec{sec:proposed} gives a detailed 
    description about the proposed method. \xsec{sec:results} begins 
    with parameters setting and provides the simulation results in 
    different search spaces. The conclusion and further 
    prospect are gived in \xsec{sec:conclusion}.

    \section{Related Works}
    \label{sec:related_work}
    \subsection{Training-free Score Functions}
    In \cite{https://doi.org/10.48550/arxiv.2006.04647}, Mellor et al. 
    proposed a score function without the requirement for training, NASWOT. 
    \xfig{fig:naswot} gives a simple example 
    to illustrate the procedure of NASWOT score function. Consider a 
    mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
    architecture. The $j$-th activated ReLU units in every layer of the architecture 
    form a binary code $c_{i,j}$ that define the linear region. The correlation 
    between binary codes for the whole mini-batch can be examined by computing 
    the kernel matrix 
    \begin{equation}
        K_H=\begin{pmatrix}L-\sum_{i=1}^{N_A}d_H(c_{1,i},c_{1,i})&\cdots&L-\sum_{i=1}^{N_A}d_H(c_{1,i},c_{N,i})\\\vdots&\ddots&\vdots\\L-\sum_{i=1}^{N_A}d_H(c_{N,i},c_{1,i})&\cdots&L-\sum_{i=1}^{N_A}d_H(c_{N,i},c_{N,i})\end{pmatrix},
    \end{equation}
    where $N_A$ is the number of ReLU units, $d_H(\cdot,\cdot)$ is the hamming 
    distance between two binary codes, and $L$ is the total length of the binary 
    code. With the kernel matrix, the score of an architecture is evaluated as 
    follow: 
    \begin{equation}
        s=\log\lvert K_H\rvert,
    \end{equation}
    The rationale behind is that, the more different between the binary codes 
    the better the architecture learns. And the determinant of the kernel matrix 
    measures how "different" they are by calculating the volume formed by the 
    row vector of $K_H$.

    Wu et al. \cite{10092788} found in some cases, an architecture with a high 
    NASWOT score may classify the same kind of input data into different classes. 
    To fix this defect, Wu et al. proposed using noise immunity (NI) to 
    evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
    NI evaluates an architecture. The score function picks a 
    mini-batch of data, denoted $X$, and then applies Gaussian noise to it. 
    The process is defined by $X'=X+z$ where $z$ is the Gaussian noise. 
    By passing $X$ and $X'$ through the untrained architecture, then computing 
    the difference of square of each feature map captured at all pooling layers. 
    Calculate the matrix $\kappa$ defined by 
    \begin{equation}
        \label{equ:ni_kappa}
        \kappa=\begin{pmatrix}\frac{(\tau_{1,1}-\tau'_{1,1})^2}{\lvert \tau_{1,1}\rvert}&\cdots&\frac{(\tau_{N,1}-\tau'_{N,1})^2}{\lvert \tau_{N,1}\rvert}\\\vdots&\ddots&\vdots\\\frac{(\tau_{1,N_P}-\tau'_{1,N_P})^2}{\lvert \tau_{1,N_P}\rvert}&\cdots&\frac{(\tau_{N,N_P}-\tau'_{N,N_P})^2}{\lvert \tau_{N,N_P}\rvert}\end{pmatrix},
    \end{equation}
    where $N_P$ is the total number of pooling layers; $N$ the size of mini-batch, 
    and $\tau_{i,j}$ and $\tau'_{i,j}$ are the feature maps which $X$ passing and 
    the one perturbed by $X'$ at the $j$-th pooling layer and $i$-th input 
    data of the mini-batch, respectively. 
    Then $\eta$ can be calculated by 
    \begin{equation}
        \label{equ:ni_eta}
        \eta=\ln(\epsilon+e_L\kappa e_N),
    \end{equation}
    where $\epsilon$ is a small positive number, and $e_{N_P}$ and $e_N$ are a row 
    vector of 1's of size $N_P$ and a column vector of 1's of size $N$, respectively. 
    According to the fact that the input data are the same kind, the smaller $\eta$ 
    is, the better the noise immunity of the architecture is.

    \begin{figure*}[tb]
        \vspace{-\baselineskip}
        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
        \caption{A simple example to illustrate the procedure of NI.}
        \label{fig:ni}
        \centering
        \vspace{-\baselineskip}
    \end{figure*}

    % synflow
    Besides image-related measurements, there is another characteristic to evaluate a network. 
    \textit{The Lottery Ticket Hypothesis} \cite{frankle2019lottery} reveals that a 
    network may have a "core" which decides the final accuracy of the network. 
    How to prune a network correctly is thereby tempting. Lee et al. 
    \cite{lee2019snip} proposed to use connection sensitivity as a criterion to prune 
    the network which can be briefly viewed as 
    \begin{equation}
        \label{equ:snip_connection_sensitivity}
        s_j=\lvert \frac{\partial \mathcal L}{\partial w_j}w_j\rvert,
    \end{equation}
    where $w_j$ the $j$-th element of the weight of the netwrok, and $\mathcal L$ is 
    the empirical risk. The meaning behind is to approximate the contribution 
    to the change of the loss function from a specific connection. By pruning the 
    connections that are relatively not contributive, the expensive prune, retrain 
    cycles, can be prevented. 
    Later, Wang et al. \cite{wang2020picking} noticed that SNIP with a high pruning ratio 
    tends to cause \textit{layer-collapse}, which prunes all parameters in a single weight 
    layer. Therefore, they propose Gradient Signal Preservation (GraSP) algorithm, which 
    aims to preserve the gradient flow at initialization by approximating the change in 
    gradient norm defined as 
    \begin{equation}
        \label{equ:grap}
        S_p(\theta)=-(\textbf{H}\frac{\partial \mathcal L}{\partial \theta})\odot\theta,
    \end{equation}
    where $\textbf{H}$ is the Hessian matrix, $\theta$ the parameters, and $\odot$ is Hadamard product. 
    In \cite{tanaka2020pruning}, to solve the problem that the existing pruning algorithms using 
    global masking, e.g., Magnitude, SNIP, GraSP, usually encounter layer-collapse, which makes 
    the pruned network untrainable. 
    Tanaka et al. generalized the synaptic saliency scores as 
    \begin{equation}
        \label{equ:synflow}
        S_p(\theta)=\frac{\partial \mathcal R}{\partial \theta}\odot\theta,
    \end{equation}
    where $\mathcal R$ is a scalar loss function, and proposed Iterative Synaptic Flow Pruning (SynFlow) 
    algorithm, an extension of magnitude pruning algorithm that avoids layer-collapse. 
    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, and proposed to score a 
    network by summing the synaptic saliency score over all parameters in the model, which is 
    defined as 
    \begin{equation}
        \label{equ:zero_cost}
        S_n=\sum^N_i S_p(\theta)_i.
    \end{equation}
    The rationale behind is to calculate all the contributions to the loss function of parameters. 
    The higher the score of an architecture, the more trainable this architecture is. 
    Finally, Cavagnero et al. \cite{Cavagnero_2023} improved SynFlow, which is likely to fall into 
    gradient explosion problem, and proposed LogSynFlow which scales down the gradient. 
    The formula is defined by 
    \begin{equation}
        \label{equ:logsynflow}
        S(\theta)=\theta\cdot\log(\frac{\partial \mathcal L}{\partial \theta}+1)
    \end{equation}

    Except using the synaptic saliency score to measure the trainability, 
    \cite{https://doi.org/10.48550/arxiv.2102.11535} uses the condition number of neural tangent 
    kernel (NTK) \cite{jacot2020neural} to measure it, which the score can be defined as 
    \begin{equation}
        \label{equ:cn_ntk}
        \frac{\lambda_m}{\lambda_0}, 
    \end{equation}
    where $\lambda_0$ is the biggest eigenvalue and $\lambda_m$ is the smallest eigenvalue of the 
    NTK. The rationale behind is the converge rate of the network is condition by the rate 
    $\frac{\lambda_m}{\lambda_0}$. The higher the condition is, the faster the converge.

    \subsection{Search Algorithms}
    First, assume that $D_r$ and $D_t$ are two subsets of input data $D$. Furthermore, 
    assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $\mathcal A_s$ the 
    search algorithm of NAS, and $\mathcal A_L$ the learning algorithm. Then, the NAS problem can be 
    described as an optimization problem as follows: 
    \begin{equation}
        \label{equ:nas}
        \mathbb N^*=\max_{\mathbb N^b\in\mathbb N}\mathcal F_A(\mathcal A_L(\mathbb N^b, D_r), D_t)
    \end{equation}
    where $\mathbb N$ is a set of neural architectures, namely, the search space of NAS. 
    For non-training-free NAS 
    \begin{equation}
        \label{equ:non-training_free_nas}
        \mathbb N^b=\mathcal A_S(\mathcal F_A(\mathcal A_L(\mathbb N^s, D_r), D_t), \mathbb N)
    \end{equation}
    and for training-free NAS 
    \begin{equation}
        \label{equ:training_free_nas}
        \mathbb N^b=\mathcal A_S(\mathcal F_S(\mathbb N^s, D_r), \mathbb N)
    \end{equation}
    It can be seen that training-free NAS is comprised of two part, search algorithm $\mathcal A_S$ and score 
    function $\mathcal F_S$. 
    There are several search algorithms applied on NAS, including random search, reinforcement learning, and
    metaheuristic algorithms.

    In \cite{https://doi.org/10.48550/arxiv.2006.04647} \cite{Lopes_2021}, random search is applied. 
    The advantage of random search is simple and easy to implement, and the result can be taken as a 
    baseline compared to more comprehensive search algorithms. Generally speaking, when applying random 
    search on a small search space, e.g., NAS-Bench-201 \cite{dong2020nasbench201}, the performance is 
    similar to other search algorithms. But when it comes to a relatively larger search space, e.g., NAS-Bench-101 
    \cite{ying2019nasbench101} and NATS-Bench-SSS \cite{Dong_2021}, random search can no longer standout 
    in other search algorithms.

    In \cite{zoph2017neural}, reinforcement learning is used to find the maximum accuracy of an architecture 
    generated by a network architecture controller. The actions $a_{1:T}$ of the reinforcement learning is 
    equivalent to updating the parameters $\theta_c$ for the controller. The goal is to maximize 
    its expected reward, defined by 
    \begin{equation}
        \label{equ:reinforcement_rw}
        J(\theta_c)=E_{P(a_{1:T};\theta_c)}[R]
    \end{equation}
    and the gradient of $J(\theta_c)$ is defined by
    \begin{equation}
        \label{equ:reinforcement_grad}
        \nabla_{\theta_c} J(\theta_c)=\sum^T_t=1 E_{P(a_{1:T};\theta_c)}[\nabla_{\theta_c}\log P(a_t\mid a_{(t-1):1};\theta_c)R]
    \end{equation}

    As for an example of metaheuristic algorithm, in \cite{10.1145/3491396.3506510}, Wu et al. leveraged 
    genetic algorithm (GA) as a search strategy. 
    By encoding the network architecture, the architecture can be viewed as a gene. Therefore, GA can be 
    easily applied. 
    Later in \cite{10092788}, Wu et al. used search economic (SE) \cite{7379579} as a search strategy. The 
    basic idea of SEs is to first divide the search space into a set of subspaces and investigate those 
    subspaces based on the expected value of each subspace. The expected value is comprised of 
    \begin{itemize}
        \item The number of times the subspace has been investiagted. 
        \item The average objective value of the new candidate solutions in the subspace at current iteration. 
        \item The best solution so far in this subspace. 
    \end{itemize}
    Based on these designs, SE avoids falling into local optimum, while searching for high expected value instead.

    \section{Methods}
    \label{sec:proposed}

    The motivation origins from these three questions:

    \textit{1. Can we combine multiple score functions to improve the search performance 
    or the correlation between score values and the final accuracy of architectures?}

    The answer is yes. If the chosen score functions are complementary, the new correlation 
    can overtake the original ones. \cite{10.1145/3491396.3506510} 
    shows that possibility. When an architecture gains a high NASWOT score, 
    it may misclassify images in the same class into different classes. NI here comes 
    to the rescue. By measuring the noise immunity of an architecture, the misclassifying problem 
    can be solved. Thus, combine NASWOT and NI, the correlation and performance increase. 
    An example shows in \xfig{fig:ninaswot}.
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \begin{center}
            \begin{tabular}{ccc}
                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/naswot-acc.pdf}}}
                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ni-acc.pdf}}}
                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ninaswot-acc.pdf}}}
            \end{tabular}
            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NAS-Bench-201 in the CIFAR-10 dataset 
            (b) NI score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset. 
            (c) NI score + NASWOT score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset.}
            \label{fig:ninaswot}
        \end{center}
        \vspace{-\baselineskip}
    \end{figure*}

    \textit{2. How to choose the score functions?}

    As mentioned, the key is choose the complement of a score function. For example, 
    score functions that evaluate the expressivity/distinction ability shall have other 
    score functions to evaluate the generalization ability. For these two graphic recognition 
    score functions, the complements can be measurements of trainability.

    \textit{3. How to combine multiple kinds of score functions together 
    and prevent one from overwhelming the others numerically?}

    One possible way is normalization, but the necessary information is known only 
    after evaluating the whole search space, e.g., range, mean, or standard deviation, 
    which is practically impossible. To make the proposed score function 
    agnostic to the search space, it leverages multiple score functions by ranking, 
    which also provides a solution to have equal contributions from each score function.

    \subsection{Simulated Annealing with Ranking Algorithm}

    The modified version of the simulated annealing (SA) algorithm with ranking algorithm (\palg{})
    is outlined in \xalg{alg:SA}. The first step is to sample an architecture as the current 
    solution, denoted $s$, from search space. Use $s$ as a seed to generate the 
    neighborhood of it, denoted $U$, and the size of it is decided by a presetting parameter, 
    the number of neighbours, $N$. 
    After ranking the seed with the neighborhood and the historical best architectures, recorded by $H$, 
    the best architecture (including $s$) is added into $H$.
    And the best architecture (excluding $s$) which has highest rank is denoted by $s^*$. 
    If the rank of $s^*$ is higher than $s$, the current solution is replaced by $s^*$, or be 
    replaced by probability, defined by 
    \begin{equation}
        \label{equ:SA_rk_prob}
        e^{-\alpha\frac{\Delta E}{T}},
    \end{equation}
    where $T$ is the current temperature, $\Delta E$ the difference of the rank between 
    $s$ and $s^*$, and $\alpha$ is a constant number adjusts the probability. The more 
    the difference between $s$ and $s^*$, the smaller the probability of accepting the new solution. 
    After the $I$ iterations, the temperature scales down by $r_t$. The algorithm 
    is done when $T\leq\tau$, and the current architecture is returned. 
    Notbly, the size of $H$ is based on the maximum search number of SA, defined by 
    \begin{equation}
        \label{equ:SA_rk_size_of_H}
        \beta (I\cdot N\cdot\frac{\ln{\tau/T}}{\ln{r_t}}),
    \end{equation}
    where $\beta$ is the coefficient of the size of $H$ and is a constant number between 0 and 1.

    \begin{algorithm}[h]
        \caption{The Simulated Annealing with Ranking Algorithm}\label{alg:SA}
        \begin{algorithmic}[1]
            \Input{search space $\mathbb N^*$}
            \Parameter Initial temperature $T$, ending temperature $\tau$, a real number between 0 and 1, $r_t$, the number of iteration, $I$, the number of generated neighbours, $N$, a real number, $\alpha$, the coefficient of the size of $H$, $\beta$
            \State Initialize historical best architectures set $H$
            \State $s=\text{Randomly sample an architecture from }\mathbb N^*$
            \While{$T>\tau$}
                \For{$\text{each }i \in [1\ldots I]$}
                    \State $U = \text{Neighbor}(s, N)$
                    \State $r=\text{Rank}(\{s\}\cup U\cup H)$
                    \State $\text{Maintain}(H)$
                    %\State $s'=\text{Best architecture excluding }s$
                    \State $s'=\arg\min_{\mathbb N^i\neq s}(r)$
                    \State $\Delta E=\text{Diff}(s', s)$
                    \State $x\sim U[0,1]$
                    \If{$\Delta E<0$}
                        \State $s\leftarrow s'$
                    \ElsIf{$x\leq e^{-\alpha\frac{\Delta E}{T}}$}
                            \State $s\leftarrow s'$
                    \EndIf
                \EndFor
                \State $T\leftarrow T\times r_t$
            \EndWhile
            \State $\textbf{Return }s$ \Comment{Return the current architecture}
        \end{algorithmic}
    \end{algorithm}

    \subsection{Encoding Schema}

    The encoding schema determines the efficiency of searching. The naïve encoding 
    schema is to use a binary/integer vector as a representation of an architecture. 
    For example, NAS-Bench-201 provides 5 operations and 6 nodes for a cell, 
    and cells form an architecture, which implies the whole search space can be 
    encoded into 6-integer vectors. However, a broken architecture appears since 
    one of the operations is "zeroize", which means the measurement of a broken 
    architecture is meaningless. To exclude the broken architectures, the encoding 
    schema in \cite{10092788} is used in this paper. The detail of the encoding 
    schema differs from search spaces, but they all share the common core idea, 
    preserving the critical path in architecture. The encoding schema guarantees 
    the existence of at least one path from input to output in a cell, and no 
    zeroize operation is in it. By excluding the broken architectures, the efficiency 
    improves.

    \subsection{Ranking Algorithm}

    The general proposed ranking algorithm is in \xalg{alg:rank-based}. 
    The first step is to evaluate the network architectures in the subset, 
    denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The 
    evaluation of an architecture determined by $j$-th score function 
    is $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating the subset 
    of search space, the rank of each score function is calculated, denoted 
    $r_{\mathcal F}$. Then the final rank, $r$, calculated by summing up 
    the ranks. If a network architecture gains higher score in these score 
    functions, the final rank should be higher (smaller index) too. Therefore, 
    the highest (minimum) rank in $r$ shall be the best network architecture. 
    In summary, the ranking algorithm makes the contribution of 
    each score function even and therefore evaluate an architecture from 
    different aspects.

    \begin{algorithm}[h]
        \caption{The Ranking Algorithm}\label{alg:rank-based}
        \begin{algorithmic}[1]
            \Input{A subspace, ${\mathbb N}^{s}$, from search space, ${\mathbb N}^{*}$}
            \For{$\text{each }{\mathbb N}^i\text{ in }{\mathbb N}^s$}
                \For{$\text{each }j\in\{1,\ldots,M\}$}
                    \State $s_{{\mathcal F}_{j}}({\mathbb N}^i)={\mathcal F}_{j}({\mathbb N}^i)$
                \EndFor
            \EndFor
            \For{$\text{each }j\in\{1,\ldots,M\}$}
                \State $r_{{\mathcal F}_{j}}({\mathbb N}^i)$ = index of ${\mathbb N}^i$ in list $[s_{{\mathcal F}_{j}}({\mathbb N}^1),\ldots,s_{{\mathcal F}_{j}}({\mathbb N}^{\lvert {\mathbb N}^s\rvert})]$ \par sorted by descending order
            \EndFor
            \State $r({\mathbb N}^i)=\sum^M_{j=0} r_{{\mathcal F}_{j}}({\mathbb N}^i)$
            %\State $i^*=\arg\min_{i}\{r({\mathbb N}^i)\}$
            %\State $\textbf{Return }{\mathbb N}^{i^*}$
            \State $\textbf{Return }r$
        \end{algorithmic}
    \end{algorithm}

    With the proposed ranking algorithm as a framework, the next question is 
    to choose complementary score functions. The recent training-free 
    score functions can be roughly classified into different kinds. NASWOT, 
    linear regions distribution \cite{https://doi.org/10.48550/arxiv.2102.11535} \cite{lin2021zennas}, 
    maximum entropy of architecture \cite{sun2022maedet} are measurements 
    to the ability of distinction and expressivity of an architecture; 
    NI is a measurement to image generalization ability of an architecture; 
    the condition number of NTK, modified version of SNIP, GraSP, SynFlow, and 
    LogSynFlow are measurements to trainability of an architecture. 
    As mentioned, the chosen score function shall be complementary to each other. 
    In this paper, NI and NASWOT are a complementary set, which takes 
    the ability of image generalization and distinction into account. 
    This complementary set is viewed as the measurement of the ability of graphic 
    recognition. Therefore, the last missing piece is the trainability of an 
    architecture, which, LogSynFlow is chosen to measure it.

    \section{Experiment Result}
    \label{sec:results}

    We evalute the performance of the proposed algorithm, \palg{}, 
    for searching the architectures of high accuracy. For comparison, several NAS 
    algorithms are included, e.g., random search (RS), regularized evolution algorithm 
    (REA) \cite{real2019regularized}, reinforcement learning (RL) \cite{Williams:92}, 
    Bayesian optimization with hyper band (BOHB) \cite{falkner2018bohb}, RS with 
    weight sharing (RSWS) \cite{li2019random}, differentiable architecture search 
    with first order (DARTS-V1) \cite{liu2019darts}, DARTS with second order 
    (DARTS-V2) \cite{liu2019darts}, gradient-based search using differentiable 
    architecture sampler (GDAS) \cite{dong2019searching}, self-evaluated template 
    network (SETN) \cite{Dong_2019}, efficient NAS (ENAS) \cite{pham2018efficient}, 
    assisted REA (AREA) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
    zero-cost NAS \cite{https://doi.org/10.48550/arxiv.2101.08134}, 
    TE-NAS \cite{https://doi.org/10.48550/arxiv.2102.11535}, gradient kernel-based 
    NAS (KNAS) \cite{xu2021knas}, RS with NASWOT \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
    RS with noise immunity (NI) \cite{10092788}, RS with LogSynFlow \cite{Cavagnero_2023}, 
    and RS with ranking.

    The three search spaces, NATS-bench-SSS, NATS-bench-TSS 
    \cite{Dong_2021} and NAS-Bench-101 \cite{ying2019nasbench101}, are used 
    here to evalute the performance of the NAS algorithms. The architectures 
    of NATS-bench-TSS is same as NAS-Bench-201 \cite{dong2020nasbench201}. 
    The architectures in NATS-bench-SSS and NATS-bench-TSS are trained by the three datasets: 
    CIFAR10, CIFAR100, ImageNet-16-120, while NAS-Bench-101 is trained by one: 
    CIFAR10.

    \subsection{Environment and Parameter Settings}
    The experiment is conducted on a PC with Intel Core i7-11700K (3.60 GHz, 16-MB Cache, and 16 cores), 
    a single NVIDIA RTX3070 Ti GPU with 8 GB memory, driver version 520.61.05, CUDA version 11.8, and 
    65 GB available memory running on Ubuntu 20.04.1 with linux kernel 5.15.0-73-generic. All the program 
    is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. The simulations of all 
    non-weight sharing NASs are carried out for 500 runs on all the search spaces except AREA which is 50 runs. 
    For weight sharing NAS algorithms, each is carried out for 3 runs. And for training-free 
    algorithms, each is carried out for 100 runs and are given an evaluation 
    budget of 1000 for all the search space. The parameter settings of \palg{} are as follows: 
    initial temperature, ending temperature, rate of decrease of temperature, the number of iteration, 
    the constant number adjusting acceptance probability, the number of generated neighbours, and 
    the coefficient of the size of historical best architectures set are set 
    to 1, 0.0008, 0.745, 4, 0.25, 10, 1, so that the maximum number of searching candidates is 1000.

    \subsection{NATS-bench-SSS}
    In \xtab{table:overall_sss}, the proposed NAS algorithm and ranking function is 
    compared with the other five non-weight sharing algorithm and NI, NASWOT, and LogSynFlow. 
    For fairness, the searching architectures for the RS with training-free score 
    functions are identical. The performance of the ranking algorithm is similar to NI but 
    lower than LogSynFlow. However, the proposed NAS algorithm improves the results 
    significantly and outperforms almost all the compared algorithms.

    \begin{table*}[htb]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-SSS.}}
          \vspace{-\baselineskip}
        \begin{tabular}{@{}lccccccc@{}}\toprule
        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
                            &          & validation       & test             & validation       & test              & validation       & test \\ \midrule
                            &          &                  &                  & \textbf{Non-weight sharing} &        &                  &                  \\
        AREA                & $12,000$ & $84.62 \pm 0.41$ & $93.16 \pm 0.16$ & $59.24 \pm 1.11$ & $69.56 \pm 0.96$  & $37.58 \pm 1.09$ & $45.30 \pm 0.91$ \\
        REA                 & $12,000$ & $90.37 \pm 0.20$ & $93.22 \pm 0.16$ & $70.23 \pm 0.50$ & $70.11 \pm 0.61$  & $45.30 \pm 0.69$ & $45.94 \pm 0.92$ \\
        RS                  & $12,000$ & $90.10 \pm 0.26$ & $93.03 \pm 0.25$ & $69.57 \pm 0.57$ & $69.72 \pm 0.61$  & $45.01 \pm 0.74$ & $45.42 \pm 0.86$ \\
        RL                  & $12,000$ & $90.25 \pm 0.23$ & $93.16 \pm 0.21$ & $69.84 \pm 0.59$ & $69.96 \pm 0.57$  & $45.06 \pm 0.77$ & $45.71 \pm 0.93$ \\
        BOHB                & $12,000$ & $90.07 \pm 0.28$ & $93.01 \pm 0.24$ & $69.75 \pm 0.60$ & $69.90 \pm 0.60$  & $45.11 \pm 0.69$ & $45.56 \pm 0.81$ \\ \midrule
                            &          &                  &                  & \textbf{Training-free} &             &                  &                  \\
        RS-NI (N=1,000)         & $293$& $89.55 \pm 0.16$ & $92.56 \pm 0.21$ & $67.67 \pm 0.91$ & $67.61 \pm 1.06$  & $43.19 \pm 0.73$ & $43.22 \pm 0.53$ \\ 
        RS-NASWOT (N=1,000)     & $208$& $89.25 \pm 0.44$ & $92.21 \pm 0.31$ & $65.09 \pm 2.89$ & $64.61 \pm 3.16$  & $41.29 \pm 2.32$ & $41.35 \pm 2.31$ \\ 
        RS-LogSynFlow (N=1,000) & $123$& $89.60 \pm 0.11$ & $92.61 \pm 0.18$ & $68.23 \pm 0.49$ & $68.30 \pm 0.54$  & $43.58 \pm 0.58$ & $43.48 \pm 0.40$ \\ 
        RS-rank (ours) (N=1000) & $612$& $89.59 \pm 0.14$ & $92.51 \pm 0.17$ & $67.56 \pm 0.75$ & $67.55 \pm 0.82$  & $43.36 \pm 0.62$ & $43.27 \pm 0.45$ \\ 
        \palg{} (ours)          & $725$& $90.33 \pm 0.15$ & $93.26 \pm 0.24$ & $69.89 \pm 0.48$ & $70.24 \pm 0.42$  & $45.41 \pm 0.41$ & $46.43 \pm 0.75$ \\ \midrule
        Optimal             &          & $90.71$          & $93.65$          & $70.92$          & $71.34$           & $46.73$          & $47.40$          \\ \bottomrule
        \end{tabular}
        \label{table:overall_sss}
          \vspace{-\baselineskip}
    \end{table*}

    \subsection{NATS-Bench-TSS}
    \xtab{table:overall_201} compares \palg{} with the other non-weight sharing algorithms, six 
    weight sharing algorithms, and three different training-free score functions, i.e., NI, NASWOT, and 
    LogSynFlow. Same as the experiment of NATS-Bench-TSS, the searching architectures are identical 
    for the RS with score functions. Non-weight sharing algorithms like REA and AREA outperform all 
    the other search algorithms, though the time cost is tremendous. In CIFAR10 and ImageNet16-120 datasets, 
    the performance of ranking algorithm and \palg{} outperform other training-free and non-weight sharing 
    algorithms and show a lower standard deviation compared with the others. In CIFAR100, 
    NI though outperforms the ranking algorithm, \palg{} still has better performance.

    \begin{table*}[htb]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-TSS.}}
        \vspace{-\baselineskip}
        \begin{tabular}{@{}lrcccccc@{}}\toprule
        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
                            &          & validation           & test             & validation           & test             & validation       & test \\ \midrule
                            &          &                      &                  & \textbf{Non-weight sharing} &           &                  &                  \\
        AREA                & $12,000$ & $91.18 \pm \z{0.43}$ & $93.95 \pm 0.39$ & $71.84 \pm 1.21$ & $71.92 \pm 1.29$ & $45.04 \pm 1.03$ & $45.40 \pm 1.14$ \\
        REA                 & $12,000$ & $91.25 \pm \z{0.31}$ & $94.02 \pm 0.31$ & $72.28 \pm 0.95$ & $72.23 \pm 0.84$ & $45.71 \pm 0.77$ & $45.77 \pm 0.80$ \\
        RS                  & $12,000$ & $91.07 \pm \z{0.26}$ & $93.86 \pm 0.23$ & $71.46 \pm 0.97$ & $71.55 \pm 0.97$ & $45.03 \pm 0.91$ & $45.28 \pm 0.97$ \\
        RL                  & $12,000$ & $91.12 \pm \z{0.25}$ & $93.90 \pm 0.26$ & $71.80 \pm 0.94$ & $71.86 \pm 0.89$ & $45.37 \pm 0.74$ & $45.64 \pm 0.78$ \\
        BOHB                & $12,000$ & $91.17 \pm \z{0.27}$ & $93.94 \pm 0.28$ & $72.04 \pm 0.93$ & $72.00 \pm 0.86$ & $45.55 \pm 0.79$ & $45.70 \pm 0.86$ \\ \midrule
                            &          &                      &                  & \textbf{Weight sharing} &               &                  &                  \\
        RSWS                & $4,154$  & $87.60 \pm \z{0.61}$ & $91.05 \pm 0.66$ & $68.27 \pm 0.72$ & $68.26 \pm 0.96$ & $39.73 \pm 0.34$ & $40.69 \pm 0.36$ \\
        DARTS-V1            & $5,475$  & $49.27 \pm 13.44$    & $59.84 \pm 7.84$ & $61.08 \pm 4.37$ & $61.26 \pm 4.43$ & $38.07 \pm 2.90$ & $37.88 \pm 2.91$ \\
        DARTS-V2            & $16,114$ & $58.78 \pm 13.44$    & $65.38 \pm 7.84$ & $59.48 \pm 5.13$ & $60.49 \pm 4.95$ & $37.56 \pm 7.10$ & $36.79 \pm 7.59$ \\
        GDAS                & $11,183$ & $89.68 \pm \z{0.72}$ & $93.23 \pm 0.13$ & $68.35 \pm 2.71$ & $68.17 \pm 2.50$ & $39.55 \pm 0.00$ & $39.40 \pm 0.00$ \\
        SETN                & $16,787$ & $90.00 \pm \z{0.97}$ & $92.72 \pm 4.52$ & $69.19 \pm 1.42$ & $69.36 \pm 1.72$ & $39.77 \pm 0.33$ & $39.51 \pm 0.33$ \\
        ENAS                & $7,061$  & $90.20 \pm \z{0.00}$ & $93.76 \pm 0.00$ & $70.21 \pm 0.71$ & $70.67 \pm 0.62$ & $40.78 \pm 0.00$ & $41.44 \pm 0.00$ \\ \midrule
                            &          &                      &                  & \textbf{Training-free} &                &                  &                  \\
        RS-NI (N=1,000)         & $592$  & $90.03 \pm \z{0.30}$ & $93.21 \pm 0.63$ & $70.27 \pm 0.70$ & $70.40 \pm 0.84$ & $42.92 \pm 2.18$ & $43.34 \pm 2.43$ \\ 
        RS-NASWOT (N=1,000)     & $201$  & $89.63 \pm \z{0.94}$ & $92.80 \pm 1.07$ & $69.76 \pm 1.25$ & $69.66 \pm 1.23$ & $43.51 \pm 2.90$ & $43.84 \pm 2.93$ \\ 
        RS-LogSynFlow (N=1,000) & $90$   & $89.67 \pm \z{0.89}$ & $92.92 \pm 0.70$ & $69.19 \pm 1.86$ & $68.98 \pm 1.97$ & $39.93 \pm 6.34$ & $40.23 \pm 6.45$ \\ 
        RS-rank (ours) (N=1000) & $887$  & $90.07 \pm \z{0.41}$ & $93.32 \pm 0.42$ & $70.06 \pm 1.34$ & $70.10 \pm 1.45$ & $43.68 \pm 2.11$ & $44.07 \pm 2.19$ \\ 
        TE-NAS                  & $459$  & $90.02 \pm \z{0.56}$ & $93.31 \pm 0.45$ & $70.12 \pm 1.04$ & $70.26 \pm 1.07$ & $43.15 \pm 2.23$ & $43.49 \pm 2.26$ \\
        \palg{} (ours)          & $902$  & $90.20 \pm \z{0.24}$ & $93.53 \pm 0.22$ & $70.51 \pm 0.71$ & $70.63 \pm 0.66$ & $43.80 \pm 1.86$ & $44.63 \pm 1.64$ \\ \midrule
        Optimal             &          & $91.61$              & $94.37$          & $73.49$          & $73.51$          & $46.73$          & $47.31$          \\ \bottomrule
        \end{tabular}
        \label{table:overall_201}
        \vspace{-\baselineskip}
    \end{table*}

    \subsection{NAS-Bench-101}
    The result of the experiment in NAS-Bench-101 search space shows in \xtab{table:overall_101}, 
    which compares rank function and \palg{} with two non-weight sharing algorithms and two weight 
    sharing algorithms. ENAS has the best performance, while the computation time is the highest. 
    Compared \palg{} with other training-free score functions, the performance and stability are better 
    than others with a reasonable time cost.

    \begin{table*}[t]
        %\normalsize
        %\centering
        \newcommand{\z}{\phantom{0}}
        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-101.}}
        \vspace{-\baselineskip}
        \resizebox{0.5 \textwidth}{!}{
        \begin{tabular}{@{}lrcc@{}}\toprule
            Method              & Search (s) & \multicolumn{2}{c}{CIFAR-10}        \\ \cmidrule(lr){3-4}
                                &            & validation       & test             \\ \midrule
                                &            & \textbf{Non-weight sharing} &       \\
            AREA                & $12,000$   & $93.67 \pm 0.48$ & $93.02 \pm 0.48$ \\
            REA                 & $12,000$   & $93.63 \pm 0.50$ & $93.02 \pm 0.52$ \\ \midrule
                                &            & \textbf{Weight sharing}     &       \\
            DARTS-V1            & $20,483$   & $83.50 \pm 0.11$ & $83.74 \pm 0.03$ \\
            ENAS                & $22,325$   & $93.83 \pm 0.28$ & $93.34 \pm 0.26$ \\ \midrule
                                &            & \textbf{Training-free}      &       \\
            RS-NI (N=1,000)         & $280$  & $92.89 \pm 2.10$ & $92.55 \pm 1.33$ \\ 
            RS-NASWOT (N=1,000)     & $162$  & $92.27 \pm 6.60$ & $92.10 \pm 4.44$ \\ 
            RS-LogSynFlow (N=1,000) & $105$  & $91.81 \pm 1.52$ & $91.21 \pm 1.71$ \\ 
            RS-rank (ours) (N=1000) & $516$  & $92.44 \pm 1.42$ & $91.94 \pm 2.01$ \\ 
            \palg{} (ours)          & $374$  & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \midrule
            Optimal             &            & $95.12$          & $94.32$          \\ \bottomrule
            \end{tabular}
        }
        \label{table:overall_101}
        \vspace{-\baselineskip}
    \end{table*}

    \section{Conclusion}
    \label{sec:conclusion}
    In this paper, a novel concept of "complementary" is proposed and used as a basis to choose 
    training-free score functions. The new rank algorithm is then applied to simulated annealing 
    algorithm. The simulation result shows that the proposed algorithm, named SA-rk, not only outperforms the most 
    state-of-art training-free score functions but also some of the non-training-free methods. 
    The proposed algorithm also shows robustness, which performs well between different search 
    spaces vary with neural network structures and size. 
    The limitation of SA-rk is the lack of versatility since the score functions are mainly chosen 
    for common image recognition. That means SA-rk may not be applied in the search of architectures 
    designed for other usages, i.e., speech recognition, NLP. However, the problem is able to be solved 
    by choosing the corresponding complementary score functions. Some further questions are how many 
    score functions are required for precisely estimating the performance of architectures and what are they?

    \bibliographystyle{IEEEtran}
    \bibliography{manuscript}
\end{document}

### 2023-08-07 paper/manuscript.tex
update paper

@@
     two score functions to evaluate how a neural network architecture performs. 
-    However, an architecture shall be treated as a complex system that has 
-    distinct characteristics to measure. 
+    However, an architecture should be treated as a complex system that has 
+    unique characteristics to measure. 
     To achieve the goal, we propose a rank-based training-free NAS algorithm, 
@@
     patterns, named NASWOT, considers image distinction ability, and LogSynFlow 
-    takes trainability into account. With that, a modified version of simulated 
-    annealing (SA) algorithm, \palg{}, can apply and obtain a better 
-    performance on searching high-accuracy architectures. 
+    takes trainability into account. By the three measurements, an 
+    architecture can be evaluated from different aspects. 
+    With that, simulated annealing (SA) algorithm, \palg{}, 
+    can be applied and obtain a better performance on searching high-accuracy architectures.  
     To evaluate the performance of the proposed algorithm, this paper compared 
@@
     \cite{https://doi.org/10.48550/arxiv.1611.01578}, NAS algorithms can 
-    explore a search space, which is comprised of numerous potential 
-    architectures, to find out the architectures that outperform those 
-    designed by human experts. Recently, the use of NAS has been widespread, 
+    automatically search numerous architectures to find out the ones 
+    that outperform those designed by human experts. Recently, the use of NAS has been widespread, 
     from object detection \cite{https://doi.org/10.48550/arxiv.2111.13336}, 
@@
     and speech recognition \cite{https://doi.org/10.48550/arxiv.2011.05649} 
-    \cite{mehrotra2021nasbenchasr} to natural language processing (NLP). 
-    \cite{jiang-etal-2019-improved} \cite{https://doi.org/10.48550/arxiv.2006.07116} 
-    \cite{https://doi.org/10.48550/arxiv.2005.14187} 
+    to natural language processing \cite{jiang-etal-2019-improved}. 
     Despite the promising results of NAS, there are still many challenges 
@@
     impractical for real-world applications, particularly on resource-constrained 
-    platforms like embedded system. The reason why NAS is costly is that 
+    platforms like embedded system. The main reason why NAS is costly is that 
     during searching, a candidate architecture must be trained to 
@@
 
-    To overcome this challenge, recent works developed and proposed lots 
+    To eliminate the training cost, recent works proposed lots 
     of methods which is so called training-free NAS. 
@@
     % synflow
-    On the other hand, Lee et al. \cite{lee2019snip} proposed pruning 
-    parameters based on a saliency matric, which is then extended by Tanaka 
-    et al. \cite{tanaka2020pruning}. In \cite{tanaka2020pruning}, Tanaka 
-    et al. proposed Iterative Synaptic Flow Pruning (SynFlow) algorithm 
+    For another example, Lee et al. \cite{lee2019snip} proposed pruning 
+    parameters based on a saliency metric, which is then extended by 
+    Tanaka et al. \cite{tanaka2020pruning}. Tanaka et al. proposed 
+    Iterative Synaptic Flow Pruning (SynFlow) algorithm 
     which intends to deal with the layer collapse problem when pruning a 
@@
     architecture by summing synaptic saliency score over all parameters 
-    in the model. Cavagnero et al. \cite{Cavagnero_2023} found that 
+    in the model. The outcome score represents the trainability of an 
+    architecture. Cavagnero et al. \cite{Cavagnero_2023} found that 
     SynFlow is likely to suffer from gradient explosion, then proposed 
@@
     % NTK
-    For another example, Chen et al. 
+    Instead of using saliency metric to measure the trainability, Chen et al. 
     \cite{https://doi.org/10.48550/arxiv.2102.11535} proposed to compute 
     the condition number of neural tangent kernel (NTK) 
-    \cite{https://doi.org/10.48550/arxiv.2203.09137} 
     \cite{https://doi.org/10.48550/arxiv.2109.00817}, which is used as 
@@
     the length but its height and width.
-    %compares the different search algorithms for NAS, e.g., random search, genetic 
-    %algorithm (GA) \cite{mitchell1998introduction}, simulated annealing algorithm (SA)
-    %\cite{kirkpatrick1983optimization}.
 
     % conclusion
-    %The major contribution of this paper can be summarized as follow:
-    %\begin{itemize}
-    %    \item Cooperating three score functions to obtain better ability for searching top accuracy neural architectures. 
-    %    \item Develope simulated annealing algorithms with rank-based score. 
-    %\end{itemize}
-    % expect what
+    % contribution
+    The major contribution of this paper can be summarized as follow:
+    \begin{itemize}
+        \item A novel concept of "complementary" is proposed and used as a metric to choose score functions. 
+        \item Cooperating the complementary score functions by ranking algorithm, which prevents one score overwhelming others numerically. 
+        \item Applying simulated annealing algorithm on the ranking algorithm to imporve the searching ability. 
+    \end{itemize}
 
+    %orginzation
     The remainder of this paper is organized as follows: 
@@
     \label{sec:related_work}
+
+    \subsection{Problem Definition}
+    First, assume that $D_{\text{train}}$ and $D_{\text{test}}$ are two subsets of input data $D$. Furthermore, 
+    assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $\mathcal A_s$ the 
+    search algorithm of NAS, and $\mathcal A_T$ the training function. Then, the NAS problem can be 
+    described as an optimization problem as follows: 
+    \begin{equation}
+        \label{equ:nas}
+        \mathbb N^*=\max_{\mathbb N^b\in\mathbb N}\mathcal F_A(\mathcal A_T(\mathbb N^b, D_{\text{train}}), D_{\text{test}})
+    \end{equation}
+    where $\mathbb N$ is a set of neural architectures, namely, the search space of NAS. 
+    For non-training-free NAS 
+    \begin{equation}
+        \label{equ:non-training_free_nas}
+        \mathbb N^b=\mathcal A_S(\mathcal F_A(\mathcal A_T(\mathbb N^s, D_{\text{train}}), D_{\text{test}}), \mathbb N)
+    \end{equation}
+    and for training-free NAS 
+    \begin{equation}
+        \label{equ:training_free_nas}
+        \mathbb N^b=\mathcal A_S(\mathcal F_S(\mathbb N^s, D_{\text{train}}), \mathbb N)
+    \end{equation}
+    Since the training function is removed in training-free NAS algorithms, they need much less 
+    computational resource than non-training-free NAS algorithms. 
+    Training-free NAS is comprised of two part, training-free score function $\mathcal F_S$ and 
+    search algorithm $\mathcal A_S$.
+
     \subsection{Training-free Score Functions}
@@
     How to prune a network correctly is thereby tempting. Lee et al. 
-    \cite{lee2019snip} proposed to use connection sensitivity as a criterion to prune 
-    the network which can be briefly viewed as 
+    \cite{lee2019snip} presented a high performance algorithm that uses connection 
+    sensitivity as a criterion to prune the network, named single-shot network pruning (SNIP). 
+    which can be briefly viewed as 
     \begin{equation}
@@
     \subsection{Search Algorithms}
-    First, assume that $D_r$ and $D_t$ are two subsets of input data $D$. Furthermore, 
-    assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $\mathcal A_s$ the 
-    search algorithm of NAS, and $\mathcal A_L$ the learning algorithm. Then, the NAS problem can be 
-    described as an optimization problem as follows: 
-    \begin{equation}
-        \label{equ:nas}
-        \mathbb N^*=\max_{\mathbb N^b\in\mathbb N}\mathcal F_A(\mathcal A_L(\mathbb N^b, D_r), D_t)
-    \end{equation}
-    where $\mathbb N$ is a set of neural architectures, namely, the search space of NAS. 
-    For non-training-free NAS 
-    \begin{equation}
-        \label{equ:non-training_free_nas}
-        \mathbb N^b=\mathcal A_S(\mathcal F_A(\mathcal A_L(\mathbb N^s, D_r), D_t), \mathbb N)
-    \end{equation}
-    and for training-free NAS 
-    \begin{equation}
-        \label{equ:training_free_nas}
-        \mathbb N^b=\mathcal A_S(\mathcal F_S(\mathbb N^s, D_r), \mathbb N)
-    \end{equation}
-    It can be seen that training-free NAS is comprised of two part, search algorithm $\mathcal A_S$ and score 
-    function $\mathcal F_S$. 
+
     There are several search algorithms applied on NAS, including random search, reinforcement learning, and
@@
     \subsection{Simulated Annealing with Ranking Algorithm}
-
-    The modified version of the simulated annealing (SA) algorithm with ranking algorithm (\palg{})
-    is outlined in \xalg{alg:SA}. The first step is to sample an architecture as the current 
-    solution, denoted $s$, from search space. Use $s$ as a seed to generate the 
-    neighborhood of it, denoted $U$, and the size of it is decided by a presetting parameter, 
-    the number of neighbours, $N$. 
-    After ranking the seed with the neighborhood and the historical best architectures, recorded by $H$, 
-    the best architecture (including $s$) is added into $H$.
-    And the best architecture (excluding $s$) which has highest rank is denoted by $s^*$. 
-    If the rank of $s^*$ is higher than $s$, the current solution is replaced by $s^*$, or be 
-    replaced by probability, defined by 
+    The simulated annealing (SA) algorithm with ranking algorithm (\palg{})
+    is outlined in \xalg{alg:SA}. In line $1\sim2$, the historical best architectures 
+    set, denoted $H$, is initialized to an empty set, and an architecture is randomly sampled from 
+    search space, denoted $s$. Line $3\sim18$ are the major part of \palg{}, when the temperature 
+    is lower than ending temperature, the algorithm is terminated. Line $4\sim16$ 
+    represent every time the temperature decreases, $I$ iterations with following steps are executed. 
+    In line $5$, $s$ is used as a seed to generate the neighborhood of it, denoted $U$, 
+    and the size of it is decided by a presetting parameter, the number of neighbours, $N$. 
+    In line $6$, $s$, $U$ and the architectures recorded in historical best architectures set are 
+    put into ranking function. 
+    After ranking, the best architecture (including $s$) is added into $H$, and the size of the set is 
+    maintained by removing the low-rank architectures. 
+    And the best architecture (excluding $s$) which has the highest rank is denoted by $s'$. 
+    In line $9$, the difference of the rank between $s'$ and $s$ is calculated and detnote $\Delta E$. 
+    Then in line $10$, a random variable $x$ is sampled from the uniform distribution on $[0,1]$. 
+    Line $11\sim15$ are the transition process. If the rank of $s'$ is higher than $s$ ($\Delta E<0$), 
+    the current solution is replaced by $s'$, or be replaced by probability, defined by 
     \begin{equation}
@@
     where $T$ is the current temperature, $\Delta E$ the difference of the rank between 
-    $s$ and $s^*$, and $\alpha$ is a constant number adjusts the probability. The more 
-    the difference between $s$ and $s^*$, the smaller the probability of accepting the new solution. 
-    After the $I$ iterations, the temperature scales down by $r_t$. The algorithm 
-    is done when $T\leq\tau$, and the current architecture is returned. 
+    $s$ and $s'$, and $\alpha$ is a constant number adjusts the probability. The more 
+    the difference between $s$ and $s'$, the smaller the probability of accepting the new solution. 
+    After the $I$ iterations, the temperature scales down by $r_t$ in line $17$. When $T$ is 
+    lower or equal to $\tau$, the algorithm is terminated and the current architecture is returned in line $19$. 
     Notbly, the size of $H$ is based on the maximum search number of SA, defined by 
@@
             \Parameter Initial temperature $T$, ending temperature $\tau$, a real number between 0 and 1, $r_t$, the number of iteration, $I$, the number of generated neighbours, $N$, a real number, $\alpha$, the coefficient of the size of $H$, $\beta$
-            \State Initialize historical best architectures set $H$
+            \State Initialize historical best architectures set $H$ to empty set
             \State $s=\text{Randomly sample an architecture from }\mathbb N^*$
@@
             \EndWhile
-            \State $\textbf{Return }s$ \Comment{Return the current architecture}
+            \State $\textbf{Return }s$ \Comment{Return the solution}
         \end{algorithmic}
@@
     The encoding schema determines the efficiency of searching. The naïve encoding 
-    schema is to use a binary/integer vector as a representation of an architecture. 
+    schema is to use a binary or integer vector as a representation of an architecture. 
     For example, NAS-Bench-201 provides 5 operations and 6 nodes for a cell, 
@@
 
-    \section{Experiment Result}
+    \section{Experiment Results}
     \label{sec:results}
@@
     assisted REA (AREA) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
-    zero-cost NAS \cite{https://doi.org/10.48550/arxiv.2101.08134}, 
+    %zero-cost NAS \cite{https://doi.org/10.48550/arxiv.2101.08134}, 
     TE-NAS \cite{https://doi.org/10.48550/arxiv.2102.11535}, gradient kernel-based 
@@
     is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. The simulations of all 
-    non-weight sharing NASs are carried out for 500 runs on all the search spaces except AREA which is 50 runs. 
+    non-weight sharing NASs are carried out for 500 runs on all the search spaces except AREA, which is 50 runs. 
     For weight sharing NAS algorithms, each is carried out for 3 runs. And for training-free 
@@
 
-    \subsection{NATS-bench-SSS}
-    In \xtab{table:overall_sss}, the proposed NAS algorithm and ranking function is 
-    compared with the other five non-weight sharing algorithm and NI, NASWOT, and LogSynFlow. 
+    % 3 search spaces merge
+    \subsection{Simulation Results}
+    The simulation results in NATS-Bench-SSS \cite{Dong_2021} is shown in \xtab{table:overall_sss}. The proposed 
+    NAS algorithm and ranking function is compared with the other five non-weight sharing 
+    algorithm and NI, NASWOT, and LogSynFlow. 
     For fairness, the searching architectures for the RS with training-free score 
@@
 
-    \subsection{NATS-Bench-TSS}
-    \xtab{table:overall_201} compares \palg{} with the other non-weight sharing algorithms, six 
+    In NATS-Bench-TSS \cite{Dong_2021}, \xtab{table:overall_201} compares \palg{} with the other non-weight sharing algorithms, six 
     weight sharing algorithms, and three different training-free score functions, i.e., NI, NASWOT, and 
@@
 
-    \subsection{NAS-Bench-101}
-    The result of the experiment in NAS-Bench-101 search space shows in \xtab{table:overall_101}, 
-    which compares rank function and \palg{} with two non-weight sharing algorithms and two weight 
+    Lastly, the result of the experiment in NAS-Bench-101 \cite{ying2019nasbench101} is shown in \xtab{table:overall_101}. 
+    It compares rank function and \palg{} with two non-weight sharing algorithms and two weight 
     sharing algorithms. ENAS has the best performance, while the computation time is the highest. 
@@
             RS-rank (ours) (N=1000) & $516$  & $92.44 \pm 1.42$ & $91.94 \pm 2.01$ \\ 
-            \palg{} (ours)          & $374$  & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \midrule
+            \palg{} (ours)          & $595$  & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \midrule
             Optimal             &            & $95.12$          & $94.32$          \\ \bottomrule

### 2023-08-17 paper/manuscript.tex
update

@@
 
-\author{Hsieh Cheng-Han}
+\author{Cheng-Han Hsieh}
 \email{emiliaistruelove@gmail.com}
@@
 \begin{abstract}
-    The training-free neural architecture search (NAS) typically uses one or 
-    two score functions to evaluate how a neural network architecture performs. 
-    However, an architecture should be treated as a complex system that has 
-    unique characteristics to measure. 
+    The training-free neural architecture search (NAS) typically uses one  
+    score function to evaluate how a neural network architecture performs. 
+    However, an architecture is a system having unique characteristics to measure. %% 
+	The evaluation of neural architectures should measure the different aspects of 
+	neural architectures. 
     To achieve the goal, we propose a rank-based training-free NAS algorithm, 
-    which combines three training-free score functions which is "complementary" 
-    to each other to evaluate an architecture by ranking. 
-    In this work, noise immunity (NI) considers the image generalization 
-    ability of the architecture, the correlation between binary activation 
-    patterns, named NASWOT, considers image distinction ability, and LogSynFlow 
-    takes trainability into account. By the three measurements, an 
-    architecture can be evaluated from different aspects. 
+    which combines three ``complementary'' training-free score functions to 
+	evaluate an architecture. %% 
+	In this paper, the score function, NASWOT, measures image distinction ability. 
+	Noise immunity (NI) measures the image generalization ability. 
+	And LogSynFlow measures the trainability of the architecture. 
+    %In this work, noise immunity (NI) considers the image generalization 
+    %ability of the architecture, the correlation between binary activation 
+    %patterns, named NASWOT, considers image distinction ability, and LogSynFlow 
+    %takes trainability into account. %%
+    Through the three measurements, an architecture can be evaluated from different aspects. 
     With that, simulated annealing (SA) algorithm, \palg{}, 
@@
     Neural architecture search (NAS) has recently drawn a big amount of 
-    attention, since the ability to automatically design a "good" neural 
+    attention, since the ability to automatically design a ``good'' neural 
     architecture. By leveraging machine learning algorithms 
@@
     Despite the promising results of NAS, there are still many challenges 
-    to conquer. One major problem is the extremely high computational 
+    to deal with. One major problem is the extremely high computational %
     cost for searching an optimal architecture, which makes NAS 
@@
     % synflow
-    For another example, Lee et al. \cite{lee2019snip} proposed pruning 
-    parameters based on a saliency metric, which is then extended by 
-    Tanaka et al. \cite{tanaka2020pruning}. Tanaka et al. proposed 
+    %For another example, Lee et al. \cite{lee2019snip} proposed pruning 
+    %parameters based on a saliency metric, which is then extended by %%
+    %\cite{tanaka2020pruning}. Tanaka et al. proposed %%
+	For another example, Tanaka et al. proposed pruning a network by using 
     Iterative Synaptic Flow Pruning (SynFlow) algorithm 
-    which intends to deal with the layer collapse problem when pruning a 
-    network. The score function used in the algorithm is so-called 
-    \it{synaptic saliency} \rm{score}. Later, Abdelfattah et al. 
+    which intends to deal with the layer collapse problem. The score function 
+	used in the algorithm is so-called \it{synaptic saliency} \rm{score}. 
+	Later, Abdelfattah et al. 
     \cite{abdelfattah2021zerocost} extended SynFlow to score a network 
@@
     in the model. The outcome score represents the trainability of an 
-    architecture. Cavagnero et al. \cite{Cavagnero_2023} found that 
+    architecture. Cavagnero et al. \cite{Cavagnero_2023} pointed out that 
     SynFlow is likely to suffer from gradient explosion, then proposed 
@@
     from the low correlation between score values and the final accuracy of 
-    architectures, leading to a predicament that no matter how good the 
-    searching algorithm, we can hardly find an optimal architecture. 
+    architectures. The shortcoming leads to a predicament that no matter how good the 
+    searching algorithm, we can not find the optimal architecture. %% ... cannot find optimal, the main reason is ...
     The major problem that causes the low correlation is that a single score 
@@
     \begin{itemize}
-        \item A novel concept of "complementary" is proposed and used as a metric to choose score functions. 
+        \item A novel concept of ``complementary'' is proposed and used as a metric to choose score functions. 
         \item Cooperating the complementary score functions by ranking algorithm, which prevents one score overwhelming others numerically. 
         \item Applying simulated annealing algorithm on the ranking algorithm to imporve the searching ability. 
+        \item Improving simulated annealing algorithm by using a historical best set. 
     \end{itemize}
@@
     \subsection{Problem Definition}
-    First, assume that $D_{\text{train}}$ and $D_{\text{test}}$ are two subsets of input data $D$. Furthermore, 
-    assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $\mathcal A_s$ the 
+    First, assume that $D_{\text{train}}$ and $D_{\text{test}}$ are two subsets of input data $D$. 
+    Assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $\mathcal A_s$ the 
     search algorithm of NAS, and $\mathcal A_T$ the training function. Then, the NAS problem can be 
@@
         \label{equ:nas}
-        \mathbb N^*=\max_{\mathbb N^b\in\mathbb N}\mathcal F_A(\mathcal A_T(\mathbb N^b, D_{\text{train}}), D_{\text{test}})
+        \mathbb N^*=\max_{\mathbb N^b\in\mathbb N}\mathcal F_A(\mathcal A_T(\mathbb N^b, D_{\text{train}}), D_{\text{test}}),
     \end{equation}
@@
         \label{equ:non-training_free_nas}
-        \mathbb N^b=\mathcal A_S(\mathcal F_A(\mathcal A_T(\mathbb N^s, D_{\text{train}}), D_{\text{test}}), \mathbb N)
+        \mathbb N^b=\mathcal A_S(\mathcal F_A(\mathcal A_T(\mathbb N^s, D_{\text{train}}), D_{\text{test}}), \mathbb N),
     \end{equation}
@@
         \label{equ:training_free_nas}
-        \mathbb N^b=\mathcal A_S(\mathcal F_S(\mathbb N^s, D_{\text{train}}), \mathbb N)
+        \mathbb N^b=\mathcal A_S(\mathcal F_S(\mathbb N^s, D_{\text{train}}), \mathbb N),
     \end{equation}
-    Since the training function is removed in training-free NAS algorithms, they need much less 
+    Since the training function is replaced by training-free NAS algorithms, they need much less 
     computational resource than non-training-free NAS algorithms. 
@@
     the better the architecture learns. And the determinant of the kernel matrix 
-    measures how "different" they are by calculating the volume formed by the 
+    measures how ``different'' they are by calculating the volume formed by the 
     row vector of $K_H$.
 
-    Wu et al. \cite{10092788} found in some cases, an architecture with a high 
+    \begin{figure*}[tb]
+        \vspace{-\baselineskip}
+        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
+        \caption{A simple example to illustrate the procedure of NI.}
+        \label{fig:ni}
+        \centering
+        \vspace{-\baselineskip}
+    \end{figure*}
+
+    Wu et al. \cite{10092788} found in some cases, an architecture with a high %%
     NASWOT score may classify the same kind of input data into different classes. 
-    To fix this defect, Wu et al. proposed using noise immunity (NI) to 
+    %%, Wu et al. proposed using noise immunity (NI) to 
     evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
@@
 
-    \begin{figure*}[tb]
-        \vspace{-\baselineskip}
-        \resizebox{1.0\textwidth}{!}{\includegraphics{asset/ni.pdf}}
-        \caption{A simple example to illustrate the procedure of NI.}
-        \label{fig:ni}
-        \centering
-        \vspace{-\baselineskip}
-    \end{figure*}
-
     % synflow
     Besides image-related measurements, there is another characteristic to evaluate a network. 
-    \textit{The Lottery Ticket Hypothesis} \cite{frankle2019lottery} reveals that a 
-    network may have a "core" which decides the final accuracy of the network. 
-    How to prune a network correctly is thereby tempting. Lee et al. 
+    %%\textit{The Lottery Ticket Hypothesis} \cite{frankle2019lottery} reveals that a 
+    %%network may have a 'core' which decides the final accuracy of the network. %%
+    %%How to prune a network correctly is thereby tempting. Lee et al. 
     \cite{lee2019snip} presented a high performance algorithm that uses connection 
@@
         \label{equ:logsynflow}
-        S(\theta)=\theta\cdot\log(\frac{\partial \mathcal L}{\partial \theta}+1)
+        S(\theta)=\theta\cdot\log(\frac{\partial \mathcal L}{\partial \theta}+1).
     \end{equation}
@@
     \subsection{Search Algorithms}
-
+    %%
+    \begin{figure*}[htb]
+        \vspace{-\baselineskip}
+        \begin{center}
+            \begin{tabular}{ccc}
+                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/naswot-acc.pdf}}}
+                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ni-acc.pdf}}}
+                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ninaswot-acc.pdf}}}
+            \end{tabular}
+            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NAS-Bench-201 in the CIFAR-10 dataset 
+            (b) NI score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset. 
+            (c) NI score + NASWOT score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset.}
+            \label{fig:ninaswot}
+        \end{center}
+        \vspace{-\baselineskip}
+    \end{figure*}
+    %%
     There are several search algorithms applied on NAS, including random search, reinforcement learning, and
     metaheuristic algorithms. 
-
     In \cite{https://doi.org/10.48550/arxiv.2006.04647} \cite{Lopes_2021}, random search is applied. 
@@
         \label{equ:reinforcement_rw}
-        J(\theta_c)=E_{P(a_{1:T};\theta_c)}[R]
+        J(\theta_c)=E_{P(a_{1:T};\theta_c)}[R], 
     \end{equation}
@@
         \label{equ:reinforcement_grad}
-        \nabla_{\theta_c} J(\theta_c)=\sum^T_t=1 E_{P(a_{1:T};\theta_c)}[\nabla_{\theta_c}\log P(a_t\mid a_{(t-1):1};\theta_c)R]
+        \nabla_{\theta_c} J(\theta_c)=\sum^T_t=1 E_{P(a_{1:T};\theta_c)}[\nabla_{\theta_c}\log P(a_t\mid a_{(t-1):1};\theta_c)R]. 
     \end{equation}
@@
     An example shows in \xfig{fig:ninaswot}.
-    \begin{figure*}[htb]
-        \vspace{-\baselineskip}
-        \begin{center}
-            \begin{tabular}{ccc}
-                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/naswot-acc.pdf}}}
-                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ni-acc.pdf}}}
-                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ninaswot-acc.pdf}}}
-            \end{tabular}
-            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NAS-Bench-201 in the CIFAR-10 dataset 
-            (b) NI score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset. 
-            (c) NI score + NASWOT score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset.}
-            \label{fig:ninaswot}
-        \end{center}
-        \vspace{-\baselineskip}
-    \end{figure*}
 
@@
 
-    As mentioned, the key is choose the complement of a score function. For example, 
-    score functions that evaluate the expressivity/distinction ability shall have other 
+    As mentioned, the key is to choose the complement of a score function. For example, 
+    score functions that evaluate the expressivity/distinction ability should have other 
     score functions to evaluate the generalization ability. For these two graphic recognition 
@@
     \subsection{Simulated Annealing with Ranking Algorithm}
+
     The simulated annealing (SA) algorithm with ranking algorithm (\palg{})
-    is outlined in \xalg{alg:SA}. In line $1\sim2$, the historical best architectures 
+    is outlined in \xalg{alg:SA}. In line 1-2, the historical best architectures 
     set, denoted $H$, is initialized to an empty set, and an architecture is randomly sampled from 
-    search space, denoted $s$. Line $3\sim18$ are the major part of \palg{}, when the temperature 
-    is lower than ending temperature, the algorithm is terminated. Line $4\sim16$ 
-    represent every time the temperature decreases, $I$ iterations with following steps are executed. 
-    In line $5$, $s$ is used as a seed to generate the neighborhood of it, denoted $U$, 
+    search space, denoted $s$. Line 3-18 are the major part of \palg{}, when the temperature 
+    is lower than ending temperature, the algorithm is terminated. Line 4-16 
+    represent every time the temperature decreases, $t$ iterations with following steps are executed. 
+    In line 5, $s$ is used as a seed to generate the neighborhood of it, denoted $U$, 
     and the size of it is decided by a presetting parameter, the number of neighbours, $N$. 
-    In line $6$, $s$, $U$ and the architectures recorded in historical best architectures set are 
+    In line 6, $s$, $U$ and the architectures recorded in historical best architectures set are 
     put into ranking function. 
@@
     And the best architecture (excluding $s$) which has the highest rank is denoted by $s'$. 
-    In line $9$, the difference of the rank between $s'$ and $s$ is calculated and detnote $\Delta E$. 
-    Then in line $10$, a random variable $x$ is sampled from the uniform distribution on $[0,1]$. 
-    Line $11\sim15$ are the transition process. If the rank of $s'$ is higher than $s$ ($\Delta E<0$), 
+    In line 9, the difference of the rank between $s'$ and $s$ is calculated and detnote $\Delta E$. 
+    Then in line 10, a random variable $x$ is sampled from the uniform distribution on $[0,1]$. 
+    Line 11-15 are the transition process. If the rank of $s'$ is higher than $s$ ($\Delta E<0$), 
     the current solution is replaced by $s'$, or be replaced by probability, defined by 
@@
         \label{equ:SA_rk_prob}
-        e^{-\alpha\frac{\Delta E}{T}},
+        e^{-\alpha\frac{\Delta E}{\Psi}},
     \end{equation}
-    where $T$ is the current temperature, $\Delta E$ the difference of the rank between 
+    where $\Psi$ is the current temperature, $\Delta E$ the difference of the rank between 
     $s$ and $s'$, and $\alpha$ is a constant number adjusts the probability. The more 
     the difference between $s$ and $s'$, the smaller the probability of accepting the new solution. 
-    After the $I$ iterations, the temperature scales down by $r_t$ in line $17$. When $T$ is 
+    After the $t$ iterations, the temperature scales down by $r_\Psi$ in line $17$. When $\Psi$ is 
     lower or equal to $\tau$, the algorithm is terminated and the current architecture is returned in line $19$. 
@@
         \label{equ:SA_rk_size_of_H}
-        \beta (I\cdot N\cdot\frac{\ln{\tau/T}}{\ln{r_t}}),
+        \beta (I\cdot N\cdot\frac{\ln{\tau/\Psi}}{\ln{r_\Psi}}),
     \end{equation}
@@
             \Input{search space $\mathbb N^*$}
-            \Parameter Initial temperature $T$, ending temperature $\tau$, a real number between 0 and 1, $r_t$, the number of iteration, $I$, the number of generated neighbours, $N$, a real number, $\alpha$, the coefficient of the size of $H$, $\beta$
+            \Parameter Initial temperature $\Psi$, ending temperature $\tau$, a real number between 0 and 1, $r_\Psi$, the number of iteration, $t$, the number of generated neighbours, $N$, a real number, $\alpha$, the coefficient of the size of $H$, $\beta$
             \State Initialize historical best architectures set $H$ to empty set
             \State $s=\text{Randomly sample an architecture from }\mathbb N^*$
-            \While{$T>\tau$}
-                \For{$\text{each }i \in [1\ldots I]$}
+            \While{$\Psi>\tau$}
+                \For{$\text{each }i \in [1\ldots t]$}
                     \State $U = \text{Neighbor}(s, N)$
@@
                     \State $s'=\arg\min_{\mathbb N^i\neq s}(r)$
-                    \State $\Delta E=\text{Diff}(s', s)$
+                    \State $\Delta E=r(s')-r(s)$
                     \State $x\sim U[0,1]$
@@
                         \State $s\leftarrow s'$
-                    \ElsIf{$x\leq e^{-\alpha\frac{\Delta E}{T}}$}
+                    \ElsIf{$x\leq e^{-\alpha\frac{\Delta E}{\Psi}}$}
                             \State $s\leftarrow s'$
@@
                 \EndFor
-                \State $T\leftarrow T\times r_t$
+                \State $\Psi\leftarrow \Psi\times r_\Psi$
             \EndWhile
@@
     \end{algorithm}
+
+    An example of an iteration in \palg{} is shown in \xfig{fig:SA-rank-iteration}. 
+    Assume that at the beginning there is a current solution $s$ and the historical best 
+    architectures set $H=\{H_1,H_2\}$. Next, the neighborhood of $s$ is generated, 
+    denoted $U=\{s_A,s_B,s_C,s_D,s_E\}$. The rank of the architectures in the union 
+    set of $H$, $\{s\}$ and $U$ are calculated. The architecture with highest rank 
+    $s_C$ will be recorded by $H$, and the architecture with highest rank excluding 
+    $s$ is denoted $s'$. Then the difference $\Delta E$ of the rank is used for 
+    solution transition. If $\Delta E<0$, the solution is better than the the current 
+    solution. If it is not better, the solution can still be accepted by probability 
+    $e^{-\alpha\frac{\Delta E}{\Psi}}$.
+
+    \begin{figure}[htb]
+        \begin{center}
+            \resizebox*{0.48\textwidth}{!}{\includegraphics{asset/SA-rank-iteration.pdf}}
+            \caption{An example of an iteration of \palg{}.}
+            \label{fig:SA-rank-iteration}
+        \end{center}
+    \end{figure}
 
@@
     encoded into 6-integer vectors. However, a broken architecture appears since 
-    one of the operations is "zeroize", which means the measurement of a broken 
+    one of the operations is ``zeroize'', which means the measurement of a broken 
     architecture is meaningless. To exclude the broken architectures, the encoding 
@@
     The general proposed ranking algorithm is in \xalg{alg:rank-based}. 
-    The first step is to evaluate the network architectures in the subset, 
-    denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The 
-    evaluation of an architecture determined by $j$-th score function 
-    is $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating the subset 
-    of search space, the rank of each score function is calculated, denoted 
-    $r_{\mathcal F}$. Then the final rank, $r$, calculated by summing up 
-    the ranks. If a network architecture gains higher score in these score 
-    functions, the final rank should be higher (smaller index) too. Therefore, 
-    the highest (minimum) rank in $r$ shall be the best network architecture. 
-    In summary, the ranking algorithm makes the contribution of 
-    each score function even and therefore evaluate an architecture from 
-    different aspects.
+    Line 1-3 are to evaluate the network architectures in the subset 
+    by each score function, and then the rank of each architecture is 
+    obtained through the index of sorted scores. The subset, denoted 
+    $\mathbb N^s$, is sampled from the search space, $\mathbb N^*$. And 
+    the $j$-th score function is $\mathcal F_j(\cdot)$. The rank of the 
+    $i$-th architecture in the results of $j$-th score function are 
+    $r_{\mathcal F_j}(\mathbb N^i)$, as shown in line 2. In Line 4, 
+    the final rank of $i$-th architecture is calculated by summing up 
+    its rank in $j$-th score function. Then the ranking result of each 
+    architecture is returned. In summary, the ranking algorithm makes the 
+    contribution of each score function even and evaluate an architecture 
+    from different aspects. If an architecture gains higher score in these 
+    score functions, the final rank should be higher, i.e., smaller index. 
+    Therefore, the highest rank (numerically lowest) in $r$ is the best 
+    network architecture. 
+    %The first step is to evaluate the network architectures in the subset, 
+    %denoted $\mathbb N^s$, of search space, denoted $\mathbb N^*$. The 
+    %evaluation of an architecture determined by $j$-th score function 
+    %is $s_{\mathcal F_j}(\mathbb N^i)$. After evaluating the subset 
+    %of search space, the rank of each score function is calculated, denoted 
+    %$r_{\mathcal F}$. Then the final rank, $r$, calculated by summing up 
+    %the ranks. If a network architecture gains higher score in these score 
+    %functions, the final rank should be higher (smaller index) too. Therefore, 
+    %the highest (minimum) rank in $r$ shall be the best network architecture. 
+    %In summary, the ranking algorithm makes the contribution of 
+    %each score function even and therefore evaluate an architecture from 
+    %different aspects.
 
@@
             \Input{A subspace, ${\mathbb N}^{s}$, from search space, ${\mathbb N}^{*}$}
-            \For{$\text{each }{\mathbb N}^i\text{ in }{\mathbb N}^s$}
             \For{$\text{each }j\in\{1,\ldots,M\}$}
-                    \State $s_{{\mathcal F}_{j}}({\mathbb N}^i)={\mathcal F}_{j}({\mathbb N}^i)$
-                \EndFor
-            \EndFor
-            \For{$\text{each }j\in\{1,\ldots,M\}$}
-                \State $r_{{\mathcal F}_{j}}({\mathbb N}^i)$ = index of ${\mathbb N}^i$ in list $[s_{{\mathcal F}_{j}}({\mathbb N}^1),\ldots,s_{{\mathcal F}_{j}}({\mathbb N}^{\lvert {\mathbb N}^s\rvert})]$ \par sorted by descending order
+                \State $r_{{\mathcal F}_{j}}({\mathbb N}^i)$ = index of ${\mathbb N}^i$ in list $[{\mathcal F}_{j}({\mathbb N}^1),\ldots,{\mathcal F}_{j}({\mathbb N}^{\lvert {\mathbb N}^s\rvert})]$ \par sorted by descending order
             \EndFor
             \State $r({\mathbb N}^i)=\sum^M_{j=0} r_{{\mathcal F}_{j}}({\mathbb N}^i)$
-            %\State $i^*=\arg\min_{i}\{r({\mathbb N}^i)\}$
-            %\State $\textbf{Return }{\mathbb N}^{i^*}$
             \State $\textbf{Return }r$
@@
 
-    With the proposed ranking algorithm as a framework, the next question is 
-    to choose complementary score functions. The recent training-free 
+    The next question is %%
+    choosing ``complementary'' score functions. The recent training-free 
     score functions can be roughly classified into different kinds. NASWOT, 
@@
     LogSynFlow are measurements to trainability of an architecture. 
-    As mentioned, the chosen score function shall be complementary to each other. 
+    As mentioned, the chosen score function should be complementary to each other. 
     In this paper, NI and NASWOT are a complementary set, which takes 
@@
     \label{sec:conclusion}
-    In this paper, a novel concept of "complementary" is proposed and used as a basis to choose 
+    In this paper, a novel concept of ``complementary'' is proposed and used as a basis to choose 
     training-free score functions. The new rank algorithm is then applied to simulated annealing 
-    algorithm. The simulation result shows that the proposed algorithm, named SA-rk, not only outperforms the most 
+    algorithm. The simulation result shows that the proposed algorithm, named \palg{}, not only outperforms the most 
     state-of-art training-free score functions but also some of the non-training-free methods. 
@@
     spaces vary with neural network structures and size. 
-    The limitation of SA-rk is the lack of versatility since the score functions are mainly chosen 
-    for common image recognition. That means SA-rk may not be applied in the search of architectures 
+    The limitation of \palg{} is the lack of versatility since the score functions are mainly chosen 
+    for common image recognition. That means \palg{} may not be applied in the search of architectures 
     designed for other usages, i.e., speech recognition, NLP. However, the problem is able to be solved 

### 2023-09-04 paper/manuscript.tex
update

@@
     score function to evaluate how a neural network architecture performs. 
-    However, an architecture is a system having unique characteristics to measure. %% 
-	The evaluation of neural architectures should measure the different aspects of 
-	neural architectures. 
+    However, every architecture has unique characteristics. To accurately 
+    evaluate an architecture, the score function should take the different 
+    aspects of an neural architecture into account. 
     To achieve the goal, we propose a rank-based training-free NAS algorithm, 
     which combines three ``complementary'' training-free score functions to 
-	evaluate an architecture. %% 
-	In this paper, the score function, NASWOT, measures image distinction ability. 
-	Noise immunity (NI) measures the image generalization ability. 
-	And LogSynFlow measures the trainability of the architecture. 
-    %In this work, noise immunity (NI) considers the image generalization 
-    %ability of the architecture, the correlation between binary activation 
-    %patterns, named NASWOT, considers image distinction ability, and LogSynFlow 
-    %takes trainability into account. %%
-    Through the three measurements, an architecture can be evaluated from different aspects. 
-    With that, simulated annealing (SA) algorithm, \palg{}, 
-    can be applied and obtain a better performance on searching high-accuracy architectures.  
-    To evaluate the performance of the proposed algorithm, this paper compared 
+	evaluate an architecture. 
+	NAS without training score function measures the difference 
+    of the activation patterns between a batch of data passing through an 
+    architecture, i.e., the image distinction ability. 
+	Noise immunity measures the difference between the pooling layers 
+    of an architecture by passing an image and the same image with Gaussian noise, 
+    i.e., the image generalization ability. 
+	And LogSynFlow measures the importance of connections of an architecture, 
+    i.e., the trainability. 
+    Through the three measurements, an architecture can be evaluated from 
+    different aspects. With an integrated score function, the proposed 
+    method, \palg{} applies simulated annealing algorithm to obtain 
+    better performance on searching high-accuracy architectures. 
+    To evaluate the performance of \palg{}, this paper compared 
     it with several NAS algorithms, including weight sharing methods, 
     non-weight sharing methods, and several state-of-the-art training-free 
-    score functions. The final result indicates that \palg{} outperforms most 
+    score functions. The ultimate results show that \palg{} outperforms most 
     training-free score functions and shows the robustness between different 
@@
     Despite the promising results of NAS, there are still many challenges 
-    to deal with. One major problem is the extremely high computational %
+    to deal with. One major problem is the extremely high computational 
     cost for searching an optimal architecture, which makes NAS 
     impractical for real-world applications, particularly on resource-constrained 
-    platforms like embedded system. The main reason why NAS is costly is that 
+    platforms like embedded system. NAS is costly because 
     during searching, a candidate architecture must be trained to 
-    evaluate how good of this architecture.
+    evaluate how good of this architecture. %% compare architectures each of which must be trained
 
-    To eliminate the training cost, recent works proposed lots 
-    of methods which is so called training-free NAS. 
+    To eliminate the training cost, recent works proposed lots of methods 
+    which is so called training-free NAS. 
     % NASWOT
@@
     % synflow
-    %For another example, Lee et al. \cite{lee2019snip} proposed pruning 
-    %parameters based on a saliency metric, which is then extended by %%
-    %\cite{tanaka2020pruning}. Tanaka et al. proposed %%
-	For another example, Tanaka et al. proposed pruning a network by using 
-    Iterative Synaptic Flow Pruning (SynFlow) algorithm 
-    which intends to deal with the layer collapse problem. The score function 
-	used in the algorithm is so-called \it{synaptic saliency} \rm{score}. 
-	Later, Abdelfattah et al. 
+	Another example can be found in \cite{tanaka2020pruning}, Tanaka et al. 
+    presented pruning a network by using Iterative Synaptic Flow Pruning 
+    (SynFlow) algorithm which intends to deal with the layer collapse 
+    problem. The score function used in the algorithm is so-called 
+    \it{synaptic saliency} \rm{score}. Later, Abdelfattah et al. 
     \cite{abdelfattah2021zerocost} extended SynFlow to score a network 
@@
 % what is unknown?
-    % 做成圖表放第一頁
-    However, \xtab{table:corr_score} shows most score functions suffer 
+    Although the training-free score functions are capable of reducing the 
+    computational cost, \xtab{table:corr_score} shows most score functions suffer %
     from the low correlation between score values and the final accuracy of 
-    architectures. The shortcoming leads to a predicament that no matter how good the 
-    searching algorithm, we can not find the optimal architecture. %% ... cannot find optimal, the main reason is ...
+    architectures. The shortcoming leads to a predicament that no matter 
+    how good the searching algorithm is, the optimal architectures are still 
+    buried in dirt. %
     The major problem that causes the low correlation is that a single score 
@@
                 \midrule
-                \bf{NTK}                     & -0.50    & -0.47     & -0.49 \\
+                \bf{condition number of NTK}                     & -0.50    & -0.47     & -0.49 \\
                 \bf{Snip}                    & 0.46     & 0.46      & 0.42  \\
@@
 % method
-    To address the problem, we propose cooperating three complementary 
-    score functions by ranking, which allows every score functions 
-    evaluate an architecture without losing fairness. 
-    The first score function is noise immunity (NI) \cite{10092788}, as 
-    a measurement of the ability of image generalization. 
-    The second one is NASWOT, used as a score to estimate the ability of distinction 
-    of architecture and also a complement of NI. 
-    The last one is LogSynFlow used as the measurement of trainability 
-    and also as a complement to NI and NASWOT. 
-    With these three complementary score functions, an evaluation of an 
+    To address the problem, we propose cooperating three heterogeneous 
+    score functions by ranking, which allows every score function 
+    evaluates an architecture without losing fairness. 
+    %The first score function is noise immunity (NI) \cite{10092788}, as 
+    %a measurement of the ability of image generalization. 
+    %The second one is NASWOT, used as a score to estimate the ability of distinction 
+    %of architecture and also a complement of NI. 
+    %The last one is LogSynFlow used as the measurement of trainability 
+    %and also as a complement to NI and NASWOT. 
+    And with these three score functions, the evaluation of an 
     architecture is not simply from a single aspect but three different 
@@
     The major contribution of this paper can be summarized as follow:
-    \begin{itemize}
-        \item A novel concept of ``complementary'' is proposed and used as a metric to choose score functions. 
-        \item Cooperating the complementary score functions by ranking algorithm, which prevents one score overwhelming others numerically. 
-        \item Applying simulated annealing algorithm on the ranking algorithm to imporve the searching ability. 
-        \item Improving simulated annealing algorithm by using a historical best set. 
-    \end{itemize}
-
+    (1) A novel concept of ``complementary'' is presented and used as 
+    a metric to choose score functions. 
+    (2) Cooperating the score functions by ranking algorithm, 
+    which prevents one score overwhelming others numerically. 
+    (3) Applying simulated annealing algorithm on the ranking algorithm 
+    to imporve the searching ability. 
+    (4) Improving simulated annealing algorithm by using a historical 
+    best set. 
     %orginzation
@@
     \xsec{sec:related_work} provides the detail about the training-free 
-    score functions. \xsec{sec:proposed} gives a detailed 
-    description about the proposed method. \xsec{sec:results} begins 
-    with parameters setting and provides the simulation results in 
-    different search spaces. The conclusion and further 
-    prospect are gived in \xsec{sec:conclusion}.
+    score functions. 
+    \xsec{sec:proposed} gives a detailed description about the proposed method. 
+    \xsec{sec:results} begins with parameters setting and provides the 
+    simulation results in different search spaces. 
+    The conclusion and further prospect are gived in \xsec{sec:conclusion}.
 
@@
     \label{sec:related_work}
-
     \subsection{Problem Definition}
-    First, assume that $D_{\text{train}}$ and $D_{\text{test}}$ are two subsets of input data $D$. 
+    In \cite{10092788}, the NAS is defined as following: 
+    first, assume that $D_{\text{train}}$ and $D_{\text{test}}$ are two subsets of input data $D$. 
     Assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $\mathcal A_s$ the 
@@
 
-    Wu et al. \cite{10092788} found in some cases, an architecture with a high %%
+    Wu et al. \cite{10092788} discovered in some cases, an architecture with a high %%
     NASWOT score may classify the same kind of input data into different classes. 
-    %%, Wu et al. proposed using noise immunity (NI) to 
-    evaluate an architecture. \xfig{fig:ni} gives an example to illustrate how 
-    NI evaluates an architecture. The score function picks a 
-    mini-batch of data, denoted $X$, and then applies Gaussian noise to it. 
-    The process is defined by $X'=X+z$ where $z$ is the Gaussian noise. 
-    By passing $X$ and $X'$ through the untrained architecture, then computing 
-    the difference of square of each feature map captured at all pooling layers. 
-    Calculate the matrix $\kappa$ defined by 
+    \xfig{fig:ni} gives an example to illustrate how NI evaluates an architecture. 
+    The score function picks a mini-batch of data, denoted $X$, and then applies 
+    Gaussian noise to it. The process is defined by $X'=X+z$ where $z$ is the 
+    Gaussian noise. By passing $X$ and $X'$ through the untrained architecture, 
+    then computing the difference of square of each feature map captured at all 
+    pooling layers. Calculate the matrix $\kappa$ defined by 
     \begin{equation}
@@
     % synflow
-    Besides image-related measurements, there is another characteristic to evaluate a network. 
+    Besides image-related measurements, there is another characteristic to 
+    evaluate a network, trainability. 
     %%\textit{The Lottery Ticket Hypothesis} \cite{frankle2019lottery} reveals that a 
@@
     %%How to prune a network correctly is thereby tempting. Lee et al. 
-    \cite{lee2019snip} presented a high performance algorithm that uses connection 
-    sensitivity as a criterion to prune the network, named single-shot network pruning (SNIP). 
-    which can be briefly viewed as 
+    \cite{lee2019snip} presented an algorithm that uses synaptic saliency score as a 
+    criterion to prune the network, named single-shot network pruning (SNIP). 
+    The synaptic saliency score is defined by 
     \begin{equation}
@@
     algorithm, an extension of magnitude pruning algorithm that avoids layer-collapse. 
-    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, and proposed to score a 
+    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, and presented to score a 
     network by summing the synaptic saliency score over all parameters in the model, which is 
@@
     subspaces based on the expected value of each subspace. The expected value is comprised of 
-    \begin{itemize}
-        \item The number of times the subspace has been investiagted. 
-        \item The average objective value of the new candidate solutions in the subspace at current iteration. 
-        \item The best solution so far in this subspace. 
-    \end{itemize}
+    (1) The number of times the subspace has been investiagted. 
+    (2) The average objective value of the new candidate solutions in the subspace at current iteration. 
+    (3) The best solution so far in this subspace. 
     Based on these designs, SE avoids falling into local optimum, while searching for high expected value instead.
@@
     after evaluating the whole search space, e.g., range, mean, or standard deviation, 
-    which is practically impossible. To make the proposed score function 
+    which is practically impossible. To make the presented score function 
     agnostic to the search space, it leverages multiple score functions by ranking, 
@@
 
+    \begin{table*}[htb]
+        %\normalsize
+        %\centering
+        \newcommand{\z}{\phantom{0}}
+        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-SSS.}}
+          \vspace{-\baselineskip}
+        \begin{tabular}{@{}lccccccc@{}}\toprule
+        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
+                            &          & validation       & test             & validation       & test              & validation       & test \\ \midrule
+                            &          &                  &                  & \textbf{Non-weight sharing} &        &                  &                  \\
+        AREA                & $12,000$ & $84.62 \pm 0.41$ & $93.16 \pm 0.16$ & $59.24 \pm 1.11$ & $69.56 \pm 0.96$  & $37.58 \pm 1.09$ & $45.30 \pm 0.91$ \\
+        REA                 & $12,000$ & $90.37 \pm 0.20$ & $93.22 \pm 0.16$ & $70.23 \pm 0.50$ & $70.11 \pm 0.61$  & $45.30 \pm 0.69$ & $45.94 \pm 0.92$ \\
+        RS                  & $12,000$ & $90.10 \pm 0.26$ & $93.03 \pm 0.25$ & $69.57 \pm 0.57$ & $69.72 \pm 0.61$  & $45.01 \pm 0.74$ & $45.42 \pm 0.86$ \\
+        RL                  & $12,000$ & $90.25 \pm 0.23$ & $93.16 \pm 0.21$ & $69.84 \pm 0.59$ & $69.96 \pm 0.57$  & $45.06 \pm 0.77$ & $45.71 \pm 0.93$ \\
+        BOHB                & $12,000$ & $90.07 \pm 0.28$ & $93.01 \pm 0.24$ & $69.75 \pm 0.60$ & $69.90 \pm 0.60$  & $45.11 \pm 0.69$ & $45.56 \pm 0.81$ \\ \midrule
+                            &          &                  &                  & \textbf{Training-free} &             &                  &                  \\
+        RS-NI (N=1,000)         & $293$& $89.55 \pm 0.16$ & $92.56 \pm 0.21$ & $67.67 \pm 0.91$ & $67.61 \pm 1.06$  & $43.19 \pm 0.73$ & $43.22 \pm 0.53$ \\ 
+        RS-NASWOT (N=1,000)     & $208$& $89.25 \pm 0.44$ & $92.21 \pm 0.31$ & $65.09 \pm 2.89$ & $64.61 \pm 3.16$  & $41.29 \pm 2.32$ & $41.35 \pm 2.31$ \\ 
+        RS-LogSynFlow (N=1,000) & $123$& $89.60 \pm 0.11$ & $92.61 \pm 0.18$ & $68.23 \pm 0.49$ & $68.30 \pm 0.54$  & $43.58 \pm 0.58$ & $43.48 \pm 0.40$ \\ 
+        RS-rank (ours) (N=1000) & $612$& $89.59 \pm 0.14$ & $92.51 \pm 0.17$ & $67.56 \pm 0.75$ & $67.55 \pm 0.82$  & $43.36 \pm 0.62$ & $43.27 \pm 0.45$ \\ 
+        \palg{} (ours)          & $725$& $90.33 \pm 0.15$ & $93.26 \pm 0.24$ & $69.89 \pm 0.48$ & $70.24 \pm 0.42$  & $45.41 \pm 0.41$ & $46.43 \pm 0.75$ \\ \midrule
+        %SA-NI                  &      & $90.24 \pm 0.10$ & $93.20 \pm 0.19$ & $69.83 \pm 0.56$ & $70.10 \pm 0.40$  & $45.49 \pm 0.50$ & $45.98 \pm 0.89$
+        Optimal             &          & $90.71$          & $93.65$          & $70.92$          & $71.34$           & $46.73$          & $47.40$          \\ \bottomrule
+        \end{tabular}
+        \label{table:overall_sss}
+          \vspace{-\baselineskip}
+    \end{table*}
+
     The general proposed ranking algorithm is in \xalg{alg:rank-based}. 
@@
 
-    The next question is %%
-    choosing ``complementary'' score functions. The recent training-free 
+    The next question is choosing ``complementary'' score functions. The recent training-free 
     score functions can be roughly classified into different kinds. NASWOT, 
@@
     LogSynFlow are measurements to trainability of an architecture. 
-    As mentioned, the chosen score function should be complementary to each other. 
-    In this paper, NI and NASWOT are a complementary set, which takes 
-    the ability of image generalization and distinction into account. 
-    This complementary set is viewed as the measurement of the ability of graphic 
+    As mentioned, the chosen score function should cover every characteristics 
+    of an architecture. In this paper, NI and NASWOT are a complementary set, 
+    which takes the ability of image generalization and distinction into account. 
+    This set is viewed as the measurement of the ability of graphic 
     recognition. Therefore, the last missing piece is the trainability of an 
@@
     \label{sec:results}
-
-    We evalute the performance of the proposed algorithm, \palg{}, 
-    for searching the architectures of high accuracy. For comparison, several NAS 
-    algorithms are included, e.g., random search (RS), regularized evolution algorithm 
-    (REA) \cite{real2019regularized}, reinforcement learning (RL) \cite{Williams:92}, 
-    Bayesian optimization with hyper band (BOHB) \cite{falkner2018bohb}, RS with 
-    weight sharing (RSWS) \cite{li2019random}, differentiable architecture search 
-    with first order (DARTS-V1) \cite{liu2019darts}, DARTS with second order 
-    (DARTS-V2) \cite{liu2019darts}, gradient-based search using differentiable 
-    architecture sampler (GDAS) \cite{dong2019searching}, self-evaluated template 
-    network (SETN) \cite{Dong_2019}, efficient NAS (ENAS) \cite{pham2018efficient}, 
-    assisted REA (AREA) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
-    %zero-cost NAS \cite{https://doi.org/10.48550/arxiv.2101.08134}, 
-    TE-NAS \cite{https://doi.org/10.48550/arxiv.2102.11535}, gradient kernel-based 
-    NAS (KNAS) \cite{xu2021knas}, RS with NASWOT \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
-    RS with noise immunity (NI) \cite{10092788}, RS with LogSynFlow \cite{Cavagnero_2023}, 
-    and RS with ranking.
-
-    The three search spaces, NATS-bench-SSS, NATS-bench-TSS 
-    \cite{Dong_2021} and NAS-Bench-101 \cite{ying2019nasbench101}, are used 
-    here to evalute the performance of the NAS algorithms. The architectures 
-    of NATS-bench-TSS is same as NAS-Bench-201 \cite{dong2020nasbench201}. 
-    The architectures in NATS-bench-SSS and NATS-bench-TSS are trained by the three datasets: 
-    CIFAR10, CIFAR100, ImageNet-16-120, while NAS-Bench-101 is trained by one: 
-    CIFAR10.
-
-    \subsection{Environment and Parameter Settings}
-    The experiment is conducted on a PC with Intel Core i7-11700K (3.60 GHz, 16-MB Cache, and 16 cores), 
-    a single NVIDIA RTX3070 Ti GPU with 8 GB memory, driver version 520.61.05, CUDA version 11.8, and 
-    65 GB available memory running on Ubuntu 20.04.1 with linux kernel 5.15.0-73-generic. All the program 
-    is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. The simulations of all 
-    non-weight sharing NASs are carried out for 500 runs on all the search spaces except AREA, which is 50 runs. 
-    For weight sharing NAS algorithms, each is carried out for 3 runs. And for training-free 
-    algorithms, each is carried out for 100 runs and are given an evaluation 
-    budget of 1000 for all the search space. The parameter settings of \palg{} are as follows: 
-    initial temperature, ending temperature, rate of decrease of temperature, the number of iteration, 
-    the constant number adjusting acceptance probability, the number of generated neighbours, and 
-    the coefficient of the size of historical best architectures set are set 
-    to 1, 0.0008, 0.745, 4, 0.25, 10, 1, so that the maximum number of searching candidates is 1000.
-
-    % 3 search spaces merge
-    \subsection{Simulation Results}
-    The simulation results in NATS-Bench-SSS \cite{Dong_2021} is shown in \xtab{table:overall_sss}. The proposed 
-    NAS algorithm and ranking function is compared with the other five non-weight sharing 
-    algorithm and NI, NASWOT, and LogSynFlow. 
-    For fairness, the searching architectures for the RS with training-free score 
-    functions are identical. The performance of the ranking algorithm is similar to NI but 
-    lower than LogSynFlow. However, the proposed NAS algorithm improves the results 
-    significantly and outperforms almost all the compared algorithms.
-
-    \begin{table*}[htb]
-        %\normalsize
-        %\centering
-        \newcommand{\z}{\phantom{0}}
-        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-SSS.}}
-          \vspace{-\baselineskip}
-        \begin{tabular}{@{}lccccccc@{}}\toprule
-        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
-                            &          & validation       & test             & validation       & test              & validation       & test \\ \midrule
-                            &          &                  &                  & \textbf{Non-weight sharing} &        &                  &                  \\
-        AREA                & $12,000$ & $84.62 \pm 0.41$ & $93.16 \pm 0.16$ & $59.24 \pm 1.11$ & $69.56 \pm 0.96$  & $37.58 \pm 1.09$ & $45.30 \pm 0.91$ \\
-        REA                 & $12,000$ & $90.37 \pm 0.20$ & $93.22 \pm 0.16$ & $70.23 \pm 0.50$ & $70.11 \pm 0.61$  & $45.30 \pm 0.69$ & $45.94 \pm 0.92$ \\
-        RS                  & $12,000$ & $90.10 \pm 0.26$ & $93.03 \pm 0.25$ & $69.57 \pm 0.57$ & $69.72 \pm 0.61$  & $45.01 \pm 0.74$ & $45.42 \pm 0.86$ \\
-        RL                  & $12,000$ & $90.25 \pm 0.23$ & $93.16 \pm 0.21$ & $69.84 \pm 0.59$ & $69.96 \pm 0.57$  & $45.06 \pm 0.77$ & $45.71 \pm 0.93$ \\
-        BOHB                & $12,000$ & $90.07 \pm 0.28$ & $93.01 \pm 0.24$ & $69.75 \pm 0.60$ & $69.90 \pm 0.60$  & $45.11 \pm 0.69$ & $45.56 \pm 0.81$ \\ \midrule
-                            &          &                  &                  & \textbf{Training-free} &             &                  &                  \\
-        RS-NI (N=1,000)         & $293$& $89.55 \pm 0.16$ & $92.56 \pm 0.21$ & $67.67 \pm 0.91$ & $67.61 \pm 1.06$  & $43.19 \pm 0.73$ & $43.22 \pm 0.53$ \\ 
-        RS-NASWOT (N=1,000)     & $208$& $89.25 \pm 0.44$ & $92.21 \pm 0.31$ & $65.09 \pm 2.89$ & $64.61 \pm 3.16$  & $41.29 \pm 2.32$ & $41.35 \pm 2.31$ \\ 
-        RS-LogSynFlow (N=1,000) & $123$& $89.60 \pm 0.11$ & $92.61 \pm 0.18$ & $68.23 \pm 0.49$ & $68.30 \pm 0.54$  & $43.58 \pm 0.58$ & $43.48 \pm 0.40$ \\ 
-        RS-rank (ours) (N=1000) & $612$& $89.59 \pm 0.14$ & $92.51 \pm 0.17$ & $67.56 \pm 0.75$ & $67.55 \pm 0.82$  & $43.36 \pm 0.62$ & $43.27 \pm 0.45$ \\ 
-        \palg{} (ours)          & $725$& $90.33 \pm 0.15$ & $93.26 \pm 0.24$ & $69.89 \pm 0.48$ & $70.24 \pm 0.42$  & $45.41 \pm 0.41$ & $46.43 \pm 0.75$ \\ \midrule
-        Optimal             &          & $90.71$          & $93.65$          & $70.92$          & $71.34$           & $46.73$          & $47.40$          \\ \bottomrule
-        \end{tabular}
-        \label{table:overall_sss}
-          \vspace{-\baselineskip}
-    \end{table*}
-
-    In NATS-Bench-TSS \cite{Dong_2021}, \xtab{table:overall_201} compares \palg{} with the other non-weight sharing algorithms, six 
-    weight sharing algorithms, and three different training-free score functions, i.e., NI, NASWOT, and 
-    LogSynFlow. Same as the experiment of NATS-Bench-TSS, the searching architectures are identical 
-    for the RS with score functions. Non-weight sharing algorithms like REA and AREA outperform all 
-    the other search algorithms, though the time cost is tremendous. In CIFAR10 and ImageNet16-120 datasets, 
-    the performance of ranking algorithm and \palg{} outperform other training-free and non-weight sharing 
-    algorithms and show a lower standard deviation compared with the others. In CIFAR100, 
-    NI though outperforms the ranking algorithm, \palg{} still has better performance.
 
@@
         \palg{} (ours)          & $902$  & $90.20 \pm \z{0.24}$ & $93.53 \pm 0.22$ & $70.51 \pm 0.71$ & $70.63 \pm 0.66$ & $43.80 \pm 1.86$ & $44.63 \pm 1.64$ \\ \midrule
+        %SA-NI                  &        & $90.06 \pm 0.29$     & $93.38 \pm 0.50$ & $70.41 \pm 0.74$ & $70.34 \pm 1.34$ & $42.69 \pm 1.87$ & $43.22 \pm 1.93$
         Optimal             &          & $91.61$              & $94.37$          & $73.49$          & $73.51$          & $46.73$          & $47.31$          \\ \bottomrule
@@
 
-    Lastly, the result of the experiment in NAS-Bench-101 \cite{ying2019nasbench101} is shown in \xtab{table:overall_101}. 
-    It compares rank function and \palg{} with two non-weight sharing algorithms and two weight 
-    sharing algorithms. ENAS has the best performance, while the computation time is the highest. 
-    Compared \palg{} with other training-free score functions, the performance and stability are better 
-    than others with a reasonable time cost.
+    We evalute the performance of the proposed algorithm, \palg{}, 
+    for searching the architectures of high accuracy. For comparison, several NAS 
+    algorithms are included, e.g., random search (RS), regularized evolution algorithm 
+    (REA) \cite{real2019regularized}, reinforcement learning (RL) \cite{Williams:92}, 
+    Bayesian optimization with hyper band (BOHB) \cite{falkner2018bohb}, RS with 
+    weight sharing (RSWS) \cite{li2019random}, differentiable architecture search 
+    with first order (DARTS-V1) \cite{liu2019darts}, DARTS with second order 
+    (DARTS-V2) \cite{liu2019darts}, gradient-based search using differentiable 
+    architecture sampler (GDAS) \cite{dong2019searching}, self-evaluated template 
+    network (SETN) \cite{Dong_2019}, efficient NAS (ENAS) \cite{pham2018efficient}, 
+    assisted REA (AREA) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
+    %zero-cost NAS \cite{https://doi.org/10.48550/arxiv.2101.08134}, 
+    TE-NAS \cite{https://doi.org/10.48550/arxiv.2102.11535}, RS with NASWOT (RS-NASWOT) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
+    RS with noise immunity (RS-NI) \cite{10092788}, RS with LogSynFlow (RS-LogSynFlow) \cite{Cavagnero_2023}, 
+    and RS with ranking (RS-rank).
 
-    \begin{table*}[t]
+    The three search spaces, NATS-bench-SSS, NATS-bench-TSS 
+    \cite{Dong_2021} and NAS-Bench-101 \cite{ying2019nasbench101}, are used 
+    here to evalute the performance of the NAS algorithms. The architectures 
+    of NATS-bench-TSS is same as NAS-Bench-201 \cite{dong2020nasbench201}. 
+    The architectures in NATS-bench-SSS and NATS-bench-TSS are trained by the three datasets: 
+    CIFAR10, CIFAR100, ImageNet-16-120, while NAS-Bench-101 is trained by one: 
+    CIFAR10.
+
+    \subsection{Environment and Parameter Settings}
+    The experiment is conducted on a PC with Intel Core i7-11700K (3.60 GHz, 16-MB Cache, and 16 cores), 
+    a single NVIDIA RTX3070 Ti GPU with 8 GB memory, driver version 520.61.05, CUDA version 11.8, and 
+    65 GB available memory running on Ubuntu 20.04.1 with linux kernel 5.15.0-73-generic. All the program 
+    is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. The simulations of all 
+    non-weight sharing NASs are carried out for 500 runs on all the search spaces except AREA, which is 50 runs. 
+    For weight sharing NAS algorithms, each is carried out for 3 runs. And for training-free 
+    algorithms, each is carried out for 100 runs and are given an evaluation 
+    budget of 1000 for all the search space. The parameter settings of \palg{} are as follows: 
+    initial temperature, ending temperature, rate of decrease of temperature, the number of iteration, 
+    the constant number adjusting acceptance probability, the number of generated neighbours, and 
+    the coefficient of the size of historical best architectures set are set 
+    to 1, 0.0008, 0.745, 4, 0.25, 10, 1, so that the maximum number of searching candidates is 1000.
+
+    \subsection{Simulation Results} % 補實驗描述
+    % sss
+    The simulation results in NATS-Bench-SSS \cite{Dong_2021} is shown in \xtab{table:overall_sss}. 
+    The proposed NAS algorithm and ranking function is compared with the other five non-weight sharing 
+    algorithm and three training-free score functions with random search (RS), i.e., RS-NI, RS-NASWOT, 
+    and RS-LogSynFlow. For fairness, the searching architectures for the RS with training-free 
+    score functions are identical. Among the four training-free score functions with RS, RS-LogSynFlow 
+    has the highest accuracy in CIFAR10. The accuracy of RS-NI and RS-rank are similar, but the stability 
+    of RS-rank is better. In CIFAR100, RS-LogSynFlow performs best, then is RS-NI, RS-rank, RS-NASWOT. 
+    In ImageNet16, RS-LogSynFlow still has the highest accuracy and stability, then is RS-rank, RS-NI, 
+    RS-NASWOT. However, \palg{} improves the results significantly and outperforms almost all the 
+    compared algorithms, including AREA, REA, and RL. It can be seen that, search algorithms guides 
+    the searching direction for searching better architectures, and the training-free score functions
+    accelerate the whole searching process by eliminating the training stage.
+
+    % tss
+    In NATS-Bench-TSS \cite{Dong_2021}, \xtab{table:overall_201} compares \palg{} with the other 
+    non-weight sharing algorithms, six weight sharing algorithms, three different training-free 
+    score functions with RS, i.e., RS-NI, RS-NASWOT, and RS-LogSynFlow and one 
+    training-free method, TE-NAS. Same as the experiment of NATS-Bench-SSS, the searching 
+    architectures are identical for the RS with score functions. Non-weight sharing algorithms 
+    like REA and AREA outperform all the other search algorithms, though the time cost is 
+    tremendous. Among the four training-free score functions with random search, RS-rank has the 
+    highest accuracy in CIFAR10 and ImageNet16. But in CIFAR100, RS-NI has the highest accuracy. 
+    In CIFAR10 validation dataset, RS-NI is the most stable, RS-rank the second, RS-LogSynFlow the 
+    third and RS-NASWOT the last. In CIFAR10 test dataset, RS-rank is the most stable, then is RS-NI, 
+    RS-LogSynFlow, RS-NASWOT. In CIFAR100, RS-NI is the most stable, RS-NASWOT the second but 
+    has lower accuracy, RS-rank the third, the last is RS-LogSynFlow. In ImageNet16, RS-rank is the 
+    most stable, then is RS-NI, RS-NASWOT, RS-LogSynFlow. According to the results, RS-rank does 
+    integrate the score functions and use them to evaluate an architecture by different characteristics. 
+    With the help of search algorithm, \palg{} outperforms all the others training-free methods, 
+    and obtains a better stability. In CIFAR10 and CIFAR100, the standard deviation of \palg{} is lower 
+    than all the non-weight sharing algorithms. And in ImageNet16, the standard deviation of \palg{} is 
+    lower than all the training-free methods.
+
+    % 101
+    The result of the experiment in NAS-Bench-101 \cite{ying2019nasbench101} is shown in \xtab{table:overall_101}. 
+    It compares rank function and \palg{} with two non-weight sharing algorithms, two weight 
+    sharing algorithms, and three training-free score functions with RS. The training-free 
+    score functions are same to the ones in NATS-Bench-TSS and NATS-Bench-SSS. In the experiment, ENAS has 
+    the best performance, while the computation time is the highest. AREA and REA performs similarly. 
+    In CIFAR10 validation dataset, the accuracy of RS-NI is better than RS-rank, but the standard 
+    deviation is worse than RS-rank. And RS-NASWOT though is higher than RS-LogSynFlow, RS-NASWOT 
+    is the most unstable. \palg{} has better accuracy and stability than all the other training-free 
+    score functions. In CIFAR10 test dataset, RS-NI has higher accuracy than RS-rank, however, the 
+    stability of RS-NI is much worse than RS-rank. The accuracy and stability of \palg{} is the best 
+    among the training-free methods. Compared with \palg{} and the other NAS methods, though the 
+    performance and stability are a little bit worse than AREA, REA and ENAS, the time cost of \palg{} is 
+    much less than them.
+
+    \begin{table}[t]
         %\normalsize
@@
             RS-rank (ours) (N=1000) & $516$  & $92.44 \pm 1.42$ & $91.94 \pm 2.01$ \\
+            %RS-NI (N=5,000)         & $280$  & $92.89 \pm 2.10$ & $92.35 \pm 2.69$ \\ 
+            %RS-NASWOT (N=5,000)     & $162$  & $92.27 \pm 6.60$ & $90.60 \pm 6.64$ \\ 
+            %RS-LogSynFlow (N=5,000) & $105$  & $91.81 \pm 1.52$ & $91.17 \pm 1.86$ \\ 
+            %RS-rank (ours) (N=5,000) & $516$  & $92.44 \pm 1.42$ & $92.32 \pm 1.47$ \\ 
             \palg{} (ours)          & $595$  & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \midrule
+            %SA-NI                  &        & $92.38 \pm 3.50$ & $92.71 \pm 1.97$
             Optimal             &            & $95.12$          & $94.32$          \\ \bottomrule
@@
         \vspace{-\baselineskip}
-    \end{table*}
+    \end{table}
 

### 2023-09-12 RD_search.py
add prompt

@@ -67,7 +67,7 @@ random.seed(args.seed)
 np.random.seed(args.seed)
 torch.manual_seed(args.seed)
 
-enroll_sc_fn_names = ["ni", "naswot", "logsynflow", "synflow", "ntk", "grasp", "snip"]
+enroll_sc_fn_names = ["ni", "naswot", "logsynflow"]
 enroll_sc_fns = {"ni": ni_score, "naswot": naswot_score, "logsynflow": logsynflow_score, "synflow": synflow_score, "ntk": ntk_score, "grasp": grasp_score, "snip": snip_score}
 accs = dict((fn_names, []) for fn_names in enroll_sc_fn_names)
 taus = dict((fn_names, []) for fn_names in enroll_sc_fn_names)
@@ -76,6 +76,8 @@ accs["rank"] = []
 taus["rank"] = []
 times["rank"] = []
 bestacc = []
+
+print(f"score functions for RS: {enroll_sc_fn_names}")
 
 cnt = 0
 runs = trange(args.n_runs, desc='RS algorithm')

### 2023-09-12 SA_search.py

@@ -70,6 +70,7 @@ torch.manual_seed(args.seed)
 acc = []
 enroll_sc_fn_names = ["ni", "naswot", "logsynflow"]
 enroll_sc_fns = {"ni": ni_score, "naswot": naswot_score, "logsynflow": logsynflow_score}
+print(f"score functions used in SA: {enroll_sc_fn_names}")
 
 cnt = 0
 runs = trange(args.n_runs, desc='acc: ')

### 2023-09-12 search.sh
update full version

@@ -4,73 +4,64 @@
 # DATASET=cifar100 # [cifar10, cifar100, ImageNet16-120]
 # DATA_LOC=./cifardata/ # [./cifardata/, ../ImageNet16/]
 
-# search_algo GA_rk SA_rk random
-# GA_rk spec: maxn_pop maxn_iter prob_mut prob_cr 
+# search_algo SA_rk random
 # SA_rk spec: end_T maxn_iter Rt init_T
-#python RD_search.py --save_string RD --sigma 1 --nasspace natsbenchsss --api_loc ../NATS-sss-v1_0-50262-simple/ --batch_size 128 --GPU 0 --n_samples 1000 --n_runs 50 --data_loc ./cifardata/ --dataset cifar100 --test
-#python RD_search.py --save_string RD --sigma 1 --nasspace natsbenchsss --api_loc ../NATS-sss-v1_0-50262-simple/ --batch_size 128 --GPU 0 --n_samples 1000 --n_runs 50 --data_loc ../ImageNet16/ --dataset ImageNet16-120 --test
 
 # ==================================================================================
 
 # natsbenchsss
-# GA
-# cifar10
-#python GA_search.py --maxn_pop 100 --maxn_iter 10 --prob_mut 0.08 --prob_cr 0.7 --save_string GA --augtype none --repeat 1 --sigma 1 --nasspace natsbenchsss --api_loc ../NATS-sss-v1_0-50262-simple/ --batch_size 128 --GPU 0 --n_samples 50 --n_runs 50 --data_loc ./cifardata/ --dataset cifar10 --test
-# cifar100
-#python GA_search.py --maxn_pop 100 --maxn_iter 10 --prob_mut 0.08 --prob_cr 0.7 --save_string GA --augtype none --repeat 1 --sigma 1 --nasspace natsbenchsss --api_loc ../NATS-sss-v1_0-50262-simple/ --batch_size 128 --GPU 0 --n_samples 50 --n_runs 50 --data_loc ./cifardata/ --dataset cifar100 --test
-# ImageNet16-120
[…]

### 2023-09-12 paper/manuscript.tex

@@
         %SA-NI                  &      & $90.24 \pm 0.10$ & $93.20 \pm 0.19$ & $69.83 \pm 0.56$ & $70.10 \pm 0.40$  & $45.49 \pm 0.50$ & $45.98 \pm 0.89$
+        %SA-NASWOT              &      & $90.21 \pm 0.30$ & $93.16 \pm 0.28$ & $69.16 \pm 1.28$ & $69.27 \pm 1.46$  & $44.89 \pm 1.27$ & $45.49 \pm 1.33$
         Optimal             &          & $90.71$          & $93.65$          & $70.92$          & $71.34$           & $46.73$          & $47.40$          \\ \bottomrule
@@
     Therefore, the highest rank (numerically lowest) in $r$ is the best 
-    network architecture. 
+    network architecture. In practical implementation, to reduce the 
+    evaluation time of training-free score functions, the scores of 
+    architecture can be stored and used in the future. 
     %The first step is to evaluate the network architectures in the subset, 
@@
         \palg{} (ours)          & $902$  & $90.20 \pm \z{0.24}$ & $93.53 \pm 0.22$ & $70.51 \pm 0.71$ & $70.63 \pm 0.66$ & $43.80 \pm 1.86$ & $44.63 \pm 1.64$ \\ \midrule
-        %SA-NI                  &        & $90.06 \pm 0.29$     & $93.38 \pm 0.50$ & $70.41 \pm 0.74$ & $70.34 \pm 1.34$ & $42.69 \pm 1.87$ & $43.22 \pm 1.93$
+        %SA-NI                  &        & $90.06 \pm \z{0.29}$ & $93.38 \pm 0.50$ & $70.41 \pm 0.74$ & $70.34 \pm 1.34$ & $42.69 \pm 1.87$ & $43.22 \pm 1.93$
+        %SA-NASWOT              &        & $89.11 \pm \z{1.22}$ & $92.22 \pm 1.32$ & $69.38 \pm 1.23$ & $69.48 \pm 1.46$ & $41.77 \pm 3.96$ & 
         Optimal             &          & $91.61$              & $94.37$          & $73.49$          & $73.51$          & $46.73$          & $47.31$          \\ \bottomrule
@@
     to 1, 0.0008, 0.745, 4, 0.25, 10, 1, so that the maximum number of searching candidates is 1000. 
+    Notbly, in NAS-Bench-101 search space, we conduct experiments with an evaluation budget of 5000 for RS, 
+    since NAS-Bench-101 contains much more architectures.
 
@@
     The proposed NAS algorithm and ranking function is compared with the other five non-weight sharing 
-    algorithm and three training-free score functions with random search (RS), i.e., RS-NI, RS-NASWOT, 
+    algorithm and three training-free score functions with RS, i.e., RS-NI, RS-NASWOT, 
     and RS-LogSynFlow. For fairness, the searching architectures for the RS with training-free 
@@
     the best performance, while the computation time is the highest. AREA and REA performs similarly. 
-    In CIFAR10 validation dataset, the accuracy of RS-NI is better than RS-rank, but the standard 
-    deviation is worse than RS-rank. And RS-NASWOT though is higher than RS-LogSynFlow, RS-NASWOT 
-    is the most unstable. \palg{} has better accuracy and stability than all the other training-free 
-    score functions. In CIFAR10 test dataset, RS-NI has higher accuracy than RS-rank, however, the 
-    stability of RS-NI is much worse than RS-rank. The accuracy and stability of \palg{} is the best 
-    among the training-free methods. Compared with \palg{} and the other NAS methods, though the 
-    performance and stability are a little bit worse than AREA, REA and ENAS, the time cost of \palg{} is 
-    much less than them.
+    Both have higher accuracy than most of others. 
+    In CIFAR10 validation dataset, with $1000$ sampled architectures ($N=1000$), the accuracy of 
+    RS-NI is better than RS-rank, but the standard deviation is worse than RS-rank. And RS-NASWOT 
+    though is higher than RS-LogSynFlow, RS-NASWOT is the most unstable. With $5000$ sampled architectures 
+    ($N=5000$), RS-rank outperforms RS-NI instead and becomes the best method. RS-NASWOT and RS-LogSynFlow
+    performs similarly, but RS-NASWOT is more unstable. Lastly, \palg{} has better accuracy 
+    and stability than all the other training-free score functions. In CIFAR10 test dataset, with $1000$ 
+    sampled architectures ($N=1000$), RS-NI has higher accuracy than RS-rank, however, the stability of 
+    RS-NI is much worse than RS-rank. The accuracy and stability of \palg{} is the best among the 
+    training-free methods. With $5000$ sampled architectures ($N=5000$), RS-NI performs better than 
+    RS-rank but has much lower stability. RS-LogSynFlow performs better than RS-NASWOT which not only 
+    has low accuracy but also low stability. \palg{} is still best among these training-free score 
+    functions. Compared with \palg{} and the other NAS methods, though the performance and stability 
+    are a little bit worse than AREA, REA and ENAS, the time cost of \palg{} is much less than them.
 
@@
                                 &            & \textbf{Training-free}      &       \\
-            RS-NI (N=1,000)         & $280$  & $92.89 \pm 2.10$ & $92.55 \pm 1.33$ \\ 
-            RS-NASWOT (N=1,000)     & $162$  & $92.27 \pm 6.60$ & $92.10 \pm 4.44$ \\ 
-            RS-LogSynFlow (N=1,000) & $105$  & $91.81 \pm 1.52$ & $91.21 \pm 1.71$ \\ 
-            RS-rank (ours) (N=1000) & $516$  & $92.44 \pm 1.42$ & $91.94 \pm 2.01$ \\
-            %RS-NI (N=5,000)         & $280$  & $92.89 \pm 2.10$ & $92.35 \pm 2.69$ \\ 
-            %RS-NASWOT (N=5,000)     & $162$  & $92.27 \pm 6.60$ & $90.60 \pm 6.64$ \\ 
-            %RS-LogSynFlow (N=5,000) & $105$  & $91.81 \pm 1.52$ & $91.17 \pm 1.86$ \\ 
-            %RS-rank (ours) (N=5,000) & $516$  & $92.44 \pm 1.42$ & $92.32 \pm 1.47$ \\ 
+            RS-NI (N=1,000)         & $476$  & $92.89 \pm 2.10$ & $92.55 \pm 1.33$ \\ 
+            RS-NASWOT (N=1,000)     & $127$  & $92.27 \pm 6.60$ & $92.10 \pm 4.44$ \\ 
+            RS-LogSynFlow (N=1,000) & $76$   & $91.81 \pm 1.52$ & $91.21 \pm 1.71$ \\ 
+            RS-rank (ours) (N=1000) & $679$  & $92.44 \pm 1.42$ & $91.94 \pm 2.01$ \\
+            RS-NI (N=5,000)         & $2390$ & $92.84 \pm 1.55$ & $92.35 \pm 2.69$ \\ 
+            RS-NASWOT (N=5,000)     & $635$  & $91.67 \pm 4.99$ & $90.60 \pm 6.64$ \\ 
+            RS-LogSynFlow (N=5,000) & $408$  & $91.66 \pm 1.72$ & $91.17 \pm 1.86$ \\ 
+            RS-rank (ours) (N=5,000)& $3434$  & $92.87 \pm 0.97$ & $92.32 \pm 1.47$ \\ 
             \palg{} (ours)          & $595$  & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \midrule
             %SA-NI                  &        & $92.38 \pm 3.50$ & $92.71 \pm 1.97$
+            %SA-NASWOT
             Optimal             &            & $95.12$          & $94.32$          \\ \bottomrule

### 2023-09-15 paper/manuscript.tex
update paper

@@
     evaluate an architecture, the score function should take the different 
-    aspects of an neural architecture into account. 
+    aspects of a neural architecture into account. 
     To achieve the goal, we propose a rank-based training-free NAS algorithm, 
@@
                             &          &                  &                  & \textbf{Training-free} &             &                  &                  \\
-        RS-NI (N=1,000)         & $293$& $89.55 \pm 0.16$ & $92.56 \pm 0.21$ & $67.67 \pm 0.91$ & $67.61 \pm 1.06$  & $43.19 \pm 0.73$ & $43.22 \pm 0.53$ \\ 
-        RS-NASWOT (N=1,000)     & $208$& $89.25 \pm 0.44$ & $92.21 \pm 0.31$ & $65.09 \pm 2.89$ & $64.61 \pm 3.16$  & $41.29 \pm 2.32$ & $41.35 \pm 2.31$ \\ 
-        RS-LogSynFlow (N=1,000) & $123$& $89.60 \pm 0.11$ & $92.61 \pm 0.18$ & $68.23 \pm 0.49$ & $68.30 \pm 0.54$  & $43.58 \pm 0.58$ & $43.48 \pm 0.40$ \\ 
-        RS-rank (ours) (N=1000) & $612$& $89.59 \pm 0.14$ & $92.51 \pm 0.17$ & $67.56 \pm 0.75$ & $67.55 \pm 0.82$  & $43.36 \pm 0.62$ & $43.27 \pm 0.45$ \\ 
+        RS-NI (N=1,000)         & $265$& $89.55 \pm 0.16$ & $92.56 \pm 0.21$ & $67.67 \pm 0.91$ & $67.61 \pm 1.06$  & $43.19 \pm 0.73$ & $43.22 \pm 0.53$ \\ 
+        RS-NASWOT (N=1,000)     & $187$& $89.25 \pm 0.44$ & $92.21 \pm 0.31$ & $65.09 \pm 2.89$ & $64.61 \pm 3.16$  & $41.29 \pm 2.32$ & $41.35 \pm 2.31$ \\ 
+        RS-LogSynFlow (N=1,000) & $127$& $89.60 \pm 0.11$ & $92.61 \pm 0.18$ & $68.23 \pm 0.49$ & $68.30 \pm 0.54$  & $43.58 \pm 0.58$ & $43.48 \pm 0.40$ \\ 
+        RS-rank (ours) (N=1000) & $567$& $89.59 \pm 0.14$ & $92.51 \pm 0.17$ & $67.56 \pm 0.75$ & $67.55 \pm 0.82$  & $43.36 \pm 0.62$ & $43.27 \pm 0.45$ \\ 
+        %SA-NI                   & $214$& $90.24 \pm 0.10$ & $93.20 \pm 0.19$ & $69.83 \pm 0.56$ & $70.10 \pm 0.40$  & $45.49 \pm 0.50$ & $45.98 \pm 0.89$ \\
+        %SA-NASWOT               & $242$& $90.21 \pm 0.30$ & $93.16 \pm 0.28$ & $69.16 \pm 1.28$ & $69.27 \pm 1.46$  & $44.89 \pm 1.27$ & $45.49 \pm 1.33$ \\
+        %SA-LogSynFlow           & $176$& $90.71 \pm 0.00$ & $93.40 \pm 0.00$ & $70.30 \pm 0.04$ & $70.72 \pm 0.00$  & $44.73 \pm 0.00$ & $47.17 \pm 0.00$ \\
         \palg{} (ours)          & $725$& $90.33 \pm 0.15$ & $93.26 \pm 0.24$ & $69.89 \pm 0.48$ & $70.24 \pm 0.42$  & $45.41 \pm 0.41$ & $46.43 \pm 0.75$ \\ \midrule
-        %SA-NI                  &      & $90.24 \pm 0.10$ & $93.20 \pm 0.19$ & $69.83 \pm 0.56$ & $70.10 \pm 0.40$  & $45.49 \pm 0.50$ & $45.98 \pm 0.89$
-        %SA-NASWOT              &      & $90.21 \pm 0.30$ & $93.16 \pm 0.28$ & $69.16 \pm 1.28$ & $69.27 \pm 1.46$  & $44.89 \pm 1.27$ & $45.49 \pm 1.33$
         Optimal             &          & $90.71$          & $93.65$          & $70.92$          & $71.34$           & $46.73$          & $47.40$          \\ \bottomrule
@@
 
-    \begin{table*}[htb]
-        %\normalsize
-        %\centering
-        \newcommand{\z}{\phantom{0}}
-        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-TSS.}}
-        \vspace{-\baselineskip}
-        \begin{tabular}{@{}lrcccccc@{}}\toprule
-        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
-                            &          & validation           & test             & validation           & test             & validation       & test \\ \midrule
-                            &          &                      &                  & \textbf{Non-weight sharing} &           &                  &                  \\
-        AREA                & $12,000$ & $91.18 \pm \z{0.43}$ & $93.95 \pm 0.39$ & $71.84 \pm 1.21$ & $71.92 \pm 1.29$ & $45.04 \pm 1.03$ & $45.40 \pm 1.14$ \\
-        REA                 & $12,000$ & $91.25 \pm \z{0.31}$ & $94.02 \pm 0.31$ & $72.28 \pm 0.95$ & $72.23 \pm 0.84$ & $45.71 \pm 0.77$ & $45.77 \pm 0.80$ \\
-        RS                  & $12,000$ & $91.07 \pm \z{0.26}$ & $93.86 \pm 0.23$ & $71.46 \pm 0.97$ & $71.55 \pm 0.97$ & $45.03 \pm 0.91$ & $45.28 \pm 0.97$ \\
-        RL                  & $12,000$ & $91.12 \pm \z{0.25}$ & $93.90 \pm 0.26$ & $71.80 \pm 0.94$ & $71.86 \pm 0.89$ & $45.37 \pm 0.74$ & $45.64 \pm 0.78$ \\
-        BOHB                & $12,000$ & $91.17 \pm \z{0.27}$ & $93.94 \pm 0.28$ & $72.04 \pm 0.93$ & $72.00 \pm 0.86$ & $45.55 \pm 0.79$ & $45.70 \pm 0.86$ \\ \midrule
-                            &          &                      &                  & \textbf{Weight sharing} &               &                  &                  \\
-        RSWS                & $4,154$  & $87.60 \pm \z{0.61}$ & $91.05 \pm 0.66$ & $68.27 \pm 0.72$ & $68.26 \pm 0.96$ & $39.73 \pm 0.34$ & $40.69 \pm 0.36$ \\
-        DARTS-V1            & $5,475$  & $49.27 \pm 13.44$    & $59.84 \pm 7.84$ & $61.08 \pm 4.37$ & $61.26 \pm 4.43$ & $38.07 \pm 2.90$ & $37.88 \pm 2.91$ \\
-        DARTS-V2            & $16,114$ & $58.78 \pm 13.44$    & $65.38 \pm 7.84$ & $59.48 \pm 5.13$ & $60.49 \pm 4.95$ & $37.56 \pm 7.10$ & $36.79 \pm 7.59$ \\
-        GDAS                & $11,183$ & $89.68 \pm \z{0.72}$ & $93.23 \pm 0.13$ & $68.35 \pm 2.71$ & $68.17 \pm 2.50$ & $39.55 \pm 0.00$ & $39.40 \pm 0.00$ \\
-        SETN                & $16,787$ & $90.00 \pm \z{0.97}$ & $92.72 \pm 4.52$ & $69.19 \pm 1.42$ & $69.36 \pm 1.72$ & $39.77 \pm 0.33$ & $39.51 \pm 0.33$ \\
-        ENAS                & $7,061$  & $90.20 \pm \z{0.00}$ & $93.76 \pm 0.00$ & $70.21 \pm 0.71$ & $70.67 \pm 0.62$ & $40.78 \pm 0.00$ & $41.44 \pm 0.00$ \\ \midrule
-                            &          &                      &                  & \textbf{Training-free} &                &                  &                  \\
-        RS-NI (N=1,000)         & $592$  & $90.03 \pm \z{0.30}$ & $93.21 \pm 0.63$ & $70.27 \pm 0.70$ & $70.40 \pm 0.84$ & $42.92 \pm 2.18$ & $43.34 \pm 2.43$ \\ 
-        RS-NASWOT (N=1,000)     & $201$  & $89.63 \pm \z{0.94}$ & $92.80 \pm 1.07$ & $69.76 \pm 1.25$ & $69.66 \pm 1.23$ & $43.51 \pm 2.90$ & $43.84 \pm 2.93$ \\ 
-        RS-LogSynFlow (N=1,000) & $90$   & $89.67 \pm \z{0.89}$ & $92.92 \pm 0.70$ & $69.19 \pm 1.86$ & $68.98 \pm 1.97$ & $39.93 \pm 6.34$ & $40.23 \pm 6.45$ \\ 
-        RS-rank (ours) (N=1000) & $887$  & $90.07 \pm \z{0.41}$ & $93.32 \pm 0.42$ & $70.06 \pm 1.34$ & $70.10 \pm 1.45$ & $43.68 \pm 2.11$ & $44.07 \pm 2.19$ \\ 
-        TE-NAS                  & $459$  & $90.02 \pm \z{0.56}$ & $93.31 \pm 0.45$ & $70.12 \pm 1.04$ & $70.26 \pm 1.07$ & $43.15 \pm 2.23$ & $43.49 \pm 2.26$ \\
-        \palg{} (ours)          & $902$  & $90.20 \pm \z{0.24}$ & $93.53 \pm 0.22$ & $70.51 \pm 0.71$ & $70.63 \pm 0.66$ & $43.80 \pm 1.86$ & $44.63 \pm 1.64$ \\ \midrule
-        %SA-NI                  &        & $90.06 \pm \z{0.29}$ & $93.38 \pm 0.50$ & $70.41 \pm 0.74$ & $70.34 \pm 1.34$ & $42.69 \pm 1.87$ & $43.22 \pm 1.93$
-        %SA-NASWOT              &        & $89.11 \pm \z{1.22}$ & $92.22 \pm 1.32$ & $69.38 \pm 1.23$ & $69.48 \pm 1.46$ & $41.77 \pm 3.96$ & 
-        Optimal             &          & $91.61$              & $94.37$          & $73.49$          & $73.51$          & $46.73$          & $47.31$          \\ \bottomrule
-        \end{tabular}
-        \label{table:overall_201}
-        \vspace{-\baselineskip}
-    \end{table*}
-
     We evalute the performance of the proposed algorithm, \palg{}, 
@@
     The proposed NAS algorithm and ranking function is compared with the other five non-weight sharing 
-    algorithm and three training-free score functions with RS, i.e., RS-NI, RS-NASWOT, 
-    and RS-LogSynFlow. For fairness, the searching architectures for the RS with training-free 
+    algorithm and three training-free score functions with RS, i.e., RS-NI, RS-NASWOT, and 
+    RS-LogSynFlow. For fairness, the searching architectures for the RS with training-free 
     score functions are identical. Among the four training-free score functions with RS, RS-LogSynFlow 
@@
     In ImageNet16, RS-LogSynFlow still has the highest accuracy and stability, then is RS-rank, RS-NI, 
-    RS-NASWOT. However, \palg{} improves the results significantly and outperforms almost all the 
+    RS-NASWOT. 
+    However, \palg{} improves the results significantly and outperforms almost all the 
     compared algorithms, including AREA, REA, and RL. It can be seen that, search algorithms guides 
@@
 
+    \begin{table*}[htb]
+        %\normalsize
+        %\centering
+        \newcommand{\z}{\phantom{0}}
+        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NATS-Bench-TSS.}}
+        \vspace{-\baselineskip}
+        \begin{tabular}{@{}lrcccccc@{}}\toprule
+        Method & Search (s) & \multicolumn{2}{c}{CIFAR-10} & \multicolumn{2}{c}{CIFAR-100} & \multicolumn{2}{c}{ImageNet-16-120} \\ \cmidrule(lr){3-4}\cmidrule(lr){5-6}\cmidrule(lr){7-8}
+                            &          & validation           & test             & validation           & test             & validation       & test \\ \midrule
+                            &          &                      &                  & \textbf{Non-weight sharing} &           &                  &                  \\
+        AREA                & $12,000$ & $91.18 \pm \z{0.43}$ & $93.95 \pm 0.39$ & $71.84 \pm 1.21$ & $71.92 \pm 1.29$ & $45.04 \pm 1.03$ & $45.40 \pm 1.14$ \\
+        REA                 & $12,000$ & $91.25 \pm \z{0.31}$ & $94.02 \pm 0.31$ & $72.28 \pm 0.95$ & $72.23 \pm 0.84$ & $45.71 \pm 0.77$ & $45.77 \pm 0.80$ \\
+        RS                  & $12,000$ & $91.07 \pm \z{0.26}$ & $93.86 \pm 0.23$ & $71.46 \pm 0.97$ & $71.55 \pm 0.97$ & $45.03 \pm 0.91$ & $45.28 \pm 0.97$ \\
+        RL                  & $12,000$ & $91.12 \pm \z{0.25}$ & $93.90 \pm 0.26$ & $71.80 \pm 0.94$ & $71.86 \pm 0.89$ & $45.37 \pm 0.74$ & $45.64 \pm 0.78$ \\
+        BOHB                & $12,000$ & $91.17 \pm \z{0.27}$ & $93.94 \pm 0.28$ & $72.04 \pm 0.93$ & $72.00 \pm 0.86$ & $45.55 \pm 0.79$ & $45.70 \pm 0.86$ \\ \midrule
+                            &          &                      &                  & \textbf{Weight sharing} &               &                  &                  \\
+        RSWS                & $4,154$  & $87.60 \pm \z{0.61}$ & $91.05 \pm 0.66$ & $68.27 \pm 0.72$ & $68.26 \pm 0.96$ & $39.73 \pm 0.34$ & $40.69 \pm 0.36$ \\
+        DARTS-V1            & $5,475$  & $49.27 \pm 13.44$    & $59.84 \pm 7.84$ & $61.08 \pm 4.37$ & $61.26 \pm 4.43$ & $38.07 \pm 2.90$ & $37.88 \pm 2.91$ \\
+        DARTS-V2            & $16,114$ & $58.78 \pm 13.44$    & $65.38 \pm 7.84$ & $59.48 \pm 5.13$ & $60.49 \pm 4.95$ & $37.56 \pm 7.10$ & $36.79 \pm 7.59$ \\
+        GDAS                & $11,183$ & $89.68 \pm \z{0.72}$ & $93.23 \pm 0.13$ & $68.35 \pm 2.71$ & $68.17 \pm 2.50$ & $39.55 \pm 0.00$ & $39.40 \pm 0.00$ \\
+        SETN                & $16,787$ & $90.00 \pm \z{0.97}$ & $92.72 \pm 4.52$ & $69.19 \pm 1.42$ & $69.36 \pm 1.72$ & $39.77 \pm 0.33$ & $39.51 \pm 0.33$ \\
+        ENAS                & $7,061$  & $90.20 \pm \z{0.00}$ & $93.76 \pm 0.00$ & $70.21 \pm 0.71$ & $70.67 \pm 0.62$ & $40.78 \pm 0.00$ & $41.44 \pm 0.00$ \\ \midrule
+                            &          &                      &                  & \textbf{Training-free} &                &                  &                  \\
+        RS-NI (N=1,000)         & $352$  & $90.03 \pm \z{0.30}$ & $93.21 \pm 0.63$ & $70.27 \pm 0.70$ & $70.40 \pm 0.84$ & $42.92 \pm 2.18$ & $43.34 \pm 2.43$ \\ 
+        RS-NASWOT (N=1,000)     & $241$  & $89.63 \pm \z{0.94}$ & $92.80 \pm 1.07$ & $69.76 \pm 1.25$ & $69.66 \pm 1.23$ & $43.51 \pm 2.90$ & $43.84 \pm 2.93$ \\ 
+        RS-LogSynFlow (N=1,000) & $155$  & $89.67 \pm \z{0.89}$ & $92.92 \pm 0.70$ & $69.19 \pm 1.86$ & $68.98 \pm 1.97$ & $39.93 \pm 6.34$ & $40.23 \pm 6.45$ \\ 
+        RS-rank (ours) (N=1000) & $747$  & $90.07 \pm \z{0.41}$ & $93.32 \pm 0.42$ & $70.06 \pm 1.34$ & $70.10 \pm 1.45$ & $43.68 \pm 2.11$ & $44.07 \pm 2.19$ \\ 
+        TE-NAS                  & $459$  & $90.02 \pm \z{0.56}$ & $93.31 \pm 0.45$ & $70.12 \pm 1.04$ & $70.26 \pm 1.07$ & $43.15 \pm 2.23$ & $43.49 \pm 2.26$ \\
+        %SA-NI                   & $319$  & $90.06 \pm \z{0.29}$ & $93.38 \pm 0.50$ & $70.41 \pm 0.74$ & $70.34 \pm 1.34$ & $42.69 \pm 1.87$ & $43.22 \pm 1.93$ \\
+        %SA-NASWOT               & $273$  & $89.11 \pm \z{1.22}$ & $92.22 \pm 1.32$ & $69.38 \pm 1.23$ & $69.48 \pm 1.46$ & $41.77 \pm 3.96$ & $42.13 \pm 4.11$ \\
+        %SA-LogSynFlow           & $213$  & $89.57 \pm \z{1.14}$ & $93.00 \pm 0.81$ & $69.30 \pm 1.86$ & $69.57 \pm 1.41$ & $40.42 \pm 4.61$ & $40.79 \pm 4.77$ \\
+        \palg{} (ours)          & $902$  & $90.20 \pm \z{0.24}$ & $93.53 \pm 0.22$ & $70.51 \pm 0.71$ & $70.63 \pm 0.66$ & $43.80 \pm 1.86$ & $44.63 \pm 1.64$ \\ \midrule
+        Optimal                 &        & $91.61$              & $94.37$          & $73.49$          & $73.51$          & $46.73$          & $47.31$          \\ \bottomrule
+        \end{tabular}
+        \label{table:overall_201}
+        \vspace{-\baselineskip}
+    \end{table*}
     % tss
@@
     lower than all the training-free methods.
+
+    \begin{table}[t]
+        %\normalsize
+        %\centering
+        \newcommand{\z}{\phantom{0}}
+        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-101.}}
+        \vspace{-\baselineskip}
+        \resizebox{0.5 \textwidth}{!}{
+        \begin{tabular}{@{}lrcc@{}}\toprule
+            Method              & Search (s) & \multicolumn{2}{c}{CIFAR-10}        \\ \cmidrule(lr){3-4}
+                                &            & validation       & test             \\ \midrule
+                                &            & \textbf{Non-weight sharing} &       \\
+            AREA                & $12,000$   & $93.67 \pm 0.48$ & $93.02 \pm 0.48$ \\
+            REA                 & $12,000$   & $93.63 \pm 0.50$ & $93.02 \pm 0.52$ \\ \midrule
+                                &            & \textbf{Weight sharing}     &       \\
+            DARTS-V1            & $20,483$   & $83.50 \pm 0.11$ & $83.74 \pm 0.03$ \\
+            ENAS                & $22,325$   & $93.83 \pm 0.28$ & $93.34 \pm 0.26$ \\ \midrule
+                                &            & \textbf{Training-free}      &       \\
+            RS-NI (N=1,000)         & $256$  & $92.84 \pm 2.43$ & $92.74 \pm 0.90$ \\ 
+            RS-NASWOT (N=1,000)     & $137$  & $92.76 \pm 2.85$ & $91.84 \pm 3.68$ \\ 
+            RS-LogSynFlow (N=1,000) & $93$   & $91.62 \pm 1.68$ & $91.42 \pm 1.82$ \\ 
+            RS-rank (ours) (N=1000) & $485$  & $92.65 \pm 1.44$ & $92.25 \pm 1.31$ \\
+
+            RS-NI (N=5,000)         & $2390$ & $92.84 \pm 1.55$ & $92.35 \pm 2.69$ \\ 
+            RS-NASWOT (N=5,000)     & $635$  & $91.67 \pm 4.99$ & $90.60 \pm 6.64$ \\ 
+            RS-LogSynFlow (N=5,000) & $408$  & $91.66 \pm 1.72$ & $91.17 \pm 1.86$ \\ 
+            RS-rank (ours) (N=5,000)& $3434$ & $92.87 \pm 0.97$ & $92.32 \pm 1.47$ \\ 
+            %SA-NI                   & $244$  & $92.38 \pm 3.50$ & $92.71 \pm 1.97$ \\
+            %SA-NASWOT               & $136$  & $92.72 \pm 4.35$ & $91.95 \pm 3.62$ \\
+            %SA-LogSynFlow           & $102$  & $92.21 \pm 1.50$ & $91.48 \pm 1.67$ \\
+            \palg{} (ours)          & $595$  & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \midrule
+
+            Optimal             &            & $95.12$          & $94.32$          \\ \bottomrule
+            \end{tabular}
+        }
+        \label{table:overall_101}
+        \vspace{-\baselineskip}
+    \end{table}
 
@@
 
-    \begin{table}[t]
-        %\normalsize
-        %\centering
-        \newcommand{\z}{\phantom{0}}
-        \caption{\textsc{Comparison of rank-based NAS and all the other NAS algorithms in NAS-Bench-101.}}
-        \vspace{-\baselineskip}
-        \resizebox{0.5 \textwidth}{!}{
-        \begin{tabular}{@{}lrcc@{}}\toprule
-            Method              & Search (s) & \multicolumn{2}{c}{CIFAR-10}        \\ \cmidrule(lr){3-4}
-                                &            & validation       & test             \\ \midrule
-                                &            & \textbf{Non-weight sharing} &       \\
-            AREA                & $12,000$   & $93.67 \pm 0.48$ & $93.02 \pm 0.48$ \\
-            REA                 & $12,000$   & $93.63 \pm 0.50$ & $93.02 \pm 0.52$ \\ \midrule
-                                &            & \textbf{Weight sharing}     &       \\
-            DARTS-V1            & $20,483$   & $83.50 \pm 0.11$ & $83.74 \pm 0.03$ \\
-            ENAS                & $22,325$   & $93.83 \pm 0.28$ & $93.34 \pm 0.26$ \\ \midrule
-                                &            & \textbf{Training-free}      &       \\
-            RS-NI (N=1,000)         & $476$  & $92.89 \pm 2.10$ & $92.55 \pm 1.33$ \\ 
-            RS-NASWOT (N=1,000)     & $127$  & $92.27 \pm 6.60$ & $92.10 \pm 4.44$ \\ 
-            RS-LogSynFlow (N=1,000) & $76$   & $91.81 \pm 1.52$ & $91.21 \pm 1.71$ \\ 
-            RS-rank (ours) (N=1000) & $679$  & $92.44 \pm 1.42$ & $91.94 \pm 2.01$ \\
-            RS-NI (N=5,000)         & $2390$ & $92.84 \pm 1.55$ & $92.35 \pm 2.69$ \\ 
-            RS-NASWOT (N=5,000)     & $635$  & $91.67 \pm 4.99$ & $90.60 \pm 6.64$ \\ 
-            RS-LogSynFlow (N=5,000) & $408$  & $91.66 \pm 1.72$ & $91.17 \pm 1.86$ \\ 
-            RS-rank (ours) (N=5,000)& $3434$  & $92.87 \pm 0.97$ & $92.32 \pm 1.47$ \\ 
-            \palg{} (ours)          & $595$  & $93.16 \pm 0.97$ & $92.77 \pm 1.03$ \\ \midrule
-            %SA-NI                  &        & $92.38 \pm 3.50$ & $92.71 \pm 1.97$
-            %SA-NASWOT
-            Optimal             &            & $95.12$          & $94.32$          \\ \bottomrule
-            \end{tabular}
-        }
-        \label{table:overall_101}
-        \vspace{-\baselineskip}
-    \end{table}
-
     \section{Conclusion}

### 2023-11-19 paper/manuscript.tex
revise

@@
     However, every architecture has unique characteristics. To accurately 
-    evaluate an architecture, the score function should take the different 
-    aspects of a neural architecture into account. 
+    assess an architecture, the score function should consider the different 
+    aspects of a neural architecture. 
     To achieve the goal, we propose a rank-based training-free NAS algorithm, 
@@
     score functions. The ultimate results show that \palg{} outperforms most 
-    training-free score functions and shows the robustness between different 
+    training-free score functions, showing the robustness between different 
     search spaces.
@@
 % introduction
-    Neural architecture search (NAS) has recently drawn a big amount of 
-    attention, since the ability to automatically design a ``good'' neural 
-    architecture. By leveraging machine learning algorithms 
+    Neural architecture search (NAS) has recently drawn significant attention 
+    to the ability to automatically design a ``good'' neural architecture. 
+    By leveraging machine learning algorithms 
     \cite{https://doi.org/10.48550/arxiv.1611.01578}, NAS algorithms can 
-    automatically search numerous architectures to find out the ones 
-    that outperform those designed by human experts. Recently, the use of NAS has been widespread, 
+    automatically search numerous architectures to find the ones 
+    that outperform those created by human experts. The use of NAS has recently been widespread, 
     from object detection \cite{https://doi.org/10.48550/arxiv.2111.13336}, 
-    image recognition \cite{https://doi.org/10.48550/arxiv.2006.04647} 
+    image recognition \cite{https://doi.org/10.48550/arxiv.2006.04647},  
     and speech recognition \cite{https://doi.org/10.48550/arxiv.2011.05649} 
@@
     to deal with. One major problem is the extremely high computational 
-    cost for searching an optimal architecture, which makes NAS 
-    impractical for real-world applications, particularly on resource-constrained 
-    platforms like embedded system. NAS is costly because 
+    cost of searching for an optimal architecture. The problem makes NAS 
+    impractical for real-world applications, particularly resource-constrained 
+    platforms like embedded systems. NAS is costly because, 
     during searching, a candidate architecture must be trained to 
-    evaluate how good of this architecture. %% compare architectures each of which must be trained
+    evaluate how good this architecture is.
 
-    To eliminate the training cost, recent works proposed lots of methods 
-    which is so called training-free NAS. 
+    Recent works have proposed many methods to eliminate the training cost, 
+    named training-free NAS. 
     % NASWOT
     For example, Mellor et al. \cite{https://doi.org/10.48550/arxiv.2006.04647} 
-    proposed the measurement of the correlation between the binary 
-    activation paterns, induced by the untrained network at two inputs, 
-    abbreviated as NASWOT. 
+    proposed measuring the correlation between the binary 
+    activation patterns induced by the untrained network at two inputs, 
+    abbreviated NASWOT. 
     % synflow
-	Another example can be found in \cite{tanaka2020pruning}, Tanaka et al. 
-    presented pruning a network by using Iterative Synaptic Flow Pruning 
-    (SynFlow) algorithm which intends to deal with the layer collapse 
+	Another example can be found in \cite{tanaka2020pruning}. Tanaka et al. 
+    presented pruning a network using Iterative Synaptic Flow Pruning 
+    (SynFlow) algorithm, intending to deal with the layer collapse 
     problem. The score function used in the algorithm is so-called 
@@
     \cite{abdelfattah2021zerocost} extended SynFlow to score a network 
-    architecture by summing synaptic saliency score over all parameters 
+    architecture by summing the synaptic saliency score over all parameters 
     in the model. The outcome score represents the trainability of an 
     architecture. Cavagnero et al. \cite{Cavagnero_2023} pointed out that 
-    SynFlow is likely to suffer from gradient explosion, then proposed 
-    the LogSynFlow score function which prevents the problem. 
+    SynFlow is likely to suffer from gradient explosion and proposed 
+    the LogSynFlow score function, which prevents the problem. 
     % NTK
@@
 % what is unknown?
-    Although the training-free score functions are capable of reducing the 
+    Although the training-free score functions can reduce the 
     computational cost, \xtab{table:corr_score} shows most score functions suffer %
     from the low correlation between score values and the final accuracy of 
-    architectures. The shortcoming leads to a predicament that no matter 
-    how good the searching algorithm is, the optimal architectures are still 
-    buried in dirt. %
+    architectures. The shortcoming leads to a predicament: no matter 
+    how good the search algorithm is, the optimal architectures are still 
+    buried in the dirt. %
     The major problem that causes the low correlation is that a single score 
@@
     \begin{table}[tb]
-        \caption{\textsc{The Kendall correlation between training-free score and test accuracy, evaluated on the three datasets of NATS-Bench-TSS \cite{Dong_2021}. }}
+        \caption{\textsc{The Kendall correlation between the training-free score functions and test accuracy, evaluated on the three datasets of NATS-Bench-TSS \cite{Dong_2021}. }}
         \resizebox{0.45\textwidth}{!}{
@@
                 \bf{NI}                      & 0.57     & 0.59      & 0.55  \\
-                \bf{Rank (ours)}             & -0.69    & -0.70     & -0.67 \\ \bottomrule
+                \bf{Rank (ours)}             & \bf{-0.69}    & \bf{-0.70}     & \bf{-0.67} \\ \bottomrule
                 \label{table:corr_score}
@@
 % method
-    To address the problem, we propose cooperating three heterogeneous 
-    score functions by ranking, which allows every score function 
-    evaluates an architecture without losing fairness. 
-    %The first score function is noise immunity (NI) \cite{10092788}, as 
-    %a measurement of the ability of image generalization. 
-    %The second one is NASWOT, used as a score to estimate the ability of distinction 
-    %of architecture and also a complement of NI. 
-    %The last one is LogSynFlow used as the measurement of trainability 
-    %and also as a complement to NI and NASWOT. 
-    And with these three score functions, the evaluation of an 
-    architecture is not simply from a single aspect but three different 
+    To address the problem, we propose combining three heterogeneous 
+    score functions by ranking, which allows every score function to 
+    evaluate an architecture without losing fairness. 
+    With these three score functions, the evaluation of 
+    architectures is not simply from a single aspect but three different 
     parts, which is like estimating the weight of an object by not only 
-    the length but its height and width.
+    the length but also its height and width.
 
@@
     % contribution
-    The major contribution of this paper can be summarized as follow:
+    The major contribution of this paper can be summarized as follows: 
     (1) A novel concept of ``complementary'' is presented and used as 
     a metric to choose score functions. 
-    (2) Cooperating the score functions by ranking algorithm, 
-    which prevents one score overwhelming others numerically. 
+    (2) Cooperating the score functions by ranking algorithm prevents 
+    one score overwhelming others numerically. 
     (3) Applying simulated annealing algorithm on the ranking algorithm 
-    to imporve the searching ability. 
+    to improve the searching ability. 
     (4) Improving simulated annealing algorithm by using a historical 
@@
     The remainder of this paper is organized as follows: 
-    \xsec{sec:related_work} provides the detail about the training-free 
+    \xsec{sec:related_work} details about the training-free 
     score functions. 
-    \xsec{sec:proposed} gives a detailed description about the proposed method. 
-    \xsec{sec:results} begins with parameters setting and provides the 
+    \xsec{sec:proposed} gives a detailed description of the proposed method. 
+    \xsec{sec:results} begins with the parameters setting and provides the 
     simulation results in different search spaces. 
-    The conclusion and further prospect are gived in \xsec{sec:conclusion}.
+    The conclusion and further prospects are given in \xsec{sec:conclusion}.
 
@@
     \subsection{Problem Definition}
-    In \cite{10092788}, the NAS is defined as following: 
+    In \cite{10092788}, the NAS is defined as follows: 
     first, assume that $D_{\text{train}}$ and $D_{\text{test}}$ are two subsets of input data $D$. 
-    Assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $\mathcal A_s$ the 
+    Assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the training-free score function, $\mathcal A_S$ the 
     search algorithm of NAS, and $\mathcal A_T$ the training function. Then, the NAS problem can be 
@@
     where $\mathbb N$ is a set of neural architectures, namely, the search space of NAS. 
-    For non-training-free NAS 
+    For non-training-free NAS, 
     \begin{equation}
@@
     \end{equation}
-    and for training-free NAS 
+    and for training-free NAS, 
     \begin{equation}
@@
     \end{equation}
-    Since the training function is replaced by training-free NAS algorithms, they need much less 
-    computational resource than non-training-free NAS algorithms. 
-    Training-free NAS is comprised of two part, training-free score function $\mathcal F_S$ and 
+    where $\mathbb N^s$ is the searching architectures generated by search algorithm. 
+    Since the training-free score function replaces the training function and the accuracy 
+    function, they need much less computational resources than non-training-free NAS algorithms. 
+    Training-free NAS is comprised of two parts: training-free score function $\mathcal F_S$ and 
     search algorithm $\mathcal A_S$.
@@
     mini-batch of data $X=\{x_i\}^N_{i=1}$ passing through a neural network 
-    architecture. The $j$-th activated ReLU units in every layer of the architecture 
-    form a binary code $c_{i,j}$ that define the linear region. The correlation 
+    architecture. The $j$-th activated ReLU units in every layer  
+    form a binary code $c_{i,j}$ that defines the linear region. The correlation 
     between binary codes for the whole mini-batch can be examined by computing 
@@
     \end{equation}
-    The rationale behind is that, the more different between the binary codes 
-    the better the architecture learns. And the determinant of the kernel matrix 
+    The rationale is that the more different between the binary codes 
+    the better the architecture learns. The determinant of the kernel matrix 
     measures how ``different'' they are by calculating the volume formed by the 
-    row vector of $K_H$.
+    row vectors of $K_H$.
 
@@
 
-    Wu et al. \cite{10092788} discovered in some cases, an architecture with a high %%
-    NASWOT score may classify the same kind of input data into different classes. 
-    \xfig{fig:ni} gives an example to illustrate how NI evaluates an architecture. 
+    Wu et al. \cite{10092788} discovered that in some cases, an architecture with a high %%
+    NASWOT score may classify the input data of the same kind into different classes. 
+    \xfig{fig:ni} gives an example of how NI evaluates an architecture. 
     The score function picks a mini-batch of data, denoted $X$, and then applies 
-    Gaussian noise to it. The process is defined by $X'=X+z$ where $z$ is the 
-    Gaussian noise. By passing $X$ and $X'$ through the untrained architecture, 
-    then computing the difference of square of each feature map captured at all 
-    pooling layers. Calculate the matrix $\kappa$ defined by 
+    Gaussian noise. The process is defined by $X'=X+z$ where $z$ is the 
+    Gaussian noise. $X$ and $X'$ will pass through the untrained architecture, 
+    and then the square of the difference of each feature map captured at all 
+    pooling layers is computed in the matrix, $\kappa$, which is defined by 
     \begin{equation}
@@
     the one perturbed by $X'$ at the $j$-th pooling layer and $i$-th input 
-    data of the mini-batch, respectively. 
-    Then $\eta$ can be calculated by 
+    data of the mini-batch, respectively. Then $\eta$ can be calculated by 
     \begin{equation}
@@
     % synflow
-    Besides image-related measurements, there is another characteristic to 
-    evaluate a network, trainability. 
-    %%\textit{The Lottery Ticket Hypothesis} \cite{frankle2019lottery} reveals that a 
-    %%network may have a 'core' which decides the final accuracy of the network. %%
-    %%How to prune a network correctly is thereby tempting. Lee et al. 
+    Besides image-related measurements, \textit{trainability} is another characteristic to 
+    evaluate a network. 
     \cite{lee2019snip} presented an algorithm that uses synaptic saliency score as a 
@@
     where $w_j$ the $j$-th element of the weight of the netwrok, and $\mathcal L$ is 
-    the empirical risk. The meaning behind is to approximate the contribution 
+    the empirical risk. The meaning is to approximate the contribution 
     to the change of the loss function from a specific connection. By pruning the 
-    connections that are relatively not contributive, the expensive prune, retrain 
-    cycles, can be prevented. 
+    connections that are relatively not contributive, the expensive pruning-retraining 
+    cycles can be prevented. 
     Later, Wang et al. \cite{wang2020picking} noticed that SNIP with a high pruning ratio 
@@
     \end{equation}
-    where $\mathcal R$ is a scalar loss function, and proposed Iterative Synaptic Flow Pruning (SynFlow) 
-    algorithm, an extension of magnitude pruning algorithm that avoids layer-collapse. 
-    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work, and presented to score a 
+    where $\mathcal R$ is a scalar loss function. Based on the generalized synaptic saliency scores, 
+    they proposed Iterative Synaptic Flow Pruning (SynFlow) algorithm, an extension of magnitude 
+    pruning algorithm that avoids layer-collapse. 
+    Abdelfattah et al. \cite{abdelfattah2021zerocost} extended the work and presented to score a 
     network by summing the synaptic saliency score over all parameters in the model, which is 
@@
     \end{equation}
-    The rationale behind is to calculate all the contributions to the loss function of parameters. 
+    The rationale is to calculate all the contributions to the loss function of parameters. 
     The higher the score of an architecture, the more trainable this architecture is. 
-    Finally, Cavagnero et al. \cite{Cavagnero_2023} improved SynFlow, which is likely to fall into 
-    gradient explosion problem, and proposed LogSynFlow which scales down the gradient. 
+    Finally, Cavagnero et al. \cite{Cavagnero_2023} improved SynFlow, likely to fall into 
+    gradient explosion, and proposed LogSynFlow, which scales down the gradient. 
     The formula is defined by 
@@
     \end{equation}
-    where $\lambda_0$ is the biggest eigenvalue and $\lambda_m$ is the smallest eigenvalue of the 
-    NTK. The rationale behind is the converge rate of the network is condition by the rate 
-    $\frac{\lambda_m}{\lambda_0}$. The higher the condition is, the faster the converge.
+    where $\lambda_0$ is the biggest eigenvalue, and $\lambda_m$ is the smallest eigenvalue of the 
+    NTK. The rationale is the converge rate of the network is conditioned by the rate 
+    $\frac{\lambda_m}{\lambda_0}$. The higher the condition is, the faster the convergence.
 
@@
             \end{tabular}
-            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NAS-Bench-201 in the CIFAR-10 dataset 
-            (b) NI score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset. 
-            (c) NI score + NASWOT score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset.}
+            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NATS-Bench-TSS in the CIFAR-10 dataset 
+            (b) NI score for 1,000 identical architectures from NATS-Bench-TSS in the CIFAR-10 dataset. 
+            (c) NI score + NASWOT score for 1,000 identical architectures from NATS-Bench-TSS in the CIFAR-10 dataset.}
             \label{fig:ninaswot}
@@
     %%
-    There are several search algorithms applied on NAS, including random search, reinforcement learning, and
-    metaheuristic algorithms. 
-    In \cite{https://doi.org/10.48550/arxiv.2006.04647} \cite{Lopes_2021}, random search is applied. 
-    The advantage of random search is simple and easy to implement, and the result can be taken as a 
-    baseline compared to more comprehensive search algorithms. Generally speaking, when applying random 
-    search on a small search space, e.g., NAS-Bench-201 \cite{dong2020nasbench201}, the performance is 
-    similar to other search algorithms. But when it comes to a relatively larger search space, e.g., NAS-Bench-101 
-    \cite{ying2019nasbench101} and NATS-Bench-SSS \cite{Dong_2021}, random search can no longer standout 
-    in other search algorithms.
+    Several search algorithms have been applied to NAS, including random search, reinforcement learning, 
+    and metaheuristic algorithms. 
+    In \cite{https://doi.org/10.48550/arxiv.2006.04647} \cite{Lopes_2021}, random search (RS) is applied. 
+    The advantage of RS is simple and easy to implement, and the result can be taken as a 
+    baseline compared to more comprehensive search algorithms. Generally speaking, the performance of RS 
+    is similar to other search algorithms when applying RS on a small search space, e.g., 
+    NATS-Bench-TSS \cite{Dong_2021}. However, RS can no longer stand out in other search algorithms     
+    when dealing with a relatively larger search space, e.g., NAS-Bench-101 \cite{ying2019nasbench101} 
+    and NATS-Bench-SSS \cite{Dong_2021}.
 
@@
 
-    As for an example of metaheuristic algorithm, in \cite{10.1145/3491396.3506510}, Wu et al. leveraged 
+    For an example of metaheuristic algorithms, in \cite{10.1145/3491396.3506510}, Wu et al. leveraged 
     genetic algorithm (GA) as a search strategy. 
@@
     Later in \cite{10092788}, Wu et al. used search economic (SE) \cite{7379579} as a search strategy. The 
-    basic idea of SEs is to first divide the search space into a set of subspaces and investigate those 
+    basic idea of SE is first to divide the search space into a set of subspaces and investigate those 
     subspaces based on the expected value of each subspace. The expected value is comprised of 
-    (1) The number of times the subspace has been investiagted. 
-    (2) The average objective value of the new candidate solutions in the subspace at current iteration. 
+    (1) The number of times the subspace has been investigated. 
+    (2) The average objective value of the new candidate solutions in the subspace at the current iteration. 
     (3) The best solution so far in this subspace. 
-    Based on these designs, SE avoids falling into local optimum, while searching for high expected value instead.
+    Based on these designs, SE avoids falling into local optimum while searching for high expected value instead.
 
@@
     to the rescue. By measuring the noise immunity of an architecture, the misclassifying problem 
-    can be solved. Thus, combine NASWOT and NI, the correlation and performance increase. 
-    An example shows in \xfig{fig:ninaswot}.
+    can be solved. Thus, by combining NASWOT and NI, the correlation and performance increase. 
+    An example is shown in \xfig{fig:ninaswot}.
 
@@
 
-    \textit{3. How to combine multiple kinds of score functions together 
-    and prevent one from overwhelming the others numerically?}
+    \textit{3. How to combine multiple kinds of score functions and prevent one from 
+    overwhelming the others numerically?}
 
-    One possible way is normalization, but the necessary information is known only 
+    Normalization is one of the typical ways, but the necessary information is known only 
     after evaluating the whole search space, e.g., range, mean, or standard deviation, 
@@
     agnostic to the search space, it leverages multiple score functions by ranking, 
-    which also provides a solution to have equal contributions from each score function.
+    providing a solution to have equal contributions from each score function.
 
@@
     The simulated annealing (SA) algorithm with ranking algorithm (\palg{})
-    is outlined in \xalg{alg:SA}. In line 1-2, the historical best architectures 
-    set, denoted $H$, is initialized to an empty set, and an architecture is randomly sampled from 
-    search space, denoted $s$. Line 3-18 are the major part of \palg{}, when the temperature 
-    is lower than ending temperature, the algorithm is terminated. Line 4-16 
-    represent every time the temperature decreases, $t$ iterations with following steps are executed. 
-    In line 5, $s$ is used as a seed to generate the neighborhood of it, denoted $U$, 
-    and the size of it is decided by a presetting parameter, the number of neighbours, $N$. 
-    In line 6, $s$, $U$ and the architectures recorded in historical best architectures set are 
-    put into ranking function. 
+    is outlined in \xalg{alg:SA}. In lines 1-2, the historical best architectures 
+    set, denoted $H$, is initialized to an empty set, and a network architecture is randomly sampled from 
+    search space, denoted $s$. Lines 3-18 are the central part of \palg{}; when the temperature 
+    is lower than the ending temperature, the algorithm is terminated. Lines 4-16 
+    represent every time the temperature decreases, $t$ iterations with the following steps are executed. 
+    In line 5, $s$ is used as a seed to generate its neighborhood, denoted $U$. 
+    The size of the neighborhood is decided by a presetting parameter, $N$. 
+    In line 6, $s$, $U$, and the architectures recorded in the historical best architectures set are 
+    put into the ranking function. 
     After ranking, the best architecture (including $s$) is added into $H$, and the size of the set is 
     maintained by removing the low-rank architectures. 
-    And the best architecture (excluding $s$) which has the highest rank is denoted by $s'$. 
-    In line 9, the difference of the rank between $s'$ and $s$ is calculated and detnote $\Delta E$. 
-    Then in line 10, a random variable $x$ is sampled from the uniform distribution on $[0,1]$. 
-    Line 11-15 are the transition process. If the rank of $s'$ is higher than $s$ ($\Delta E<0$), 
-    the current solution is replaced by $s'$, or be replaced by probability, defined by 
+    The best architecture (excluding $s$), which has the highest rank, is denoted by $s'$. 
+    In line 9, the rank difference between $s'$ and $s$ is calculated and denotes $\Delta E$. 
+    Then, in line 10, a random variable $x$ is sampled from the uniform distribution on $[0,1]$. 
+    Lines 11-15 are the transition process. If the rank of $s'$ is higher than $s$ ($\Delta E<0$), 
+    the current solution is replaced by $s'$. If not, the algorithm can accept $s'$ as the 
+    current solution by the probability, defined by 
     \begin{equation} 
@@
     \end{equation}
-    where $\Psi$ is the current temperature, $\Delta E$ the difference of the rank between 
+    where $\Psi$ is the current temperature, $\Delta E$ the rank difference between 
     $s$ and $s'$, and $\alpha$ is a constant number adjusts the probability. The more 
@@
     After the $t$ iterations, the temperature scales down by $r_\Psi$ in line $17$. When $\Psi$ is 
-    lower or equal to $\tau$, the algorithm is terminated and the current architecture is returned in line $19$. 
-    Notbly, the size of $H$ is based on the maximum search number of SA, defined by 
+    lower or equal to $\tau$, the algorithm is terminated, and the current architecture is returned in line $19$. 
+    Notably, the size of $H$ is based on the maximum search number of SA, defined by 
     \begin{equation}
@@
             \Input{search space $\mathbb N^*$}
-            \Parameter Initial temperature $\Psi$, ending temperature $\tau$, a real number between 0 and 1, $r_\Psi$, the number of iteration, $t$, the number of generated neighbours, $N$, a real number, $\alpha$, the coefficient of the size of $H$, $\beta$
+            \Parameter Initial temperature $\Psi$; ending temperature $\tau$; a real number between 0 and 1, $r_\Psi$; the number of iteration, $I$; the number of generated neighbours, $N$; a real number, $\alpha$; the coefficient of the size of $H$, $\beta$
             \State Initialize historical best architectures set $H$ to empty set
@@
             \While{$\Psi>\tau$}
-                \For{$\text{each }i \in [1\ldots t]$}
+                \For{$\text{each }i \in [1\ldots I]$}
                     \State $U = \text{Neighbor}(s, N)$
@@
     An example of an iteration in \palg{} is shown in \xfig{fig:SA-rank-iteration}. 
-    Assume that at the beginning there is a current solution $s$ and the historical best 
-    architectures set $H=\{H_1,H_2\}$. Next, the neighborhood of $s$ is generated, 
+    Assume that at the beginning, there is a current solution $s$ and the historical best 
+    architectures set $H$ contains two networks $H_1, H_2$. Next, the neighborhood of $s$ is generated, 
     denoted $U=\{s_A,s_B,s_C,s_D,s_E\}$. The rank of the architectures in the union 
-    set of $H$, $\{s\}$ and $U$ are calculated. The architecture with highest rank 
-    $s_C$ will be recorded by $H$, and the architecture with highest rank excluding 
-    $s$ is denoted $s'$. Then the difference $\Delta E$ of the rank is used for 
-    solution transition. If $\Delta E<0$, the solution is better than the the current 
+    set of $H$, $\{s\}$ and $U$ are calculated. The architecture with the highest rank 
+    $s_C$ will be recorded by $H$, and the architecture with the highest rank excluding 
+    $s$ denotes $s'$. Then, the difference $\Delta E$ of the rank is used for 
+    solution transition. If $\Delta E<0$, the solution is better than the current 
     solution. If it is not better, the solution can still be accepted by probability 
@@
     schema is to use a binary or integer vector as a representation of an architecture. 
-    For example, NAS-Bench-201 provides 5 operations and 6 nodes for a cell, 
+    For example, NATS-Bench-TSS provides five operations and six nodes for a cell, 
     and cells form an architecture, which implies the whole search space can be 
     encoded into 6-integer vectors. However, a broken architecture appears since 
-    one of the operations is ``zeroize'', which means the measurement of a broken 
-    architecture is meaningless. To exclude the broken architectures, the encoding 
-    schema in \cite{10092788} is used in this paper. The detail of the encoding 
-    schema differs from search spaces, but they all share the common core idea, 
-    preserving the critical path in architecture. The encoding schema guarantees 
-    the existence of at least one path from input to output in a cell, and no 
-    zeroize operation is in it. By excluding the broken architectures, the efficiency 
-    improves.
+    one of the operations is ``zeroize,'' which means the measurement of a broken 
+    architecture is meaningless. This paper uses the encoding schema in \cite{10092788} 
+    to exclude the broken architectures. The detail of the encoding schema differs from 
+    search spaces, but they all share the common core idea, preserving the critical path 
+    in architecture. The encoding schema guarantees the existence of at least one path 
+    from input to output in a cell, and no zeroize operation is in it. By excluding the 
+    broken architectures, the efficiency improves.
 
@@
     The general proposed ranking algorithm is in \xalg{alg:rank-based}. 
-    Line 1-3 are to evaluate the network architectures in the subset 
+    Lines 1-3 are to evaluate the network architectures in the subset 
     by each score function, and then the rank of each architecture is 
@@
     the $j$-th score function is $\mathcal F_j(\cdot)$. The rank of the 
-    $i$-th architecture in the results of $j$-th score function are 
+    $i$-th architecture in the results of $j$-th score function is 
     $r_{\mathcal F_j}(\mathbb N^i)$, as shown in line 2. In Line 4, 
     the final rank of $i$-th architecture is calculated by summing up 
-    its rank in $j$-th score function. Then the ranking result of each 
+    its rank in the $j$-th score function. Then, the ranking result of each 
     architecture is returned. In summary, the ranking algorithm makes the 
-    contribution of each score function even and evaluate an architecture 
-    from different aspects. If an architecture gains higher score in these 
-    score functions, the final rank should be higher, i.e., smaller index. 
+    contribution of each score function even and evaluates an architecture 
+    from different aspects. If an architecture gains higher scores in these 
+    score functions, the final rank should be higher, i.e., a smaller index. 
     Therefore, the highest rank (numerically lowest) in $r$ is the best 
-    network architecture. In practical implementation, to reduce the 
-    evaluation time of training-free score functions, the scores of 
-    architecture can be stored and used in the future. 
+    network architecture. In practical implementation, the architecture scores 
+    can be stored and used in the future to reduce the evaluation time of 
+    training-free score functions. 
     %The first step is to evaluate the network architectures in the subset, 
@@
     LogSynFlow are measurements to trainability of an architecture. 
-    As mentioned, the chosen score function should cover every characteristics 
-    of an architecture. In this paper, NI and NASWOT are a complementary set, 
-    which takes the ability of image generalization and distinction into account. 
+    As mentioned, the chosen score function should cover every characteristic 
+    of an architecture. In this paper, NI and NASWOT are a complementary set 
+    that takes the ability of image generalization and distinction into account. 
     This set is viewed as the measurement of the ability of graphic 
     recognition. Therefore, the last missing piece is the trainability of an 
-    architecture, which, LogSynFlow is chosen to measure it.
+    architecture, which, LogSynFlow is chosen to measure.
 
@@
 
-    We evalute the performance of the proposed algorithm, \palg{}, 
+    We evaluate the performance of the proposed algorithm, \palg{}, 
     for searching the architectures of high accuracy. For comparison, several NAS 
@@
     \cite{Dong_2021} and NAS-Bench-101 \cite{ying2019nasbench101}, are used 
-    here to evalute the performance of the NAS algorithms. The architectures 
-    of NATS-bench-TSS is same as NAS-Bench-201 \cite{dong2020nasbench201}. 
+    here to evaluate the performance of the NAS algorithms. The architectures 
+    of NATS-bench-TSS are the same as NAS-Bench-201 \cite{dong2020nasbench201}. 
     The architectures in NATS-bench-SSS and NATS-bench-TSS are trained by the three datasets: 
-    CIFAR10, CIFAR100, ImageNet-16-120, while NAS-Bench-101 is trained by one: 
+    CIFAR10, CIFAR100, and ImageNet-16-120, while NAS-Bench-101 is trained by one: 
     CIFAR10.
@@
     a single NVIDIA RTX3070 Ti GPU with 8 GB memory, driver version 520.61.05, CUDA version 11.8, and 
-    65 GB available memory running on Ubuntu 20.04.1 with linux kernel 5.15.0-73-generic. All the program 
+    65 GB available memory running on Ubuntu 20.04.1 with Linux kernel 5.15.0-73-generic. All the program 
     is written in Python 3.7.16 with PyTorch 1.7.1+cu110 package. The simulations of all 
     non-weight sharing NASs are carried out for 500 runs on all the search spaces except AREA, which is 50 runs. 
-    For weight sharing NAS algorithms, each is carried out for 3 runs. And for training-free 
-    algorithms, each is carried out for 100 runs and are given an evaluation 
+    For weight sharing NAS algorithms, each is carried out for three runs. For training-free 
+    algorithms, each is carried out for 100 runs and is given an evaluation 
     budget of 1000 for all the search space. The parameter settings of \palg{} are as follows: 
-    initial temperature, ending temperature, rate of decrease of temperature, the number of iteration, 
-    the constant number adjusting acceptance probability, the number of generated neighbours, and 
+    initial temperature, ending temperature, rate of decrease of temperature, the number of iterations, 
+    the constant number adjusting acceptance probability, the number of generated neighbors, and 
     the coefficient of the size of historical best architectures set are set 
-    to 1, 0.0008, 0.745, 4, 0.25, 10, 1, so that the maximum number of searching candidates is 1000. 
-    Notbly, in NAS-Bench-101 search space, we conduct experiments with an evaluation budget of 5000 for RS, 
+    to 1, 0.0008, 0.745, 4, 0.25, 10, 1 so that the maximum number of searching candidates is 1000. 
+    Notably, in NAS-Bench-101 search space, we conduct experiments with an evaluation budget of 5000 for RS, 
     since NAS-Bench-101 contains much more architectures.
 
-    \subsection{Simulation Results} % 補實驗描述
+    \subsection{Simulation Results}
     % sss
-    The simulation results in NATS-Bench-SSS \cite{Dong_2021} is shown in \xtab{table:overall_sss}. 
+    The simulation results in NATS-Bench-SSS \cite{Dong_2021} are shown in \xtab{table:overall_sss}. 
     The proposed NAS algorithm and ranking function is compared with the other five non-weight sharing 
@@
     has the highest accuracy in CIFAR10. The accuracy of RS-NI and RS-rank are similar, but the stability 
-    of RS-rank is better. In CIFAR100, RS-LogSynFlow performs best, then is RS-NI, RS-rank, RS-NASWOT. 
-    In ImageNet16, RS-LogSynFlow still has the highest accuracy and stability, then is RS-rank, RS-NI, 
-    RS-NASWOT. 
-    However, \palg{} improves the results significantly and outperforms almost all the 
-    compared algorithms, including AREA, REA, and RL. It can be seen that, search algorithms guides 
-    the searching direction for searching better architectures, and the training-free score functions
+    of RS-rank is better. In CIFAR100, RS-LogSynFlow performs best, then RS-NI, RS-rank, RS-NASWOT. 
+    In ImageNet16, RS-LogSynFlow still has the highest accuracy and stability, then RS-rank, RS-NI, 
+    and RS-NASWOT. However, \palg{} improves the results significantly and outperforms almost all the 
+    compared algorithms, including AREA, REA, and RL. It can be seen that search algorithms guide 
+    the searching direction for better architectures, and the training-free score functions
     accelerate the whole searching process by eliminating the training stage.
@@
     non-weight sharing algorithms, six weight sharing algorithms, three different training-free 
-    score functions with RS, i.e., RS-NI, RS-NASWOT, and RS-LogSynFlow and one 
-    training-free method, TE-NAS. Same as the experiment of NATS-Bench-SSS, the searching 
-    architectures are identical for the RS with score functions. Non-weight sharing algorithms 
-    like REA and AREA outperform all the other search algorithms, though the time cost is 
-    tremendous. Among the four training-free score functions with random search, RS-rank has the 
-    highest accuracy in CIFAR10 and ImageNet16. But in CIFAR100, RS-NI has the highest accuracy. 
+    score functions with RS, i.e., RS-NI, RS-NASWOT, and RS-LogSynFlow and one training-free method, 
+    TE-NAS. For fairness, the searching architectures are identical between the four score 
+    functions with RS. Non-weight sharing algorithms like REA and AREA outperform all the other 
+    search algorithms despite the tremendous time cost. RS-rank has the highest accuracy in CIFAR10 
+    and ImageNet16 among the four training-free score functions with RS. But in CIFAR100, RS-NI has the highest accuracy. 
     In CIFAR10 validation dataset, RS-NI is the most stable, RS-rank the second, RS-LogSynFlow the 
-    third and RS-NASWOT the last. In CIFAR10 test dataset, RS-rank is the most stable, then is RS-NI, 
-    RS-LogSynFlow, RS-NASWOT. In CIFAR100, RS-NI is the most stable, RS-NASWOT the second but 
-    has lower accuracy, RS-rank the third, the last is RS-LogSynFlow. In ImageNet16, RS-rank is the 
-    most stable, then is RS-NI, RS-NASWOT, RS-LogSynFlow. According to the results, RS-rank does 
-    integrate the score functions and use them to evaluate an architecture by different characteristics. 
-    With the help of search algorithm, \palg{} outperforms all the others training-free methods, 
-    and obtains a better stability. In CIFAR10 and CIFAR100, the standard deviation of \palg{} is lower 
+    third, and RS-NASWOT the last. In CIFAR10 test dataset, RS-rank is the most stable, then RS-NI, 
+    RS-LogSynFlow, and RS-NASWOT. In CIFAR100, RS-NI is the most stable, RS-NASWOT the second but 
+    has lower accuracy, RS-rank the third, and the last is RS-LogSynFlow. In ImageNet16, RS-rank is the 
+    most stable, then RS-NI, RS-NASWOT, and RS-LogSynFlow. According to the results, RS-rank does 
+    integrate the score functions and uses them to evaluate an architecture by different characteristics. 
+    With the help of the search algorithm, \palg{} outperforms all the other training-free methods 
+    and obtains better stability. In CIFAR10 and CIFAR100, the standard deviation of \palg{} is lower 
     than all the non-weight sharing algorithms. And in ImageNet16, the standard deviation of \palg{} is 
@@
     sharing algorithms, and three training-free score functions with RS. The training-free 
-    score functions are same to the ones in NATS-Bench-TSS and NATS-Bench-SSS. In the experiment, ENAS has 
-    the best performance, while the computation time is the highest. AREA and REA performs similarly. 
-    Both have higher accuracy than most of others. 
+    score functions are identical to the ones in NATS-Bench-TSS and NATS-Bench-SSS. The evaluation setting 
+    of training-free score functions with RS is the same as the previous experiments; the evaluating 
+    architectures are identical between the four score functions. In the experiment, ENAS 
+    performs best, while the computation time is the highest. AREA and REA perform similarly. 
+    Both have higher accuracy than most of the others. 
     In CIFAR10 validation dataset, with $1000$ sampled architectures ($N=1000$), the accuracy of 
-    RS-NI is better than RS-rank, but the standard deviation is worse than RS-rank. And RS-NASWOT 
-    though is higher than RS-LogSynFlow, RS-NASWOT is the most unstable. With $5000$ sampled architectures 
-    ($N=5000$), RS-rank outperforms RS-NI instead and becomes the best method. RS-NASWOT and RS-LogSynFlow
-    performs similarly, but RS-NASWOT is more unstable. Lastly, \palg{} has better accuracy 
+    RS-NI is better than RS-rank, but the standard deviation is worse than RS-rank. Both RS-NASWOT 
+    and RS-LogSynFlow are lower than RS-rank. The accuracy of RS-NASWOT is higher than RS-LogSynFlow, 
+    but RS-NASWOT is the most unstable. With $5000$ sampled architectures ($N=5000$), RS-rank 
+    outperforms RS-NI instead and becomes the best method. RS-NASWOT and RS-LogSynFlow
+    perform similarly, but RS-NASWOT is more unstable. Lastly, \palg{} has better accuracy 
     and stability than all the other training-free score functions. In CIFAR10 test dataset, with $1000$ 
-    sampled architectures ($N=1000$), RS-NI has higher accuracy than RS-rank, however, the stability of 
+    sampled architectures ($N=1000$), RS-NI has higher accuracy than RS-rank. However, the stability of 
     RS-NI is much worse than RS-rank. The accuracy and stability of \palg{} is the best among the 
     training-free methods. With $5000$ sampled architectures ($N=5000$), RS-NI performs better than 
-    RS-rank but has much lower stability. RS-LogSynFlow performs better than RS-NASWOT which not only 
-    has low accuracy but also low stability. \palg{} is still best among these training-free score 
+    RS-rank but has much lower stability. RS-LogSynFlow performs better than RS-NASWOT, which 
+    has low accuracy and stability. \palg{} is still best among these training-free score 
     functions. Compared with \palg{} and the other NAS methods, though the performance and stability 
-    are a little bit worse than AREA, REA and ENAS, the time cost of \palg{} is much less than them.
+    are a little bit worse than AREA, REA, and ENAS, the time cost of \palg{} is much less than theirs.
 
@@
     training-free score functions. The new rank algorithm is then applied to simulated annealing 
-    algorithm. The simulation result shows that the proposed algorithm, named \palg{}, not only outperforms the most 
-    state-of-art training-free score functions but also some of the non-training-free methods. 
+    algorithm. The simulation result shows that the proposed algorithm, named \palg{}, outperforms 
+    most of training-free score functions and some of the non-training-free methods. 
     The proposed algorithm also shows robustness, which performs well between different search 
-    spaces vary with neural network structures and size. 
-    The limitation of \palg{} is the lack of versatility since the score functions are mainly chosen 
-    for common image recognition. That means \palg{} may not be applied in the search of architectures 
-    designed for other usages, i.e., speech recognition, NLP. However, the problem is able to be solved 
-    by choosing the corresponding complementary score functions. Some further questions are how many 
+    spaces that vary with neural network structures and size. 
+    The limitation of \palg{} is the need for more versatility since the score functions are mainly chosen 
+    for common image recognition. That means \palg{} may not be applied in search of architectures 
+    designed for other usages, i.e., speech recognition, NLP. However, the problem can be solved 
+    by choosing the corresponding complementary score functions. Some further questions are: how many 
     score functions are required for precisely estimating the performance of architectures and what are they?

### 2023-11-19 search/SA/SA_rk_abstract.py
mantain the size of historical best set

@@ -30,12 +30,12 @@ class abstract_SA():
 
     def neighbor(self, arch):
         #TODO
-        assert False, f"implemenation isn't completed"
+        assert False, f"Implemenation isn't completed."
         pass
     
     def rand_arch_generate(self):
         #TODO
-        assert False, f"implemenation isn't completed"
+        assert False, f"Implemenation isn't completed."
         pass
 
     def search(self):
@@ -50,7 +50,6 @@ class abstract_SA():
                     neighbors.add(tuple(self.neighbor(list(now_arch))))
                 neighbors.add(tuple(now_arch))
 
-                # maintain 
                 for arch in history_best_arch:
                     neighbors.add(tuple(arch))
                 
@@ -59,13 +58,21 @@ class abstract_SA():
                 indices = [self.searchspace.query_index_by_arch(self.list2arch(arch)) for arch in neighbors]
                 
                 # E
-                best_uids, maxacc, rk_maxacc, scores = self.ranking2(np.array(indices))
+                best_uids, maxacc, rk_maxacc, scores = self.ranking(np.array(indices))
                 bestrk_uid = best_uids["rank"]
                 ind_rk = scores["rank"]
 
                 best_sol_uid = bestrk_uid
                 best_arch = neighbors[indices.index(bestrk_uid)]
                 history_best_arch.add(best_arch)
+                # maintain the size of set H
+                while len(history_best_arch) > self.beta * (self.maxn_iter * self.maxN * math.log(self.end_T / self.init_T) / math.log(self.Rt)):
+                    history_best_arch = list(history_best_arch)
+                    indices = [self.searchspace.query_index_by_arch(self.list2arch(arch)) for arch in history_best_arch]
+                    best_uids, maxacc, rk_maxacc, scores = self.ranking(np.array(indices))
+                    worst_arch_ind = np.argmax(scores["rank"])
+                    del history_best_arch[worst_arch_ind]
+                    history_best_arch = set(history_best_arch)
 
                 bestrk = np.inf
                 if bestrk_uid == now_uid:
@@ -86,7 +93,7 @@ class abstract_SA():
                 now_uid = int(now_uid)
         return best_sol_uid, self.searchspace.get_final_accuracy(best_sol_uid, self.acc_type, self.args.valid), now_uid, self.searchspace.get_final_accuracy(now_uid, self.acc_type, self.args.valid)
 
[…]

### 2023-11-19 SA_search.py
update

@@ -17,7 +17,6 @@ from score import *
 
 args = parser.SA_search_argsparser()
 
-os.environ['CUDA_VISIBLE_DEVICES'] = args.GPU
 os.environ['TF_ENABLE_ONEDNN_OPTS'] = '0'
 
 # Reproducibility
@@ -29,7 +28,7 @@ torch.manual_seed(args.seed)
 
 print("SA search algo")
 print(f"Use GPU {args.GPU}...")
-device = torch.device("cuda:0" if torch.cuda.is_available() else "cpu")
+device = torch.device(f"cuda:{args.GPU}" if torch.cuda.is_available() else "cpu")
 print(f"The current device used is {device}")
 
 print(f"Initialize the train loader...")

### 2023-11-19 plt.py
update plt.py

@@ -1,0 +1,103 @@
+import random
+import numpy as np
+import matplotlib.pyplot as plt
+import statistics
+from numpy import std, mean
+from scipy.stats import kendalltau
+import nasspace
+from utils import add_dropout, remap_dataset_names
+import datasets
+import torch
+from Parser import parser
+from score import *
+import tqdm
+from tqdm import trange
+
+args = parser.SA_search_argsparser()
+device = torch.device(f"cuda:{args.GPU}" if torch.cuda.is_available() else "cpu")
+if args.nasspace == "nasbench201":
+    args.dataset, acc_type = remap_dataset_names(args.dataset, args.valid, args.test, args.train)
+else:
+    acc_type = None
+print(f"dataset = {args.dataset}, validation = {args.valid}")
+searchspace = nasspace.get_search_space(args)
+train_loader = datasets.get_data(args.dataset, args.data_loc, args.valid, args.batch_size, args.augtype, args.repeat, args)
+
+torch.backends.cudnn.deterministic = True
+torch.backends.cudnn.benchmark = False
+random.seed(args.seed)
+np.random.seed(args.seed)
+torch.manual_seed(args.seed)
+
+runs = tqdm.tqdm(total = len(searchspace), desc='progress: ')
+scs = {"ni": [], "naswot": [], "acc": []}
+n = 0
+for uid, net in searchspace:
+    if n > 10:
+        break
+    n += 1
+    net = net.to(device)
+    ni_sc = ni_score(net, train_loader, device, args)
+    scs["ni"].append(ni_sc)
+    naswot_sc = naswot_score(net, train_loader, device, args)
+    scs["naswot"].append(naswot_sc)
+    acc = searchspace.get_final_accuracy(uid, acc_type, args.valid)
+    scs["acc"].append(acc)
+    runs.update(1)
+
+scs["ni"] = np.array(scs["ni"])
+scs["naswot"] = np.array(scs["naswot"])
+scs["acc"] = np.array(scs["acc"])
+
+## NASWOT+NI
+fig = plt.figure()
+ax = fig.add_subplot()
[…]

### 2023-11-19 paper/manuscript.tex

@@
             \Input{search space $\mathbb N^*$}
-            \Parameter Initial temperature $\Psi$; ending temperature $\tau$; a real number between 0 and 1, $r_\Psi$; the number of iteration, $I$; the number of generated neighbours, $N$; a real number, $\alpha$; the coefficient of the size of $H$, $\beta$
+            \Parameter Initial temperature $\Psi$; ending temperature $\tau$; a real number between 0 and 1, $r_\Psi$; the number of iteration, $t$; the number of generated neighbours, $N$; a real number, $\alpha$; the coefficient of the size of $H$, $\beta$
             \State Initialize historical best architectures set $H$ to empty set
@@
             \While{$\Psi>\tau$}
-                \For{$\text{each }i \in [1\ldots I]$}
+                \For{$\text{each }i \in [1\ldots t]$}
                     \State $U = \text{Neighbor}(s, N)$

### 2023-11-20 search/SA/SA_rk_abstract.py
bug fix

@@ -5,6 +5,7 @@ import sys
 from tqdm import trange
 import time
 from score import *
+import math
 
 class abstract_SA():
     def __init__(self, searchspace, train_loader, acc_type, device, args):

### 2023-11-20 plt.py
update plt.py

@@ -13,6 +13,7 @@ from score import *
 import tqdm
 from tqdm import trange
 
+"""
 args = parser.SA_search_argsparser()
 device = torch.device(f"cuda:{args.GPU}" if torch.cuda.is_available() else "cpu")
 if args.nasspace == "nasbench201":
@@ -31,11 +32,7 @@ torch.manual_seed(args.seed)
 
 runs = tqdm.tqdm(total = len(searchspace), desc='progress: ')
 scs = {"ni": [], "naswot": [], "acc": []}
-n = 0
 for uid, net in searchspace:
-    if n > 10:
-        break
-    n += 1
     net = net.to(device)
     ni_sc = ni_score(net, train_loader, device, args)
     scs["ni"].append(ni_sc)
@@ -48,13 +45,26 @@ for uid, net in searchspace:
 scs["ni"] = np.array(scs["ni"])
 scs["naswot"] = np.array(scs["naswot"])
 scs["acc"] = np.array(scs["acc"])
+"""
+scs = np.load("score_info.npz")
+#np.savez("score_info", ni = scs["ni"], naswot = scs["naswot"], acc = scs["acc"])
+scs = {"ni": scs["ni"], "naswot": scs["naswot"], "acc": scs["scs"]}
+mask = np.isfinite(scs["naswot"])
+scs["naswot"] = scs["naswot"][mask]
+scs["acc"] = scs["acc"][mask]
+scs["ni"] = scs["ni"][mask]
+
+mask = np.random.choice(len(scs["acc"]), 1000)
+scs["naswot"] = scs["naswot"][mask]
+scs["acc"] = scs["acc"][mask]
+scs["ni"] = scs["ni"][mask]
 
 ## NASWOT+NI
 fig = plt.figure()
 ax = fig.add_subplot()
 #['ind_rk', 'score_ni', 'score_naswot', 'score_synflow', 'acc', 'rk_tau', 'ni_tau', 'naswot_tau', 'synflow_tau']
 ax.set_xlabel(f'acc')
-ax.set_ylabel(f'NI + NASWOT')
+ax.set_ylabel(f'NINASWOT')
 
 std_naswot = std(scs['naswot'])
 mean_naswot = mean(scs['naswot'])
[…]

### 2024-02-28 Parser/parser.py
update score parser

@@ -81,7 +81,7 @@ def SA_search_argsparser():
     parser.add_argument('--data_loc', default='./cifardata/', type=str, help='dataset folder')
     parser.add_argument('--api_loc', default='./NAS-Bench-201.pth',
                         type=str, help='path to API')
-    parser.add_argument('--save_loc', default='results/ICML', type=str, help='folder to save results')
+    parser.add_argument('--save_loc', default='results/', type=str, help='folder to save results')
     parser.add_argument('--save_string', default='SA', type=str, help='prefix of results file')
     parser.add_argument('--nasspace', default='nasbench201', type=str, help='the nas search space to use')
     parser.add_argument('--batch_size', default=128, type=int)
@@ -120,17 +120,19 @@ def SA_search_argsparser():
     return parser.parse_args()
 
 def score_argsparser():
-    parser = argparse.ArgumentParser(description='Genetic-Based NAS with Hybrid Score Functions')
-    parser.add_argument('--data_loc', default='../cifardata/', type=str, help='dataset folder')
+    parser = argparse.ArgumentParser(description='rk-based-nas')
+    parser.add_argument('--data_loc', default='./cifardata/', type=str, help='dataset folder')
     parser.add_argument('--api_loc', default='./NAS-Bench-201.pth',
                         type=str, help='path to API')
-    parser.add_argument('--save_loc', default='results', type=str, help='folder to save results')
-    parser.add_argument('--save_string', default='score_networks', type=str, help='prefix of results file')
+    parser.add_argument('--save_loc', default='results/ICML', type=str, help='folder to save results')
+    parser.add_argument('--save_string', default='SA', type=str, help='prefix of results file')
     parser.add_argument('--nasspace', default='nasbench201', type=str, help='the nas search space to use')
     parser.add_argument('--batch_size', default=128, type=int)
+    parser.add_argument('--kernel', action='store_true')
+    parser.add_argument('--dropout', action='store_true')
     parser.add_argument('--repeat', default=1, type=int, help='how often to repeat a single image with a batch')
     parser.add_argument('--augtype', default='none', type=str, help='which perturbations to use')
-    parser.add_argument('--sigma', default=0.05, type=float, help='noise level if augtype is "gaussnoise"')
+    parser.add_argument('--sigma', default=1, type=float, help='noise level if augtype is "gaussnoise"')
     parser.add_argument('--GPU', default='0', type=str)
[…]

### 2024-02-28 encoder/encoder.py
update 201 encoder strategy

@@ -1,19 +1,36 @@
-from ast import Pass
 import numpy as np
 import random
 
 class nasbench201_encoder:
     def __init__(self):
-        pass
+        self.search_space = self.construct_search_space()
+
+    def __getitem__(self, n):
+        return self.search_space[n]
+
+    def __len__(self):
+        return len(self.search_space)
+    
+    def construct_search_space(self):
+        mapping = {'a':0,'b':2,'c':5,'d':1,'e':3,'f':4}
+        backbone_choices = {0:np.array(['c','d','z']),1:np.array(['e','z','z']),2:np.array(['a','b','c']),3:np.array(['a','f','z'])}
+
+        def has_backbone(net):
+            has = [True, True, True, True]
+            for i, backbones in enumerate(backbone_choices.values()):
+                for backbone in backbones:
+                    has[i] &= (net[backbone] != 0)
+            return np.array(has).any()
+                
+        all_nets = list(itertools.product(range(5), repeat=6))
+        all_nets = filter(has_backbone, all_nets)
+        return all_nets
 
     def get_rand_code(self):
         return tuple(np.concatenate((np.random.randint(5,size=6),np.random.randint(4,size=1),np.random.randint(1,5,size=3))))
     
     def get_nrand_code(self, n):
-        s = set()
-        while len(s) < n:
-            s.add(self.get_rand_code())
-        return [list(c) for c in s]
+        return random.sample(self.search_space, n)
 
     def get_rand_backbone_branch(self):
         pass
@@ -35,6 +52,7 @@ class nasbench201_encoder:
         return np.random.randint(3, size=5)
     
     def parse_code(self,code):
+        """
         newcode = code[:6]
         mapping = {'a':0,'b':2,'c':5,'d':1,'e':3,'f':4}
         backbone_choices = {0:np.array(['c','d','z']),1:np.array(['e','z','z']),2:np.array(['a','b','c']),3:np.array(['a','f','z'])}
@@ -43,13 +61,20 @@ class nasbench201_encoder:
                 break
             newcode[mapping[i]] = code[6+1+n]
         return newcode
+        """
+        return code
 
 class natsbenchSSS_encoder:
     def __init__(self):
         self.candidates = [8, 16, 24, 32, 40, 48, 56, 64]
         self.num_choices = 8
+
+    def __getitem__(self, n):
+        return n
+
     def __len__(self):
-        return 5
+        return 32768
+
     def get_rand_code(self):
[…]

### 2024-02-28 score.py
update score script

@@ -1,0 +1,109 @@
+import argparse
+import nasspace
+import datasets
+import random
+import numpy as np
+import torch
+from torch import nn
+import importlib
+import os
+import sys
+from sklearn.metrics.pairwise import cosine_similarity
+from tqdm import trange, tqdm
+from statistics import mean
+from numpy import std
+import time
+from utils import add_dropout, remap_dataset_names
+from score import *
+from scipy.stats import kendalltau
+from Parser import parser
+
+args = parser.score_argsparser()
+
+os.environ['TF_ENABLE_ONEDNN_OPTS'] = '0'
+
+# Reproducibility
+torch.backends.cudnn.deterministic = True
+torch.backends.cudnn.benchmark = False
+random.seed(args.seed)
+np.random.seed(args.seed)
+torch.manual_seed(args.seed)
+
+print("score networks")
+print(f"Use GPU {args.GPU}...")
+device = torch.device(f"cuda:{args.GPU}" if torch.cuda.is_available() else "cpu")
+print(f"The current device used is {device}.")
+
+print(f"Initialize the train loader...")
+print(f"dataset = {args.dataset}, data location = {args.data_loc}, validation = {args.valid}")
+train_loader = datasets.get_data(args.dataset, args.data_loc, args.valid, args.batch_size, args.augtype, args.repeat, args)
+
+print(f"Initialize the nas bench api ({args.nasspace}) ...")
+if args.nasspace == "nasbench201":
+    args.dataset, acc_type = remap_dataset_names(args.dataset, args.valid, args.test, args.train)
+else:
+    acc_type = None
+print(f"dataset = {args.dataset}, validation = {args.valid}")
+searchspace = nasspace.get_search_space(args)
+
+print(f"Making sure {args.save_loc} exist.\n")
+os.makedirs(args.save_loc, exist_ok=True)
+
+# Reproducibility
+torch.backends.cudnn.deterministic = True
+torch.backends.cudnn.benchmark = False
+random.seed(args.seed)
+np.random.seed(args.seed)
+torch.manual_seed(args.seed)
+
+enroll_sc_fn_names = ["ni", "naswot", "logsynflow", "snip", "grasp"]
[…]

### 2024-02-28 score.sh
update score script

@@ -1,0 +1,3 @@
+python score.py --save_string score --augtype none --repeat 1 --sigma 1 --nasspace nasbench201 --api_loc ../NATS-tss-v1_0-3ffb9-simple/ --batch_size 128 --GPU 0 --n_runs 1 --data_loc ./cifardata/ --dataset cifar10 --test
+
+#python score.py --save_string score --augtype none --repeat 1 --sigma 1 --nasspace natsbenchsss --api_loc ../NATS-sss-v1_0-50262-simple/ --batch_size 128 --GPU 0 --n_runs 1 --data_loc ./cifardata/ --dataset cifar10 --test

### 2024-02-28 paper/manuscript.tex

--- 2023-11-19 paper/manuscript.tex
@@
             \end{tabular}
-            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NATS-Bench-TSS in the CIFAR-10 dataset 
-            (b) NI score for 1,000 identical architectures from NATS-Bench-TSS in the CIFAR-10 dataset. 
-            (c) NI score + NASWOT score for 1,000 identical architectures from NATS-Bench-TSS in the CIFAR-10 dataset.}
+            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NAS-Bench-201 in the CIFAR-10 dataset 
+            (b) NI score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset. 
+            (c) NI score + NASWOT score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset.}
             \label{fig:ninaswot}
@@
     algorithms are included, e.g., random search (RS), regularized evolution algorithm 
-    (REA) \cite{real2019regularized}, reinforcement learning (RL) \cite{Williams:92}, 
+    (REA) \cite{real2019regularized}, reinforcement learning (RL) \cite{williams1992simple}, 
     Bayesian optimization with hyper band (BOHB) \cite{falkner2018bohb}, RS with 
